### 2017-10-26 inst/3primeRACE/3primeRACE.Rmd
first commit

---
title: "3-prime RACE"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

##Introduction
In order to define the 3' transcription stop site for the miR34a asRNA, 3'-RACE was performed.

##Methods
All cell lines were cultured at 5% CO2 and 37° C with U2OS cells grown in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. U2OS cell RNA was polyA-tailed using yeast polyA polymerase after which cDNA was synthesized using oligo(dT) primers. Nested-PCR was performed first using a forward primer in miR34a asRNA exon 1 (miR-34a asRNA F10 forward primer - ACGCGTCTCTCCAGCCCGGGAT) and a tailed oligo(dT) primer (poly T T7-FAM) followed by a second PCR using an alternate miR34a asRNA exon 1 primer (miR-34a asRNA F1 forward primer - AGCGGCATCTCCTCCACCTGAAA) and a reverse primer binding to the tail of the previously used oligo(dT) primer (FAM primer). PCR products were gel purified and cloned the Strata Clone Kit (Agilent Technologies), and sequenced.

##Results
<br></br>
<center>![3'-RACE.](results_hg38.png)</center>
<br></br>
3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript from GENCODE.

##Conclusions
Sequencing of the resulting cloned cDNA indicated the transcripts 3’ transcription termination site to be 125bp upstream of the RP3-510D11.2 transcript’s annotated termination site

### 2017-10-26 inst/HctHekDox/HctHekDox.Rmd
first commit

---
title: "HCT116 and HEK293t doxorubicin treatment"
author: "Jason T. Serviss"
date: "12/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
miR34a is a known downstream target of p53 and has been previously shown to exhibit increased expression with cellular apoptotic signaling. We hypothesized that miR34a asRNA may be regulated in a similar fashion whereby transcription is stimulated by activation of p53. To test this we treated HCT116 and HEK293t cells with 200 ng/ml of the DNA damaging agent doxorubicin for 24 hours and monitored miR34a asRNA expression.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 300,000 cells per well in a 6-well plate and cultured overnight. The following day cells were treated with 0, 100, 200, or 500 ng/ml doxorubicin for 24hrs. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers
```

#Results
```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/HctHekDox/QPCRdata.txt', header=TRUE, sep="\t")

goi <- subset(data, gene %in% c("miR34a asRNA", "miR34a HG"))
hk <- subset(data, gene == "B-actin")

colnames(goi)[c(5:6)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(5:6)] <- c("Ct1HK", "Ct2HK")

data <- cbind(goi, hk[,c("Ct1HK", "Ct2HK")])

#ddct
data$meanGOI <- rowMeans(data[,c("Ct1GOI", "Ct2GOI")])
data$meanHK <- rowMeans(data[,c("Ct1HK", "Ct2HK")])
data$dct <- data$meanGOI - data$meanHK
ddct <- ddply(
    data,
    c("gene", "cellLine", "treatment", "experiment"),
    summarize,
    ddct=dct-data[data$gene == gene & data$cellLine == cellLine & data$experiment == 1 & data$treatment == "untreated", "dct"]
)

data <- merge(data, ddct, by=c("gene", "cellLine", "treatment", "experiment"))
data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data, 
    c("gene", "cellLine", "treatment"),
    summarize,
    mean=mean(log2fold),
    pValue=t.test(log2fold, data[data$gene == gene & data$cellLine == cellLine & data$treatment == "untreated", "log2fold"])$p.value,
    CI95l=t.test(log2fold)$conf.int[1],
    CI95h=t.test(log2fold)$conf.int[2]
)

data <- merge(data, stats, by=c("gene", "cellLine", "treatment"))
data$pValue <- ifelse(data$pValue == 1, NA, data$pValue)

data$pStars <- ifelse(
    data$pValue < 0.05 & data$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        data$pValue < 0.005 & data$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            data$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

#prepare for plotting
data$treatment <- factor(data$treatment, levels=c("untreated", "doxorubicin"))
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data, aes(x=treatment, y=log2fold))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        show.legend = FALSE
    )+
    geom_point( 
        aes(colour=gene),
        size=4,
        position=position_dodge(width=0.9)
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    facet_grid(.~cellLine)+
    geom_label(
        aes(y=CI95h+0.15, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=5,
        family="Arial Unicode MS",
        position=position_dodge(width=0.9)
    )+
    scale_y_continuous(
        "\u0394\u0394Ct",
        breaks=c(-1,0,1,2,3,4,5),
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(2^-1,2^0,2^1,2^2,2^3,2^4,2^5)
        )
    )+
    labs(
      x="Treatment",
      title="miR34a asRNA response to p53 induction",
      caption=
            "Q-PCR showing miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after treatment with 200 ng/ml doxorubicin for 24hrs.\nError bars (black vertical) indicate 95% CI and means are represented \nby black dots. \u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(color = guide_legend(title = "Gene", override.aes = list(size=3)))

#plot for pdf
p <- ggplot(data, aes(x=treatment, y=log2fold))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=gene),
    #    size=0.6,
    #    position=position_dodge(width=0.9)
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        lwd=0.15
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        size=0.5
    )+
    facet_grid(.~cellLine)+
    geom_label(
        aes(y=CI95h+0.15, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS",
        position=position_dodge(width=0.9)
    )+
    scale_y_continuous(
        "\u0394\u0394Ct",
        breaks=c(-1,0,1,2,3,4,5)
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(2^-1,2^0,2^1,2^2,2^3,2^4,2^5)
        #)
    )+
    labs(
      x="Treatment"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(fill = guide_legend(title = "Gene", override.aes = list(size=2)))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/HctHekDox/HctHekDox.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

#Conclusions
We observed increases in miR34a HG and asRNA expression upon doxorubicin treatment indicating that these two transcripts are co-regulated.

### 2017-10-26 inst/P1shRNAdox/p1shRNAdox.Rmd
first commit

---
title: "Promoter experiments with shRNA and doxorubicin treatment"
author: "Jason T. Serviss"
date: "09/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
Our previous results showed that miR34a HG and asRNA are simultaneously up-regulated in response to doxorubicin treatment leading us to consider the possibility that miR34a asRNA may be necessary for an appropriate miR34a response to apoptotic signaling. To explore this possibility we again utilized the p1 construct, co-transfecting it with an shRNA targeting renilla, and treating HCT116 cells with increasing levels of doxorubicin.

#Methods
We utilized the P1 construct where the overlapping region of miR34a HG and miR34a AS is cloned with luciferase downstream of miR34a HG and renilla downstream of miR34a AS. The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis. Mol Cell, 2007. 26(5): p. 731-43. All cell lines were cultured at 5% CO2 and 37° C with HCT116 cells cultured in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. 2.5x10^5 HCT116wt cells were seeded in a 12-well plate. After 24hrs these were co-transfected with the P1 construct (25ng) and shRenilla2.1 (250ng) using lipo2000 (Life Technologies) standard protocol. 24hrs post-transfection, doxorubicin treatment was initiated using 0, 300, or 500ng/ml. 24hrs post-treatment, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

##Constructs
```{r}
library(printr)
p1 <- data.frame(
    name="p1",
    sequence="GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
              CCT GCT C"
)
p1
```

##shRNAs
```{r}
shRNAs <- data.frame(
    name=c(
        "shRenilla2.1"
    ),
    sequence=c(
        "TAA CGG GAT TTC ACG AGG C"
    )
)
shRNAs
```

##Primers
```{r}
primers <- data.frame(
    name=c(
        "Luc_set_II_F",
        "Luc_set_II_R",
        "Renilla_pBiDir_F1",
        "Renilla_pBiDir_R1",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers
```

#Results

```{r, warning=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/P1shRNAdox/QPCRdata.txt', header=TRUE, sep="\t")

#analyze Luciferase expression 
luc <- subset(data, correspondsWith %in% c("Luciferase"))
goi <- subset(luc, gene %in% c("Luciferase"))
hk <- subset(luc, gene  == "B-actin")
hk[,c("gene", "alias")] <- NULL
colnames(goi)[c(7,8)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(5,6)] <- c("Ct1HK", "Ct2HK")

if(all(as.logical(hk[,1:3] == goi[,1:3]) == TRUE)) {
    luc <- cbind(goi, hk[,c("Ct1HK", "Ct2HK")])
}

luc$meanCtGOI <- rowMeans(luc[,c("Ct1GOI", "Ct2GOI")])
luc$meanCtHK <- rowMeans(luc[,c("Ct1HK", "Ct2HK")])
luc$dct <- luc$meanCtGOI - luc$meanCtHK
ddct <- ddply(
    luc,
    c("experiment", "treatment", "shRNA"),
    summarize,
    ddct = dct - luc[luc$experiment == experiment & luc$treatment == 0 & luc$shRNA == "shCtrl", "dct"]
)

luc <- merge(luc, ddct, by=c("experiment", "treatment", "shRNA"), all.x=TRUE)

#analyze renilla expression
ren <- subset(data, correspondsWith %in% c("Renilla"))
goi <- subset(ren, gene %in% c("Renilla"))
hk <- subset(ren, gene  == "B-actin")
hk[,c("gene", "alias")] <- NULL
colnames(goi)[c(7,8)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(5,6)] <- c("Ct1HK", "Ct2HK")

if(all(as.logical(hk[,1:3] == goi[,1:3]) == TRUE)) {
    ren <- cbind(goi, hk[,c("Ct1HK", "Ct2HK")])
}

ren$meanCtGOI <- rowMeans(ren[,c("Ct1GOI", "Ct2GOI")])
ren$meanCtHK <- rowMeans(ren[,c("Ct1HK", "Ct2HK")])
ren$dct <- ren$meanCtGOI - ren$meanCtHK
ddct <- ddply(
    ren,
    c("experiment", "treatment", "shRNA"),
    summarize,
    ddct = dct - ren[ren$experiment == experiment & ren$treatment == 0 & ren$shRNA == "shCtrl", "dct"]
)

ren <- merge(ren, ddct, by=c("experiment", "treatment", "shRNA"), all.x=TRUE)

#concatenate 
data <- rbind(luc, ren)
data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data,
    c("treatment", "shRNA", "gene", "correspondsWith"),
    summarize,
    mean=mean(log2fold),
    pValue = t.test(log2fold, data[data$treatment == treatment & data$shRNA == "shCtrl" & data$gene == gene & data$correspondsWith == correspondsWith, "log2Fold"])$p.value,
    CI95l = t.test(log2fold)$conf.int[1],
    CI95h = t.test(log2fold)$conf.int[2]
)
stats[stats$shRNA == "shCtrl", c("pValue")] <- NA
data <- merge(data, stats, by=c("treatment", "shRNA", "gene", "correspondsWith"), all.x=TRUE)

data$pStars <- ifelse(
    data$pValue < 0.05 & data$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        data$pValue < 0.005 & data$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            data$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

#prepare for plotting
data$correspondsWith <- NULL
data$shRNA <- ifelse(data$shRNA == "shCtrl", "shRNA Control", "shRNA Renilla")
data$gene <- ifelse(data$gene == "Luciferase", "  Luciferase\n(miR34a HG)", "        Renilla\n(miR34a asRNA)")
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for rmarkdown
ggplot(data, aes(x=factor(treatment), y=log2fold))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        scale="width",
        alpha=0.3,
        colour=NA,
        show.legend = FALSE
    )+
    geom_point( 
        aes(colour=gene),
        size=4,
        position=position_dodge(width=0.9)
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    facet_grid(.~shRNA, scale="free")+
    geom_label(
        aes(y=CI95h+0.1, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        position=position_dodge(width=0.9),
        fill="white",
        size=5,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "\u0394\u0394Ct", 
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(0.025,0.1,0.5,0.25,1,2.5,5)
        )
    )+
    labs(
      x="Doxorubicin (ng/ml)",
      title="HCT116",
      caption=
            "miR34a (luficerase) and miR34a asRNA (renilla) in HCT116 cells which were co-transfected with the P1 construct and the specified shRNA after which they\nwere treated with the indicated dose of doxorubicin. Error bars (black vertical) indicate 95% CI and black points represent the mean.\n\u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_color_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15, hjust=0.5),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15)
    )+ 
    guides(
        color=guide_legend(
        title="Gene", 
        override.aes = list(size=4)
        )
    )

#plot for pdf
p <- ggplot(data, aes(x=factor(treatment), y=log2fold))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        scale="width",
        alpha=0.3,
        colour=NA,
        lwd = 0.1
    )+
    #geom_point( 
    #    aes(colour=gene),
    #    size=0.4,
    #    position=position_dodge(width=0.9)
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        lwd=0.2
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        size=0.1,
        show.legend = FALSE
    )+
    facet_grid(.~shRNA, scale="free")+
    geom_label(
        aes(y=CI95h+0.2, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        position=position_dodge(width=0.9),
        fill="white",
        size=1,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "\u0394\u0394Ct"
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(0.025,0.1,0.5,0.25,1,2.5,5)
        #)
    )+
    labs(
      x="Doxorubicin (ng/ml)"
      #title="HCT116"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_color_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position="top",
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=5),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm"),
        panel.border = element_rect(fill=NA, size=0.15)
    )+ 
    guides(fill=guide_legend(
        title="Gene", 
        override.aes = list(size=2)
    ))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/P1shRNAdox/P1shRNAdox.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

#Conclusion
Levels of luciferase were abrogated in the shRenilla-transfected cells compared to control shRNA-transfected cells. Collectively, these results indicate that miR34a asRNA positively regulates levels of miR34a HG and is crucial for a proper miR34a response to apoptotic stimuli.

### 2017-10-26 inst/StableLineCCND1exp/stableLineCCND1exp.Rmd
first commit

---
title: "CCND1 expression in PC3 stable cell lines"
author: "Jason T. Serviss"
date: "12/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
To further investigate the characteristics of the miR34a asRNA stable lines, we measured the expression level of known miR34a target cyclin D1. miR34a has been previously shown to inhibit cell cycle progression, partially via its regulation of cyclin D1.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were seeded at 2x10^5 cells per well in a 12-well plate. After 24 hours, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "CCND1 Fwd",	
        "CCND1 Rev",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "CGT GGC CTC TAA GAT GAA GG",
        "CTG GCA TTT TGG AGA GGA AG",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers
```

#Results

```{r, warning=FALSE, message=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
library(scales)
library(extrafont)

data <- read.table('~/GitHub/miR34aFigures/inst/StableLineCCND1exp/QPCRdata.txt', header=TRUE, sep="\t")
goi <- data[data$gene == "CCND1", ]
hk <- data[data$gene == "B-actin", ]
colnames(goi)[c(5,6)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(5,6)] <- c("Ct1HK", "Ct2HK")
hk$gene <- NULL

data <- merge(goi, hk, by=c("experiment", "cellLine", "condition"))
data$meanGOI <- rowMeans(data[,c("Ct1GOI", "Ct2GOI")])
data$meanHK <- rowMeans(data[,c("Ct1HK", "Ct2HK")])

#ddct
data$dct <- data$meanGOI - data$meanHK
ddct <- ddply(
    data,
    c("experiment", "condition"),
    summarize,
    ddct=dct-data[data$experiment == 2 & data$condition == "mock", "dct"]
)
data <- merge(data, ddct, by=c("experiment", "condition"), all.x=TRUE)
data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data,
    c("condition"),
    summarize, 
    mean=mean(log2fold),
    pValue=t.test(log2fold, data[data$condition == "mock", "log2fold"])$p.value,
    CI95l=t.test(log2fold)$conf.int[1],
    CI95h=t.test(log2fold)$conf.int[2]
)
stats[stats$condition == "mock", "pValue"] <- NA

stats$pStars <- ifelse(
    stats$pValue < 0.05 & stats$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        stats$pValue < 0.005 & stats$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            stats$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

data <- merge(data, stats, by="condition", all.x=TRUE)

#prepare for plotting
data$condition <- ifelse(data$condition == "mock", "mock", "miR34a\nasRNA")
data$condition <- factor(data$condition, levels=c("mock", "miR34a\nasRNA"))
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data, aes(x=condition, y=log2fold))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width"
    )+
    geom_point( 
        aes(colour=condition),
        size=4
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black"
    )+
    geom_point(
        aes(x=condition, y=mean),
        colour="black"
    )+
    geom_segment(
        aes(x=1, y=0.175, xend=2, yend=0.175),
        colour="grey43"
    )+
    geom_label(
        data=stats,
        aes(x=1.5, y=0.19, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=5,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "\u0394\u0394Ct", 
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(0.7,0.8,0.9,1,1.1,1.3)
        )
    )+
    labs(
      x="Cell line",
      title="CCND1",
      caption=
            "Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines. Error bars (black vertical) indicate 95% CI and means are represented \nby black dots. \u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="none",
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15)
    )

#plot for pdf
p <- ggplot(data, aes(x=condition, y=log2fold))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=condition),
    #    size=0.4
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black",
        lwd=0.15
    )+
    geom_point(
        aes(x=condition, y=mean),
        colour="black",
        size=0.5
    )+
    geom_segment(
        aes(x=1, y=0.175, xend=2, yend=0.175),
        colour="grey43",
        lwd=0.15
    )+
    geom_label(
        data=stats,
        aes(x=1.5, y=0.19, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        family="Arial Unicode MS",
        size=1
    )+
    scale_y_continuous(
        "\u0394\u0394Ct"
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(0.7,0.8,0.9,1,1.1,1.3)
        #)
    )+
    labs(
      x="Cell line",
      title="CCND1 gene"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position="none",
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text=element_text(size=8),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLineCCND1exp/stableLineCCND1exp.pdf", device=cairo_pdf, height=60, width=42, units="mm")

```

#Conclusions
CCND1 expression levels are decreased in PC3 cell lines stably over-expressing miR34a asRNA.

### 2017-10-26 inst/StableLineCCND1prot/stableLineCCND1prot.Rmd
first commit

---
title: "CCND1 protein expression in PC3 stable lines"
author: "Jason T. Serviss"
date: "09/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

##Introduction

After observing decreased mRNA levels for the miR34a target CCND1, we were interested whether this has also consequences for its protein levels.

##Methods
All cell lines were cultured at 5% CO2 and 37° C with PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. We seeded three independent experiments of 150,000 cells/well in a six well plate (PC3 mock vs. PC3 miR34a AS F4) and grew them for 24 hours. Before harvesting cells were controlled for their confluency. Cells with a confluence of 60-75%, were harvested using trypsin. Cell pellets were frozen down at -80°C before lysed for Western Blot analysis. Western Blot analysis was performed following Lottes’ protocol. Cells were lysed in RIPA Buffer and run on a 4-12% Bis-Tris-SDS Gel using MOPS running buffer. Proteins were transferred onto a nitrocellulose membrane using iBlot Turbo Blotting Device. Proteins were transferred for 7 minutes. Membranes were blocked for 1 hour at room temperature in 5% milk. Membranes were incubated with a cyclin D1 antibody (92G2 Rabbit mAb, Cell Signalling) overnight at 4°C. The membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature. Membranes were washed 3-times for 5min each in TBS-T. Membranes were developed using chemiluminescence. After the picture was taken, the membrane was stripped using 0.4M NaOH solution for 20min. Blocking step was repeated and primary antibody against GAPDH was incubated for overnight at 4°C. Consequently, the membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature. Membranes were washed 3-times for 5min in TBS-T. Membranes were developed using chemiluminescence.

##Results

###Representative experiment
<center>![Representative experiment.](singleExp.png)</center>
<br></br><br></br><br></br>

###Quantification
```{r, warning=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/StableLineCCND1prot/WBdata.txt', header=TRUE, sep="\t")
data$value <- (data$Intensity - data$background) * data$pixel

#normalize to GAPDH
ccnd1 <- subset(data, protein == "CCND1")
ccnd1$normValue <- ccnd1$value / data[data$protein == "GAPDH", "value"]

#normalize to control
#ccnd1$percentOfMock <- ccnd1$normValue / ccnd1[ccnd1$condition == "mock" , "normValue"]
toCtrl <- ddply(
    ccnd1,
    c("condition", "experiment"),
    summarize,
    percentOfMock = normValue / ccnd1[ccnd1$condition == "mock" & ccnd1$experiment == 1, "normValue"]
)
ccnd1 <- merge(ccnd1, toCtrl, by=c("condition", "experiment"), all.x=TRUE)

#move data to normal distribution
ccnd1$log2percentOfMock <- log2(ccnd1$percentOfMock)

#calculate statistics
stats <- ddply(
    ccnd1,
    "condition",
    summarize, 
    mean=mean(log2percentOfMock),
    pValue=t.test(log2percentOfMock, ccnd1[ccnd1$condition == "mock", "log2percentOfMock"])$p.value,
    CI95l=t.test(log2percentOfMock)$conf.int[1],
    CI95h=t.test(log2percentOfMock)$conf.int[2]
)

stats$pStars <- ifelse(
    stats$pValue < 0.05 & stats$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        stats$pValue < 0.005 & stats$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            stats$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

ccnd1 <- merge(ccnd1, stats, by=c("condition"))

#prepare for plotting
ccnd1$condition <- ifelse(ccnd1$condition == "mock", "mock", "miR34a\nasRNA")
ccnd1$condition <- factor(ccnd1$condition, levels=c("mock", "miR34a\nasRNA"))

```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(ccnd1, aes(x=condition, y=log2percentOfMock))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width"
    )+
    geom_point( 
        aes(colour=condition),
        size=4
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black"
    )+
    geom_point(
        aes(x=condition, y=mean),
        colour="black"
    )+
    geom_segment(
        aes(x=1, y=0.5, xend=2, yend=0.5),
        colour="grey43"
    )+
    geom_label(
        aes(x=1.5, y=0.6, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=5,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "log2(Fold)", 
        sec.axis = sec_axis(
            ~2^., 
            name = "Fold", 
            breaks=c(0.1,0.25,0.5,1,1.25,1.5)
        )
    )+
    labs(
      x="Cell line",
      title="CCND1 protein",
      caption=
            "Western blot showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines.\nFold = Fraction mock std. to GAPDH. Error bars (black vertical) indicate 95% CI and means are represented by black dots.\n\u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="none",
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15)
    )

#plot for pdf
p <- ggplot(ccnd1, aes(x=condition, y=log2percentOfMock))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=condition),
    #    size=0.6
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black",
        lwd=0.15
    )+
    geom_point(
        aes(x=condition, y=mean),
        colour="black",
        size=0.5
    )+
    geom_segment(
        aes(x=1, y=0.5, xend=2, yend=0.5),
        colour="grey43",
        lwd=0.15
    )+
    geom_label(
        aes(x=1.5, y=0.6, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "log2(Fold)"
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = "Fold", 
        #    breaks=c(0.1,0.25,0.5,1,1.25,1.5)
        #)
    )+
    labs(
      x="Cell line",
      title="CCND1 protein"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position="none",
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text=element_text(size=8),
        axis.line=element_line(size=0.25),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )

#deafult width and height = 7
ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLineCCND1prot/stableLineCCND1prot.pdf", device=cairo_pdf, height=60, width=42, units="mm")

```

##Conclusions
Cyclin D1 protein levels are significantly reduced in PC3 cells overexpressing miR34a asRNA, consistent with increased miR34a expression levels and the reduced G1 cell cycle phase observed in PC3 cells.

### 2017-10-26 inst/StableLineCellCycle/stableLineCellCycle.Rmd
first commit

---
title: "StableLineCellCycle"
author: "Jason T. Serviss"
date: "05/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
miR34a is known to regulate cell cycle and, specifically, induce G1-phase arrest. Due to the increase observed in miR34a expression levels in cell lines over-expressing miR34a asRNA, we investigated if the cell cycle was perturbed in these cells.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with Skov3 and PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. 1x10^5 cells per well in a 6-well plate and harvested after 24hrs. Cells were washed in PBS and fixed in 4% PFA at room temperature overnight. PFA was removed, and cells were resuspended in 95% EtOH. The samples were then rehydrated in distilled water, stained with DAPI and analyzed by flow cytometry on a LSRII (BD Biosciences) machine. Resulting data was further processed using Flowjo software.

#Results

```{r, warning=FALSE, message=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
library(scales)
library(extrafont)

data <- read.table('~/GitHub/miR34aFigures/inst/StableLineCellCycle/cellCycleData.txt', header=TRUE, sep="\t")
data$value <- data$value/100
data$log2Value <- log2(data$value)

#qqplot shows that the data is reasonably normal. The shapiro test is also used below. Note that a p < 0.05 indicates non-normality.
#qqnorm(data$log2Value)

#calculate statistics
stats <- ddply(
    data,
    c("cellLine", "condition", "phase"),
    summarize,
    mean=2^mean(log2Value),
    shapiroTest = shapiro.test(log2Value)$p.value,
    pValue=t.test(value, data[data$cellLine == unique(cellLine) & data$condition == "mock" & data$phase == unique(phase), "value"])$p.value,
    CI95l=2^t.test(log2Value)$conf.int[1],
    CI95h=2^t.test(log2Value)$conf.int[2]

)

data <- merge(data, stats, by=c("cellLine", "condition", "phase"), all.x=TRUE)

data$pStars <- ifelse(
    data$pValue < 0.05 & data$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        data$pValue < 0.005 & data$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            data$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

#prepare for plotting
data$condition <- factor(data$condition, levels=c("mock", "miR34a AS"))
data$phase <- factor(data$phase, levels=c("G1", "S", "G2"))

Ys <- ddply(data, c("phase", "cellLine"), summarize, Ys=max(CI95h))

pBars <- data.frame(
    cellLine = c(rep("PC3", 3), rep("Skov3", 3)),
    phase = rep(c("G1", "S", "G2"), 2),
    condition = rep("miR34a AS", 6),
    x = rep(c(1,NA,3), 2)-0.25,
    xend = rep(c(1,NA,3), 2)+0.25,
    xStars = rep(c(1,2,3), 2)
)

pBars <- merge(pBars, Ys, by=c("cellLine", "phase"), all.x=TRUE)
data <-  merge(data, pBars, by=c("cellLine", "phase", "condition"), all.x=TRUE)

```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for rmarkdown
ggplot(data=data, aes(x=phase, y=value))+
    geom_violin(
        aes(fill=condition),
        scale="width", 
        alpha=0.3, 
        weight=10,
        trim=TRUE,
        color=NA,
        show.legend = FALSE
    )+
    geom_point(
        aes(group=interaction(phase, condition), color=condition),
        position=position_dodge(width=0.9),
        size=2
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=interaction(phase, condition)),
        position=position_dodge(width=0.9),
        colour="grey25",
        show.legend = FALSE
    )+
    facet_grid(
        .~cellLine, 
        scale="free"
    )+
    geom_point(
        aes(x=phase, y=mean, group=condition), 
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    scale_y_continuous(labels = percent_format())+
    geom_segment(
        aes(x=x, y=Ys+0.01, xend=xend, yend=Ys+0.01),
        colour="grey43",
        show.legend = FALSE
    )+
    geom_label(
        aes(y=Ys+0.02, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=3,
        family="Arial Unicode MS"
    )+
    labs(
      x="Cell cycle phase",
      title="Cell cycle",
      caption=
            "Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control.\nError bars (black vertical) indicate 95% CI and horizontal lines (black) represent the mean.\n\u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=22
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x = element_text(size = 15),
        axis.title.y=element_blank(),
        legend.title=element_text(size=17),
        legend.text=element_text(size=15)
    )+ 
    guides(color=guide_legend(title="Condition"))

#plot for pdf
p <- ggplot(data=data, aes(x=phase, y=value))+
    geom_violin(
        aes(fill=condition),
        scale="width", 
        alpha=0.3, 
        trim=TRUE,
        color=NA,
        lwd = 0.1
    )+
    #geom_point(
    #    aes(group=interaction(phase, condition), color=condition),
    #    position=position_dodge(width=0.9),
    #    size=0.1
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=interaction(phase, condition)),
        position=position_dodge(width=0.9),
        colour="black",
        show.legend = FALSE,
        lwd=0.15
    )+
    facet_grid(
        .~cellLine, 
        scale="free"
    )+
    geom_point(
        aes(x=phase, y=mean, group=condition), 
        colour="black",
        position=position_dodge(width=0.9),
        size=0.1,
        show.legend = FALSE
    )+
    scale_y_continuous(labels = percent_format())+
    geom_segment(
        aes(x=x, y=Ys+0.01, xend=xend, yend=Ys+0.01),
        colour="grey43",
        show.legend = FALSE,
        lwd=0.2
    )+
    geom_label(
        aes(y=Ys+0.02, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS"
    )+
    labs(
      x="Cell cycle phase"
      #title="Cell cycle"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(rep(0.1, 4), "lines"),
        legend.margin=unit(1,"mm"),
        legend.position="top",
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.title.y=element_blank(),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm"),
        axis.text=element_text(size=8),
        #axis.line=element_line(size=0.15),
        panel.border = element_rect(fill=NA, size=0.15),
        panel.margin=unit(2, "mm"),
        strip.text.x = element_text(size = 8, margin = margin(0.01, 0, 0.1, 0, "cm"))
    )+ 
    guides(
        fill=guide_legend(
            title="Cell line", 
            override.aes = list(
                size=2
            )
        )
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLineCellCycle/StableLineCellCycle.pdf", device=cairo_pdf, height=60, width=83, units="mm")
```

#Conclusion
An increase in the percentage of cells in G1-phase can be seen in cell lines overexpressing miR34a asRNA. In addition, a concominant decrease of cells in G2-phase can be observed.

### 2017-10-26 inst/StableLineExpressionHEK/stableLineExpressionHEK.Rmd
first commit

---
title: "miR34a asRNA stable over-expression cell lines"
author: "Jason T. Serviss"
date: "04/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
miR34a asRNA over-expressing cell lines, previously generated, showed a high overexpression level of miR34a asRNA despite a low multiplicity of infection. This is most likley due to the fact that all infected cell lines have practically no endogenous miR34a asRNA expression. To investigate the physiological relevance of the over-expression the miR34a asRNA levels were compared to the expression levels in HEK293t cells, which have a high endogenous miR34a expression level.

#Methods
See "stableLineExpression.rmd" file.

#Results

```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/StableLineExpressionHEK/QPCR.txt', header=TRUE, sep="\t")

#extract AS experiment
as <- data
asRNA <- data[data$Gene == "miR34a asRNA F1R1", ]
colnames(asRNA)[c(5,6,7)] <- c("Ct1GOI", "Ct2GOI", "Ct3GOI")

bact <- data[data$Gene == "B-actin", ]
colnames(bact)[c(5,6,7)] <- c("Ct1HK", "Ct2HK", "Ct3HK")

asRNA <- cbind(asRNA, bact[ ,c("Ct1HK", "Ct2HK", "Ct3HK")])
asRNA$Condition <- ifelse(asRNA$Condition == "F4", "miR34a AS", as.character(asRNA$Condition))

#remove PC3 experiment 6, B-act mean Ct > 30, too high.
asRNA <- asRNA[asRNA$experiment != 6 | asRNA$cellLine != "PC3", ]

asRNA$meanGOI <- rowMeans(asRNA[ ,c("Ct1GOI", "Ct2GOI", "Ct3GOI")], na.rm=TRUE)
asRNA$meanHK <- rowMeans(asRNA[ ,c("Ct1HK", "Ct2HK", "Ct3HK")], na.rm=TRUE)

#perform ddct
asRNA$dct <- asRNA$meanGOI - asRNA$meanHK

ddct <- ddply(
    asRNA, 
    c("experiment", "cellLine", "Condition"), 
    summarize, 
    ddct=dct-asRNA[asRNA$experiment == 3 & asRNA$cellLine == "HEK293t" & asRNA$Condition == "wt", "dct"]
)

asRNA <- merge(asRNA, ddct, by=c("experiment", "cellLine", "Condition"), all=TRUE)
asRNA$fold <- 2^-asRNA$ddct
asRNA$log2Fold <- log2(asRNA$fold)

#run statistics
pValues <- ddply(
    asRNA, 
    c("cellLine", "Condition"), 
    summarize,
    mean=mean(log2Fold),
    conf.intLow = t.test(log2Fold, mu=0)$conf.int[1],
    conf.intHigh = t.test(log2Fold, mu=0)$conf.int[2]
)

asRNA <- merge(asRNA, pValues, by=c("cellLine", "Condition"), all.x=TRUE)

#prepare for plotting
asRNA$cellLine <- factor(asRNA$cellLine, levels=c("HEK293t", "PC3", "Skov3", "Saos2"))
asRNA$Condition <- ifelse(asRNA$Condition == "miR34a AS", "miR34a asRNA", as.character(asRNA$Condition))
asRNA$Condition <- factor(asRNA$Condition, levels=c("wt", "mock", "miR34a asRNA"))

```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for rmarkdown
ggplot(asRNA, aes(x=Condition, y=log2Fold))+
    geom_violin(
        aes(fill=Condition),
        scale="width",
        trim=TRUE,
        alpha=0.3,
        color=NA,
        show.legend = FALSE
    )+
    geom_point(
        data=asRNA, 
        aes(colour=Condition), 
        size=3, 
        alpha=0.8
    )+
    geom_point(
        aes(y=mean),
        colour="black",
        show.legend = FALSE
    )+
    geom_linerange(
        aes(ymin=conf.intLow, ymax=conf.intHigh),
        show.legend = FALSE
    )+
    facet_grid(.~cellLine, scales = "free")+
    scale_y_continuous(
        "\u0394\u0394Ct", 
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), breaks=c(0.00001, 0.00005, 0.0001, 0.0005, 0.001, 0.005, 0.01, 0.05, 0.1, 0.5, 1, 5, 10, 50))
    )+
    labs(
        x="Cell line",
        title="miR34a asRNA",
        caption=
            "miR34a asRNA over-expression levels in PC3, Skov3, and Saos2 stable cell lines compared to HEK293t cells.\n\u0394\u0394ct = target gene - House keeping gene - HEK293t. Error bars indicate 95% CI and black points represent the mean."
    )+
    theme_few()+
    scale_color_ptol()+
    scale_fill_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15)
        ),
        legend.position="none",
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x = element_text(size = 15)
    )

p <- ggplot(asRNA, aes(x=Condition, y=log2Fold))+
    geom_violin(
        aes(fill=Condition),
        scale="width",
        trim=TRUE,
        alpha=0.3,
        color=NA,
        show.legend = FALSE,
        lwd=0.1
    )+
    geom_point(
        data=asRNA, 
        aes(colour=Condition), 
        size=0.6, 
        alpha=0.8
    )+
    geom_point(
        aes(y=mean),
        colour="black",
        show.legend = FALSE,
        size=0.5
    )+
    geom_linerange(
        aes(ymin=conf.intLow, ymax=conf.intHigh),
        show.legend = FALSE,
        lwd=0.2
    )+
    facet_grid(.~cellLine, scales = "free")+
    scale_y_continuous(
        "\u0394\u0394Ct"
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), breaks=c(0.00001, 0.0001, 0.001, 0.01, 0.1, 1, 10))
    )+
    labs(
        x="Cell line"
        #title="miR34a asRNA"
    )+
    theme_few()+
    scale_color_ptol()+
    scale_fill_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position="none",
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.x=element_text(size=8, angle=90, vjust=0.5, hjust=1),
        axis.text.y=element_text(size=6),
        strip.text.x = element_text(size = 9),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm"),
        axis.line=element_line(size=0.15),
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLineExpressionHEK/StableLineExpHEK293t.pdf", device=cairo_pdf, height=60, width=83, units="mm")
```

#Conclusions
Results indicate that miR34a asRNA is over-expressed 13-22 fold greater that endogenous HEK293t levels.

### 2017-10-26 inst/allFigures/miR34aProjectFigures.Rmd
first commit

---
title: "miR34a asRNA figures"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

```{r}
library(printr)
```

#miR34a asRNA characterization
###miR34a locus
<br></br>
<center>![miR34a locus.](../miR34aLocus/miR34aLocus.png)</center>
<br></br>
A schematic picture of the miR34a locus from UCSC genome browser including miR34a HG and mature miR34a (purple) as well as bioinformatic evidence for antisense transcription from 
GENCODE v19 (green) and the spliced human EST track (black). H3K4me3 ChIP-seq data from ENCODE indicating the promoter region and conservation over the locus is also shown.

##miR34a asRNA tissue expression
<br></br>
<center>![miR34a cell panel screening (miranda).](../miR34aASExpressionCellPanel/mirandaCellPanel.png)</center>
<br></br>
<center>![miR34a cell panel screening (large).](../miR34aASExpressionCellPanel/cellPanelLarge.png)</center>
<br></br>

Semi-quantitative PCR data from the screening of a panel of cell lines. 
* Indicates that, although the cell line is p53wt, other mechanisms are present which inhibit p53 function.

##Coding Potential
###Coding Potential Assesment Tool
```{r}
cpat <- read.table('../codingPotential/CodingPotentialAssessmentTool/results.txt', header=TRUE, sep="\t")
cpat
```

Coding potential analysis results from the Coding-potential Assessment Tool including miR34a asRNA and 
2 characterized non-coding transcripts (HOTAIR and XIST) and 3 known coding transcripts (β-actin, tubulin, and MYC).

###Coding Potential Calculator
```{r}
cpc <- read.table('../codingPotential/CodingPotentialCalculator/results.txt', header=TRUE, sep="\t")
colnames(cpc) <- gsub("\\.", " ", colnames(cpc))
cpc
```

Coding potential analysis results using the Coding-potential calculator for miR34a asRNA, HOTAIR, and β-actin.

##3-prime RACE
<br></br>
<center>![miR34a asRNA 3-prime RACE.](../3primeRACE/results.png)</center>
<br></br>

3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript from GENCODE.

##Primer walk assay
<br></br>
<center>![primer walk schematic.](../primerWalk/schematic.png)</center>
<br></br>
<center><img src="../primerWalk/gel.png" alt="some text"  width="500" height="500"></center>
<br></br>
A schematic picture of the miR34a asRNA locus including the location of the primers used in the primer walk assay and 
the semi-quantitative PCR results from the primer walk assay performed using HEK293T cells.

##Stability
<br></br>
<center><img src="../transcriptStability/transcriptStability.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Q-PCR showing miR34a asRNA and miR34a HG levels in U2OS cells after treatment with 10nM actinomycin D. Error bars (black vertical) indicate standard deviation and means are represented by black dots.

##Cellular localization
<br></br>
<center><img src="../cellularLocalization/cellularLocalization.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
 Q-PCR results from fractionated HEK293T cells investigating the cellular localization of the miR34a asRNA transcript.

##miR34a asRNA isoforms
<br></br>
<center>![isoforms.](../isoforms/isoforms.png)</center>
<br></br>
Cloned isoforms of the miR34a asRNA gene.

##Polyadenylation
<br></br>
<center><img src="../polyadenylation/polyadenylation.png" alt="some text"  width="500" height="500"></center>
<br></br>
Polyadenylation status of the spliced and unspliced variants of miR34a asRNA in HEK293t cells.

#Regulation of miR34a asRNA
<br></br>
<center><img src="../HCT116p53null/HCT116p53null.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in p53+/+ and p53-/- HCT116 cells.

<br></br>
<center><img src="../HctHekDox/HctHekDox.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Q-PCR showing miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after treatment with 200 ng/ml doxorubicin for 24hrs. Error bars (black vertical) indicate 95% CI and means are represented by black dots. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

##miR34a asRNA promoter
<br></br>
<center><img src="../P1-HCTandHEK/locus.png" alt="some text"  width="1000" height="1000"></center>
<br></br>
A UCSC genome browser illustration indicating the location of the promoter region cloned into the p1 construct including the conserved p53-binding site.
<br></br>
<center><img src="../P1-HCTandHEK/constructs.png" alt="some text"  width="750" height="750"></center>
<br></br>
A representative picture of the p1 construct including forward (F) and reverse (R) primer locations.
<br></br><br></br>
<center><img src="../P1-HCTandHEK/P1-HCTandHEK_P1.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 and P2 constructs. Luciferase represents miR34a HG and renilla represents miR34a asRNA. Error bars (black vertical) indicate 95% CI and means are represented by black dots. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

##miR34a asRNA and HG correlation in primary cancer cells
<br></br>
<center><img src="../TCGAcorrelation/correlation.png" alt="some text"  width="1000" height="1000"></center>
<br></br>
TCGA RNA sequencing data illustrating the correlation between miR34a HG and miR34a asRNA in p53 wt and mutated primary cancer cells.
<br></br>
<center><img src="../TCGAcorrelation/table.png" alt="some text"  width="500" height="500"></center>
<br></br>
A table showing R-squared and p-values for each illustrated correlation.
<br></br><br></br>

#Function of miR34a asRNA
<br></br>
<center><img src="../P1shRNAdox/P1shRNAdox.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
miR34a (luficerase) and miR34a asRNA (renilla) in HCT116 cells which were co-transfected with the P1 construct and the specified shRNA after which they were treated with the indicated dose of doxorubicin. Error bars (black vertical) indicate 95% CI and black points represent the mean. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../StableLineExpression/StableLineExp.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control. &#916;&#916;ct = House keeping gene - Target gene - mock control. Error bars indicate 95% CI and black points represent the mean. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../StableLineExpressionHEK/StableLineExpHEK293t.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
miR34a asRNA over-expression levels in PC3, Skov3, and Saos2 stable cell lines compared to HEK293t cells. &#916;&#916;ct = target gene - House keeping gene - HEK293t. Error bars indicate 95% CI and black points represent the mean.

<br></br>
<center><img src="../StableLineCellCycle/StableLineCellCycle.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control. Error bars (black vertical) indicate 95% CI and horizontal lines (black) represent the mean. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../StableLinePolIIChIP/StableLinePolIIChIP.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Phosphorylated Poll II ChIP in miR34a asRNA over-expressing PC3 stable cell lines compared to their respective mock control. Error bars (black vertical) indicate 95% CI and black points represent the mean. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../StableLineCCND1exp/stableLineCCND1exp.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines. Error bars (black vertical) indicate 95% CI and means are represented by black dots. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../StableLineCCND1prot/singleExp.png" alt="some text"  width="500" height="500"></center>
<br></br>
A representative experiment.
<br></br>
<center><img src="../StableLineCCND1prot/stableLineCCND1prot.pdf" alt="some text"  width="750" height="750"></center>
<br></br>
Western blot showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines. Fold = Fraction mock std. to GAPDH. Error bars (black vertical) indicate 95% CI and means are represented by black dots. &#9733; = p < 0.05; &#9733;&#9733; = p < 0.005, &#9733;&#9733;&#9733; = p < 0.0005.

<br></br>
<center><img src="../survival/survival.png" alt="some text"  width="750" height="750"></center>
<br></br>
Suvival in TCGA cancer types dependent on miR34a asRNA expression levels.
<br></br>

### 2017-10-26 inst/codingPotential/codingPotential.Rmd
first commit

---
title: "Coding Potenital of the miR34a asRNA"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We utilized a bioinformatic approach to evaluate the coding potential of the miR34a asRNA transcript. The Coding-potential assessment tool uses a linear regression model to evaluate coding-potential by examining ORF length, ORF coverage, Fickett score and hexamer score. We further confirmed these results using the Coding-potential Calculator which utilizes a support based machine-based classifier and accesses an alternate set of discriminatory features.

#Methods
Protein-coding capacity was evaluated using the Coding-potential Assessment Tool [43] and Coding-potential Calculator [44] with default settings. Transcript sequences for use with Coding-potential Assessment Tool were downloaded from the UCSC genome browser using the following IDs: HOTAIR (ENST00000455246.1), XIST (ENST00000429829.1), β-actin (ENST00000331789.5), Tubulin (ENST00000427480.1), and MYC (ENST00000377970). Transcript sequences for use with Coding-potential Calculator were downloaded from the UCSC genome browser using the following IDs: HOTAIR (uc031qho.1), β-actin (uc003soq.4).

#Results
```{r}
library(printr)
```

##Coding Potential
###Coding Potential Assesment Tool
```{r}
cpat <- read.table('CodingPotentialAssessmentTool/results.txt', header=TRUE, sep="\t")
cpat
```

Coding potential analysis results from the Coding-potential Assessment Tool including miR34a asRNA and 
2 characterized non-coding transcripts (HOTAIR and XIST) and 3 known coding transcripts (β-actin, tubulin, and MYC).

###Coding Potential Calculator
```{r}
cpc <- read.table('CodingPotentialCalculator/results.txt', header=TRUE, sep="\t")
colnames(cpc) <- gsub("\\.", " ", colnames(cpc))
cpc
```

Coding potential analysis results using the Coding-potential calculator for miR34a asRNA, HOTAIR, and β-actin.

#Conclusions
Results indicated that miR34a asRNA has a similar lack of coding capacity to the known non-coding transcripts HOTAIR and XIST and differs greatly when examining these parameters to the known coding transcripts beta-actin, tubulin, and MYC. However, to fully evaluate coding potential methods such as mass spectrometry or ribosome profiling must be used.

### 2017-10-26 inst/growthStarvation/growthStarvation.Rmd
first commit

---
title: "Monitoring growth of miR34a asRNA overexpressings cells under conditions of starvation."
author: "Jason T. Serviss"
date: "30/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
As p53 is a well-known regulator of senescence and apoptosis and has been shown to specifically importatnt under conditions of cellular stress, such as starvation. Therefore, we investigated whether overexpression of miR34a AS affects growth rate under normal and starvation conditions by measuring changes in confluency over time.

#Methods
10^4 PC3 cells, either miR34a asRNA overexpressing or WT, were seeded in 96 well plates. After attachment (3-4h) media was replaced with either RPMI (Gibco, life technology) (supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum) or HBSS. Cells were incubated in Spark Multimode Microplate reader for 48 hours at 37°C with 5% CO2 in a humidity chamber. Confluency was measured every hour.

#Analysis

Load the data.
```{r, message = FALSE}
packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

data <- read.table('~/GitHub/miR34aFigures/inst/growthStarvation/rawData.txt', header=TRUE, sep="\t") %>%
    filter(Time <= 35) %>%
    mutate(Time = parse_factor(Time, levels = as.character(0:max(Time)))) %>%
    mutate(Treatment = parse_factor(Treatment, levels = c("RPMI", "HBSS"))) %>%
    mutate(cellLine = paste(Cell.line, Condition, sep = "-")) %>%
    mutate(cellLine = case_when(
        cellLine == "PC3-F4" ~ "miR34a asRNA",
        cellLine == "PC3-Mock" ~ "mock"
    )) %>%
    select(-Cell.line, -Condition) %>%
    mutate(cellLine = parse_factor(cellLine, levels = c("mock", "miR34a asRNA"))) %>%
    as_tibble()

```

Normalize the data to time point 0 for each condition.
```{r}
#normalize to first time point for control (Mock)
data <- data %>%
    group_by(Treatment, Biological.replicate, Technical.replicate, Time, cellLine) %>%
    mutate(normConfluency = Confluency / pull(data, Confluency)[data$Treatment == Treatment & data$Biological.replicate == Biological.replicate & data$Technical.replicate == Technical.replicate & data$Time == 0 & data$cellLine == cellLine]) %>%
    ungroup()
```

Plot each biological replicate with the technical replicates representing the variation.
```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
data %>%
    ggplot(aes(Time, normConfluency)) +
        geom_boxplot(aes(fill = cellLine)) +
        facet_grid(Biological.replicate~Treatment) +
        theme_few() +
        theme(
            axis.text.x = element_text(angle = 90)
        )
```

Conclusion: miR34a asRNA overexpression leads to decreased growth in both conditions in all biological replicates with the effect being more pronounced in HBSS (starvation).

Calculate the mean of the technical replicates for each condition and plot with the biological replicates representing the variability. 
```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#calculate mean for each technical replicate
data <- data %>%
    group_by(Treatment, Biological.replicate, Time, cellLine) %>%
    summarize(
        tech.mean = mean(normConfluency)
    ) %>%
    ungroup()

data %>%
    ggplot(aes(Time, tech.mean)) +
    geom_boxplot(aes(fill = cellLine)) +
    facet_grid(.~Treatment) +
        theme_few() +
        theme(
            axis.text.x = element_text(angle = 90)
        )
```

Calculate the mean, median, and 95% CI for each condition (using the biological replicates).
```{r}
stats <- data %>%
    filter(Time != 0) %>%
    group_by(cellLine, Treatment, Time) %>%
    summarize(
        min = min(tech.mean),
        max = max(tech.mean),
        mean = mean(tech.mean),
        median = median(tech.mean),
        CI95l = t.test(tech.mean)$conf.int[1],
        CI95h = t.test(tech.mean)$conf.int[2]
    )
```

#Results

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data = NULL) + 
    geom_ribbon(
        data = stats,
        aes(x = Time, ymin = CI95l, ymax = CI95h, group = cellLine, fill = cellLine), 
        alpha = 0.2,
        show.legend = TRUE
    ) +
    geom_linerange(
        data = stats,
        aes(x = Time, colour = cellLine, ymin = min, ymax = max), 
        position = position_dodge(width = 1),
        show.legend = FALSE
    ) + 
    geom_point(
        data = stats,
        aes(x = Time, y = median, group = cellLine, colour = cellLine), 
        position = position_dodge(width = 1),
        show.legend = FALSE
    ) +
    facet_grid(. ~ Treatment) +
    scale_x_discrete(breaks = seq(0, 47, 5)) +
    theme_few() +
    scale_fill_ptol() +
    scale_colour_ptol() +
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face = "bold",
            size = 20
        ),
        plot.caption = element_text(
            hjust = 0, 
            margin = margin(t = 15),
            family = "Arial Unicode MS"
        ),
        legend.position = "top",
        legend.title = element_text(size = 17),
        legend.text = element_text(size = 15),
        axis.title = element_text(size = 17),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.text = element_text(size = 15),
        strip.text.x = element_text(size = 17)
    ) +
    labs(
        x = "Time (hours)", 
        y = "Normalized % confluency",
        title = "miR34a asRNA's role in growth regulation.",
        caption = "The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line."
    ) +
    guides(
        fill = guide_legend(title = "Cell line"), 
        colour = guide_legend(title = "Cell line")
    )

p <- ggplot(data = NULL) +
    geom_ribbon(
        data = stats,
        aes(x = Time, ymin = CI95l, ymax = CI95h, group = cellLine, fill = cellLine), 
        alpha = 0.2,
        show.legend = TRUE
    ) +
    geom_linerange(
        data = stats,
        aes(x = Time, colour = cellLine, ymin = min, ymax = max), 
        position = position_dodge(width = 1),
        show.legend = FALSE,
        lwd = 0.1
    ) + 
    geom_point(
        data = stats,
        aes(x = Time, y = median, group = cellLine, colour = cellLine), 
        position = position_dodge(width = 1),
        size = 0.05,
        show.legend = FALSE
    ) + 
    facet_grid(. ~ Treatment) +
    scale_x_discrete(breaks = seq(0, 47, 5)) +
    labs(
        x = "Time (hours)", 
        y = "Normalized % confluency"
    ) +
    theme_few() +
    scale_fill_ptol() +
    scale_colour_ptol() +
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.spacing=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(
        fill = guide_legend(title = "Cell line"),
        colour = guide_legend(title = "Cell line")
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/growthStarvation/growthStarvation.pdf", device=cairo_pdf, height=60, width=83, units="mm")
```

#Conclusions
miR34a asRNA overexpression causes a minor decrease in cell growth under normal conditions (RPMI) although under conditions of cellular stress through starvation, this effect is increased dramatically.

### 2017-10-26 inst/isoforms/isoforms.Rmd
first commit

---
title: "miR34a asRNA isoforms"
author: "Jason T. Serviss"
date: "01/02/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We investigated the propensity of miR34a asRNA to be alternatively spliced, using PCR cloning and sequencing.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies), . All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was performed with the specified primer sets with annealing temperature 60˚C unless otherwise indicated. PCR was run for 35 cycles for those primer sets with annealing temperature 60˚C and 40 cycles in other cases. Resulting PCR products were run on a agarose gel, gel extracted with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced.

<br></br>
<center>![cloning gel](cloningGel.png)</center>
<br></br>
Cloned isoforms of the miR34a asRNA gene.

##Primers
```{r}
library(printr)
primers <- data.frame(
    name=c(
        "F12",
        "R1",
        "R2",
        "R3",
        "Ex3R1"
    ),
    sequence=c(
        "AAACACAAGCGTTTACCTGGGTGC",
        "TTGCCTCGTGAGTCCAAGGAGAAT",
        "ATAGGTTCATTTGCCCGATGTGCC",
        "CCACAGCTGTTGCTTCTGAATGCT",
        "TCAGATAGGTACCAAAAATGATGGCCGCAACTAATGACGGAT"
    )
)
primers
```

#Results

Product 8 resulted in miR34a AS 1  
Product 6 resulted in miR34a AS 2  
Product 2 resulted in miR34a AS 3  
Product 5 resulted in miR34a AS 4

<br></br>
<center>![isoforms.](isoforms.png)</center>
<br></br>
Cloned isoforms of the miR34a asRNA gene.

#Conclusions
Results indicate that the miR34a asRNA transcript is post-transcriptionally spliced to form several different isoforms.

### 2017-10-26 inst/miR34aLocus/miR34aLocus.Rmd
first commit

---
title: "miR34a locus"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
An antisense transcript to the miR34a HG was detected using the UCSC genome browser.

#Methods
The USCS genome browser was utilized for the bioinformatic evaluation of antisense transcription utilizing the Human EST and ENCODE RNAseq tracks.

#Results
<br></br>
<center>![miR34a locus and cloning of P1 and P2 constructs.](miR34aLocus_hg38.png)</center>
<br></br>
A schematic picture of the miR34a locus from UCSC genome browser including miR34a HG and mature miR34a and LINC01759. H3K4me3 ChIP-seq data from ENCODE indicating the promoter region and conservation over the locus is also shown.

#Conclusion
GENCODE annotation supports the presence of a transcript orinionating in the antisense orientation from the miR34a gene.

### 2017-10-26 inst/primerWalk/primerWalk.Rmd
first commit

---
title: "Primer walk assay"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We desired to determine the 5'-start site for the miR34a asRNA.

#Methods
To accomplish this we performed the primer walk assay. All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was performed for 35 cycles at 62°C annealing temperature and the resulting products were analyzed on a 2% agarose gel.

```{r}
primers <- data.frame(
    name=c(
        "miR34aAS_F10",
        "miR34aAS_F11",
        "miR34aAS_F12",
        "miR34aAS_F13",
        "miR34aAS_F14",
        "miR34aAS_F15",
        "miR34aAS_R1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "ATC TGC GTG GTC ACC GAG AAG CA",
        "CGC ACG GAC TGA GAA ACA CAA G",
        "ACG GAG GCT ACA CAA TTG AAC AGG",
        "AGG GAA GAA AGA ACT AGC CGA GCA",
        "CAT TTG CTG CAA TAT CAC CGT GGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT"
    )
)
```

#Results

<br></br>
<center>![primer walk schematic.](schematic_hg38.png)</center>
<br></br>
<center>![primer walk gel.](gel.png)</center>
<br></br>
 A schematic picture of the miR34a asRNA locus including the location of the primers used in the primer walk assay and 
the semi-quantitative PCR results from the primer walk assay performed using HEK293T cells.

#Conclusion
It appears as though the miR34a asRNA transcript start site is somewhat upstream of the annotated start site. Although there is some product present for the F12 primer, the majority of transcription seems to be origionating from the F11 primer. This indicates that the start site is between 71-224bp upstream of the annotated start site.

### 2017-10-26 inst/primers/primers.Rmd
first commit

---
title: "Primers used in the miR34a asRNA study"
output:
  pdf_document:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(message=FALSE, 
tidy.opts=list(width.cutoff=60))
library(pander)
```

```{r, echo=FALSE}
d1 <- data.frame(
    name="miR155_asF",
    sequence="AAG CTG GTC CAG\nGGC CAT TAT ACA",
    figures="Supplementary Fig. 1A"
)

d2 <- data.frame(
    name="miR155_asR",
    sequence="TGA CCT CAT GAT CCA GTC ACC TCA",
    figures="Supplementary Fig. 1A"
)

d3 <- data.frame(
    name="miR301a_asF2",
    sequence="CAA CGG CAG AAG CTT CAC CAC AAA",
    figures="Supplementary Fig. 1A"
)

d4 <- data.frame(
    name="miR301a_asR2",
    sequence="CGC TGC TGG ATT CGT TTG GCA TAA",
    figures="Supplementary Fig. 1A"
)

d5 <- data.frame(
    name="miR34bc_asF2",
    sequence="ACA GAA GTC ACT GGC ACT CTG A",
    figures="Supplementary Fig. 1A"
)

d6 <- data.frame(
    name="miR34bc_asR2",
    sequence="ACC CAT ATG GTC ATC TCC TTC GGA",
    figures="Supplementary Fig. 1A"
)

d7 <- data.frame(
    name="miR21_asF",
    sequence="AGT CTT ACC TGT GGT GTG CCC ATT",
    figures="Supplementary Fig. 1A"
)

d8 <- data.frame(
    name="miR21_asR",
    sequence="AGG TCC ATC TCT GCA GAA GCC ATT",
    figures="Supplementary Fig. 1A"
)

d9 <- data.frame(
    name="miR29b_asF",
    sequence="TGT AAT AAG AAG GGC GGT GCT CGT",
    figures="Supplementary Fig. 1A"
)

d10 <- data.frame(
    name="miR29b_asR",
    sequence="AAC CTG TCT TTG TCG CAG GTC TCA",
    figures="Supplementary Fig. 1A"
)

d11 <- data.frame(
    name="miR142_asRNA_F",
    sequence="TTG ATC GTC ATG CTG ACC CAG TGA",
    figures="Supplementary Fig. 1A"
)

d12 <- data.frame(
    name="miR142_asRNA_R",
    sequence="GGG CGG TCT TAC ATG CCT TTG AAT",
    figures="Supplementary Fig. 1A"
)

d13 <- data.frame(
    name="miR34a_asF10",
    sequence="ACG CGT CTC TCC AGC CCG GGA T",
    figures="Fig. 1C, Fig. 1E"
)

d14 <- data.frame(
    name="miR34a_asF11",
    sequence="ATC TGC GTG GTC ACC GAG AAG CA",
    figures="Fig. 1E"
)

d15 <- data.frame(
    name="miR34a_asF12",
    sequence="AAA CAC AAG CGT TTA CCT GGG TGC",
    figures="Fig. 1E, Supplementary Fig. 1C"
)

d16 <- data.frame(
    name="miR34a_asF13",
    sequence="ACG GAG GCT ACA CAA TTG AAC AGG",
    figures="Fig. 1E"
)

d17 <- data.frame(
    name="miR34a_asF14",
    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
    figures="Fig. 1E"
)

d18 <- data.frame(
    name="miR34a_asF15",
    sequence="CAT TTG CTG CAA TAT CAC CGT GGC",
    figures="Fig. 1E"
)

d19 <- data.frame(
    name="miR34a_as_int1R1",
    sequence="TGC GCA AAC TAC GCG CTC T",
    figures="Fig. 1F"
)

d20 <- data.frame(
    name="miR34a_asR2",
    sequence="ATA GGT TCA TTT GCC CGA TGT GCC",
    figures="Supplementary Fig. 1C"
)

d21 <- data.frame(
    name="miR34a_asR3",
    sequence="CCA CAG CTG TTG CTT CTG AAT GCT",
    figures="Supplementary Fig. 1C"
)

d22 <- data.frame(
    name="miR34a_asEx3_R1",
    sequence="GTT GCC TTC TTC GCA ACT CCT TGT",
    figures="Supplementary Fig. 1C"
)

d23 <- data.frame(
    name="miR34a_asF1",
    sequence="AGC GGC ATC TCC TCC ACC TGA AA",
    figures="Fig. 1B, Fig. 1C, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d24 <- data.frame(
    name="miR34a_asR1",
    sequence="TTG CCT CGT GAG TCC AAG GAG AAT",
    figures="Fig. 1B, Fig. 1E, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1C, Supplementary Fig. 1E"
)

d25 <- data.frame(
    name="miR34a_HG_F",
    sequence="TCT GCT CCA GTG GCT GAT GAG AAA",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
)

d26 <- data.frame(
    name="miR34a_HG_R",
    sequence="GTT CAC TGG CCT CAA AGT TGG CAT",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
)

d27 <- data.frame(
    name="miR34a_mature_F",
    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
    figures="Fig. 3B"
)

d28 <- data.frame(
    name="miR34a_mature_R",
    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
    figures="Fig. 3B"
)

d29 <- data.frame(
    name="B-actin_F",
    sequence="AGG TCA TCA CCA TTG GCA ATG AG",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d30 <- data.frame(
    name="B-actin_R",
    sequence="CTT TGC GGA TGT CCA CGT CA",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d31 <- data.frame(
    name="T7_long_reverse",
    sequence="CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
    figures="Fig. 1C"
)

d32 <- data.frame(
    name="FAM_primer",
    sequence="CCG TAG CTC GTC CAG GAC CC",
    figures="Fig. 1C"
)

d33 <- data.frame(
    name="U48_F (sybr)",
    sequence="AGT GAT GAT GAC CCC AGG TA",
    figures="Fig. 1F, Fig. 1G"
)

d34 <- data.frame(
    name="U48_R (sybr)",
    sequence="GGT CAG AGC GCT GCG GTG AT",
    figures="Fig. 1F, Fig. 1G"
)

d35 <- data.frame(
    name="U48_F (taqman)",
    sequence="Control miRNA Assay, RNU48, human",
    figures="Fig. 3B"
)

d36 <- data.frame(
    name="U48_R (taqman)",
    sequence="Control miRNA Assay, RNU48, human",
    figures="Fig. 3B"
)

d37 <- data.frame(
    name="Renilla_pBiDir_F1",
    sequence="TAA CGC GGC CTC TTC TTA TTT",
    figures="Fig. 3A"
)

d38 <- data.frame(
    name="Renilla_pBiDir_R1",
    sequence="GAT TTG CCT GAT TTG CCC ATA",
    figures="Fig. 3A"
)

d39 <- data.frame(
    name="Luc_set_II_F",
    sequence="AAG ATT CAA AGT GCG CTG CTG",
    figures="Fig. 3A"
)

d40 <- data.frame(
    name="Luc_set_II_R",
    sequence="TTG CCT GAT ACC TGG CAG ATG",
    figures="Fig. 3A"
)

d41 <- data.frame(
    name="CCND1 Fwd",
    sequence="CGT GGC CTC TAA GAT GAA GG",
    figures="Fig. 3D"
)

d42 <- data.frame(
    name="CCND1 Rev",
    sequence="CTG GCA TTT TGG AGA GGA AG",
    figures="Fig. 3D"
)

d43 <- data.frame(
    name="miR34a ChIP_F1",
    sequence="AAA GTT TGC AAA GAA GGA GGC GGG",
    figures="Fig. 3F"
)

d44 <- data.frame(
    name="miR34aChIP_R1",
    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
    figures="Fig. 3F"
)

primers <- rbind(
    d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18, d19, d20,
    d21, d22, d23, d24, d25, d26, d27, d28, d29, d30, d31, d32, d33, d34, d35, d36, d37, d38, d39, d40,
    d41, d42, d43, d44
)

primers$primerType <- c(
    rep("Other asRNA", 12),
    rep("miR34a asRNA", 12),
    rep("miR34a HG", 2),
    rep("miR34a mature", 2),
    rep("Other primers", 14),
    rep("miR34a asRNA", 2)
)
primers <- primers[order(as.character(primers$primerType)),]

primers$primerType <- c(
    "miR34a asRNA", rep("", 13),
    "miR34a HG", "",
    "miR34a mature", "",
    "Other asRNA", rep("", 11),
    "Other primers", rep("", 13)
)

colnames(primers) <- c("Name", "Sequence", "Figure", "Primer type")
rownames(primers) <- 1:nrow(primers)
primers <- primers[,c("Primer type", "Name", "Sequence", "Figure")]
```

```{r, results='asis', echo=FALSE}
panderOptions('table.split.table', Inf)
pandoc.table(primers, keep.line.breaks = TRUE)
```

### 2017-10-26 inst/transcriptStability/transcriptStability.Rmd
first commit

---
title: "miR34a asRNA transcript stability"
author: "Jason T. Serviss"
date: "02/02/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We desired to deduce the relative stability of the miR34a asRNA and HG transcripts.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with U2OS cells grown in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were treated with 10nM actinomycin D (Sigma) for the indicated times. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers
```

#Results

```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/transcriptStability/QPCRdata.txt', header=TRUE, sep="\t")

goi <- subset(data, gene %in% c("miR34a asRNA", "miR34a HG"))
hk <- subset(data, gene == "B-actin")

colnames(goi)[c(4:5)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(4:5)] <- c("Ct1HK", "Ct2HK")

data <- merge(goi, hk[,!colnames(hk) %in% "gene"], by=c("experiment", "treatment"))

#ddct
data$meanGOI <- rowMeans(data[,c("Ct1GOI", "Ct2GOI")])
data$meanHK <- rowMeans(data[,c("Ct1HK", "Ct2HK")])
data$dct <- data$meanGOI - data$meanHK
ddct <- ddply(
    data,
    c("gene", "treatment", "experiment"),
    summarize,
    ddct=dct-data[data$gene == gene & data$experiment == experiment & data$treatment == 0, "dct"]
)

data <- merge(data, ddct, by=c("gene", "treatment", "experiment"))
data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data, 
    c("gene", "treatment"),
    summarize,
    mean=mean(log2fold),
    sd=sd(log2fold)
)

data <- merge(data, stats, by=c("gene", "treatment"))

#prepare for plotting
data$treatment <- factor(data$treatment, levels=c("0", "1", "2", "4"))
data$gene <- factor(data$gene, levels=c("miR34a asRNA", "miR34a HG"))
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data, aes(x=treatment, y=log2fold))+
    geom_point( 
        aes(colour=gene),
        fill="white",
        size=4,
        alpha=0.6,
        position=position_dodge(width=0.9)
    )+
    geom_linerange(
        aes(ymin=mean-sd, ymax=mean+sd, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    scale_y_continuous(
        "\u0394\u0394Ct",
        #breaks=c(-1,0,1,2,3,4,5),
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(2^-4,2^-3,2^-2,2^-1,2^0)
        )
    )+
    labs(
      x="Treatment (hours)",
      title="miR34a asRNA and HG stability",
      caption=
            "Q-PCR showing miR34a asRNA and miR34a HG levels in U2OS cells after treatment with 10nM actinomycin D.\nError bars (black vertical) indicate standard deviation and means are represented by black dots."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(color = guide_legend(title = "Gene", override.aes = list(size=3)))

#plot for pdf
p <- ggplot(data, aes(x=treatment, y=log2fold))+
    geom_point( 
        aes(colour=gene),
        stroke=0,
        size=2,
        alpha=0.6,
        position=position_dodge(width=0.9)
    )+
    geom_linerange(
        aes(ymin=mean-sd, ymax=mean+sd, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        lwd=0.2
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        stroke=0.75,
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        size=0
    )+
    scale_y_continuous(
        "\u0394\u0394Ct",
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(2^-4,2^-3,2^-2,2^-1,2^0)
        #)
    )+
    labs(
      x="Treatment (hours)"
      #title="miR34a asRNA and HG stability"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(color = guide_legend(title = "Gene", override.aes = list(size=2)))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/transcriptStability/transcriptStability.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

#Conclusions
We observed increases in miR34a HG and asRNA expression upon doxorubicin treatment indicating that these two transcripts are co-regulated.

### 2017-10-26 R/downloadTCGA.R

@@ -1,0 +1,242 @@
+#' downloadTCGA
+#'
+#' @name downloadTCGA
+#' @rdname downloadTCGA
+#' @aliases downloadTCGA
+#' @param save logical. Should the data be saved locally.
+#' @param path character. A path indicating where the data should be saved if
+#'    \code{save} is TRUE.
+#' @param type character. Can be \code{gene expression} or \code{clinical}.
+#' @param ... additional arguments to pass on
+#' @return data.frame.
+#' @author Jason T. Serviss
+#' @keywords downloadTCGA
+#'
+NULL
+
+#' @rdname downloadTCGA
+#' @export
+
+
+###THE CLINICAL OPTION HERE IS NOT FINISHED!!!!
+setGeneric("downloadTCGA", function(
+    save,
+    path,
+    type,
+    ...
+){
+    standardGeneric("downloadTCGA")
+})
+
+#' @rdname downloadTCGA
+#' @export
+#' @importFrom XML xmlParse xmlToList
+
+setMethod("downloadTCGA", c("logical"), function(
+    save = FALSE,
+    path = NULL,
+    type = "gene expression"
+    ...
+){
+    #setup paths
+    tmp <- .setupPaths()
+    pkgPath <- tmp[[1]]
+    outPath <- tmp[[2]]
+    mutPath <- tmp[[3]]
+    wtPath <- tmp[[4]]
+    
+    #download data
+    if(type == "gene expression") {
+        file1 <- "p53mut.txt"
+        file2 <- "p53wt.txt"
+    } else {
+        file1 <- "p53mutClinical.txt"
+        file2 <- "p53wtClinical.txt"
+    }
+    
+    .downloadData(file1, mutPath)
+    .downloadData(file2, wtPath)
+
+    #move all files out of subdirectories
+    .moveFromSubDir(mutPath)
+    .moveFromSubDir(wtPath)
+    
+    #unzip
+    .unzip(mutPath)
+    .unzip(wtPath)
+    
+    #read and concatenate
+    if(type == "gene expression") {
+        mut <- .readAndConcat(mutPath)
+        wt <- .readAndConcat(wtPath)
+        output <- list(mut, wt)
+        names(output) <- c("mutated", "wt")
+    } else {
+        output <- .processClinical(mutPath)
+    }
+    
+    
+    
+    
+    if(save) {
+        if(type == "gene expression") {
+            save(
+                output,
+                file = paste(path, "tcgaGeneExpression.rda", sep = ""),
[…]

### 2017-10-26 data-raw/saveRDA.R
working on vignette, now downloading all raw data from git

@@ -1,0 +1,6 @@
+#HCTp53null
+data <- read.table('./data-raw/HCTp53null.txt', sep = "\t", header = TRUE)
+save(data, file = './data/HCT116null.rda', compress = "bzip2")
+
+
+#source('./data-raw/saveRDA.R')

### 2017-10-26 data-raw/saveRDA.R
further work on vignette, fixing HCT116null.rda

@@ -1,5 +1,6 @@
 #HCTp53null
 data <- read.table('./data-raw/HCTp53null.txt', sep = "\t", header = TRUE)
+colnames(data)[which(colnames(data) == "Target")] <- "Gene"
 save(data, file = './data/HCT116null.rda', compress = "bzip2")
 
 

### 2017-10-26 data-raw/saveRDA.R
adding data files for all regular figures

@@ -3,5 +3,34 @@ data <- read.table('./data-raw/HCTp53null.txt', sep = "\t", header = TRUE)
 colnames(data)[which(colnames(data) == "Target")] <- "Gene"
 save(data, file = './data/HCT116null.rda', compress = "bzip2")
 
+#HctHekDox
+data <- read.table('./data-raw/HctHekDox.txt', sep = "\t", header = TRUE)
+save(data, file = './data/HctHekDox.rda', compress = "bzip2")
+
+#P1-HCTandHEK
+data <- read.table('./data-raw/P1-HCTandHEK.txt', sep = "\t", header = TRUE)
+save(data, file = './data/P1-HCTandHEK.rda', compress = "bzip2")
+
+#p1shRNAdox
+data <- read.table('./data-raw/p1shRNAdox.txt', sep = "\t", header = TRUE)
+save(data, file = './data/p1shRNAdox.rda', compress = "bzip2")
+
+#stableLineExpression
+data <- read.table('./data-raw/stableLineExpression.txt', sep = "\t", header = TRUE)
+save(data, file = './data/stableLineExpression.rda', compress = "bzip2")
+
+#stableLineCellCycle
+data <- read.table('./data-raw/stableLineCellCycle.txt', sep = "\t", header = TRUE)
+save(data, file = './data/stableLineCellCycle.rda', compress = "bzip2")
+
+#growthStarvation
+data <- read.table('./data-raw/growthStarvation.txt', sep = "\t", header = TRUE)
+save(data, file = './data/growthStarvation.rda', compress = "bzip2")
+
+#stableLinePolIIChIP
+data <- read.table('./data-raw/stableLinePolIIChIP.txt', sep = "\t", header = TRUE)
+save(data, file = './data/stableLinePolIIChIP.rda', compress = "bzip2")
+
+
 
 #source('./data-raw/saveRDA.R')

### 2017-10-26 data-raw/saveRDA.R
rewrote all the data-raw code to use tidyverse

@@ -1,36 +1,37 @@
+library(tidyverse)
+
 #HCTp53null
-data <- read.table('./data-raw/HCTp53null.txt', sep = "\t", header = TRUE)
-colnames(data)[which(colnames(data) == "Target")] <- "Gene"
-save(data, file = './data/HCT116null.rda', compress = "bzip2")
+read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
+    rename(gene = Target) %>%
+    write_rds(., path = './data/HCT116p53null.rds', compress = "bz2")
 
 #HctHekDox
-data <- read.table('./data-raw/HctHekDox.txt', sep = "\t", header = TRUE)
-save(data, file = './data/HctHekDox.rda', compress = "bzip2")
+read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
+    write_rds(., path = './data/HctHekDox.rds', compress = "bz2")
 
 #P1-HCTandHEK
-data <- read.table('./data-raw/P1-HCTandHEK.txt', sep = "\t", header = TRUE)
-save(data, file = './data/P1-HCTandHEK.rda', compress = "bzip2")
+read_tsv('./data-raw/P1-HCTandHEK.txt', col_names = TRUE) %>%
+    write_rds(., path = './data/P1-HCTandHEK.rds', compress = "bz2")
 
 #p1shRNAdox
-data <- read.table('./data-raw/p1shRNAdox.txt', sep = "\t", header = TRUE)
-save(data, file = './data/p1shRNAdox.rda', compress = "bzip2")
+read_tsv('./data-raw/p1shRNAdox.txt', col_names = TRUE) %>%
+    write_rds(., path = './data/p1shRNAdox.rds', compress = "bz2")
 
 #stableLineExpression
-data <- read.table('./data-raw/stableLineExpression.txt', sep = "\t", header = TRUE)
-save(data, file = './data/stableLineExpression.rda', compress = "bzip2")
+read_tsv('./data-raw/stableLineExpression.txt', col_names = TRUE) %>%
+    rename(gene = Gene) %>%
+    write_rds(., path = './data/stableLineExpression.rds', compress = "bz2")
 
 #stableLineCellCycle
-data <- read.table('./data-raw/stableLineCellCycle.txt', sep = "\t", header = TRUE)
-save(data, file = './data/stableLineCellCycle.rda', compress = "bzip2")
[…]

### 2017-10-27 R/QpcrFuns.R
work on vignette and QpcrFuns

@@ -12,7 +12,81 @@ dct <- function(data) {
     mutate(dct = meanGOI - meanHK)
 }
 
-ddct <- function(data, ) {
-    group_by(Treatment, Biological.replicate, Technical.replicate, Time, cellLine) %>%
-    mutate(normConfluency = Confluency / pull(data, Confluency)[data$Treatment == Treatment & data$Biological.replicate == Biological.replicate & data$Technical.replicate == Technical.replicate & data$Time == 0 & data$cellLine == cellLine])
+#grouping variable should not include cnt.group
+ddct <- function(data, cnt.group, cnt.value, grouping) {
+    quo.cnt.group <- enquo(cnt.group)
+    cnt <- dplyr::filter(data, (!!quo.cnt.group) == cnt.value) %>%
+    select(grouping, dct)
+    
+    data %>%
+    left_join(cnt, by = grouping) %>%
+    mutate(ddct = dct.x - dct.y) %>%
+    select(-dct.y) %>%
+    rename(dct = dct.x)
 }
+
+folds <- function(data) {
+    data %>%
+    mutate(
+        fold = 2^-.data$ddct,
+        log2fold = log2(2^-.data$ddct)
+    )
+}
+
+calcStats <- function(data, cnt.group, cnt.value, grouping) {
+    quo.cnt.group <- enquo(cnt.group)
+    cnt <- dplyr::filter(data, (!!quo.cnt.group) == cnt.value) %>%
+    select(grouping, log2fold, cnt.group)
+    
+    
+    data %>%
+    select(grouping, log2fold, cnt.group) %>%
+    left_join(cnt, by = grouping) %>%
+    group_by_at(grouping[grouping != "Biological Replicate"]) %>%
+    summarize(
+        n = n(),
+        mean = mean(.data$log2fold.x),
+        CI95l = t.test(.data$log2fold.x)$conf.int[1],
+        CI95h = t.test(.data$log2fold.x)$conf.int[2],
+        pValue = t.test(.data$log2fold.x, .data$log2fold.y)$p.value
+    )
+}
+
+t.test(subset(data, gene == "miR34a AS" & Treatment == 100 & Condition == "WT", select = "log2fold")[[1]], subset(data, gene == "miR34a AS" & Treatment == 100 & Condition == "p53 null", select = "log2fold")[[1]])
+
+
+library(tidyverse)
+
+
+
[…]

### 2017-10-29 R/QpcrFuns.R
done preprocessing of HctHekDox.rda

@@ -1,4 +1,4 @@
-
+#' @export
 technicalMeans <- function(data) {
     data %>%
     mutate(
@@ -7,12 +7,14 @@ technicalMeans <- function(data) {
     )
 }
 
+#' @export
 dct <- function(data) {
     data %>%
     mutate(dct = meanGOI - meanHK)
 }
 
 #grouping variable should not include cnt.group
+#' @export
 ddct <- function(data, cnt.group, cnt.value, grouping) {
     quo.cnt.group <- enquo(cnt.group)
     cnt <- filter(data, (!!quo.cnt.group) == cnt.value) %>%
@@ -25,6 +27,7 @@ ddct <- function(data, cnt.group, cnt.value, grouping) {
     rename(dct = dct.x)
 }
 
+#' @export
 folds <- function(data) {
     data %>%
     mutate(
@@ -33,6 +36,7 @@ folds <- function(data) {
     )
 }
 
+#' @export
 calcStats <- function(data, cnt.group, cnt.value, grouping) {
     quo.cnt.group <- enquo(cnt.group)
     cnt <- filter(data, (!!quo.cnt.group) == cnt.value) %>%
@@ -51,7 +55,7 @@ calcStats <- function(data, cnt.group, cnt.value, grouping) {
         CI95h = t.test(.data$log2fold.x)$conf.int[2],
         pValue = t.test(.data$log2fold.x, .data$log2fold.y)$p.value
     ) %>%
-    filter((!!quo.cnt.group) != cnt.value) %>%
+    mutate((!!quo.cnt.group) != cnt.value) %>%
     ungroup()
 }
 
@@ -80,10 +84,13 @@ calcStats <- function(data, cnt.group, cnt.value, grouping) {
 #testthat::expect_identical(expected1, output1)
 #sessionInfo()
 
+#' @export
 pFormat <- function(stats) {
     idx <- which(colnames(stats) == "pValue")
-    mutate(stats, pFormat = format(stats[[idx]], scientific = TRUE, digits = 2))
-    
+    mutate(stats, pFormat = case_when(
+        is.nan(pValue) | pValue == 1 ~ "",
+        TRUE ~ format(stats[[idx]], scientific = TRUE, digits = 2))
+    )
 }
 
 xAndxend <- function() {

### 2017-10-29 R/downloadTCGA.R

@@ -1,242 +1,0 @@
-#' downloadTCGA
-#'
-#' @name downloadTCGA
-#' @rdname downloadTCGA
-#' @aliases downloadTCGA
-#' @param save logical. Should the data be saved locally.
-#' @param path character. A path indicating where the data should be saved if
-#'    \code{save} is TRUE.
-#' @param type character. Can be \code{gene expression} or \code{clinical}.
-#' @param ... additional arguments to pass on
-#' @return data.frame.
-#' @author Jason T. Serviss
-#' @keywords downloadTCGA
-#'
-NULL
-
-#' @rdname downloadTCGA
-#' @export
-
-
-###THE CLINICAL OPTION HERE IS NOT FINISHED!!!!
-setGeneric("downloadTCGA", function(
-    save,
-    path,
-    type,
-    ...
-){
-    standardGeneric("downloadTCGA")
-})
-
-#' @rdname downloadTCGA
-#' @export
-#' @importFrom XML xmlParse xmlToList
-
-setMethod("downloadTCGA", c("logical"), function(
-    save = FALSE,
-    path = NULL,
-    type = "gene expression"
-    ...
-){
-    #setup paths
-    tmp <- .setupPaths()
-    pkgPath <- tmp[[1]]
-    outPath <- tmp[[2]]
-    mutPath <- tmp[[3]]
-    wtPath <- tmp[[4]]
-    
-    #download data
-    if(type == "gene expression") {
-        file1 <- "p53mut.txt"
-        file2 <- "p53wt.txt"
-    } else {
-        file1 <- "p53mutClinical.txt"
-        file2 <- "p53wtClinical.txt"
-    }
-    
-    .downloadData(file1, mutPath)
-    .downloadData(file2, wtPath)
-
-    #move all files out of subdirectories
-    .moveFromSubDir(mutPath)
-    .moveFromSubDir(wtPath)
-    
-    #unzip
-    .unzip(mutPath)
-    .unzip(wtPath)
-    
-    #read and concatenate
-    if(type == "gene expression") {
-        mut <- .readAndConcat(mutPath)
-        wt <- .readAndConcat(wtPath)
-        output <- list(mut, wt)
-        names(output) <- c("mutated", "wt")
-    } else {
-        output <- .processClinical(mutPath)
-    }
-    
-    
-    
-    
-    if(save) {
-        if(type == "gene expression") {
-            save(
-                output,
-                file = paste(path, "tcgaGeneExpression.rda", sep = ""),
[…]

### 2017-10-29 data-raw/saveRDA.R

@@ -25,6 +25,12 @@ read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
 
 #HctHekDox
 read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
+    rename(
+        `Biological Replicate` = experiment,
+        `Cell line` = cellLine,
+        Treatment = treatment
+    ) %>%
+    mutate(Treatment = parse_factor(Treatment, levels = c("untreated", "doxorubicin"))) %>%
     save(., file = './data/HctHekDox.rda', compress = "bzip2")
 
 #P1-HCTandHEK

### 2017-10-30 R/QpcrFuns.R
more work on vignette

@@ -1,29 +1,24 @@
 #' @export
-reformatForDct <- function(data, gois, hk, grouping) {
-    goi <- data %>%
-    filter(gene %in% gois) %>%
-    rename(Ct1GOI = Ct1, Ct2GOI = Ct2)
-    
-    hk <- data %>%
-    filter(gene == hkGene) %>%
-    rename(Ct1HK = Ct1, Ct2HK = Ct2)
-    
-    full_join(goi, select(hk, -gene), by = grouping[grouping != "gene"])
+technicalMeans <- function(data, grouping) {
+    data %>%
+    gather(`Tech. Replicate`, Ct, -grouping) %>%
+    group_by(!!! rlang::syms(grouping)) %>%
+    summarize(ctMean = mean(Ct)) %>%
+    ungroup()
 }
 
 #' @export
-technicalMeans <- function(data) {
+dct <- function(data, GOIs, HK, grouping) {
+    quo.hk <- enquo(HK)
+    grouping <- grouping[grouping != "gene"]
+    
     data %>%
-    mutate(
-        meanGOI = rowMeans(select(., Ct1GOI, Ct2GOI)),
-        meanHK = rowMeans(select(., Ct1HK, Ct2HK))
-    )
-}
-
-#' @export
-dct <- function(data) {
-    data %>%
-    mutate(dct = meanGOI - meanHK)
+    spread(gene, ctMean) %>%
+    mutate(HK = quo_name(quo.hk)) %>%
+    rename(ctMeanHK = !!quo.hk) %>%
+    gather(GOI, ctMeanGOI, -one_of(names(.)[!names(.) %in% gois]), factor_key = TRUE) %>%
+    mutate(dct = ctMeanGOI - ctMeanHK) %>%
+    select(grouping, HK, ctMeanHK, GOI, ctMeanGOI, dct)
 }
 
 #' @export
@@ -53,6 +48,24 @@ ddct <- function(data, logical, grouping) {
     rename(dct = dct.x)
 }
 
+test <- function(data, logical, grouping) {
+    logical.grps <- rlang::syms(c(colnames(logical), "dct"))
+    tmp <- c("untreated_1_HCT116", "untreated_1_HEK293t")
+    
+    data %>%
+    select(grouping, dct) %>%
+    unite(variables, grouping) %>%
+    group_by(variables) %>%
+    mutate(id=1:n()) %>%
+    spread(variables, dct) %>%
+    select(-id) %>%
[…]

### 2017-10-30 data-raw/saveRDA.R

@@ -39,6 +39,18 @@ read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
 
 #P1-HCTandHEK
 read_tsv('./data-raw/P1-HCTandHEK.txt', col_names = TRUE) %>%
+    rename(
+        `Biological Replicate` = experiment,
+        `Cell line` = cellLine
+    ) %>%
+    mutate(
+        gene = case_when(
+            gene == "renilla"    ~ "Renilla",
+            gene == "luciferase" ~ "Luciferase",
+            TRUE                 ~ "error in saveRNA.R"
+        ),
+        construct = gsub("empty", "Empty", .data$construct)
+    ) %>%
     save(., file = './data/P1-HCTandHEK.rda', compress = "bzip2")
 
 #p1shRNAdox

### 2017-10-30 R/QpcrFuns.R
more work on vignette, figure 2 done

@@ -129,7 +129,3 @@ pFormat <- function(stats) {
         TRUE ~ format(stats[[idx]], scientific = TRUE, digits = 2))
     )
 }
-
-xAndxend <- function() {
-    
-}

### 2017-10-31 data-raw/saveRDA.R
preprocessing done for growthStarvation.rda

@@ -101,7 +101,15 @@ read_tsv('./data-raw/stableLineCellCycle.txt', col_names = TRUE) %>%
     save(., file = './data/stableLineCellCycle.rda', compress = "bzip2")
 
 #growthStarvation
-read_tsv('./data-raw/growthStarvation.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/growthStarvation.txt', col_names = TRUE)  %>%
+    filter(Time <= 35) %>%
+    mutate(Time = parse_factor(Time, levels = as.character(0:max(Time)))) %>%
+    mutate(Treatment = parse_factor(Treatment, levels = c("RPMI", "HBSS"))) %>%
+    mutate(`Cell line` = paste(`Cell line`, Condition, sep = " ")) %>%
+    mutate(`Cell line` = gsub("PC3 F4", "PC3 miR34a asRNA", `Cell line`)) %>%
+    select(-Condition) %>%
+    mutate(`Cell line` = parse_factor(`Cell line`, levels = c("PC3 Mock", "PC3 miR34a asRNA"))) %>%
+    rename(`Biological Replicate` = Biological.replicate, `Technical Replicate` = Technical.replicate) %>%
     save(., file = './data/growthStarvation.rda', compress = "bzip2")
 
 #stableLinePolIIChIP

### 2017-10-31 inst/growthStarvation/growthStarvation.Rmd
spelling mistake fixed in commited file

@@
 #Introduction
-As p53 is a well-known regulator of senescence and apoptosis and has been shown to specifically importatnt under conditions of cellular stress, such as starvation.
+As p53 is a well-known regulator of senescence, growth, and apoptosis and has been shown to specifically important under conditions of cellular stress, such as starvation.
 Therefore, we investigated whether overexpression of miR34a AS affects growth rate under normal and starvation conditions by measuring changes in confluency over time.

### 2017-10-31 R/QpcrFuns.R
done all main figures prelim, need to look through and make homog

@@ -48,24 +48,6 @@ ddct <- function(data, logical, grouping) {
     rename(dct = dct.x)
 }
 
-test <- function(data, logical, grouping) {
-    logical.grps <- rlang::syms(c(colnames(logical), "dct"))
-    tmp <- c("untreated_1_HCT116", "untreated_1_HEK293t")
-    
-    data %>%
-    select(grouping, dct) %>%
-    unite(variables, grouping) %>%
-    group_by(variables) %>%
-    mutate(id=1:n()) %>%
-    spread(variables, dct) %>%
-    select(-id) %>%
-    gather(variables, value, -one_of(tmp)) %>%
-    separate(variables, grouping, sep = "_")
-    
-    
-    reshape2::dcast(dct ~ variables)
-}
-
 #' @export
 folds <- function(data) {
     data %>%

### 2017-11-01 R/QpcrFuns.R
updated QPCR analysis to Elins method

@@ -10,15 +10,18 @@ technicalMeans <- function(data, grouping) {
 #' @export
 dct <- function(data, GOIs, HK, grouping) {
     quo.hk <- enquo(HK)
-    grouping <- grouping[grouping != "gene"]
+    grouping1 <- grouping[grouping != "gene"]
+    grouping2 <- grouping1[grouping1 != "Biological Replicate"]
     
     data %>%
     spread(gene, ctMean) %>%
     mutate(HK = quo_name(quo.hk)) %>%
     rename(ctMeanHK = !!quo.hk) %>%
     gather(GOI, ctMeanGOI, -one_of(names(.)[!names(.) %in% GOIs]), factor_key = TRUE) %>%
-    mutate(dct = ctMeanGOI - ctMeanHK) %>%
-    select(grouping, HK, ctMeanHK, GOI, ctMeanGOI, dct)
+    group_by(!!!rlang::syms(grouping2)) %>%
+    mutate(dct = ctMeanGOI - mean(ctMeanHK)) %>%
+    ungroup() %>%
+    select(grouping1, HK, ctMeanHK, GOI, ctMeanGOI, dct)
 }
 
 #' @export
@@ -35,6 +38,7 @@ dct <- function(data, GOIs, HK, grouping) {
 #}
 
 ddct <- function(data, logical, grouping) {
+    grouping1 <- grouping[grouping != "Biological Replicate"]
     logical.grps <- colnames(logical)
     logical <- ifelse(rowSums(logical) == ncol(logical), TRUE, FALSE)
     
@@ -43,7 +47,8 @@ ddct <- function(data, logical, grouping) {
     
     data %>%
     left_join(cnt, by = grouping[!grouping %in% logical.grps]) %>%
-    mutate(ddct = dct.x - dct.y) %>%
+    group_by(!!!rlang::syms(grouping1)) %>%
+    mutate(ddct = dct.x - mean(dct.y)) %>%
     select(-dct.y) %>%
     rename(dct = dct.x)
 }

### 2017-11-03 R/QpcrFuns.R
added med arg to ddct

@@ -1,5 +1,8 @@
 #' @export
-technicalMeans <- function(data, grouping) {
+technicalMeans <- function(
+    data,
+    grouping
+){
     data %>%
     gather(`Tech. Replicate`, Ct, -grouping) %>%
     group_by(!!! rlang::syms(grouping)) %>%
@@ -8,7 +11,12 @@ technicalMeans <- function(data, grouping) {
 }
 
 #' @export
-dct <- function(data, GOIs, HK, grouping) {
+dct <- function(
+    data,
+    GOIs,
+    HK,
+    grouping
+){
     quo.hk <- enquo(HK)
     grouping1 <- grouping[grouping != "gene"]
     grouping2 <- c(grouping1[grouping1 != "Biological Replicate"], "GOI")
@@ -17,14 +25,25 @@ dct <- function(data, GOIs, HK, grouping) {
     spread(gene, ctMean) %>%
     mutate(HK = quo_name(quo.hk)) %>%
     rename(ctMeanHK = !!quo.hk) %>%
-    gather(GOI, ctMeanGOI, -one_of(names(.)[!names(.) %in% GOIs]), factor_key = TRUE) %>%
+    gather(
+        GOI,
+        ctMeanGOI,
+        -one_of(names(.)[!names(.) %in% GOIs]),
+        factor_key = TRUE
+    ) %>%
     group_by(!!!rlang::syms(grouping2)) %>%
     mutate(dct = ctMeanGOI - median(ctMeanHK)) %>%
     ungroup() %>%
     select(grouping1, HK, ctMeanHK, GOI, ctMeanGOI, dct)
 }
 
-ddct <- function(data, logical, grouping) {
+#' @export
+ddct <- function(
+    data,
+    logical,
+    grouping,
+    med = TRUE
+){
     grouping1 <- grouping[grouping != "Biological Replicate"]
     logical.grps <- colnames(logical)
     
@@ -40,14 +59,16 @@ ddct <- function(data, logical, grouping) {
     data %>%
     left_join(cnt, by = grouping[!grouping %in% logical.grps]) %>%
     group_by(!!!rlang::syms(grouping1)) %>%
-    mutate(ddct = dct.x - dct.y) %>%
+    mutate(ddct = dct.x - case_when(med ~ median(dct.y), TRUE ~ dct.y)) %>%
     ungroup() %>%
     select(-dct.y) %>%
     rename(dct = dct.x)
 }
 
 #' @export
-folds <- function(data) {
+folds <- function(
+    data
+){
[…]

### 2017-11-06 R/QpcrFuns.R
added med arg to dct

@@ -15,7 +15,8 @@ dct <- function(
     data,
     GOIs,
     HK,
-    grouping
+    grouping,
+    med = TRUE
 ){
     quo.hk <- enquo(HK)
     grouping1 <- grouping[grouping != "gene"]
@@ -32,7 +33,10 @@ dct <- function(
         factor_key = TRUE
     ) %>%
     group_by(!!!rlang::syms(grouping2)) %>%
-    mutate(dct = ctMeanGOI - median(ctMeanHK)) %>%
+    mutate(dct = ctMeanGOI - case_when(
+        med ~ median(ctMeanHK),
+        TRUE ~ ctMeanHK
+    )) %>%
     ungroup() %>%
     select(grouping1, HK, ctMeanHK, GOI, ctMeanGOI, dct)
 }

### 2017-11-06 data-raw/saveRDA.R
fixing naming in saveRNA.R

@@ -156,13 +156,13 @@ read_tsv('./data-raw/stableLineExpressionHEK.txt', col_names = TRUE) %>%
         gene = Gene
     ) %>%
     mutate(
-        Condition = gsub("F4", "miR34a asRNA", Condition),
+        Condition = gsub("F4", "miR34a\nasRNA", Condition),
         gene = gsub("B-actin", "Actin", gene),
         gene = gsub("miR34a asRNA F1R1", "miR34a asRNA", gene)
     ) %>%
     mutate(
         `Cell line` = parse_factor(`Cell line`, levels = c("HEK293t", "PC3", "Skov3", "Saos2")),
-        Condition = parse_factor(Condition, levels = c("wt", "mock", "miR34a asRNA"))
+        Condition = parse_factor(Condition, levels = c("wt", "mock", "miR34a\nasRNA"))
     ) %>%
     save(., file = './data/stableLineExpressionHEK.rda', compress = "bzip2")
 

### 2017-11-07 inst/P1-HCTandHEK/figure2d.Rmd
added plotFigure and helpers

---
title: "P1 and P2 transfections in HCT116 and HEK293t cells"
author: "Jason T. Serviss"
date: "30/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
It is likely, due to the head-to head orientation of miR34a HG and asRNA, that transcription initiation may be activated from a single promoter in a bi-directional manner. To investigate whether miR34a HG and asRNA are transcribed from the same promoter as convergent transcripts, we cloned the miR34a HG promoter, including the p53 binding site, into a luciferase/renilla dual reporter vector which we hereafter refer to as p1. The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis. Mol Cell, 2007. 26(5): p. 731-43. Due to the observance of additional conservation sites downstream of the previously published miR34a HG promoter, we also cloned a longer "promoter region", extending 251 additional base pairs into the miR34a HG into the same bi-directional reporter vector, hereafter refered to as p2.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 10,000 cells per well in a 96-well plate with a white bottom and cultured overnight. The following day cells were co-transfected with 10ng of empty, p1, or p2 plasmid and GFP using the standard lipofektamine 2000 (Life Technologies) protocol. The expression of GFP and luminescence was measured 24 h post transfection by using the Dual-Glo Luciferase Assay System (Promega) and detected by the GloMax-Multi+ Detection System (Promega). The expression of luminescence was normalized to GFP.

##Constructs
```{r}
library(printr)
ps <- data.frame(
    name=c("p1", "p2"),
    sequence=c("GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
              CCT GCT C",
              "GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT 
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA 
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA 
              CCT GCT CGC CCC GTC CCA GCA TGC ACC CAG GTA AAC GCT TGT GTT TCT CAG TCC GTG CGA 
              AAG TTT GCA AAG AAG GAG GCG GGA ACT AGA CCA ACA ACT TTA ATA ATC ATA GTC ATA ATA 
              ATG AAA ACC CTG TTC AAT TGT GTA GCC TCC GTA AGG GGA AGA ATT TCC AAG AAG CAA CAA
              AAT GTT CTT TGA TTT CAT AAT CTC TGG GGA GAA AGG ATT CCT TTT TTG GGG TTT TGC TCG
              GCT AGT TCT TTC TTC CCT")
)
ps
```

##Primers
```{r}
primers <- data.frame(
    name=c(
        "Luc_set_II_F",
        "Luc_set_II_R",
        "Renilla_pBiDir_F1",
        "Renilla_pBiDir_R1",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers
```

#Results

<center>![miR34a locus and cloning of P1 and P2 constructs.](locus.png)</center>
<br></br><br></br>
<center>![P1 and P2 constructs.](constructs.png)</center>
<br></br><br></br><br></br>

```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/P1-HCTandHEK/luminesenseData.txt', header=TRUE, sep="\t")

summary <- ddply(
    data, 
    c("cellLine", "gene", "construct"),
    summarize,
    mean = mean(value),
    pValue = t.test(value, data[data$cellLine == cellLine & data$gene == gene & data$construct == "empty", "value"])$p.value,
    CI95l = t.test(value)$conf.int[1],
    CI95h = t.test(value)$conf.int[2]
)

data <- merge(data, summary, by=c("cellLine", "gene", "construct"))

data$pValue <- ifelse(data$pValue == 1, NA, data$pValue)

data$pStars <- ifelse(
    data$pValue < 0.05 & data$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        data$pValue < 0.005 & data$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            data$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

#prepare for plotting
data$gene <- ifelse(data$gene == "renilla", "Renilla", "Luciferase")
data$construct <-gsub("empty", "Empty", data$construct)
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data, aes(x=construct, y=value))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        show.legend = FALSE
    )+
    geom_point( 
        aes(colour=gene),
        size=4,
        position=position_dodge(width=0.9),
        stroke=0
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    facet_grid(.~cellLine)+
    geom_label(
        aes(y=CI95h+0.15, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=5,
        family="Arial Unicode MS",
        position=position_dodge(width=0.9)
    )+
    labs(
        x="Construct",
        y="Activity (a.u.)",
        title="miR34a asRNA regulation by miR34a promoter",
        caption=
            "miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 and P2 constructs.\nLuciferase represents miR34a HG and renilla represents miR34a asRNA.\nError bars (black vertical) indicate 95% CI and means are represented \nby black dots. \u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(color = guide_legend(title = "Gene", override.aes = list(size=3)))

#plot for pdf
p <- ggplot(data, aes(x=construct, y=value))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=gene),
    #    size=0.6,
    #    position=position_dodge(width=0.9)
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        lwd=0.15
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        size=0.5
    )+
    facet_grid(.~cellLine)+
    geom_label(
        aes(y=CI95h+1200, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS",
        position=position_dodge(width=0.9)
    )+
    labs(
        x="Construct",
        y="Activity (a.u.)",
        title="miR34a asRNA promoter region"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(fill = guide_legend(title = "Gene", override.aes = list(size=2)))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/P1-HCTandHEK/P1-HCTandHEK_P1andP2.pdf", device=cairo_pdf, height=60, width=83, units="mm")

#only P1
data <- subset(data, construct %in% c("Empty", "p1"))
p1 <- ggplot(data, aes(x=construct, y=value))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=gene),
    #    size=0.6,
    #    position=position_dodge(width=0.9)
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        lwd=0.15
    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        size=0.5,
    )+
    facet_grid(.~cellLine)+
    geom_label(
        aes(y=CI95h+1200, label=pStars, group=gene),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS",
        position=position_dodge(width=0.9)
    )+
    labs(
        x="Construct",
        y="Activity (a.u.)"
        #title="miR34a asRNA promoter region"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(fill = guide_legend(title = "Gene", override.aes = list(size=2)))

ggsave(plot=p1, filename="~/GitHub/miR34aFigures/inst/P1-HCTandHEK/P1-HCTandHEK_P1.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

#Conclusion
Upon transfection of this construct in two separate cell lines we observed increases in both luciferase and renilla indicating that miR34a HG and asRNA expression is regulated by a single promoter contained within the p1 construct. Transfection of the P2 construct showed to cause a reduction in luciferase (miR34a HG) levels but not renilla (miR34a AS) levels. This could be due to the presence of a STAT3 binding site in p2 which has been previously reported to negativley regulate miR34a HG.

### 2017-11-07 inst/StableLineExpression/figure3a.Rmd
added plotFigure and helpers

---
title: "miR34a asRNA stable over-expression cell lines"
author: "Jason T. Serviss"
date: "04/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a. To this end, we stably over-expressed miR34a asRNA, using lentiviral transduction, in 3 different p53-null cell lines and monitored the effects on miR34a.

#Methods

##miR34a asRNA cloning
RNA was harvested from U2OS cells using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was run using the miR34aAS_cloning_F4 and miR34aAS_cloning_Ex3_1 primers for 40 cycles at annealing temperature 58˚C and run on an agarose gel. Bands were excised and extracted using the QIAquick gel extraction kit (Qiagen). PCR products were cloned using the Strata Clone kit (Aligent) and sequenced (results below). The insert for the lentiviral construct (p-HIV-I2AG-U6) was subsequently sub-cloned from the sequenced plasmid using primers with PacI and NheI cleavage sites. The cloned transcript largley mirrors the GENCODE annotated transcript.

###Cloning primers
```{r}
library(printr)
primers <- data.frame(
    name=c(
        "miR34aAS_cloning_F4",
        "miR34aAS_cloning_Ex3_1"
    ),
    sequence=c(
        "ACGCGTCTCTCCAGCCCGGGAT",
        "AATGATGGCCGCAACTAATGACGG"
    )
)
primers
```

###Sequencing results
```{r}
construct <- data.frame(
    name="miR34a_asRNA",
    sequence="ACG CGT CTC TCC AGC CCG GGA TCC GGG GAG CTG GGC TGT CCC CAG ACC GAC GGG ACA GCG GCA
                TCT CCT CCA CCT GAA AAG GAA AGA GGA CCA GTT TGC AGG ACT CCG AAC TGG GCC CGC GAG ATC 
                TCC ACC TGC GCA AAA CGA AAG GGC GGA TTC TCC TTG GAC TCA CGA GGC AAC CGC TCC CCG GGG 
                TGA GAA CGG GGG ACT CAT TCC TCC GGC ACT GGG AGA AGA CGA TTC TTC AGG AGG AGG ACA GGG 
                AAG CGA ATG CTA CCC AGA TGT CTC AGT ATA CTG GCT CGC GGC ACA TCG GGC AAA TGA ACC TAT 
                CAG ATA ACA ACG GCA GAT CAG ATG CCT GAG CAT TCA GAA GCA ACA GCT GTG GAG CCC CCG TGG 
                GTT CAG AAG GCC TGG TTC CCG TCT CCA GAA GCC TGG CTC TCC TCC CTC CTG GGC CCA CTA CTT 
                TGG CTT CTT GTT CCT ACG TAC AAG GAG TTG CGA AGA AGG CAA CTC TTC CCC TCC CTG AAG CCA
                AAG GAA TGA AAC AGA CTA GGG CGG GAG AGG TGG CCA TCC GTC ATT AGT TGC GGC CAT CA"
)
construct
```

```{r}
###Q-PCR primers
primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers
```

##Lentivirus production and infection
HEK293T cells were transfected with viral and expression constructs using Lipofectamine 2000 (Life Technologies), after which viral supernatants were harvested 48 and 72 hours post-transfection. Viral particles were concentrated using PEG-IT solution (Systems Biosciences) according to the manufacturer’s recommendations. HEK293T cells were used for virus titration and GFP expression was evaluated 72hrs post-infection via flow cytometry after which TU/ml was calculated. Cell lines were subsequently infected with the lentiviral particals using a multuplicity of infection = 1. After 48 hours, cells were placed under mycophenolic acid selection and the selection process was monitored using GFP expression via flow cytometry. When GFP expression was present in >90% of the cells, cells were frozen for downstream analysis.

##QPCR
RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.
QPCR for miRNA expression analysis was performed according to the protocol for the TaqMan microRNA Assay kit (Life Technologies) with primer/probe sets purchased from the same company (TaqMan® MicroRNA Assay, hsa-miR-34a, human and Control miRNA Assay, RNU48, human) and the same cycling scheme as above.

#Results

```{r, message=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
library(extrafont)
data <- read.table('~/GitHub/miR34aFigures/inst/StableLineExpression/QPCR.txt', header=TRUE, sep="\t")
data$Gene <- gsub("miR34a asRNA F1R1", "miR34a asRNA", data$Gene)
colnames(data)[3] <- "condition"

#extract AS experiment
asRNA <- data[data$Gene %in% c("miR34a asRNA", "miR34a"), ]
bact <- data[data$Gene %in% c("B-actin", "RNU48"), ]
colnames(asRNA)[c(5,6,7)] <- c("Ct1GOI", "Ct2GOI", "Ct3GOI")
colnames(bact)[c(5,6,7)] <- c("Ct1HK", "Ct2HK", "Ct3HK")
asRNA <- cbind(asRNA, bact[ ,c("Ct1HK", "Ct2HK", "Ct3HK")])

#remove Skov exp 1 due to variability in technical replicates
asRNA <- asRNA[asRNA$experiment != 1 | asRNA$cellLine != "Skov3", ]

asRNA$meanGOI <- rowMeans(asRNA[ ,c("Ct1GOI", "Ct2GOI", "Ct3GOI")], na.rm=TRUE)
asRNA$meanHK <- rowMeans(asRNA[ ,c("Ct1HK", "Ct2HK", "Ct3HK")], na.rm=TRUE)

#perform ddct
asRNA$dct <- asRNA$meanGOI - asRNA$meanHK
ddct <- ddply(
    asRNA, 
    c("experiment", "cellLine", "condition", "Gene"), 
    summarize, 
    ddct=dct-asRNA[asRNA$experiment == 2 & asRNA$cellLine == cellLine & asRNA$condition == "mock" & asRNA$Gene == Gene, "dct"]
)
asRNA <- merge(asRNA, ddct, by=c("experiment", "cellLine", "condition", "Gene"), all=TRUE)
asRNA$fold <- 2^-asRNA$ddct
asRNA$log2Fold <- log2(asRNA$fold)
asRNA$sample <- paste(asRNA$cellLine, asRNA$condition, sep=" ")

#run statistics
pValues <- ddply(
    asRNA, 
    c("sample", "Gene"), 
    summarize,
    meanLog2Fold = mean(log2Fold),
    pValue=t.test(log2Fold, mu=0)$p.value, 
    conf.intLow = t.test(log2Fold, mu=0)$conf.int[1],
    conf.intHigh = t.test(log2Fold, mu=0)$conf.int[2]
)
asRNA <- merge(asRNA, pValues, by=c("sample", "Gene"), all.x=TRUE)

#prepare for plotting
asRNA$cellLine <- factor(asRNA$cellLine, levels=c("PC3", "Skov3", "Saos2"))
asRNA$condition <- ifelse(asRNA$condition == "miR34a AS", "miR34a\nasRNA", "mock")
asRNA$condition <- factor(asRNA$condition, levels=c("mock", "miR34a\nasRNA"))
asRNA$Gene <- factor(asRNA$Gene, levels=c("miR34a asRNA", "miR34a"))
asRNA[grepl("mock", asRNA$condition), "pValue"] <- NaN
asRNA$sample <- gsub("([a-zA-Z]*[0-9]{1}) (.*)", "\\1\n\\2", asRNA$sample)
asRNA$sample <- factor(asRNA$sample, levels=c("PC3\nmock", "PC3\nmiR34a AS", "Skov3\nmock", "Skov3\nmiR34a AS", "Saos2\nmock", "Saos2\nmiR34a AS"))

asRNA$pStars <- ifelse(
    asRNA$pValue < 0.05 & asRNA$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        asRNA$pValue < 0.005 & asRNA$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            asRNA$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}

pBars <- data.frame(
    Gene=rep(unique(asRNA[grepl("miR34a AS", asRNA$sample), "Gene"]), 3),
    condition=unique(asRNA[grepl("miR34a AS", asRNA$sample), "condition"]),
    cellLine=unique(asRNA[grepl("miR34a AS", asRNA$sample), "cellLine"])
)
pBars <- pBars[order(pBars$cellLine, pBars$Gene), ]
pBars$x <- rep(c(0.775,1.225), 3)
pBars$xend <- rep(c(1.775,2.225), 3)

asRNA <- merge(asRNA, pBars, by=c("Gene", "condition", "cellLine"), all.x=TRUE)

#plot for rmarkdown
ggplot(asRNA, aes(x=condition, y=log2Fold))+
    geom_violin(
        aes(group=interaction(condition, Gene)),
        trim=TRUE,
        alpha=0.5,
        fill="grey",
        colour=NA,
        scale="width",
        show.legend = FALSE
    )+
    geom_point(
        aes(colour=Gene, group=interaction(condition, Gene)),
        size=2, 
        alpha=0.75,
        position=position_dodge(width=0.9)
    )+
    geom_linerange(
        aes(ymin=conf.intLow, ymax=conf.intHigh, group=interaction(condition, Gene)),
        position=position_dodge(width=0.9),
        colour="grey25",
        show.legend = FALSE
    )+
    geom_point(
        aes(y=meanLog2Fold, group=interaction(condition, Gene)),
        colour="black",
        size=1,
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_label(
        aes(y=conf.intHigh+0.5, label=pStars, fontface="bold", group=interaction(condition, Gene)),
        fill="white",
        label.size=0,
        label.padding=unit(0.01, "lines"),
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        family="Arial Unicode MS",
        size=3
    )+
    facet_grid(
        .~cellLine, 
        scales = "free", 
        space = "free"
    )+
    scale_y_continuous(
        "\u0394\u0394Ct", 
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(1,5,10,50,100,500,1000,5000,10000,50000)
        )
    )+
    labs(
        x="Cell line",
        title="miR34a asRNA over-expressing cell lines",
        caption=
            "miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control.\n\u0394\u0394ct = House keeping gene - Target gene - mock control. Error bars indicate 95% CI and black points represent the mean.\n\u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_colour_ptol()+
    theme(
        legend.position = "top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=12),
        strip.text.x = element_text(size=17)
    )

#plot for pdf
p <- ggplot(asRNA, aes(x=condition, y=log2Fold))+
    geom_violin(
        aes(fill=Gene, group=interaction(condition, Gene)),
        trim=TRUE,
        alpha=0.3,
        colour=NA,
        scale="width",
        lwd = 0.1
    )+
    #geom_point(
    #    aes(colour=Gene, group=interaction(condition, Gene)),
    #    size=0.4, 
    #    position=position_dodge(width=0.9)
    #)+
    geom_linerange(
        aes(ymin=conf.intLow, ymax=conf.intHigh, group=interaction(condition, Gene)),
        position=position_dodge(width=0.9),
        colour="black",
        show.legend = FALSE,
        lwd=0.2
    )+
    geom_point(
        aes(y=meanLog2Fold, group=interaction(condition, Gene)),
        colour="black",
        size=0.1,
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
    geom_label(
        aes(y=conf.intHigh+0.5, label=pStars, fontface="bold", group=interaction(condition, Gene)),
        fill="white",
        label.size=0,
        label.padding=unit(0.01, "lines"),
        position=position_dodge(width=0.9),
        show.legend = FALSE,
        size=1,
        family="Arial Unicode MS"
    )+
    facet_grid(
        .~cellLine, 
        scales = "free", 
        space = "free"
    )+
    scale_y_continuous(
        "\u0394\u0394Ct" 
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(1,10,100,1000,10000,50000)
        #)
    )+
    labs(
        x="Cell line"
        #title="miR34a asRNA over-expressing cell lines"
    )+
    theme_few()+
    scale_colour_ptol()+
    scale_fill_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position = "top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=7),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        #axis.line=element_line(size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm"),
        strip.text.x = element_text(size=8, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.15)
    )+ 
    guides(
        fill=guide_legend(
            override.aes = list(
                size=2
            )
        )
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLineExpression/StableLineExp.pdf", device=cairo_pdf, height=60, width=83, units="mm")
```

#Conclusion
miR34a asRNA over-expression causes a concominant up-regulation of miR34a in all 3 cell lines. This indicates that miR34a asRNA concordantly regulates miR34a.

### 2017-11-07 inst/StableLinePolIIChIP/figure3d.Rmd
added plotFigure and helpers

---
title: "PC3 stable line pollII ChIP"
author: "Jason T. Serviss"
date: "06/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
miR34a asRNA over-expression was shown to increase the expression levels of miR34a. We investigated if this increase of miR34a was due to increased levels of transcription at the miR34a promoter.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with Skov3 and PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine and Saos2 cells cultured in DMEM high modified (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 2-3x10^6 cells in a 15cm dish and incubated overnight. Cells were cross-linked in 1% formaldehyde, quenched in glycine (0.125M), resuspended in cell lysis buffer (5mM PIPES, 85mM KCL, 0.5% NP40, protease inhibitor), and sonicated (Bioruptor Sonicator Diagenode) in nucleus lysis buffer (50mM TRIS-HCL pH 8.0, 10mM EDTA, 1% SDS, protease inhibitor). The samples were incubated overnight at 4 °C with the appropriate antibody. Salmon sperm DNA/Protein A–agarose (Upstate/Millipore) was used to pull down the antibody. DNA was eluted in elution buffer (1% SDS, 100 mM NaHCO3), followed by reverse cross-linking, RNase-A and protease-K treatment. The DNA was eluted by using a Qiagen PCR purification kit. The following antibodies were used (4 μg/sample): phospho-polymerase II (abcam: ab5095). QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
primers <- data.frame(
    name=c(
        "miR34aChIP F1",
        "miR34aChIP R1"
    ),
    sequence=c(
       "AAA GTT TGC AAA GAA GGA GGC GGG",
       "AGG GAA GAA AGA ACT AGC CGA GCA"
    )
)
```

#Results

```{r, warning=FALSE}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/StableLinePolIIChIP/ChIPdata.txt', header=TRUE, sep="\t")
data$meanQuantity <- rowMeans(data[ ,c("Quantity1", "Quantity2")])

percentPullDown <- ddply(
    data, 
    c("experiment", "condition", "sample"), 
    summarize,
    percentPullDown = meanQuantity/data[data$experiment == experiment & data$condition == condition & data$sample == "input", "meanQuantity"]
)
data <- merge(data, percentPullDown, by=c("experiment", "condition", "sample"), all.x=TRUE)
data$log2percentPulldown <- log2(data$percentPullDown)
data <- subset(data, sample != "input")

ASminusMock <- ddply(
    data, 
    c("experiment"), 
    summarize, 
    condition=unique(condition),
    ASminusMock = log2percentPulldown - data[data$experiment == experiment & data$condition == "mock", "log2percentPulldown"]
)
data <- merge(data, ASminusMock, by=c("experiment", "condition"), all.x=TRUE)

data$antilogASminusMock <- 2^data$ASminusMock

#calculate stats 
t <- t.test(data[data$condition != "mock", "ASminusMock"])
pValue <- t$p.value
CI95l <- t$conf.int[1]
CI95h <- t$conf.int[2]

#calculate summary
stats <- ddply(
    data,
    c("condition"),
    summarize, 
    mean = mean(ASminusMock) 
)

stats$CI95l <- c(CI95l, 1)
stats$CI95h <- c(CI95h, 1)

pBars <- data.frame(
    condition=c("mock", "miR34a AS"),
    xend = c(0,2),
    x=c(0,1),
    xStars=c(0,1.5),
    pStars=c("", "\u2605")
)

stats <- merge(stats, pBars, by="condition")
data <- merge(data, stats, by=c("condition"), all.x=TRUE)
data$condition <- as.character(data$condition)
data[data$condition == "miR34a AS", "condition"] <- "miR34a\nasRNA"
data$condition <- factor(data$condition, levels=c("mock", "miR34a\nasRNA"))
#data <- droplevels(data[data$condition == "miR34a AS",])
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}

#plot for Rmarkdown
ggplot(data, aes(x=condition, y=ASminusMock))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        #scale="width",
        alpha=0.3,
        colour=NA,
        show.legend = FALSE
    )+
    geom_point( 
        aes(colour=condition),
        size=4
    )+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black",
        show.legend = FALSE
    )+
    geom_point(
        aes(y=mean),
        colour="black",
        show.legend = FALSE
    )+
    geom_segment(
        aes(x=x, y=CI95h+0.25, xend=xend, yend=CI95h+0.25),
        colour="grey43"
    )+
    geom_label(
        aes(x=xStars, y=CI95h+0.35, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=5,
        family="Arial Unicode MS"
    )+
    scale_y_continuous(
        "log2(Fold)", 
        sec.axis = sec_axis(
            ~2^., 
            name = "Fold", 
            breaks=c(1,2.5,5,7.5)
        )
    )+
    labs(
      x="Cell line",
      y="log2(Fold polII enrichment)",
      title="Phosphorylated Poll II ChIP",
      caption=
            "Phosphorylated Poll II ChIP in miR34a asRNA over-expressing PC3 stable cell lines compared to their respective mock control.\nError bars (black vertical) indicate 95% CI and black points represent the mean.\n\u2605 = p < 0.05; \u2605\u2605 = p < 0.005, \u2605\u2605\u2605 = p < 0.0005."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_color_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="none",
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15)
    )

#plot for pdf
p <- ggplot(data, aes(x=condition, y=ASminusMock))+
    geom_violin(
        aes(fill=condition),
        trim=TRUE,
        #scale="width",
        alpha=0.3,
        colour=NA,
        lwd=0.1
    )+
    #geom_point( 
    #    aes(colour=condition),
    #    size=1
    #)+
    geom_linerange(
        aes(ymin=CI95l, ymax=CI95h),
        colour="black",
        show.legend = FALSE,
        lwd=0.15
    )+
    geom_point(
        aes(y=mean),
        colour="black",
        size=0.5,
        show.legend = FALSE
    )+
    geom_segment(
        aes(x=x, y=CI95h+0.25, xend=xend, yend=CI95h+0.25),
        colour="grey43",
        lwd=0.15
    )+
    geom_label(
        aes(x=xStars, y=CI95h+0.4, label=pStars),
        label.size=0,
        label.padding=unit(0.01, "lines"),
        show.legend = FALSE,
        fill="white",
        size=1,
        family="Arial Unicode MS"
    )+
    #scale_y_continuous(
    #    "log2(Fold)", 
    #    sec.axis = sec_axis(
    #        ~2^., 
    #        name = "Fold", 
    #        breaks=c(1,2.5,5,7.5)
    #    )
    #)+
    labs(
      x="Cell line",
      y="log2(Fold polII enrichment)"
      #title="Phosphorylated Poll II ChIP"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_color_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10
        ),
        plot.margin = unit(rep(0.1,4), "lines"),
        legend.position="none",
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text=element_text(size=8),
        axis.ticks.length = unit(1/15, "cm"),
        axis.ticks = element_line(size=0.25),
        panel.border = element_rect(fill=NA, size=0.15),
        panel.margin=unit(2, "mm")
    )

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/StableLinePolIIChIP/StableLinePolIIChIP.pdf", device=cairo_pdf, height=60, width=43, units="mm") #83

```

#Conclusion
Phosphorylated pol-II was increased at the miR34a promoter in miR34a asRNA over-expressing cell lines indicating that the regulation of miR34a by miR34a asRNA is transcriptional.

### 2017-11-07 inst/miR34aLocus/figure1a.Rmd
added plotFigure and helpers

---
title: "miR34a locus"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

####Introduction
An antisense transcript to the miR34a HG was detected using the UCSC genome browser.

####Methods
The USCS genome browser was utilized for the bioinformatic evaluation of antisense transcription utilizing the Human EST and ENCODE RNAseq tracks.

####Results
```{r, out.width = "800px", tidy=TRUE, tidy.opts=list(width.cutoff=60)}
projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
url <- "miR34aLocus/miR34aLocus_hg38.png"
knitr::include_graphics(file.path(projectUrl, url))
```
A schematic picture of the miR34a locus from UCSC genome browser (hg38) including miR34a HG and mature miR34a, and LINC01759. H3K4me3 ChIP-seq data and conservation over the locus is also shown.

####Conclusion
GENCODE annotation supports the presence of a transcript orinionating in the antisense orientation from the miR34a gene.

### 2017-11-07 R/processFigures.R

@@ -1,0 +1,65 @@
+
+#' @export
+#' @importFrom liftr lift render_docker
+plotFigure <- function(figure) {
+  path <- getPath(figure)
+  runDockerAndView(path)
+}
+
+####Helpers
+
+getPath <- function(figure) {
+  map <- makeMap()
+  map[figure][[1]]
+}
+
+makeMap <- function() {
+  list(
+    figure1a = "miR34aLocus/figure1a.Rmd",
+    figure1b = "miR34aASExpressionCellPanel/figure1b.Rmd",
+    figure1c = "TCGAcorrelation/figure1c.Rmd",
+    figure1d = "3primeRACE/figure1d.Rmd",
+    figure1e = "primerWalk/figure1e.Rmd",
+    figure1f = "codingPotential/figure1f.Rmd",
+    figure2a = "HCT116p53null/figure2a.Rmd",
+    figure2b = "HctHekDox/figure2b.Rmd",
+    figure2c = "P1-HCTandHEK/figure2d.Rmd",
+    figure2d = "P1-HCTandHEK/figure2d.Rmd",
+    figure2e = "P1shRNAdox/figure2e.Rmd",
+    figure3a = "StableLineExpression/figure3a.Rmd",
+    figure3b = "StableLineCellCycle/figure3b.Rmd",
+    figure3c = "growthStarvation/figure3c.Rmd",
+    figure3d = "StableLinePolIIChIP/figure3d.Rmd",
+    figure3e = "survival/figure3e.Rmd",
+    suppFigure1a = "",
+    suppFigure1b = "",
+    suppFigure1c = ""
+  )
+}
+
+runDockerAndView <- function(path) {
+  sans_ext = tools::file_path_sans_ext
+  
+  rmdPath <- system.file(path, package = "miR34AasRNAproject")
+  tmpPath <- moveToTmp(rmdPath)
+  
+  render_docker(file.path(tmpPath, basename(rmdPath)))
+  
+  htmlPath <- file.path(tmpPath, paste0(sans_ext(basename(rmdPath)), '.html'))
+  browseURL(paste0('file://', htmlPath))
+}
+
+moveToTmp <- function(rmdPath){
+  tmpPath <- tempdir()
+  
+  #copy rmd
+  sysCmd1 <- paste("cp", rmdPath, tmpPath, sep = " ")
+  system(sysCmd1)
+  
+  #copy docker
[…]

### 2017-11-07 data-raw/saveRDA.R
adding data for CCND1 exp

@@ -2,169 +2,184 @@ library(tidyverse)
 
 #HCTp53null
 read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
-    rename(gene = Target) %>%
-    mutate(
-        Condition = case_when(
-            Condition == "WT"       ~ "p53-wt",
-            Condition == "p53 null" ~ "p53-null",
-            TRUE                    ~ "error in saveRDA.R"
-        ),
-        gene = case_when(
-            gene == "miR34a AS" ~ "miR34a asRNA",
-            gene == "miR34a HG" ~ "miR34a HG",
-            gene == "Actin"     ~ "Actin",
-            TRUE                ~ "error in saveRNA.R"
-        )
-    ) %>%
-    mutate(
-        Treatment = parse_factor(Treatment, levels = c("0", "100", "200", "500")),
-        Condition = parse_factor(Condition, levels = c("p53-wt", "p53-null")),
-        gene = parse_factor(gene, levels = c("miR34a HG", "miR34a asRNA", "Actin"))
-    ) %>%
-    save(., file = './data/HCT116p53null.rda', compress = "bzip2")
+  rename(gene = Target) %>%
+  mutate(
+    Condition = case_when(
+      Condition == "WT"       ~ "p53-wt",
+      Condition == "p53 null" ~ "p53-null",
+      TRUE                    ~ "error in saveRDA.R"
+    ),
+    gene = case_when(
+      gene == "miR34a AS" ~ "miR34a asRNA",
+      gene == "miR34a HG" ~ "miR34a HG",
+      gene == "Actin"     ~ "Actin",
+      TRUE                ~ "error in saveRNA.R"
+    )
+  ) %>%
+  mutate(
+    Treatment = parse_factor(Treatment, levels = c("0", "100", "200", "500")),
+    Condition = parse_factor(Condition, levels = c("p53-wt", "p53-null")),
+    gene = parse_factor(gene, levels = c("miR34a HG", "miR34a asRNA", "Actin"))
+  ) %>%
+  save(., file = './data/HCT116p53null.rda', compress = "bzip2")
 
 #HctHekDox
 read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
-    rename(
-        `Biological Replicate` = experiment,
-        `Cell line` = cellLine,
-        Treatment = treatment
[…]

### 2017-11-07 R/plotting.R
all figures done in vignette(?)

@@ -1,0 +1,3 @@
+
+#add "geoms" for rmarkdown and pdf
+

### 2017-11-07 R/plotting.R
added pdf and markdown styles

@@ -1,3 +1,67 @@
 
 #add "geoms" for rmarkdown and pdf
 
+plotPDF <- function() {
+  style <- theme_few() +
+    scale_fill_ptol() +
+    theme(
+        plot.title = element_text(
+            hjust = 0.5,
+            face = "bold",
+            size = 10,
+            margin = margin(b = 2, unit = "mm")
+        ),
+        plot.margin = unit(rep(0.1, 4), "lines"),
+        legend.position = "top",
+        legend.margin = unit(1, "mm"),
+        legend.key.size = unit(1/5, "cm"),
+        legend.title = element_text(size = 9),
+        legend.text = element_text(size = 7),
+        axis.title = element_text(size = 9),
+        axis.title.x = element_text(margin = margin(t = 5)),
+        axis.text.y = element_text(size = 8),
+        axis.text.x = element_text(size = 7),
+        axis.ticks = element_line(size = 0.25),
+        axis.ticks.length = unit(1/15, "cm"),
+        strip.text.x = element_text(size = 8, margin = margin(0.01, 0, 0.1, 0, "cm")),
+        panel.border = element_rect(fill = NA, size = 0.15)
+    ) +
+    guides(
+        fill = guide_legend(override.aes = list(size = 2)),
+        colour = FALSE
+    )
+    
+    return(style)
+}
+
+plotRmarkdown <- function() {
+  style <- theme_few() +
+  scale_colour_ptol() +
+  scale_fill_ptol() +
+  theme(
+    legend.position = "top",
+    legend.title = element_text(size = 17),
+    legend.text = element_text(size = 15),
+    plot.title = element_text(
+      hjust = 0.5,
+      face = "bold",
+      size = 20
+    ),
+    plot.caption = element_text(
+      hjust = 0,
+      margin = margin(t = 15),
+      family = "Arial Unicode MS"
+    ),
+    axis.title = element_text(size = 17),
+    axis.title.x = element_text(margin = margin(t = 10)),
+    axis.text = element_text(size = 12),
+    strip.text.x = element_text(size = 17)
+  ) +
+  guides(
+    fill = guide_legend(title = "Gene", override.aes = list(size = 4)),
+    colour = FALSE
+  )
+  
+  return(style)
+}
+

### 2017-11-09 inst/lnc34a_CAGE/extract.pl
adding lnc34a analysis

@@ -1,0 +1,97 @@
+#!/usr/bin/perl
+#https://genome.ucsc.edu/cgi-bin/hgFileUi?db=hg19&g=wgEncodeCshlLongRnaSeq
+use warnings;
+use strict;
+use Data::Dumper;
+
+my $dir = $ARGV[0];
+unless (-d $dir) {
+    my $cmd1 = 'mkdir' . ' ' . $dir ;
+    system($cmd1);
+    
+    my @downloadFiles = (
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageA549CellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageAg04450CellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageBjCellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageCd20CellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageCd34mobilizedCellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageGm12878CellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageH1hescCellPamTssHmmV2.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageH1hescCellPapTssHmm.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageHaoafCellPapTssHmm.bedRnaElements.gz",
[…]

### 2017-11-09 inst/lnc34a_spliceJuncs/extract.pl

@@ -1,0 +1,126 @@
+#!/usr/bin/perl
+#https://genome.ucsc.edu/cgi-bin/hgFileUi?db=hg19&g=wgEncodeCshlLongRnaSeq
+use warnings;
+use strict;
+use Data::Dumper;
+
+my $dir = './sampleFiles';
+unless (-d $dir) {
+    my $cmd1 = 'mkdir' . ' ' . $dir ;
+    system($cmd1);
+    
+    my @downloadFiles = (
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqA549CellPamJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqA549CellPapJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqAg04450CellPamJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqAg04450CellPapJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqBjCellPamJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqBjCellPapJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqCd20CellPamJunctions.bedRnaElements.gz",
+    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeqCd20CellPapJunctions.bedRnaElements.gz",
[…]

### 2017-11-09 data-raw/saveRDA.R
starting to make changes in perl script for CAGE

@@ -248,5 +248,17 @@ read_tsv('./data-raw/stableLineCCND1prot.txt', col_names = TRUE) %>%
   )) %>%
   save(., file = './data/stableLineCCND1prot.rda', compress = "bzip2")
 
+#lnc34a CAGE
+tmp <- tmp.dir()
+
+#call perl script
+sysCmd1 <- ""
+system(sysCmd1)
+
+#get output
+data <- read.table(file.path(tmp, "fileResults.txt"))
+
+#save output
+
 
 #source('./data-raw/saveRDA.R')

### 2017-11-09 inst/lnc34a_CAGE/extract.pl

@@ -6,61 +6,58 @@ use Data::Dumper;
 
 my $dir = $ARGV[0];
 unless (-d $dir) {
-    my $cmd1 = 'mkdir' . ' ' . $dir ;
-    system($cmd1);
-    
-    my @downloadFiles = (
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageA549CellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageAg04450CellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageBjCellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageCd20CellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageCd34mobilizedCellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageGm12878CellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageH1hescCellPamTssHmmV2.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageH1hescCellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageHaoafCellPapTssHmm.bedRnaElements.gz",
-    "http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCageHaoecCellPapTssHmm.bedRnaElements.gz",
[…]

### 2017-11-11 inst/lnc34aSplJnc/lnc34aSplJnc.Rmd
added lnc34a splice junctions analysis

---
title: "lnc34a splice junctions"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

```{r}
#locus
data <- tibble(
  gene = readr::parse_factor(
    c(rep("miR34a asRNA", 5), rep("lnc34a", 3)),
    levels = c("miR34a asRNA", "lnc34a")
  ),
  feature = c(
    "exon", "intron", "exon", "intron",
    "exon", "exon", "intron", "exon"
  ),
  start = c(
    9242262, 9242375, 9243691, 9243866,
    9251451, 9241796, 9242354, 9256971),
  stop = c(
    9242375, 9243691, 9243866, 9251451,
    9252148, 9242354, 9256971, 9257102
  )
)

#splice junctions
load('/Users/jasonserviss/Github/miR34a_asRNA_project/data/lnc34aSpliceJncs.rda')
splJnc <- .
rm(.)

splJnc <- splJnc %>%
  mutate(
    cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename),
    feature = "splice junction",
    tag = paste(cellline, feature, sep = "-"),
    gene = "NA"
  ) %>%
  select(cellline, feature, start, stop, tag) %>%
  group_by(start, stop) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  arrange(desc(n)) %>%
  mutate(y = 1:length(.data$n))
```

```{r, fig.align='center', fig.height=8, fig.width=12}
###locus
p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

##splice junctions
p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = splJnc,
    aes(xmin = start, xmax = stop, y = y, fill = n),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  viridis::scale_fill_viridis() +
  ggthemes::theme_few() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Splice junctions") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(title = "n reads", title.position = "top", title.hjust = 0.5))

g2 <- ggplotGrob(p1)
g3 <- ggplotGrob(p2)
g <- rbind(g3, g2, size = "last")
grid.newpage()
grid.draw(g)

```

### 2017-11-11 data-raw/saveRDA.R
trying to write data with write_rds instead

@@ -31,7 +31,7 @@ read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
       levels = c("miR34a HG", "miR34a asRNA", "Actin")
     )
   ) %>%
-  save(., file = './data/HCT116p53null.rda', compress = "bzip2")
+  write_rds(path = './data/HCT116p53null.rda', compress = "bz2")
 
 #HctHekDox
 read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%

### 2017-11-11 data-raw/saveRDA.R
trying to write data with write_rds instead2

@@ -31,7 +31,7 @@ read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
       levels = c("miR34a HG", "miR34a asRNA", "Actin")
     )
   ) %>%
-  write_rds(path = './data/HCT116p53null.rda', compress = "bz2")
+  write_rds(path = './data/HCT116p53null.rds', compress = "bz2")
 
 #HctHekDox
 read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%

### 2017-11-11 data-raw/saveRDA.R
trying to write data with write_rds instead3

@@ -31,7 +31,7 @@ read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
       levels = c("miR34a HG", "miR34a asRNA", "Actin")
     )
   ) %>%
-  write_rds(path = './data/HCT116p53null.rds', compress = "bz2")
+  write_rds(., path = './data/HCT116p53null.rds')
 
 #HctHekDox
 read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%

### 2017-11-11 R/QpcrFuns.R
got a strange error with the technicalMeans fun and cellularLoc dataset, updated the fun

@@ -4,7 +4,7 @@ technicalMeans <- function(
     grouping
 ){
     data %>%
-    gather(`Tech. Replicate`, Ct, -grouping) %>%
+    gather(`Tech. Replicate`, Ct, -one_of(grouping)) %>%
     group_by(!!! rlang::syms(grouping)) %>%
     summarize(ctMean = mean(Ct, na.rm = TRUE)) %>%
     ungroup()

### 2017-11-12 data-raw/saveRDA.R
re-ran lnc34a data without any filtering, also deleted bed files

@@ -1,5 +1,4 @@
 library(tidyverse)
-library(magrittr)
 
 #HCTp53null
 read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
@@ -274,11 +273,11 @@ read_tsv('./data-raw/lnc34aCAGE.txt') %>%
     filename = basename(filename)
   ) %>%
   rename(
-    chr = X1, strand = X6, start = X2, stop = X3,
-    reads = X9, RPKM = X7, signif = X8
+    chr = X1, start = X2, stop = X3, name = X4, score = X5,
+    strand = X6, level = X7, signif = X8, score2 = X9,
   ) %>%
-  select(chr, start, stop, strand, reads, RPKM, signif, filename) %>%
-  filter(RPKM >= 1) %T>%
+#  select(chr, start, stop, strand, reads, RPKM, signif, filename) %>%
+#  filter(RPKM >= 1) %T>%
   write_rds(., path = './data/lnc34aCAGE.rds')
 
 #lnc34a splice junctions
@@ -301,11 +300,11 @@ read_tsv('./data-raw/lnc34aSpliceJncs.txt') %>%
   unnest() %>%
   mutate(filename = basename(filename)) %>%
   rename(
-    chr = X1, strand = X6, start = X2, stop = X3,
-    reads = X9, signif = X8
+    chr = X1, start = X2, stop = X3, name = X4, score = X5,
+    strand = X6, level = X7, signif = X8, score2 = X9
   ) %>%
-  select(filename, chr, start, stop, strand, reads, signif) %>%
-  filter(reads >= 2) %T>%
+#  select(filename, chr, start, stop, strand, reads, signif) %>%
+#  filter(reads >= 2) %T>%
   write_rds(., path = './data/lnc34aSpliceJncs.rds')
 
 

### 2017-11-12 inst/lnc34aSplJnc/lnc34aSplJnc.Rmd
reran lnc34aSplJnc.Rmd with new rds file and new download method
more accurate counting of splJnc reads in analysis

@@
 #splice junctions
-load('/Users/jasonserviss/Github/miR34a_asRNA_project/data/lnc34aSpliceJncs.rda')
-splJnc <- .
-rm(.)
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+url <- "lnc34aSpliceJncs.rds"
+splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
 splJnc <- splJnc %>%
-  mutate(
-    cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename),
-    feature = "splice junction",
-    tag = paste(cellline, feature, sep = "-"),
-    gene = "NA"
-  ) %>%
-  select(cellline, feature, start, stop, tag) %>%
+  mutate(cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename)) %>%
+  select(cellline, start, stop, score2) %>%
   group_by(start, stop) %>%
-  summarize(n = n()) %>%
+  summarize(n = sum(score2)) %>%
   ungroup() %>%
+  filter(n > 2) %>%
   arrange(desc(n)) %>%
@@
     arrowhead_height = unit(0, "mm"),
+    arrow_body_height = unit(1, "mm"),
     colour = "gray"

### 2017-11-12 R/plotting.R
adding resize_heights function

@@ -60,3 +60,10 @@ plotRmarkdown <- function(plot) {
   return(p)
 }
 
+#' @export
+resize_heights <- function(g, heights = unit(rep(1, length(idpanels)), "null")) {
+  idpanels <- unique(g$layout[grepl("panel",g$layout$name), "t"])
+  g$heights <- grid:::unit.list(g$heights)
+  g$heights[idpanels] <- heights
+  g
+}

### 2017-11-12 inst/lnc34aCage/lnc34aCAGE.Rmd
lnc34a figures done in inst

---
title: "lnc34a CAGE"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Add number of cell lines included in figure.

```{r, message = FALSE}
packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)
```

```{r}
data <- tibble(
  gene = readr::parse_factor(
    c(rep("miR34a asRNA", 5), rep("lnc34a", 3)),
    levels = c("miR34a asRNA", "lnc34a")
  ),
  feature = c(
    "exon", "intron", "exon", "intron",
    "exon", "exon", "intron", "exon"
  ),
  start = c(
    9242262, 9242375, 9243691, 9243866,
    9251451, 9241796, 9242354, 9256971),
  stop = c(
    9242375, 9243691, 9243866, 9251451,
    9252148, 9242354, 9256971, 9257102
  )
)

dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
url <- "lnc34aCAGE.rds"
cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
    arrange(desc(level)) %>%
    mutate(y = 1:length(pull(., level)))

```

```{r, fig.align='center', fig.height=8, fig.width=12}
###plot

p1 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = filter(data, feature == "exon"),
    aes(xmin = start, xmax = stop, y = gene, fill = gene),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    colour = "gray"
  ) +
  ggthemes::theme_few() +
  ggthemes::scale_fill_ptol() +
  geom_segment(
    data = filter(data, feature == "intron"),
    aes(x = start, xend = stop, y = gene, yend = gene),
    linetype = "dotted",
    colour = "gray",
    size = 1
  ) +
  xlim(9241000, 9257900) +
  labs(x = "Chromosome 1", y = "Genes") +
  guides(fill = FALSE)

p2 <- ggplot(data = NULL) +
  gggenes::geom_gene_arrow(
    data = cage,
    aes(xmin = start, xmax = stop, y = y, fill = level),
    arrowhead_width = unit(0, "mm"),
    arrowhead_height = unit(0, "mm"),
    arrow_body_height = unit(2, "mm"),
    colour = "gray",
    show.legend = TRUE
  ) +
  ggthemes::theme_few() +
  viridis::scale_fill_viridis() +
  theme(
    axis.title.x = element_blank(),
    legend.position = "top",
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Cage reads") +
  xlim(9241000, 9257900) +
  guides(fill = guide_colourbar(title = "RPKM", title.position = "top", title.hjust = 0.5))

p3 <- ggplot(data = NULL) + 
  geom_density(data = cage, aes(x = start)) +
  ggthemes::theme_few() +
  xlim(9241000, 9257900) +
  theme(
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(y = "Density")

grobz <- lapply(list(p1, p2, p3), ggplotGrob)
g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
grid.newpage()
grid.draw(resize_heights(g, unit(c(3,1,1), "null")))
```

### 2017-11-12 data-raw/saveRDA.R

@@ -276,8 +276,6 @@ read_tsv('./data-raw/lnc34aCAGE.txt') %>%
     chr = X1, start = X2, stop = X3, name = X4, score = X5,
     strand = X6, level = X7, signif = X8, score2 = X9,
   ) %>%
-#  select(chr, start, stop, strand, reads, RPKM, signif, filename) %>%
-#  filter(RPKM >= 1) %T>%
   write_rds(., path = './data/lnc34aCAGE.rds')
 
 #lnc34a splice junctions
@@ -303,8 +301,6 @@ read_tsv('./data-raw/lnc34aSpliceJncs.txt') %>%
     chr = X1, start = X2, stop = X3, name = X4, score = X5,
     strand = X6, level = X7, signif = X8, score2 = X9
   ) %>%
-#  select(filename, chr, start, stop, strand, reads, signif) %>%
-#  filter(reads >= 2) %T>%
   write_rds(., path = './data/lnc34aSpliceJncs.rds')
 
 

### 2017-11-13 data-raw/saveRDA.R
added library call to miR34AasRNAproject in saveRDA.R

@@ -1,4 +1,5 @@
 library(tidyverse)
+library(miR34AasRNAproject)
 
 #HCTp53null
 read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%

### 2017-11-13 inst/lnc34aCage/lnc34aCAGE.Rmd
added intro, methods, etc to lnc34a analysis

@@
 
+<style> 
+.caption { 
+  color: Black; 
+  font-family: "Times New Roman", Times, serif;
+  font-size: 1.0em; 
+}
+</style>
+
 Add number of cell lines included in figure.
@@
 ```
+
+####Introduction
+
+[Wang et al.](https://www.ncbi.nlm.nih.gov/pubmed/27077950) have previously published concerning a antisense transcript arising from the miR34a locus that they named "lnc34a".
+Wang et al.
+state find that this transcript is expressed at "significantly higher levels in colon cancer stem cells spheres (CCSCs)" compared to 9 commonly used colorectal cancer cell lines.
+After obtaining the sequence for lnc34a we could confirm that neither our primer walk analysis or our 3' RACE detected the lnc34a transcripts presence in the cell lines we had utilized.
+To further investigate the presence of lnc34a in non-CCSC cell lines we interogated CAGE data from RIKEN to investigate the possibility of an alternative transcription start site upstream of the transcription start site we had characterized.
+<br></br>
+
+####Methods
+All available CAGE data was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDA.R file.
+CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200) were filtered from the total data.
+All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance.
+In addition, a density plot shows the distribution of the CAGE reads at in the specified interval.
+ADD NUMBER OF CELL LINES.
+
+<br></br>
+
+####Results
 
@@
   )
+)
+
+pw <- tibble(
+  gene = paste("F", 10:15, sep = ""),
+  feature = rep("primer", 6),
+  start = c(9242282, 9242170, 9242037, 9241944, 9241838, 9241734),
+  stop = c(9242303, 9242192, 9242058, 9241967, 9241861, 9241757)
 )
@@
 ```
+
+<div class="caption">
+CAGE tags (top), CAGE tag density (middle), and antisense genes (bottom) at the miR34a locus. CAGE tags are colored according to their corresponding RPKM values.
+</div>
+
+<br></br>
+
+####Conclusions
+
+The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site.
+An additional peak, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site and corresponds to the upstream start site detected in our primer walk analysis (figure 1e).
+Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript.
+This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors.
+An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected.
+
+<br></br><br></br>

### 2017-11-13 inst/lnc34aSplJnc/lnc34aSplJnc.Rmd
added intro, methods, etc to lnc34a analysis

@@
 
+<style> 
+.caption { 
+  color: Black; 
+  font-family: "Times New Roman", Times, serif;
+  font-size: 1.0em; 
+}
+</style>
+
+Add number of cell lines included in figure.
+
 ```{r, echo = FALSE, message = FALSE}
@@
 ```
+
+####Introduction
+
+[Wang et al.](https://www.ncbi.nlm.nih.gov/pubmed/27077950) have previously published concerning a antisense transcript arising from the miR34a locus that they named "lnc34a".
+Wang et al.
+state find that this transcript is expressed at "significantly higher levels in colon cancer stem cells spheres (CCSCs)" compared to 9 commonly used colorectal cancer cell lines.
+After obtaining the sequence for lnc34a we could confirm that neither our primer walk analysis or our 3' RACE detected the lnc34a transcripts presence in the cell lines we had utilized.
+To further investigate the presence of lnc34a in non-CCSC cell lines we interogated RNAseq splice junction data generated in conjunction with the ENCODE project to search for introns present at the miR34a locus.
+
+<br></br>
+
+####Methods
+All available splice junction data was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDA.R file.
+Spliced reads mapping to the plus strand of chromosome 1 and in regions corresponding to the lnc34a start (9241796) and transcription termination (9257102) sites were filtered from the total data.
+All splice junctions were plotted and colored according to the number of reads corresponding to each.
+ADD NUMBER OF CELL LINES.
+
+<br></br>
+
+####Results
 
@@
   xlim(9241000, 9257900) +
-  guides(fill = guide_colourbar(title = "n reads", title.position = "top", title.hjust = 0.5))
+  guides(fill = guide_colourbar(title = "Reads", title.position = "top", title.hjust = 0.5))
 
-g2 <- ggplotGrob(p1)
-g3 <- ggplotGrob(p2)
-g <- rbind(g3, g2, size = "last")
+grobz <- lapply(list(p1, p2), ggplotGrob)
+g <- rbind(grobz[[2]], grobz[[1]], size = "last")
 grid.newpage()
-grid.draw(g)
+grid.draw(resize_heights(g, unit(c(3,1), "null")))
+```
 
-```
+<div class="caption">
+Splice junctions (top) detected in RNAseq data from the ENCODE project and antisense genes (bottom) at the miR34a locus. Splice junctions are colored according to the corresponding total read count.
+</div>
+
+<br></br>
+
+####Conclusions
+Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (Supplementary figure XX) with those being the mist highly expressed corresponding to the annotated miR34a asRNA transcript.
+Despite this, no splice junctions appear to correspond to the intron in the lnc34a transcript.
+This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors.
+An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected.
+
+<br></br><br></br>

### 2017-11-14 inst/figure1b_miR34aASExpressionCellPanel/figure1b.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

---
title: "miR34a asRNA tissue expression"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We wished to examine expression in different tissue types and, therefore, utilized a panel of common cell lines to detect miR34a asRNA expression, as well as, miR34a HG. We included both p53+/+ and p53-/- cell lines in the cell line panel due to the fact that miR34a is a known downstream target of p53.

#Methods
Cells were cultured with the appropriate growth medium and seeded at a desity between 50-75% confluency. The following day, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was run for 35 or 38 or 16 cycles for miR34a asRNA, miR34a HG, and beta-actin, respectivley, with 58˚C annealing temperature. PCR products were analyzed on a 2% agarose gel.

##Primers

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "miR34a asRNA F1",
        "miR34a asRNA R1",
        "miR34aHG_F",
        "miR34aHG_R",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers
```

#Results
<br></br>

##A)

<center>![miR34a cell panel screening (miranda).](mirandaCellPanel.png)</center>
<br></br>

##B)

<center>![miR34a cell panel screening (large).](cellPanelLarge.png)</center>
<br></br>

Semi-quantitative PCR data from the screening of a panel of cell lines. 
* Indicates that, although the cell line is p53wt, other mechanisms are present which inhibit p53 function.

#Conclusions
We were able to detect co-expression of both miR34a HG and miR34a AS in a variety of cell lines, including HCT116 human colon cancer cells and 293T human embryonic kidney cells. A correlation was observed between both miR34a HG and miR34a asRNA expression and p53 status, with p53+/+ cell lines tending to have higher expression of both transcripts.

### 2017-11-14 inst/figure2a_HCT116p53null/figure2a.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

---
title: "miR34a asRNA doxorubicin treatment of HCT116 p53 wt and null"
author: "Jason T. Serviss"
date: "30/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
miR34a is a known downstream target of p53 and has been previously shown to exhibit increased expression with cellular apoptotic signaling. We hypothesized that miR34a asRNA may be regulated in a similar fashion whereby transcription is stimulated by activation of p53. To test this we treated p53+/+ and p53-/- HCT116 cells with increasing concentrations of the DNA damaging agent doxorubicin and monitored miR34a asRNA expression.

#Methods
HCT116 cells were cultured in DMEM high modified (Hyclone, GE healthcare) supplemented with supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum.  
25 x 10^5 HCT116 cells were plated in 6 well plates. 24 hours later media was exchanged and doxorubicin was added to a final concentration of 100, 200 or 500 ng/ml. Cells were harvested for RNA extraction 24 hours later using trypsin. RNA was extracted using Nucleospin RNA kit (Machery-Nagel Ref. 740955) according to manufacturer‟s protocol and DNase treated using Ambion Turbo DNA-free according to manufacturer‟s protocol (Life Technologies Ref. AM1907). cDNA was synthesized using ~500 ng RNA with M-MLV (Life Technologies Ref 28025013) and a mixture of oligo(dT) with nanomers in accordance with the manufacturer's protocol.
qPCR quantification was carried out using the PowerUp SYBR Green Master Mix (Thermo Fisher Scientific, Ref. A25777) on the CFX96 Touch Real-Time PCR Detection System: 50°C for 2 min, 95°C for 2min, and 95°C for 1 sec followed by 60°C for 30 sec repeated for 40 cycles. The following primers were used:

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers
```

#Results
```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/HCT116p53null/QPCRdata.txt', header=TRUE, sep="\t")
colnames(data)[which(colnames(data) == "Target")] <- "Gene"

goi <- subset(data, Gene %in% c("miR34a AS", "miR34a HG")) 
hk <- subset(data, Gene == "Actin")

colnames(goi)[c(6:7)] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[c(6:7)] <- c("Ct1HK", "Ct2HK")

data <- merge(goi, hk[, colnames(hk) != "Gene"], by = c("Condition", "Treatment", "Biological.Replicate", "Cell.line"))

#ddct
data$meanGOI <- rowMeans(data[, c("Ct1GOI", "Ct2GOI")])
data$meanHK <- rowMeans(data[, c("Ct1HK", "Ct2HK")])
data$dct <- data$meanGOI - data$meanHK
ddct <- ddply(
    data,
    c("Gene", "Condition", "Treatment", "Biological.Replicate"),
    summarize,
    ddct=dct-data[data$Gene == Gene & data$Condition == Condition & data$Treatment == 0 & data$Biological.Replicate == Biological.Replicate, "dct"]
)

data <- merge(data, ddct, by=c("Gene", "Condition", "Treatment", "Biological.Replicate"))
data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data, 
    c("Gene", "Condition", "Treatment"),
    summarize,
    n=length(log2fold),
    mean=mean(log2fold),
    pValue=t.test(log2fold, data[data$Gene == Gene & data$Condition == "WT" & data$Treatment == Treatment, "log2fold"])$p.value,
    CI95l=t.test(log2fold)$conf.int[1],
    CI95h=t.test(log2fold)$conf.int[2]
)

data <- merge(data, stats, by = c("Gene", "Condition", "Treatment"))
#data$pValue <- ifelse(data$pValue == 1, NA, data$pValue)

data$pStars <- ifelse(
    data$pValue < 0.05 & data$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        data$pValue < 0.005 & data$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            data$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            "n.s."
        )
    )
)

yS <- ddply(data, c("Gene", "Treatment"), summarize, max = max(CI95h))
pBars <- ddply(
    data, 
    c("Gene", "Condition", "Treatment"),
    summarize,
    CI95l = unique(CI95l),
    CI95h = unique(CI95h),
    pStars = unique(pStars),
    pValue = unique(pValue)
)
pBars[pBars$Condition == "WT", "pStars"] <- ""
pBars <- merge(pBars, yS, by = c("Gene", "Treatment"))
pBars$x <- dplyr::case_when(
    pBars$Treatment ==   0 ~ 1 + 0.25,
    pBars$Treatment == 100 ~ 2 + 0.25,
    pBars$Treatment == 200 ~ 3 + 0.25,
    pBars$Treatment == 500 ~ 4 + 0.25
)

pBars$xend <- dplyr::case_when(
    pBars$Treatment ==   0 ~ 1 - 0.25,
    pBars$Treatment == 100 ~ 2 - 0.25,
    pBars$Treatment == 200 ~ 3 - 0.25,
    pBars$Treatment == 500 ~ 4 - 0.25
)

#prepare for plotting
data$Treatment <- factor(data$Treatment, levels=c("0", "100", "200", "500"))
pBars$Treatment <- factor(pBars$Treatment, levels=c("0", "100", "200", "500"))
data$Condition <- ifelse(data$Condition == "WT", "p53-wt", "p53-null")
pBars$Condition <- ifelse(pBars$Condition == "WT", "p53-wt", "p53-null")
data$Condition <- factor(data$Condition, levels=c("p53-wt", "p53-null"))
pBars$Condition <- factor(pBars$Condition, levels=c("p53-wt", "p53-null"))

data$Gene <- ifelse(data$Gene == "miR34a AS", "miR34a asRNA", "miR34a HG")
data$Gene <- factor(data$Gene, levels = c("miR34a HG", "miR34a asRNA"))
pBars$Gene <- ifelse(pBars$Gene == "miR34a AS", "miR34a asRNA", "miR34a HG")
pBars$Gene <- factor(pBars$Gene, levels = c("miR34a HG", "miR34a asRNA"))

```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data = NULL) +
    geom_violin(
        data = data,
        aes(x = Treatment, y = log2fold, fill = Condition),
        trim = TRUE,
        alpha = 0.3,
        color = NA,
        scale = "width",
        show.legend = TRUE
    ) +
    geom_point(
        data = data,
        aes(x = Treatment, y = mean, group = Condition), 
        position = position_dodge(width = 0.9), 
        size = 4
    ) +
    facet_grid(. ~ Gene) +
    geom_linerange(
        data = pBars,
        aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
        colour = "black",
        position = position_dodge(width = 0.9),
        show.legend = FALSE
    ) +
    geom_label(
        data = pBars,
        aes(x = Treatment, y = max + 0.22, label = pStars),
        label.size = 0,
        label.padding = unit(0.01, "lines"),
        show.legend = FALSE,
        fill = "white",
        size = 5,
        family = "Arial Unicode MS",
        position = position_dodge(width = 0.9)
    ) +
    geom_segment(
        data = pBars,
        aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
        colour="grey43",
        show.legend = FALSE
    ) +
    scale_y_continuous(
        "\u0394\u0394Ct",
        breaks=c(-1,0,1,2,3,4,5),
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
            breaks=c(2^-1,2^0,2^1,2^2,2^3,2^4,2^5)
        )
    )+
    labs(
      x="Treatment",
      title="miR34a asRNA regulation by p53 induction",
      caption=
            "Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in P53+/+ and p53-/- HCT116 cells."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position = "top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(fill = guide_legend(title = "Cell line", override.aes = list(size=3)))

#plot for pdf
p <- ggplot(data = NULL) +
    geom_violin(
        data = data,
        aes(x = Treatment, y = log2fold, fill = Condition),
        trim = TRUE,
        alpha = 0.3,
        color = NA,
        scale = "width",
        show.legend = TRUE
    ) +
    geom_point(
        data = data,
        aes(x = Treatment, y = mean, group = Condition), 
        position = position_dodge(width = 0.9), 
        size = 0.5
    ) +
    facet_grid(. ~ Gene) +
    geom_linerange(
        data = pBars,
        aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
        colour = "black",
        position = position_dodge(width = 0.9),
        show.legend = FALSE,
        lwd = 0.15
    ) +
    geom_label(
        data = pBars,
        aes(x = Treatment, y = max + 0.35, label = pStars),
        label.size = 0,
        label.padding = unit(0.01, "lines"),
        show.legend = FALSE,
        fill = "white",
        size = 1,
        family = "Arial Unicode MS",
        position = position_dodge(width = 0.9)
    ) +
    geom_segment(
        data = pBars,
        aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
        colour="grey43",
        show.legend = FALSE,
        lwd=0.2
    ) +
    scale_y_continuous(
        "\u0394\u0394Ct",
        breaks=c(-1,0,1,2,3,4,5)
        #sec.axis = sec_axis(
        #    ~2^., 
        #    name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}), 
        #    breaks=c(2^-1,2^0,2^1,2^2,2^3,2^4,2^5)
        #)
    )+
    labs(x="Treatment")+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.spacing=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(fill = guide_legend(title = "Cell line", override.aes = list(size = 2)))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/HCT116p53null/HCT116p53null.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

#Conclusions
We observed increasing miR34a HG and asRNA expression with increasing doses of doxorubicin indicating that these two transcripts are co-regulated by p53. Although p53+/+ cells showed a 25-fold increase over untreated cells in miR34a AS expression at the highest tested doxorubicin concentration, this effect was largely abrogated, 11 fold over untreated, in p53-/- cells, indicating that p53 is a major regulator of miR34a asRNA expression.

### 2017-11-14 inst/suppFigure1c_polyadenylation/polyadenylation.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

---
title: "miR34a asRNA polyadenylation"
author: "Jason T. Serviss"
date: "01/02/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
We desired to access the polyadenylation status of the miR34a asRNA transcript.

#Methods
All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "miR34aAS_F1",
        "miR34aAS_R1",
        "miR34aHG_F",
        "miR34aHG_R",
        "B-actin_F",
        "B-actin_R",
        "U48_F",
        "U48_R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA",
        "AGT GAT GAT GAC CCC AGG TA",
        "GGT CAG AGC GCT GCG GTG AT"
    )
)
primers
```

#Results

<br></br>
<center><img src="../polyadenylation/polyadenylation.png" alt="some text"  width="500" height="500"></center>
<br></br>
Polyadenylation status of the spliced and unspliced variants of miR34a asRNA in HEK293t cells.

#Conslusion
miR34a asRNA appears to be polyadenylated.

### 2017-11-14 inst/suppFigure1e_cellularLocalization/cellularLocalization.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

---
title: "Cellular localisation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

##Introduction
AsRNAs are known to be capable of exerting regulatory functions on both a transcriptional and post-transcriptional level and therefore, the cellular localization of the asRNA can be informative concerning the method of regulation.

##Methods
All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 300,000 cells per well in a 6-well plate and cultured overnight. Fractionation was performed using the PARIS kit according to the manufacturer's recommendations (Life Technologies). 0.5ul RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
library(printr)
primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1",
        "U48_F",
        "U48_R"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "AGT GAT GAT GAC CCC AGG TA",
        "GGT CAG AGC GCT GCG GTG AT"

    )
)
primers
```

##Results
```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
library(scales)

data <- read.table('~/GitHub/miR34aFigures/inst/cellularLocalization/QPCRdata.txt', header=TRUE, sep="\t")
data$meanCt <- rowMeans(data[,c("Ct1", "Ct2")])
data$meanAntilog <- 2^-data$meanCt

sums <- ddply(
    data,
    c("gene"),
    summarize,
    total = sum(meanAntilog)
)

data <- merge(data, sums, by="gene")
data$percentage <- 100 * (data$meanAntilog / data$total)

#prepare for plotting
data$gene <- gsub("miR34a asRNA", "miR34a\nasRNA", data$gene)
data$gene <- gsub("miR34a HG", "miR34a\nHG", data$gene)
data$gene <- factor(data$gene, levels=c("miR34a\nasRNA", "miR34a\nHG", "B-actin", "RNU48"))
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for Rmarkdown
ggplot(data, aes(x=gene, y=percentage))+
    geom_bar(aes(fill=fraction), position="fill", stat="identity", alpha=0.6)+
    scale_y_continuous(labels = percent_format())+
    labs(
      x="Gene",
      y="%",
      title="miR34a asRNA cellular localization",
      caption=
            "Q-PCR results from fractionated HEK293T cells investigating the cellular localization of the miR34a asRNA transcript."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(fill = guide_legend(title = "Fraction", override.aes = list(size=3)))

#plot for pdf
p <- ggplot(data, aes(x=gene, y=percentage))+
    geom_bar(aes(fill=fraction), position="fill", stat="identity", alpha=0.6)+
    scale_y_continuous(labels = percent_format())+
    labs(
      x="Gene",
      y="%"
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=10,
            margin=margin(b=2, unit="mm")
        ),
        plot.margin = unit(c(0.1,0.1,0.1,0.1), "lines"),
        legend.position="top",
        legend.margin=unit(1,"mm"),
        legend.key.size = unit(1/5, "cm"),
        legend.title=element_text(size=9),
        legend.text=element_text(size=8),
        axis.title=element_text(size=9),
        axis.title.x=element_text(margin=margin(t=5)),
        axis.text.y=element_text(size=8),
        axis.text.x=element_text(size=7),
        strip.text.x=element_text(size=9, margin = margin(0.01, 0, 0.1, 0, "cm")),
        panel.border = element_rect(fill=NA, size=0.25),
        axis.ticks = element_line(size=0.25),
        axis.ticks.length = unit(1/15, "cm")
    )+
    guides(fill = guide_legend(title = "Fraction", override.aes = list(size=2)))

ggsave(plot=p, filename="~/GitHub/miR34aFigures/inst/cellularLocalization/cellularLocalization.pdf", device=cairo_pdf, height=60, width=83, units="mm")

```

##Conclusion
Semi-quantitative PCR revealed that the miR34a asRNA transcript localizes to both the nucleus and cytoplasm although the majority is located in the cytoplasmic fraction.

### 2017-11-14 inst/suppFigure2d_lnc34aCage/lnc34aCAGE.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

--- 2017-11-13 inst/lnc34aCage/lnc34aCAGE.Rmd
@@
 dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-url <- "lnc34aCAGE.rds"
+url <- "suppFigure2d_lnc34aCage.rds"
 cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%

### 2017-11-14 inst/suppFigure2e_lnc34aSplJnc/lnc34aSplJnc.Rmd
renamed all inst directories, corresponding data-raw files, and updated Rmd input path

--- 2017-11-13 inst/lnc34aSplJnc/lnc34aSplJnc.Rmd
@@
 dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-url <- "lnc34aSpliceJncs.rds"
+url <- "suppFigure2e_lnc34aSplJnc.rds"
 splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

### 2017-11-14 data-raw/saveRDA.R

@@ -2,7 +2,7 @@ library(tidyverse)
 library(miR34AasRNAproject)
 
 #HCTp53null
-read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/figure2a_HCT116p53null.txt', col_names = TRUE) %>%
   rename(gene = Target) %>%
   mutate(
     Condition = case_when(
@@ -31,10 +31,10 @@ read_tsv('./data-raw/HCTp53null.txt', col_names = TRUE) %>%
       levels = c("miR34a HG", "miR34a asRNA", "Actin")
     )
   ) %>%
-  write_rds(., path = './data/HCT116p53null.rds')
+  write_rds(., path = './data/figure2a_HCT116p53null.rds')
 
 #HctHekDox
-read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/figure2b_HctHekDox.txt', col_names = TRUE) %>%
   rename(
     `Biological Replicate` = experiment,
     `Cell line` = cellLine,
@@ -48,10 +48,10 @@ read_tsv('./data-raw/HctHekDox.txt', col_names = TRUE) %>%
     gene == "B-actin" ~ "Actin",
     TRUE              ~ gene
   )) %>%
-  write_rds(., path = './data/HctHekDox.rds')
+  write_rds(., path = './data/figure2b_HctHekDox.rds')
 
 #P1-HCTandHEK
-read_tsv('./data-raw/P1-HCTandHEK.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/figure2d_P1-HCTandHEK.txt', col_names = TRUE) %>%
   rename(
     `Biological Replicate` = experiment,
     `Cell line` = cellLine
@@ -64,10 +64,10 @@ read_tsv('./data-raw/P1-HCTandHEK.txt', col_names = TRUE) %>%
     ),
     construct = gsub("empty", "Empty", .data$construct)
   ) %>%
-  write_rds(., path = './data/P1-HCTandHEK.rds')
+  write_rds(., path = './data/figure2d_P1-HCTandHEK.rds')
 
 #p1shRNAdox
-read_tsv('./data-raw/p1shRNAdox.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/figure2e_P1shRNAdox.txt', col_names = TRUE) %>%
   rename(`Biological Replicate` = experiment) %>%
[…]

### 2017-11-14 inst/suppFigure2d_lnc34aCage/lnc34aCAGE.Rmd
added cell nrs to lnc34a analysis

@@
 
-Add number of cell lines included in figure.
-
 ```{r, message = FALSE}
@@
 
-[Wang et al.](https://www.ncbi.nlm.nih.gov/pubmed/27077950) have previously published concerning a antisense transcript arising from the miR34a locus that they named "lnc34a".
+[Wang et al.](https://elifesciences.org/articles/14620) have previously published concerning a antisense transcript arising from the miR34a locus that they named "lnc34a".
 Wang et al.
@@
 ####Methods
-All available CAGE data was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDA.R file.
-CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200) were filtered from the total data.
+
+```{r}
+nrCellLinesDown <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
+  url <- "suppFigure2d_lnc34aCage.txt"
+  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
+    pull(14) %>% 
+    gsub(
+      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCage(.*)Cell.*", 
+      "\\1",
+      .
+    ) %>%
+    unique() %>%
+    length()
+}
+
+cellLinesInFinal <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+  url <- "suppFigure2d_lnc34aCage.rds"
+  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+    pull(filename) %>%
+    gsub(
+      "^wgEncodeRikenCage(.*)Cell.*",
+      "\\1",
+      .
+    ) %>%
+    unique()
+}
+```
+
+All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDA.R file.
+Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
+These cell lines included: `r cellLinesInFinal()`.
 All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance.
 In addition, a density plot shows the distribution of the CAGE reads at in the specified interval.
-ADD NUMBER OF CELL LINES.
 

### 2017-11-14 inst/suppFigure2e_lnc34aSplJnc/lnc34aSplJnc.Rmd
added cell nrs to lnc34a analysis

@@
 </style>
-
-Add number of cell lines included in figure.
 
@@
 ####Methods
-All available splice junction data was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDA.R file.
-Spliced reads mapping to the plus strand of chromosome 1 and in regions corresponding to the lnc34a start (9241796) and transcription termination (9257102) sites were filtered from the total data.
+
+```{r}
+nrCellLinesDown <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
+  url <- "suppFigure2e_lnc34aSplJnc.txt"
+  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
+    pull(16) %>% 
+    gsub(
+      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeCshlLongRnaSeq/wgEncodeCshlLongRnaSeq(.*)Cell.*", 
+      "\\1",
+      .
+    ) %>%
+    unique() %>%
+    length()
+}
+
+cellLinesInFinal <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+  url <- "suppFigure2e_lnc34aSplJnc.rds"
+  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+    pull(filename) %>%
+    gsub(
+      "^wgEncodeCshlLongRnaSeq(.*)Cell.*",
+      "\\1",
+      .
+    ) %>%
+    unique()
+}
+```
+
+All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDA.R file.
+Of these cell lines `r cellLinesInFinal() %>% length()` cell lines had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
+Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`.
 All splice junctions were plotted and colored according to the number of reads corresponding to each.
-ADD NUMBER OF CELL LINES.
 

### 2017-11-14 R/processFigures.R
updated plotFigures scripts and associated to use only one docker file, easier to maintain. Also updated liftr.yml to included additional pkgs

@@ -1,7 +1,28 @@
 
+#' plotFigure
+#'
+#' Subtitle
+#'
+#' Imports count, sampleType, and count.ercc data to a sp.scRNAseq object.
+#'
+#' @name plotFigure
+#' @rdname plotFigure
+#' @aliases plotFigure
+#' @param figure Character;
+#' @param ... additional arguments to pass on.
+#' @return spCounts object.
+#' @author Jason T. Serviss
+#' @examples
+#'
+#' \dontrun{plotFigure("figure1a")
+#'
+NULL
+
+#' @rdname plotFigure
 #' @export
 #' @importFrom liftr lift render_docker
-plotFigure <- function(figure) {
+
+plotFigure <- function(figure, ...) {
   path <- getPath(figure)
   runDockerAndView(path)
 }
@@ -15,25 +36,34 @@ getPath <- function(figure) {
 
 makeMap <- function() {
   list(
-    figure1a = "miR34aLocus/figure1a.Rmd",
-    figure1b = "miR34aASExpressionCellPanel/figure1b.Rmd",
-    figure1c = "TCGAcorrelation/figure1c.Rmd",
-    figure1d = "3primeRACE/figure1d.Rmd",
-    figure1e = "primerWalk/figure1e.Rmd",
-    figure1f = "codingPotential/figure1f.Rmd",
-    figure2a = "HCT116p53null/figure2a.Rmd",
-    figure2b = "HctHekDox/figure2b.Rmd",
-    figure2c = "P1-HCTandHEK/figure2d.Rmd",
-    figure2d = "P1-HCTandHEK/figure2d.Rmd",
-    figure2e = "P1shRNAdox/figure2e.Rmd",
-    figure3a = "StableLineExpression/figure3a.Rmd",
-    figure3b = "StableLineCellCycle/figure3b.Rmd",
-    figure3c = "growthStarvation/figure3c.Rmd",
-    figure3d = "StableLinePolIIChIP/figure3d.Rmd",
-    figure3e = "survival/figure3e.Rmd",
-    suppFigure1a = "",
-    suppFigure1b = "",
-    suppFigure1c = ""
+    figure1a = "figure1a_miR34aLocus/figure1a.Rmd",
+    figure1b = "figure1b_miR34aASExpressionCellPanel/figure1b.Rmd",
+    figure1c = "figure1c_TCGAcorrelation/figure1c.Rmd",
[…]

### 2017-11-14 inst/figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 1c"
subtitle: "miR34a asRNA and miR34a TCGA correlation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

<br></br>

####_Methods_

<br></br>

####_Results_

<div class="caption">
A graphical depiction of the TCGA correlation analysis. Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
</div>

See Supplementary Figure 1a for R-squared and p-values corersponding with the analysis.

Insert code here from Erik and write Intro Methods etc

```{r, out.width = "1000px"}

url <- "figure1c_TCGAcorrelation/miR34a_RP3-510D11.2_diploid_only_edited.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<br></br>

####_Conclusions_

<br></br><br></br>

### 2017-11-14 inst/figure1e_primerWalk/figure1e_primerWalk.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 1e"
subtitle: "miR34a asRNA primer walk"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We desired to determine the 5'-start site for the miR34a asRNA.

<br></br>

####_Methods_

<br></br>

_Cell culture and PCR_

To accomplish this we performed the primer walk assay. All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was performed for 35 cycles at 62°C annealing temperature and the resulting products were analyzed on a 2% agarose gel.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "miR34aAS_F10",
        "miR34aAS_F11",
        "miR34aAS_F12",
        "miR34aAS_F13",
        "miR34aAS_F14",
        "miR34aAS_F15",
        "miR34aAS_R1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "ATC TGC GTG GTC ACC GAG AAG CA",
        "CGC ACG GAC TGA GAA ACA CAA G",
        "ACG GAG GCT ACA CAA TTG AAC AGG",
        "AGG GAA GAA AGA ACT AGC CGA GCA",
        "CAT TTG CTG CAA TAT CAC CGT GGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT"
    )
)
primers

```

<br></br>

####_Results_

Primer placement at the locus can be viewed in Supplementary Figure 1b.

```{r, out.width = "500px"}

url <- "figure1e_primerWalk/gel.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class = "caption">
The semi-quantitative PCR results from the primer walk assay performed using HEK293T cells.
</div>

<br></br>

####_Conclusion_

It appears as though the miR34a asRNA transcript start site is somewhat upstream of the annotated start site. Although there is some product present for the F12 primer, the majority of transcription seems to be originating from the F11 primer. This indicates that the start site is between 71-224bp upstream of the annotated start site.

<br></br><br></br>

### 2017-11-14 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 2a"
subtitle: "miR34a asRNA doxorubicin treatment of HCT116 p53 wt and null"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

miR34a is a known downstream target of p53 and has been previously shown to exhibit increased expression upon cellular apoptotic signaling. We hypothesized that miR34a asRNA may be regulated in a similar fashion whereby transcription is stimulated by activation of p53. To test this we treated p53 wild type and p53 null HCT116 cells with increasing concentrations of the DNA damaging agent doxorubicin and monitored miR34a asRNA expression.

<br></br>

####_Methods_

<br></br>

_Cell culture and QPCR_

HCT116 cells were cultured in DMEM high modified (Hyclone, GE healthcare) supplemented with supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum. 25 x 10^5 HCT116 cells were plated in 6 well plates. 24 hours later media was exchanged and doxorubicin was added to a final concentration of 100, 200 or 500 ng/ml. Cells were harvested for RNA extraction 24 hours later using trypsin. RNA was extracted using Nucleospin RNA kit (Machery-Nagel Ref. 740955) according to manufacturer‟s protocol and DNase treated using Ambion Turbo DNA-free according to manufacturer‟s protocol (Life Technologies Ref. AM1907). cDNA was synthesized using ~500 ng RNA with M-MLV (Life Technologies Ref 28025013) and a mixture of oligo(dT) with nanomers in accordance with the manufacturer's protocol. qPCR quantification was carried out using the PowerUp SYBR Green Master Mix (Thermo Fisher Scientific, Ref. A25777) on the CFX96 Touch Real-Time PCR Detection System: 50°C for 2 min, 95°C for 2min, and 95°C for 1 sec followed by 60°C for 30 sec repeated for 40 cycles. qPCR primers are shown below.

<br></br>

_Analysis_

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples. Three independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the p-53 wild type and p-53 null group's delta-delta ct values in each treatment concentration and for both genes.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "figure2a_HCT116p53null.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate dct
groups <- c("Condition", "Treatment", "Biological Replicate", "Cell line", "gene")
gois <- c("miR34a asRNA", "miR34a HG")

data <- technicalMeans(data, groups) %>%
  dct(., gois, Actin, groups)

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  Treatment = data$Treatment == 0
)

data <- data %>%
  ddct(., logical, groups) %>%
  folds(.)

#calculate stats
stats <- calcStats(data, Condition, "HCT116 p53-wt", groups) %>%
  pFormat(.)

#setup plotting variables
stats <- stats %>%
  group_by(GOI, Treatment) %>%
  mutate(
    max = max(CI95h),
    x = case_when(
      Treatment ==   0 ~ 1 + 0.25,
      Treatment == 100 ~ 2 + 0.25,
      Treatment == 200 ~ 3 + 0.25,
      Treatment == 500 ~ 4 + 0.25
    ),
    xend = case_when(
      Treatment ==   0 ~ 1 - 0.25,
      Treatment == 100 ~ 2 - 0.25,
      Treatment == 200 ~ 3 - 0.25,
      Treatment == 500 ~ 4 - 0.25
    )
  ) %>%
  ungroup()

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = Treatment, 
      y = log2fold,
      group = interaction(Condition, Treatment)
    ),
    trim = TRUE,
    alpha = 0.3,
    fill = "gray",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(x = Treatment, y = log2fold, fill = Condition),
    colour = NA,
    binwidth = 1/10,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis='y', 
    stackdir='center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  geom_point(
    data = stats,
    aes(x = Treatment, y = mean, group = Condition), 
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 6,
    shape = 95
  ) +
  facet_grid(. ~ GOI) +
  geom_linerange(
    data = stats,
    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(x = Treatment, y = max + 0.28, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = stats,
    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
    colour="grey43",
    show.legend = FALSE
  ) +
  scale_y_continuous("\u0394\u0394Ct", breaks = c(-1,0,1,2,3,4,5))+
  labs(
    x = "Treatment",
    title = "miR34a asRNA regulation by p53 induction"
  ) +
  guides(
    fill = guide_legend(title = "Cell line", override.aes = list(size = 6))
  )

plotRmarkdown(p)

```

<div class="caption">
Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in P53+/+ and p53-/- HCT116 cells. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusions_

We observed increasing miR34a HG and asRNA expression with increasing doses of doxorubicin indicating that these two transcripts are co-regulated by p53. Although p53 wild type cells showed a 25-fold increase over untreated cells in miR34a AS expression at the highest tested doxorubicin concentration, this effect was largely abrogated, 11 fold over untreated, in p53 null cells, indicating that p53 is a major regulator of miR34a asRNA expression.

<br></br><br></br>

### 2017-11-14 inst/figure2b_HctHekDox/figure2b_HctHekDox.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 2b"
subtitle: "miR34a asRNA expression in HCT116 and HEK293t upon doxorubicin treatment"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

miR34a is a known downstream target of p53 and has been previously shown to exhibit increased expression with cellular apoptotic signaling. We hypothesized that miR34a asRNA may be regulated in a similar fashion whereby transcription is stimulated by activation of p53. To test this we treated HCT116 and HEK293t cells with 200 ng/ml of the DNA damaging agent doxorubicin for 24 hours and monitored miR34a asRNA expression.

<br></br>

####_Methods_

<br></br>

_Cell culture and QPCR_

All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 300,000 cells per well in a 6-well plate and cultured overnight. The following day cells were treated with 0, 100, 200, or 500 ng/ml doxorubicin for 24hrs. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s. qPCR primers are shown below.

<br></br>

_Analysis_

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples. Three independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the treated vs untreated group's delta-delta ct values for both genes.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "figure2b_HctHekDox.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate dct
groups <- c("Treatment", "Biological Replicate", "Cell line", "gene")
gois <- c("miR34a asRNA", "miR34a HG")

data <- technicalMeans(data, groups) %>%
  dct(., gois, Actin, groups)

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  `Biological Replicate` = pull(data, `Biological Replicate`) == 1,
  Treatment = pull(data, Treatment) == "untreated"
)

data <- data %>%
  ddct(., logical, groups) %>%
  folds(.)

#calculate stats
stats <- calcStats(data, Treatment, "untreated", groups) %>%
  pFormat(.)

#prepare for plotting

#vertical lines and labels
vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    max = max(CI95h),
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI == "miR34a asRNA" ~ 1 - 0.25,
      GOI ==    "miR34a HG" ~ 1 + 0.25
    ),
    xend = case_when(
      GOI == "miR34a asRNA" ~ 2 - 0.25,
      GOI ==    "miR34a HG" ~ 2 + 0.25
    ),
    pFormat = pFormat,
    labelX = 1.5
  )

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = Treatment,
      y = log2fold,
      group = interaction(GOI, Treatment)
    ),
    trim = TRUE,
    fill = "gray",
    alpha = 0.3,
    color = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = Treatment,
      y = log2fold,
      fill = GOI
    ),
    binwidth = 1/10,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis='y', 
    stackdir='center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  geom_point(
    data = stats,
    aes(
      x = Treatment,
      y = mean,
      group = GOI
    ),
    size = 6,
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    colour = "gray20"
  ) +
  facet_grid(. ~ `Cell line`) +
  geom_linerange(
    data = stats,
    aes(
      x = Treatment,
      ymin = CI95l,
      ymax = CI95h,
      group = GOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = labelX,
      y = max + 0.25,
      label = pFormat,
      group = GOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS",
    position = position_dodge(width = 0.9)
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max + 0.1,
      xend = xend,
      yend = max + 0.1,
      group = GOI
    ),
    colour="grey43",
    show.legend = FALSE
  ) +
  scale_y_continuous(
    "\u0394\u0394Ct",
    breaks=c(-1,0,1,2,3,4,5)
  ) +
  labs(
    x = "Treatment",
    title = "miR34a asRNA response to p53 induction"
  ) +
  guides(
    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
  )

plotRmarkdown(p)

```

<div class="caption">
Q-PCR showing miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after treatment with 200 ng/ml doxorubicin for 24hrs. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusions_

We observed increases in miR34a HG and asRNA expression upon doxorubicin treatment indicating that these two transcripts are co-regulated.

<br></br><br></br>

### 2017-11-14 inst/figure2c_P1construct/figure2c_P1construct.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 2c"
subtitle: "Schematic representation of the P1 construct"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"

```

####_Introduction_

It is likely, due to the head-to head orientation of miR34a HG and asRNA, that transcription initiation may be activated from a single promoter in a bi-directional manner. To investigate whether miR34a HG and asRNA are transcribed from the same promoter as convergent transcripts, we cloned the miR34a HG promoter, including the p53 binding site, into a luciferase/renilla dual reporter vector which we hereafter refer to as p1. The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis. Mol Cell, 2007. 26(5): p. 731-43.

<br></br>

####_Methods_

<br></br>

_Cell culture, transfection and luminescence quantification_

All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 10,000 cells per well in a 96-well plate with a white bottom and cultured overnight. The following day cells were co-transfected with 10ng of empty, p1, or p2 plasmid and GFP using the standard lipofektamine 2000 (Life Technologies) protocol. The expression of GFP and luminescence was measured 24 h post transfection by using the Dual-Glo Luciferase Assay System (Promega) and detected by the GloMax-Multi+ Detection System (Promega). The expression of luminescence was normalized to GFP.

<br></br>

_Analysis_

Three independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the empty vs p1 group's log2 activity for both genes.

<br></br>

_Constructs_

```{r}

ps <- data.frame(
  name = c("p1"),
  sequence = c("GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
              CCT GCT C"
  )
)
ps

```

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "Luc_set_II_F",
        "Luc_set_II_R",
        "Renilla_pBiDir_F1",
        "Renilla_pBiDir_R1",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers

```

<br></br>

####_Results_

```{r, out.width = "850px"}

url <- "figure2c_P1construct/locusSimple.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class="caption">
A schematic representation of the miR34a locus and the region cloned in the P1 construct including the overlapping region between miR34a host gene (purple) and miR34a asRNA (green), the region cloned into the P1 construct (red), and the P53 binding site (light blue).
</div>

<br></br>

```{r, out.width = "850px"}

url <- "figure2c_P1construct/constructSimple.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class="caption">
A schematic representation of the fully cloned P1 construct including the overlapping region between miR34a host gene and miR34a asRNA (green), the reported genes, luciferase (purple) and renilla (red), the primer binding sites, and the shRNA binding site (used in Figure 2d).
</div>

<br></br>

*For all results and conclusions please see Figure 2d.

### 2017-11-14 inst/figure2d_P1-HCTandHEK/figure2d_P1-HCTandHEK.Rmd
ALL analysis moved from vignette to individual Rmds in inst

--- 2017-11-14 inst/figure2c_P1construct/figure2c_P1construct.Rmd
@@
 ---
-title: "Figure 2c"
-subtitle: "Schematic representation of the P1 construct"
+title: "Figure 2d"
+subtitle: "P1 transfections in HCT116 and HEK293t cells"
 author: "Jason T. Serviss"
@@
 projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
 
@@
 
-```{r, out.width = "850px"}
+*For a schematic representation of the P1 construct please see Figure 2c.
 
-url <- "figure2c_P1construct/locusSimple.png"
-knitr::include_graphics(file.path(projectUrl, url))
+```{r, message = FALSE}
+
+url <- "figure2d_P1-HCTandHEK.rds"
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+.calcP <- function(`Cell line`, gene, logValue, data) {
+  bool1 <- pull(data, `Cell line`) == `Cell line`
+  bool2 <- pull(data, gene) == gene
+  bool3 <- pull(data, construct) == "Empty"
+  bool <- bool1 & bool2 & bool3
+  t.test(logValue, pull(data, logValue)[bool])$p.value
+}
+
+data <- data %>%
+    mutate(logValue = log2(value))
+
+stats <- data %>%
+  group_by(`construct`, `Cell line`, gene) %>%
+  summarize(
+    n = n(),
+    mean = mean(logValue),
+    CI95l = t.test(logValue)$conf.int[1],
+    CI95h = t.test(logValue)$conf.int[2],
+    pValue = .calcP(`Cell line`, gene, logValue, data)
+  ) %>%
+  ungroup() %>%
+  pFormat(.)
+
+#vertical lines and labels in plot
+ys <- stats %>%
+  group_by(`Cell line`) %>%
+  summarize(max = max(CI95h))
+
+vl <- stats %>%
+  group_by(`Cell line`, gene) %>%
+  summarize(
+    pValue = as.numeric(min(pValue))
+  ) %>%
+  ungroup() %>%
+  pFormat(.) %>%
+  mutate(
+    x = case_when(
+      gene == "Renilla" ~ 1 + 0.25,
+      gene == "Luciferase" ~ 1 - 0.25
+    ),
+    xend = case_when(
+      gene == "Renilla" ~ 2 + 0.25,
+      gene == "Luciferase" ~ 2 - 0.25
+    ),
+    pFormat = pFormat
+  ) %>%
+  left_join(ys) %>%
+  mutate(max = max + c(0.25, 1, 0.25, 1))
+
+#fix gene labels
+data <- data %>%
+  mutate(plotGene = case_when(
+    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
+    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
+    TRUE ~ "somehow missed a gene"
+  ))
+
+stats <- stats %>%
+  mutate(plotGene = case_when(
+    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
+    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
+    TRUE ~ "somehow missed a gene"
+  ))
+
+vl <- vl %>%
+  mutate(plotGene = case_when(
+    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
+    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
+    TRUE ~ "somehow missed a gene"
+  ))
+
+```
+
+```{r, fig.align='center', fig.height=8, fig.width=12}
+
+data <- filter(data, construct %in% c("p1", "Empty"))
+stats <- filter(stats, construct %in% c("p1", "Empty"))
+
+p <- ggplot(data = NULL) +
+  geom_violin(
+    data = data,
+    aes(
+      x = construct,
+      y = logValue,
+      group = interaction(construct, plotGene)
+    ),
+    trim = TRUE,
+    alpha = 0.3,
+    fill = "gray",
+    color = NA,
+    scale = "width",
+    show.legend = FALSE
+  ) +
+  geom_dotplot(
+    data = data, 
+    aes(
+      x = construct,
+      y = logValue,
+      fill = plotGene
+    ),
+    binwidth = 1/10,
+    alpha = 0.5,
+    colour = NA,
+    position = position_dodge(width = 0.9), 
+    binaxis = 'y', 
+    stackdir = 'center',
+    dotsize = 2,
+    show.legend = TRUE
+  ) +
+  facet_grid(. ~ `Cell line`) +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = construct,
+      ymin = CI95l,
+      ymax = CI95h,
+      group = plotGene
+    ),
+    colour = "grey20",
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = construct,
+      y = mean,
+      group = plotGene
+    ),
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE,
+    colour = "gray20",
+    size = 6,
+    shape = 95
+  ) +
+  geom_label(
+    data = vl,
+    aes(
+      x = 1.5, 
+      y = max + 0.25, 
+      label = pFormat, 
+      group = gene
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 5,
+    family = "Arial Unicode MS",
+    position = position_dodge(width = 0.9)
+  ) +
+  geom_segment(
+    data = vl,
+    aes(
+      x = x,
+      y = max,
+      xend = xend,
+      yend = max
+    ),
+    colour = "grey43",
+    show.legend = FALSE
+  ) +
+  labs(
+    x = "Construct",
+    y = "log2 activity (a.u.)",
+    title = "miR34a asRNA regulation by miR34a promoter"
+  ) +
+  guides(
+    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
+  )
+
+plotRmarkdown(p)
 
@@
 <div class="caption">
-A schematic representation of the miR34a locus and the region cloned in the P1 construct including the overlapping region between miR34a host gene (purple) and miR34a asRNA (green), the region cloned into the P1 construct (red), and the P53 binding site (light blue).
+miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 or empty constructs.
+Luciferase represents miR34a HG and renilla represents miR34a asRNA.
+The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
 </div>
@@
 
-```{r, out.width = "850px"}
+####_Conclusion_
 
-url <- "figure2c_P1construct/constructSimple.png"
-knitr::include_graphics(file.path(projectUrl, url))
+Upon transfection of this construct in two separate cell lines we observed increases in both luciferase and renilla indicating that miR34a HG and asRNA expression is regulated by a single promoter contained within the p1 construct.
 
-```
-
-<div class="caption">
-A schematic representation of the fully cloned P1 construct including the overlapping region between miR34a host gene and miR34a asRNA (green), the reported genes, luciferase (purple) and renilla (red), the primer binding sites, and the shRNA binding site (used in Figure 2d).
-</div>
-
-<br></br>
-
-*For all results and conclusions please see Figure 2d.
+<br></br><br></br>

### 2017-11-14 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 2e"
subtitle: "P1 transfections with shRNA Renilla and doxorubicin treatment"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

Our previous results showed that miR34a HG and asRNA are simultaneously up-regulated in response to doxorubicin treatment leading us to consider the possibility that miR34a asRNA may be necessary for an appropriate miR34a response to apoptotic signaling. To explore this possibility we again utilized the p1 construct, co-transfecting it with an shRNA targeting renilla, and treating HCT116 cells with increasing levels of doxorubicin.

<br></br>

####_Methods_

<br></br>

_Cell culture, treatment, and QPCR_

We utilized the P1 construct where the overlapping region of miR34a HG and miR34a AS is cloned with luciferase downstream of miR34a HG and renilla downstream of miR34a AS. The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis. Mol Cell, 2007. 26(5): p. 731-43. All cell lines were cultured at 5% CO2 and 37° C with HCT116 cells cultured in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. 2.5x10^5 HCT116wt cells were seeded in a 12-well plate. After 24hrs these were co-transfected with the P1 construct (25ng) and shRenilla2.1 (250ng) using lipo2000 (Life Technologies) standard protocol. 24hrs post-transfection, doxorubicin treatment was initiated using 0, 300, or 500ng/ml. 24hrs post-treatment, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s. All constructs are shown below.

<br></br>

_Analysis_

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. delta-delta ct was calculated for each sample by subtracting the dct value for the corresponding shControl samples at treatment concentration 0. Three independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the shControl vs shRenilla group's delta-delta ct values.

<br></br>

_Constructs_

```{r}

p1 <- data.frame(
    name="p1",
    sequence="GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
              CCT GCT C"
)
p1

```

<br></br>

_shRNAs_

```{r}

shRNAs <- data.frame(
    name=c(
        "shRenilla2.1"
    ),
    sequence=c(
        "TAA CGG GAT TTC ACG AGG C"
    )
)
shRNAs

```

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "Luc_set_II_F",
        "Luc_set_II_R",
        "Renilla_pBiDir_F1",
        "Renilla_pBiDir_R1",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers

```

<br></br>

####_Results_

See Figure 2c for a schematic representation of the P1 construct.

```{r, message = FALSE}

url <- "figure2e_P1shRNAdox.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#Luciferase = miR34a HG
#Renilla = miR34a AS

#calculate dct
groups <- c("treatment", "Biological Replicate", "shRNA", "gene")
gois <- c("Luciferase", "Renilla")

data <- data %>%
  technicalMeans(., groups) %>%
  dct(., gois, Actin, groups)

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  `shRNA` = pull(data, shRNA) == "shRNA Control",
  treatment = pull(data, treatment) == 0
)

data <- data %>%
  ddct(., logical, groups, med = FALSE) %>%
  folds(.)

#calculate stats
stats <- calcStats(data, shRNA, "shRNA Control", groups) %>%
  pFormat(.)

#prepare for plotting
data <- data %>%
  mutate(plotGOI = case_when(
    GOI == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    GOI == "Renilla" ~ "       Renilla\n(miR34a asRNA)"
  ))

stats <- stats %>%
  mutate(plotGOI = case_when(
    GOI == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
    GOI == "Renilla" ~ "       Renilla\n(miR34a asRNA)"
  ))

```

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = treatment, 
      y = log2fold, 
      group = interaction(plotGOI, treatment)
    ),
    trim = TRUE,
    scale = "width",
    alpha = 0.3,
    colour = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = treatment,
      y = log2fold,
      fill = plotGOI
    ),
    binwidth = 1/10,
    alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  facet_grid(. ~ shRNA, scale = "free") +
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = CI95h + 0.2,
      label = pFormat,
      group = plotGOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    position = position_dodge(width = 0.9),
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Doxorubicin (ng/ml)",
    title = "HCT116"
  ) +
  guides(
    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
  )

plotRmarkdown(p)

```

<div class="caption">
HCT116 cells were co-transfected with the p1 construct and shRNA renilla or shRNA control and subsequently treated with increasing doses of doxorubicin. 24 hours post-treatment, cells were harvested and renilla and luciferase levels were measured using QPCR. Statistical testing compared the shRNA control with shRNA renilla transfected cells using the respective treatment condition. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown.
</div>

<br></br>

####_Conclusion_

Levels of luciferase were abrogated in the shRenilla-transfected cells compared to control shRNA-transfected cells. Collectively, these results indicate that miR34a asRNA positively regulates levels of miR34a HG and is crucial for a proper miR34a response to apoptotic stimuli.

<br></br><br></br>

### 2017-11-14 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 3a"
subtitle: "miR34a asRNA stable over-expression cell lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a. To this end, we stably over-expressed miR34a asRNA, using lentiviral transduction, in 3 different p53-null cell lines and monitored the effects on miR34a.

<br></br>

####_Methods_

<br></br>

_miR34a asRNA cloning_

RNA was harvested from U2OS cells using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was run using the miR34aAS_cloning_F4 and miR34aAS_cloning_Ex3_1 primers for 40 cycles at annealing temperature 58˚C and run on an agarose gel. Bands were excised and extracted using the QIAquick gel extraction kit (Qiagen). PCR products were cloned using the Strata Clone kit (Aligent) and sequenced (results below). The insert for the lentiviral construct (p-HIV-I2AG-U6) was subsequently sub-cloned from the sequenced plasmid using primers with PacI and NheI cleavage sites. The cloned transcript largley mirrors the GENCODE annotated transcript.

<br></br>

_Cloning primers_

```{r}

primers <- data.frame(
    name=c(
        "miR34aAS_cloning_F4",
        "miR34aAS_cloning_Ex3_1"
    ),
    sequence=c(
        "ACGCGTCTCTCCAGCCCGGGAT",
        "AATGATGGCCGCAACTAATGACGG"
    )
)
primers

```

<br></br>

_Sequencing results_

```{r}

construct <- data.frame(
    name="miR34a_asRNA",
    sequence="ACG CGT CTC TCC AGC CCG GGA TCC GGG GAG CTG GGC TGT CCC CAG ACC GAC GGG ACA GCG GCA
                TCT CCT CCA CCT GAA AAG GAA AGA GGA CCA GTT TGC AGG ACT CCG AAC TGG GCC CGC GAG ATC 
                TCC ACC TGC GCA AAA CGA AAG GGC GGA TTC TCC TTG GAC TCA CGA GGC AAC CGC TCC CCG GGG 
                TGA GAA CGG GGG ACT CAT TCC TCC GGC ACT GGG AGA AGA CGA TTC TTC AGG AGG AGG ACA GGG 
                AAG CGA ATG CTA CCC AGA TGT CTC AGT ATA CTG GCT CGC GGC ACA TCG GGC AAA TGA ACC TAT 
                CAG ATA ACA ACG GCA GAT CAG ATG CCT GAG CAT TCA GAA GCA ACA GCT GTG GAG CCC CCG TGG 
                GTT CAG AAG GCC TGG TTC CCG TCT CCA GAA GCC TGG CTC TCC TCC CTC CTG GGC CCA CTA CTT 
                TGG CTT CTT GTT CCT ACG TAC AAG GAG TTG CGA AGA AGG CAA CTC TTC CCC TCC CTG AAG CCA
                AAG GAA TGA AAC AGA CTA GGG CGG GAG AGG TGG CCA TCC GTC ATT AGT TGC GGC CAT CA"
)
construct

```

<br></br>

_Lentivirus production and infection_

HEK293T cells were transfected with viral and expression constructs using Lipofectamine 2000 (Life Technologies), after which viral supernatants were harvested 48 and 72 hours post-transfection. Viral particles were concentrated using PEG-IT solution (Systems Biosciences) according to the manufacturer’s recommendations. HEK293T cells were used for virus titration and GFP expression was evaluated 72hrs post-infection via flow cytometry after which TU/ml was calculated. Cell lines were subsequently infected with the lentiviral particals using a multuplicity of infection = 1. After 48 hours, cells were placed under mycophenolic acid selection and the selection process was monitored using GFP expression via flow cytometry. When GFP expression was present in >90% of the cells, cells were frozen for downstream analysis.

<br></br>

_QPCR_

RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s. QPCR for miRNA expression analysis was performed according to the protocol for the TaqMan microRNA Assay kit (Life Technologies) with primer/probe sets purchased from the same company (TaqMan® MicroRNA Assay, hsa-miR-34a, human and Control miRNA Assay, RNU48, human) and the same cycling scheme as above. QPCR primers are shown below.

<br></br>

_Analysis_

Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates. delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples. At least three independant experiments (biological replicates) were performed in total (see more below). The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.

<br></br>

The sample numbers for each group are as follows:
```{r}

n <- data.frame(
  name = c(
    "PC3 mock",
    "PC3 miR34a asRNA",
    "Skov3 mock",
    "Skov3 miR34a asRNA",
    "Saos2 mock",
    "Saos2 miR34a asRNA"
  ),
  n = c(3, 5, 4, 4, 5, 5)
)
n

```

<br></br>

_QPCR primers_

```{r}

primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "figure3a_stableLineExpression.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#remove Skov exp 1 due to variability in technical replicates
data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")

#Have to divide the analysis due to the presence of several house 
#keeping genes.
gois1 <- c("miR34a asRNA", "Actin")
gois2 <- c("miR34a", "RNU48")
data1 <- filter(data, gene %in% gois1)
data2 <- filter(data, gene %in% gois2)

#calculate dct
groups <- c("Genetic mod", "Biological Replicate", "Cell line", "gene")

data1 <- data1 %>%
  technicalMeans(., groups) %>%
  dct(., gois1, Actin, groups) %>%
  mutate(GOI = as.character(GOI))

data2 <- data2 %>%
  technicalMeans(., groups) %>%
  dct(., gois2, RNU48, groups) %>%
  mutate(GOI = as.character(GOI))

data <- bind_rows(data1, data2) %>%
  mutate(GOI = parse_factor(GOI, levels = c("miR34a asRNA", "miR34a")))

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  `Biological Replicate` = pull(data, `Biological Replicate`) == 2,
  `Genetic mod` = pull(data, `Genetic mod`) == "mock"
)

data <- data %>%
  ddct(., logical, groups) %>%
  folds(.)

#calculate stats
stats <- calcStats(data, `Genetic mod`, "mock", groups) %>%
  pFormat(.)

#format for plotting
lev <- c("PC3\nmock", "PC3\nmiR34a asRNA", "Skov3\nmock", "Skov3\nmiR34a asRNA", "Saos2\nmock",   "Saos2\nmiR34a asRNA")

data <- data %>%
  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
  mutate(Condition = parse_factor(Condition, levels = lev))

stats <- stats %>%
  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
  mutate(Condition = parse_factor(Condition, levels = lev))

#vertical lines and labels in plot
ys <- stats %>%
  group_by(`Cell line`) %>%
  summarize(max = max(CI95h))

vl <- stats %>%
  group_by(`Cell line`, GOI) %>%
  summarize(
    pValue = as.numeric(min(pValue))
  ) %>%
  ungroup() %>%
  pFormat(.) %>%
  mutate(
    x = case_when(
      GOI ==    "miR34a" ~ 1 + 0.25,
      GOI == "miR34a asRNA" ~ 1 - 0.25
    ),
    xend = case_when(
      GOI ==    "miR34a" ~ 2 + 0.25,
      GOI == "miR34a asRNA" ~ 2 - 0.25
    )
  ) %>%
  inner_join(ys) %>%
  mutate(
    max = max + c(0.25, 1, 0.25, 1, 0.25, 1)
  )
```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = Condition,
      y = log2fold,
      group = interaction(Condition, GOI)
    ),
    trim = TRUE,
    alpha = 0.5,
    fill = "grey",
    colour = NA,
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = Condition,
      y = log2fold,
      fill = GOI,
      group = interaction(Condition, GOI)
    ),
    binwidth = 1/10,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scales = "free", 
    space = "free"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Condition,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(Condition, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = Condition,
      y = mean,
      group = interaction(Condition, GOI)
    ),
    colour = "gray20",
    shape = 95,
    size = 6,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.25, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 3
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    show.legend = FALSE
  ) +
  scale_y_continuous("\u0394\u0394Ct")+
  labs(
    x = "Cell line",
    title = "miR34a asRNA over-expressing cell lines"
  ) +
  guides(
    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
  )

plotRmarkdown(p)

```

<div class="caption">
miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control. The points represent the values obtained from each independant experiment (n >= 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusion_

miR34a asRNA over-expression causes a concominant up-regulation of miR34a in all 3 cell lines. This indicates that miR34a asRNA concordantly regulates miR34a.

<br></br><br></br>

### 2017-11-14 inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 3b"
subtitle: "miR34a asRNA stable cell line cell cycle"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

miR34a is known to regulate cell cycle and, specifically, induce G1-phase arrest. Due to the increase observed in miR34a expression levels in cell lines over-expressing miR34a asRNA, we investigated if the cell cycle was perturbed in these cells.

<br></br>

####_Methods_

<br></br>

_Cell culture and cell cycle analysis_

All cell lines were cultured at 5% CO2 and 37° C with Skov3 and PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. 1x10^5 cells per well in a 6-well plate and harvested after 24hrs. Cells were washed in PBS and fixed in 4% PFA at room temperature overnight. PFA was removed, and cells were resuspended in 95% EtOH. The samples were then rehydrated in distilled water, stained with DAPI and analyzed by flow cytometry on a LSRII (BD Biosciences) machine.

<br></br>

_Analysis_
Write the software used to quantify the cell cycle phases.

Percentages were converted to log2 fractions for each sample. Student's t-test was used for statistical analysis comparing the mock vs miR34a asRNA overespression conditions using five (PC3) or three (Skov3) independant experiments.

####_Results_

```{r, message = FALSE}

url <- "figure3b_stableLineCellCycle.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#convert the value (precent) to log2(fraction)
data <- mutate(data, value = log2(value / 100))

#qqplot shows that the data is reasonably normal. The shapiro test is also used below. Note that a p < 0.05 indicates non-normality.
#qqnorm(data$value)

#calculate stats
stats <- data %>%
  full_join(
    filter(data, condition == "mock"), 
    by = c("Biological Replicate", "Cell line", "phase"), 
    suffix = c("", ".y")
  ) %>%
  group_by(`Cell line`, condition, phase) %>%
  summarize(
    n = n(),
    mean = (2^mean(.data$value)),
    max = (2^max(.data$value)),
    CI95l = (2^t.test(.data$value)$conf.int[1]),
    CI95h = (2^t.test(.data$value)$conf.int[2]),
    pValue = t.test(.data$value, .data$value.y)$p.value,
    shapiroTest = shapiro.test(value)$p.value
  ) %>%
  ungroup() %>%
  pFormat(.)

#prepare for plotting
#change value back to percent
data <- data %>%
  mutate(value = 2^value)

#calculate start and end for horizontal plot lines
stats <- stats %>%
  group_by(phase, `Cell line`) %>%
  mutate(y = max(c(.data$CI95h, .data$max))) %>%
  ungroup() %>%
  arrange(`Cell line`, phase) %>%
  mutate(
    x = rep(sort(rep(1:3, 2)), 2) - 0.25,
    xend = rep(sort(rep(1:3, 2)), 2) + 0.25
  )

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = phase, 
      y = value,
      group = interaction(phase, condition)
    ),
    scale = "width",
    alpha = 0.3,
    fill = "gray",
    weight = 10,
    trim = TRUE,
    color = NA,
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = phase,
      y = value,
      fill = condition
    ),
    binwidth = 1/100,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 0.5,
    show.legend = TRUE
  ) +
  facet_grid(
    . ~ `Cell line`, 
    scale = "free"
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = phase, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = interaction(phase, condition)
    ),
    position = position_dodge(width = 0.9),
    colour = "grey25",
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = phase, 
      y = mean, 
      group = condition
    ), 
    colour = "black",
    position = position_dodge(width = 0.9),
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_segment(
    data = stats,
    aes(
      x = x,
      y = y + 0.01, 
      xend = xend, 
      yend = y + 0.01
    ),
    colour = "grey43",
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = phase, 
      y = y + 0.02, 
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 3,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    x = "Cell cycle phase",
    y = "",
    title = "Cell cycle"
  ) +
  guides(
    fill = guide_legend(title = "Condition", override.aes = list(size = 6))
  )

plotRmarkdown(p)

```

<div class="caption">
Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control. The points represent the values obtained from each independant experiment (PC3 n = 5; Skov3 n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusion_

An increase in the percentage of cells in G1-phase can be seen in cell lines overexpressing miR34a asRNA. In addition, a concominant decrease of cells in G2-phase can be observed.

<br></br><br></br>

### 2017-11-14 inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 3c"
subtitle: "Monitoring growth of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

As p53 is a well-known regulator of senescence, growth, and apoptosis and has been shown to specifically important under conditions of cellular stress, such as starvation. Therefore, we investigated whether overexpression of miR34a AS affects growth rate under normal and starvation conditions by measuring changes in confluency over time.

<br></br>

####_Methods_

<br></br>

_Cell culture and confluency quantification_

10^4 PC3 cells, either miR34a asRNA overexpressing or WT, were seeded in 96 well plates. After attachment (3-4h) media was replaced with either RPMI (Gibco, life technology) (supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum) or HBSS. Cells were incubated in Spark Multimode Microplate reader for 48 hours at 37°C with 5% CO2 in a humidity chamber. Confluency was measured every hour.

<br></br>

_Analysis_

Three technical triplicates were included in each experiment and these were independantly normalized for each condition to the 0 time point afterwhich the mean was calculated. The 95% confidence interval was then calculated based on the three independant experiments which were preformed.

<br></br>

####_Results_

```{r, message = FALSE}

url <- "figure3c_stableLineGrowthStarvation.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize to first time point for control (Mock)
.normFun <- function(
  data,
  Confluency,
  Treatment,
  Biological.Replicate,
  Technical.Replicate,
  Cell.line
){
  bool1 <- data$Treatment == Treatment
  bool2 <- data$`Biological Replicate` == Biological.Replicate
  bool3 <- data$`Technical Replicate` == Technical.Replicate
  bool4 <- data$Time == 0
  bool5 <- data$`Cell line` == Cell.line
  bool <- bool1 & bool2 & bool3 & bool4 & bool5
  Confluency / pull(data, Confluency)[bool]
}

data <- data %>%
  group_by(Treatment, `Biological Replicate`, `Technical Replicate`, Time, `Cell line`) %>%
  mutate(
    normConfluency = .normFun(
      data,
      Confluency,
      Treatment,
      `Biological Replicate`,
      `Technical Replicate`,
      `Cell line`
    )
  ) %>%
  ungroup()

#calculate mean for each technical replicate
data <- data %>%
  group_by(Treatment, `Biological Replicate`, Time, `Cell line`) %>%
  summarize(
    techMean = mean(normConfluency)
  ) %>%
  ungroup()

#calculate stats
stats <- data %>%
  filter(Time != 0) %>%
  group_by(`Cell line`, Treatment, Time) %>%
  summarize(
    min = min(techMean),
    max = max(techMean),
    mean = mean(techMean),
    median = median(techMean),
    CI95l = t.test(techMean)$conf.int[1],
    CI95h = t.test(techMean)$conf.int[2]
  )

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_ribbon(
    data = stats,
    aes(
      x = Time,
      ymin = CI95l, 
      ymax = CI95h, 
      group = `Cell line`,
      fill = `Cell line`
    ), 
    alpha = 0.2,
    show.legend = FALSE
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) +
  facet_grid(. ~ Treatment) +
  scale_x_discrete(breaks = seq(0, 35, 5)) +
  labs(
    x = "Time (hours)", 
    y = "Normalized % confluency",
    title = "miR34a asRNA's role in growth regulation."
  ) + 
  guides(
    colour = guide_legend(title = "Cell line", override.aes = list(size = 3))
  )

plotRmarkdown(p)

```

<div class="caption">
The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line. The points represent the mean values obtained from each independant experiment (n = 3) whereas, the shadow represents 95% confidence interval, and the vertical line represents the minimum and maximum values from the independant experiments.
</div>

<br></br>

####_Conclusions_

miR34a asRNA overexpression causes a minor decrease in cell growth under normal conditions (RPMI) although under conditions of cellular stress through starvation, this effect is increased dramatically.

<br></br><br></br>

### 2017-11-14 inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Figure 3d"
subtitle: "PC3 stable line pollII ChIP"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

miR34a asRNA over-expression was shown to increase the expression levels of miR34a. We investigated if this increase of miR34a was due to increased levels of transcription at the miR34a promoter.

<br></br>

####_Methods_

<br></br>

_Cell culture, QPCR, and ChIP_

All cell lines were cultured at 5% CO2 and 37° C with Skov3 and PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine and Saos2 cells cultured in DMEM high modified (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 2-3x10^6 cells in a 15cm dish and incubated overnight. Cells were cross-linked in 1% formaldehyde, quenched in glycine (0.125M), resuspended in cell lysis buffer (5mM PIPES, 85mM KCL, 0.5% NP40, protease inhibitor), and sonicated (Bioruptor Sonicator Diagenode) in nucleus lysis buffer (50mM TRIS-HCL pH 8.0, 10mM EDTA, 1% SDS, protease inhibitor). The samples were incubated overnight at 4 °C with the appropriate antibody. Salmon sperm DNA/Protein A–agarose (Upstate/Millipore) was used to pull down the antibody. DNA was eluted in elution buffer (1% SDS, 100 mM NaHCO3), followed by reverse cross-linking, RNase-A and protease-K treatment. The DNA was eluted by using a Qiagen PCR purification kit. The following antibodies were used (4 μg/sample): phospho-polymerase II (abcam: ab5095). QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

<br></br>

_Analysis_

QPCR was performed in technical replicate for each sample and the mean of the technical replicates was subsequently used to calculate the fraction of input. The fold change of the miR34a asRNA overexpression samples was then calculated by dividing the values by the values for the corresponding mock samples. The fold values were then log2 transformed and the Student's t-test was used to test for significant differences under the null hypothesis that the true mean value of log2 transformed fold changes were equal to 0.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "miR34aChIP F1",
        "miR34aChIP R1"
    ),
    sequence=c(
       "AAA GTT TGC AAA GAA GGA GGC GGG",
       "AGG GAA GAA AGA ACT AGC CGA GCA"
    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "figure3d_stableLinePolIIChIP.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate means of technical replicates
data <- mutate(data, techMean = rowMeans(select(data, Quantity1, Quantity2)))

#calculate fraction of input
.fractionOfInput <- function(data, techMean, Biological.Replicate, condition) {
  bool1 <- data$`Biological Replicate` == Biological.Replicate
  bool2 <- data$condition == condition
  bool3 <- data$sample == "input"
  bool <- bool1 & bool2 & bool3
  techMean / pull(data, techMean)[bool]
}

data <- data %>%
  group_by(`Biological Replicate`, condition, sample) %>%
  mutate(fractionInput = .fractionOfInput(data, techMean, `Biological Replicate`, condition)) %>%
  ungroup() %>%
  filter(sample != "input")

#calculate fold over mock
.foldOverControl <- function(data, fractionInput, Biological.Replicate) {
  bool1 <- data$`Biological Replicate` == 3
  bool2 <- data$condition == "PC3 mock"
  bool <- bool1 & bool2
  fractionInput / pull(data, fractionInput)[bool]
}

data <- data %>%
  mutate(
    foldOverControl = .foldOverControl(data, fractionInput, `Biological Replicate`),
    logfoldOverControl= log2(foldOverControl)
  ) %>%
  ungroup()

#calculate stats 
stats <- data %>%
  group_by(condition) %>%
  summarize(
    n = n(),
    mean = mean(logfoldOverControl),
    CI95l =t.test(logfoldOverControl)$conf.int[1],
    CI95h =t.test(logfoldOverControl)$conf.int[2],
    pValue = t.test(logfoldOverControl, mu = 0)$p.value
  ) %>%
  pFormat(.) %>%
  mutate(pFormat = case_when(
    condition == "PC3 mock" ~ "", 
    TRUE ~ pFormat
  ))

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL)+
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = logfoldOverControl,
      group = condition
    ),
    trim = TRUE,
    alpha = 0.3,
    colour = NA,
    fill = "gray",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition, 
      y = logfoldOverControl, 
      fill = condition
    ),
    binwidth = 1/10,
    alpha = 0.5,
    colour = NA,
    position = position_dodge(width = 0.9), 
    binaxis='y', 
    stackdir='center',
    dotsize = 2,
    show.legend = TRUE
  ) +
  geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a asRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("log2(Fold)") +
  labs(
    x = "Cell line",
    y = "log2(Fold polII enrichment)",
    title = "Phosphorylated Poll II ChIP"
  ) +
  guides(fill = FALSE)

plotRmarkdown(p)

```

<div class="caption">
Phosphorylated Poll II ChIP in miR34a asRNA over-expressing PC3 stable cell lines compared to their respective mock control. The points represent the values obtained from each independant experiment (n = 4) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusion_

Phosphorylated pol-II was increased at the miR34a promoter in miR34a asRNA over-expressing cell lines indicating that the regulation of miR34a by miR34a asRNA is transcriptional.

<br></br><br></br>

### 2017-11-14 inst/suppFigure1a_TCGAcorrelationTable/suppFigure1a_TCGAcorrelationTable.Rmd
ALL analysis moved from vignette to individual Rmds in inst

--- 2017-11-14 inst/figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.Rmd
@@
 ---
-title: "Figure 1c"
-subtitle: "miR34a asRNA and miR34a TCGA correlation"
+title: "Supplementary Figure 1a"
+subtitle: "TCGA correlation table"
 author: "Jason T. Serviss"
@@
 
-####_Introduction_
-
 <br></br>
 
-####_Methods_
+```{r, out.width = "850px"}
 
-<br></br>
-
-####_Results_
-
-<div class="caption">
-A graphical depiction of the TCGA correlation analysis.
-Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
-</div>
-
-See Supplementary Figure 1a for R-squared and p-values corersponding with the analysis.
-
-Insert code here from Erik and write Intro Methods etc
-
-```{r, out.width = "1000px"}
-
-url <- "figure1c_TCGAcorrelation/miR34a_RP3-510D11.2_diploid_only_edited.png"
+url <- "suppFigure1a_TCGAcorrelationTable/table.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 
-<br></br>
-
-####_Conclusions_
+<div class = "caption">
+R-squared and p-values from the correlation analysis investigating the correlation between miR34a and miR34a asRNA expression in p53 wild type (wt) and mutated (mut) samples within TCGA cancer types.
+Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
+</div>
 

### 2017-11-14 inst/suppFigure1b_primerWalkSchematic/suppFigure1b_primerWalkSchematic.Rmd
ALL analysis moved from vignette to individual Rmds in inst

--- 2017-11-14 inst/suppFigure1a_TCGAcorrelationTable/suppFigure1a_TCGAcorrelationTable.Rmd
@@
 ---
-title: "Supplementary Figure 1a"
-subtitle: "TCGA correlation table"
+title: "Supplementary Figure 1b"
+subtitle: "Primer walk schematic"
 author: "Jason T. Serviss"
@@
 
-url <- "suppFigure1a_TCGAcorrelationTable/table.png"
+url <- "suppFigure1b_primerWalkSchematic/schematic_hg38.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class = "caption">
-R-squared and p-values from the correlation analysis investigating the correlation between miR34a and miR34a asRNA expression in p53 wild type (wt) and mutated (mut) samples within TCGA cancer types.
-Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
+A schematic picture of the miR34a asRNA locus including the location of the primers used in the primer walk assay.
 </div>
 
-<br></br><br></br>
+<br></br>

### 2017-11-14 inst/suppFigure1c_polyadenylation/suppFigure1c_polyadenylation.Rmd
ALL analysis moved from vignette to individual Rmds in inst

--- 2017-11-14 inst/figure1e_primerWalk/figure1e_primerWalk.Rmd
@@
 ---
-title: "Figure 1e"
-subtitle: "miR34a asRNA primer walk"
+title: "Supplementary figure 1c"
+subtitle: "miR34a asRNA polyadenylation"
 author: "Jason T. Serviss"
@@
 
-We desired to determine the 5'-start site for the miR34a asRNA.
+We desired to access the polyadenylation status of the miR34a asRNA transcript.
 
@@
 _Cell culture and PCR_
-
-To accomplish this we performed the primer walk assay.
 All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone).
@@
 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.
-PCR was performed for 35 cycles at 62°C annealing temperature and the resulting products were analyzed on a 2% agarose gel.
+PCR was then performed and the results analyzed on a 2% agarose gel.
 
@@
     name=c(
-        "miR34aAS_F10",
-        "miR34aAS_F11",
-        "miR34aAS_F12",
-        "miR34aAS_F13",
-        "miR34aAS_F14",
-        "miR34aAS_F15",
-        "miR34aAS_R1"
+        "miR34aAS_F1",
+        "miR34aAS_R1",
+        "miR34aHG_F",
+        "miR34aHG_R",
+        "B-actin_F",
+        "B-actin_R",
+        "U48_F",
+        "U48_R"
     ),
     sequence=c(
-        "ACG CGT CTC TCC AGC CCG GGA T",
-        "ATC TGC GTG GTC ACC GAG AAG CA",
-        "CGC ACG GAC TGA GAA ACA CAA G",
-        "ACG GAG GCT ACA CAA TTG AAC AGG",
-        "AGG GAA GAA AGA ACT AGC CGA GCA",
-        "CAT TTG CTG CAA TAT CAC CGT GGC",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA",
+        "AGT GAT GAT GAC CCC AGG TA",
+        "GGT CAG AGC GCT GCG GTG AT"
     )
@@
 
-Primer placement at the locus can be viewed in Supplementary Figure 1b.
-
 ```{r, out.width = "500px"}
 
-url <- "figure1e_primerWalk/gel.png"
+url <- "suppFigure1c_polyadenylation/polyadenylation.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class = "caption">
-The semi-quantitative PCR results from the primer walk assay performed using HEK293T cells.
+Polyadenylation status of spliced and unspliced miR34a asRNA in HEK293T cells. 
 </div>
@@
 
-####_Conclusion_
+####_Conclusions_
 
-It appears as though the miR34a asRNA transcript start site is somewhat upstream of the annotated start site.
-Although there is some product present for the F12 primer, the majority of transcription seems to be originating from the F11 primer.
-This indicates that the start site is between 71-224bp upstream of the annotated start site.
+Results indicate that miR34a asRNA is polyadenylated.
 

### 2017-11-14 inst/suppFigure1e_cellularLocalization/suppFigure1e_cellularLocalization.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Supplementary Figure 1e"
subtitle: "miR34a asRNA cellular localisation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

asRNAs are known to be capable of exerting regulatory functions on both a transcriptional and post-transcriptional level and therefore, the cellular localization of the asRNA can be informative concerning the method of regulation.

<br></br>

####_Methods_

<br></br>

_Cell culture and QPCR_

All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were plated at 300,000 cells per well in a 6-well plate and cultured overnight. Fractionation was performed using the PARIS kit according to the manufacturer's recommendations (Life Technologies). 0.5ul RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

<br></br>

_Analysis_

QPCR was performed in technical replicate for each sample. Technical mean values were subsequently moved to the linear scale by raising their additive inverse to the power of 2. The percentage in each cellular fraction fraction was then calculated by dividing each individual fraction for a specific gene by the total of all fractions for that gene and multiplying by 100. The experiment was performed in one independant experiment.

<br></br>

_QPCR primers_

```{r}

primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1",
        "U48_F",
        "U48_R"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "AGT GAT GAT GAC CCC AGG TA",
        "GGT CAG AGC GCT GCG GTG AT"

    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "suppFigure1e_cellularLocalization.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate dct
groups <- c("fraction", "Cell line", "gene")
gois <- c("miR34a\nasRNA", "miR34a\nHG")

data <- data %>%
  technicalMeans(., groups) %>%
  mutate(antiLog = 2^-ctMean) %>%
  group_by(gene) %>%
  mutate(
    total = sum(antiLog),
    percent = 100 * (antiLog / total)
  )

```

```{r, fig.align='center', fig.height=8, fig.width=12, message=FALSE, warning=FALSE}

p <- ggplot(data = NULL) +
  geom_bar(
    data = data,
      aes(
        x = gene,
        y = percent,
        fill = fraction
      ),
      position = "fill",
      stat = "identity",
      alpha = 0.6
    ) +
    labs(
      x = "Gene",
      y = "",
      title = "miR34a asRNA cellular localization"
    ) +
    scale_y_continuous(labels = scales::percent_format()) +
    guides(fill = guide_legend(title = "Fraction", override.aes = list(size = 3)))

plotRmarkdown(p)

```

<div class="caption">
Q-PCR results from fractionated HEK293T cells investigating the cellular localization of the miR34a asRNA transcript.
</div>

<br></br>

####_Conclusion_

Semi-quantitative PCR revealed that the miR34a asRNA transcript localizes to both the nucleus and cytoplasm although the majority is located in the cytoplasmic fraction.

<br></br><br></br>

### 2017-11-14 inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Supplementary Figure 1f"
subtitle: "miR34a asRNA transcript stability"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We desired to deduce the relative stability of the miR34a asRNA and HG transcripts.

<br></br>

####_Methods_

<br></br>

_Cell culture and QPCR_

All cell lines were cultured at 5% CO2 and 37° C with U2OS cells grown in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were treated with 10nM actinomycin D (Sigma) for the indicated times. RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

<br></br>

_Analysis_

QPCR was performed with technical replicates for each sample. Delta ct was calculated by subtracting the mean of the technical replicates for each sample from the mean of the technical replicates for the house keeping gene for the corresponding sample. Delta-delta ct was subsequently calculated by subtracting the delta ct values for the no treatment sample from the delat ct values for each individual sample. The experiment was performed in two independant experiments which are shown individually in the plot below. 95% confidence interval was calculated for each gene and treatment time point using the values obtained from each independant experiment.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG_F",
        "miR34a HG_R",
        "miR34a_asF1",
        "miR34a_asR1"

    ),
    sequence=c(
        "AGGTCATCACCATTGGCAATGAG",
        "CTTTCGGGATGTCCACGTCA",
        "TCTGCTCCAGTGGCTGATGAGAAA",
        "GTTCACTGGCCTCAAAGTTGGCAT",
        "AGCGGCATCTCCTCCACCTGAAA",
        "TTGCCTCGTGAGTCCAAGGAGAAT"

    )
)
primers

```

<br></br>

####_Results_

```{r, message = FALSE}

url <- "suppFigure1f_transcriptStability.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate dct
groups <- c("treatment", "Biological Replicate", "gene")
gois <- c("miR34a asRNA", "miR34a HG")

data <- technicalMeans(data, groups) %>%
  dct(., gois, Actin, groups, F)

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  treatment = data$treatment == 0
)

data <- data %>%
  ddct(., logical, groups, F) %>%
  folds(.)

#calculate stats
stats <- data %>%
  group_by(GOI, treatment) %>%
  summarize(mean = mean(log2fold), sd = sd(log2fold)) %>%
  ungroup()

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL)+
  geom_point(
    data = data,
    aes(
      x = treatment,
      y = log2fold,
      colour = GOI
    ),
    fill = "white",
    size = 4,
    alpha = 0.6,
    position = position_dodge(width = 0.9)
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = treatment,
      ymin = mean - sd,
      ymax = mean + sd,
      group = GOI
    ),
    colour = "black",
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment,
      y = mean,
      group = GOI
    ),
    colour = "black",
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    shape = 95,
    size = 6
  ) +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Treatment (hours)",
    title = "miR34a asRNA and HG stability"
  ) +
  guides(color = guide_legend(title = "Gene", override.aes = list(size = 3)))

plotRmarkdown(p)

```

<div class="caption">
Q-PCR showing miR34a asRNA and miR34a HG levels in U2OS cells after treatment with 10nM actinomycin D. The points represent the values obtained from each independant experiment (n = 2). 95% confidence interval (vertical black lines) and mean (horizontal black lines) are also shown.
</div>

<br></br>

####_Conclusions_

While the levels of miR34a HG fall quickly over the 4 hour treatment period, levels of miR34a asRNA remain relativley stable.

<br></br><br></br>

### 2017-11-14 inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.Rmd
ALL analysis moved from vignette to individual Rmds in inst

--- 2017-11-14 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
@@
 ---
-title: "Figure 3a"
-subtitle: "miR34a asRNA stable over-expression cell lines"
+title: "Supplementary Figure 2a"
+subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293t"
 author: "Jason T. Serviss"
@@
 
-We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a.
-To this end, we stably over-expressed miR34a asRNA, using lentiviral transduction, in 3 different p53-null cell lines and monitored the effects on miR34a.
+miR34a asRNA over-expressing cell lines, previously generated, showed a high overexpression level of miR34a asRNA despite a low multiplicity of infection.
+This is most likley due to the fact that all infected cell lines have practically no endogenous miR34a asRNA expression.
+To investigate the physiological relevance of the over-expression the miR34a asRNA levels were compared to the expression levels in HEK293t cells, which have a high endogenous miR34a expression level.
 
@@
 QPCR for miRNA expression analysis was performed according to the protocol for the TaqMan microRNA Assay kit (Life Technologies) with primer/probe sets purchased from the same company (TaqMan® MicroRNA Assay, hsa-miR-34a, human and Control miRNA Assay, RNU48, human) and the same cycling scheme as above.
-QPCR primers are shown below.
 
@@
 Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates.
-delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples.
-At least three independant experiments (biological replicates) were performed in total (see more below).
-The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.
+Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples.
+Five independant experiments were performed in total for all cell lines with the exception of PC3.
+Six independant experiments were preformed for the PC3 cell lines although, one experiment was removed due to excessivley high ct values (>30) in the house keeping gene, indicating an insufficient amount of RNA to sucessfully detect the genes of interest.
 
@@
 
-The sample numbers for each group are as follows:
-```{r}
-
-n <- data.frame(
-  name = c(
-    "PC3 mock",
-    "PC3 miR34a asRNA",
-    "Skov3 mock",
-    "Skov3 miR34a asRNA",
-    "Saos2 mock",
-    "Saos2 miR34a asRNA"
-  ),
-  n = c(3, 5, 4, 4, 5, 5)
-)
-n
-
-```
-
-<br></br>
-
-_QPCR primers_
+_Primers_
 
@@
 
-url <- "figure3a_stableLineExpression.rds"
+url <- "suppFigure2a_stableLineExpressionHEK.rds"
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
-#remove Skov exp 1 due to variability in technical replicates
-data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")
-
-#Have to divide the analysis due to the presence of several house 
-#keeping genes.
-gois1 <- c("miR34a asRNA", "Actin")
-gois2 <- c("miR34a", "RNU48")
-data1 <- filter(data, gene %in% gois1)
-data2 <- filter(data, gene %in% gois2)
+#remove PC3 experiment 6, B-act mean Ct > 30, too high.
+data <- filter(data, `Biological Replicate` != 6 | `Cell line` != "PC3")
 
 #calculate dct
-groups <- c("Genetic mod", "Biological Replicate", "Cell line", "gene")
+groups <- c("Condition", "Biological Replicate", "Cell line", "gene")
+gois <- c("miR34a asRNA")
 
-data1 <- data1 %>%
-  technicalMeans(., groups) %>%
-  dct(., gois1, Actin, groups) %>%
-  mutate(GOI = as.character(GOI))
-
-data2 <- data2 %>%
-  technicalMeans(., groups) %>%
-  dct(., gois2, RNU48, groups) %>%
-  mutate(GOI = as.character(GOI))
-
-data <- bind_rows(data1, data2) %>%
-  mutate(GOI = parse_factor(GOI, levels = c("miR34a asRNA", "miR34a")))
+data <- technicalMeans(data, groups) %>%
+  dct(., gois, Actin, groups)
 
@@
 logical <- tibble(
-  `Biological Replicate` = pull(data, `Biological Replicate`) == 2,
-  `Genetic mod` = pull(data, `Genetic mod`) == "mock"
+  `Cell line` = data$`Cell line` == "HEK293t",
+  Condition = data$Condition == "wt"
 )
@@
 #calculate stats
-stats <- calcStats(data, `Genetic mod`, "mock", groups) %>%
-  pFormat(.)
+stats <- data %>%
+  group_by(`Cell line`, Condition) %>%
+  summarize(
+    n = n(),
+    mean = mean(log2fold),
+    CI95l = t.test(log2fold)$conf.int[1],
+    CI95h = t.test(log2fold)$conf.int[2]
+  )
 
-#format for plotting
-lev <- c("PC3\nmock", "PC3\nmiR34a asRNA", "Skov3\nmock", "Skov3\nmiR34a asRNA", "Saos2\nmock",   "Saos2\nmiR34a asRNA")
-
-data <- data %>%
-  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
-  mutate(Condition = parse_factor(Condition, levels = lev))
-
-stats <- stats %>%
-  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
-  mutate(Condition = parse_factor(Condition, levels = lev))
-
-#vertical lines and labels in plot
-ys <- stats %>%
-  group_by(`Cell line`) %>%
-  summarize(max = max(CI95h))
-
-vl <- stats %>%
-  group_by(`Cell line`, GOI) %>%
-  summarize(
-    pValue = as.numeric(min(pValue))
-  ) %>%
-  ungroup() %>%
-  pFormat(.) %>%
-  mutate(
-    x = case_when(
-      GOI ==    "miR34a" ~ 1 + 0.25,
-      GOI == "miR34a asRNA" ~ 1 - 0.25
-    ),
-    xend = case_when(
-      GOI ==    "miR34a" ~ 2 + 0.25,
-      GOI == "miR34a asRNA" ~ 2 - 0.25
-    )
-  ) %>%
-  inner_join(ys) %>%
-  mutate(
-    max = max + c(0.25, 1, 0.25, 1, 0.25, 1)
-  )
 ```
@@
 
-p <- ggplot(data = NULL) +
+p <- ggplot(data = NULL)+
   geom_violin(
@@
       x = Condition,
-      y = log2fold,
-      group = interaction(Condition, GOI)
+      y = log2fold
     ),
+    scale = "width",
     trim = TRUE,
-    alpha = 0.5,
-    fill = "grey",
-    colour = NA,
-    scale = "width",
+    alpha = 0.3,
+    color = NA,
+    fill = "gray",
     show.legend = FALSE
@@
       y = log2fold, 
-      fill = GOI,
-      group = interaction(Condition, GOI)
+      fill = Condition
     ),
+    colour = NA,
     binwidth = 1/10,
-    colour = NA,
     alpha = 0.5,
     position = position_dodge(width = 0.9), 
-    binaxis = 'y', 
-    stackdir = 'center',
+    binaxis='y', 
+    stackdir='center',
     dotsize = 4,
@@
   ) +
-  facet_grid(
-    . ~ `Cell line`, 
-    scales = "free", 
-    space = "free"
+  facet_grid(. ~ `Cell line`, scales = "free") +
+  geom_point(
+    data = stats,
+    aes(
+      x = Condition, 
+      y = mean
+    ),
+    colour = "grey20",
+    show.legend = FALSE,
+    shape = 95,
+    size = 6
   ) +
@@
       ymin = CI95l, 
-      ymax = CI95h,
-      group = interaction(Condition, GOI)
+      ymax = CI95h
     ),
-    position = position_dodge(width = 0.9),
     colour = "gray20",
@@
   ) +
-  geom_point(
-    data = stats,
-    aes(
-      x = Condition,
-      y = mean,
-      group = interaction(Condition, GOI)
-    ),
-    colour = "gray20",
-    shape = 95,
-    size = 6,
-    position = position_dodge(width = 0.9),
-    show.legend = FALSE
-  ) +
-  geom_label(
-    data = vl,
-    aes(
-      x = 1.5, 
-      y = max + 0.25, 
-      label = pFormat, 
-      group = interaction(`Cell line`, GOI)
-    ),
-    fill = "white",
-    label.size = 0,
-    label.padding = unit(0.01, "lines"),
-    position = position_dodge(width = 0.9),
-    show.legend = FALSE,
-    fontface = "bold",
-    family = "Arial Unicode MS",
-    size = 3
-  ) +
-  geom_segment(
-    data = vl,
-    aes(
-      x = x,
-      y = max,
-      xend = xend,
-      yend = max
-    ),
-    colour = "grey43",
-    show.legend = FALSE
-  ) +
-  scale_y_continuous("\u0394\u0394Ct")+
   labs(
     x = "Cell line",
-    title = "miR34a asRNA over-expressing cell lines"
+    y = "log2(Fold)",
+    title = "miR34a asRNA"
   ) +
-  guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
-  )
+  guides(fill = FALSE)
 
@@
 <div class="caption">
-miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control.
-The points represent the values obtained from each independant experiment (n >= 3) whereas, the gray shadow represents the distribution of those points.
-95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
+miR34a asRNA over-expression levels in PC3, Skov3, and Saos2 stable cell lines compared to HEK293t cells.
+The points represent the values obtained from each independant experiment (n = 5) whereas, the gray shadow represents the distribution of those points.
+95% confidence interval (vertical black lines) and mean (horizontal black lines) are shown.
 </div>
@@
 
-####_Conclusion_
+####_Conclusions_
 
-miR34a asRNA over-expression causes a concominant up-regulation of miR34a in all 3 cell lines. This indicates that miR34a asRNA concordantly regulates miR34a.
+Results indicate that miR34a asRNA is over-expressed 13-22 fold greater that endogenous HEK293t levels.
 

### 2017-11-14 inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Supplementary Figure 2b"
subtitle: "CCND1 expression in PC3 stable cell lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

To further investigate the characteristics of the miR34a asRNA stable lines, we measured the expression level of known miR34a target cyclin D1. miR34a has been previously shown to inhibit cell cycle progression, partially via its regulation of cyclin D1.

<br></br>

####_Methods_

<br></br>

_Cell culture and QPCR_

All cell lines were cultured at 5% CO2 and 37° C with PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. Cells were seeded at 2x10^5 cells per well in a 12-well plate. After 24 hours, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

<br></br>

_Analysis_

Two technical replicates were included for each sample and each QPCR run. Delta ct was calculated by subtracting the mean of the technical replicates for each sample from the mean value for the technical replicates from the house keeping gene for the corresponding sample. Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples. Six independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the mock and miR34a asRNA overexpressing group's delta-delta ct values with the null hypothesis that there was no difference in the two group's means.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "CCND1 Fwd",	
        "CCND1 Rev",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "CGT GGC CTC TAA GAT GAA GG",
        "CTG GCA TTT TGG AGA GGA AG",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers

```

<br></br>

####_Results_

```{r, warning=FALSE, message=FALSE}

url <- "suppFigure2b_stableLineCCND1exp.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#calculate dct
groups <- c("condition", "Biological Replicate", "Cell line", "gene")
gois <- c("CCND1")

data <- data %>%
  technicalMeans(., groups) %>%
  dct(., gois, Actin, groups, F)

#calculate ddct
groups[groups == "gene"] <- "GOI"
logical <- tibble(
  condition = pull(data, condition) == "PC3 mock"
)

data <- data %>%
  ddct(., logical, groups) %>%
  folds(.)

#calculate stats
stats <- calcStats(data, condition, "PC3 mock", groups) %>%
  pFormat(.)

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width"
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/200,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour = "gray20"
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour = "gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    aes(
      x = 1,
      y = 0.175, 
      xend = 2,
      yend = 0.175
    ),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = 0.19,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Cell line",
    title = "CCND1"
  ) +
  guides(fill = FALSE)

plotRmarkdown(p)

```

<div class="caption">
Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines. The points represent the values obtained from each independant experiment (n = 6) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusions_

CCND1 expression levels are decreased in PC3 cell lines stably over-expressing miR34a asRNA.

### 2017-11-14 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
ALL analysis moved from vignette to individual Rmds in inst

---
title: "Supplementary Figure 2c"
subtitle: "CCND1 protein expression in PC3 stable lines"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

After observing decreased mRNA levels for the miR34a target CCND1, we were interested whether this has also consequences for its protein levels.

<br></br>

####_Methods_

<br></br>

_Cell culture and western blot_
All cell lines were cultured at 5% CO2 and 37° C with PC3 cells in RPMI (Hyclone) and 2 mM L-glutamine. All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. We seeded three independent experiments of 150,000 cells/well in a six well plate (PC3 mock vs. PC3 miR34a AS F4) and grew them for 24 hours. Before harvesting cells were controlled for their confluency. Cells with a confluence of 60-75%, were harvested using trypsin. Cell pellets were frozen down at -80°C before lysed for Western Blot analysis. Western Blot analysis was performed following Lottes’ protocol. Cells were lysed in RIPA Buffer and run on a 4-12% Bis-Tris-SDS Gel using MOPS running buffer. Proteins were transferred onto a nitrocellulose membrane using iBlot Turbo Blotting Device. Proteins were transferred for 7 minutes. Membranes were blocked for 1 hour at room temperature in 5% milk. Membranes were incubated with a cyclin D1 antibody (92G2 Rabbit mAb, Cell Signalling) overnight at 4°C. The membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature. Membranes were washed 3-times for 5min each in TBS-T. Membranes were developed using chemiluminescence. After the picture was taken, the membrane was stripped using 0.4M NaOH solution for 20min. Blocking step was repeated and primary antibody against GAPDH was incubated for overnight at 4°C. Consequently, the membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature. Membranes were washed 3-times for 5min in TBS-T. Membranes were developed using chemiluminescence.

<br></br>

_Analysis_

Resulting bands on the western blots were quantified using the ImageJ software with three parameters being measured, intensity, background, and pixel. The quantative value was derived for each band by first subtracting the background from the intensity and subsequently multiplying this value by the pixel value. The fraction of CCND1 over the house keeping gene was then calculated using each sample's values and the corresponding house keeping genes values. Fold change was then calculated by dividing the normalized CCND1 values in the miR34a asRNA overexpressing samples by the median of the corresponding mock samples. Fold change values were subsequently log2 transformed and the Student's t-test was utilized to compare mock vs. miR34a asRNA overexpressing samples using three independant experiments with the null hypothesis that the mean values were the same in each group.

<br></br>

####_Results_

_Representative experiment_
```{r, out.width = "500px"}

url <- "suppFigure2c_stableLineCCND1prot/singleExp.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class="caption">
A resulting western blot representative of the results from the three independant experiments.
</div>

<br></br><br></br>

_Quantification_
```{r, message = FALSE}

url <- "suppFigure2c_stableLineCCND1prot.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize to house keeping gene
data <- data %>%
  mutate(value = (Intensity - background) * pixel) %>%
  select(-pixel, -Intensity, -background) %>%
  spread(protein, value) %>%
  mutate(normHK = CCND1 / GAPDH)

#normalize to mock
cnt <- filter(data, condition == "PC3 mock") %>% 
  pull(normHK) %>% 
  median

data <- mutate(data, log2fold = log2(normHK / cnt))

#calculate stats
stats <- data %>%
  group_by(condition) %>%
  summarize(
    n = n(),
    mean = mean(log2fold),
    CI95l = t.test(log2fold)$conf.int[1],
    CI95h = t.test(log2fold)$conf.int[2],
    pValue = t.test(log2fold, pull(filter(data, condition == "PC3 mock"), log2fold))$p.value
  ) %>%
  pFormat(.)

```

```{r, fig.align='center', fig.height=8, fig.width=12}

p <- ggplot(data = NULL) +
  geom_violin(
    data = data,
    aes(
      x = condition,
      y = log2fold
    ),
    trim = TRUE,
    alpha = 0.3,
    color = NA,
    fill = "gray",
    scale = "width",
    show.legend = FALSE
  ) +
  geom_dotplot(
    data = data, 
    aes(
      x = condition,
      y = log2fold,
      fill = condition
    ),
    binwidth = 1/30,
    colour = NA,
    alpha = 0.5,
    position = position_dodge(width = 0.9), 
    binaxis = 'y', 
    stackdir = 'center',
    dotsize = 4,
    show.legend = TRUE
  ) +
  geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20"
  ) +
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    size = 6,
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43"
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.5,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  ) +
  scale_y_continuous("log2(Fold)") +
  labs(
    x = "Cell line",
    title = "CCND1 protein"
  ) +
  guides(fill = FALSE)

plotRmarkdown(p)

```

<div class="caption">
Western blot quantification showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines compared to mock. The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points. 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
</div>

<br></br>

####_Conclusions_

Cyclin D1 protein levels are significantly reduced in PC3 cells overexpressing miR34a asRNA, consistent with increased miR34a expression levels and the reduced G1 cell cycle phase observed in PC3 cells.

### 2017-11-14 R/processFigures.R

@@ -38,34 +38,34 @@ getPath <- function(figure) {
 #returns a map of paths to each figures .rmd file
 makeMap <- function() {
   list(
-    figure1a = "figure1a_miR34aLocus/figure1a.Rmd",
-    figure1b = "figure1b_miR34aASExpressionCellPanel/figure1b.Rmd",
-    figure1c = "figure1c_TCGAcorrelation/figure1c.Rmd",
-    figure1d = "figure1d_3primeRACE/figure1d.Rmd",
-    figure1e = "figure1e_primerWalk/figure1e.Rmd",
-    figure1f = "figure1f_codingPotentialCPAT/figure1f.Rmd",
-    figure2a = "figure2a_HCT116p53null/figure2a.Rmd",
-    figure2b = "figure2b_HctHekDox/figure2b.Rmd",
-    figure2c = "figure2c_P1construct/figure2d.Rmd",
-    figure2d = "figure2d_P1-HCTandHEK/figure2d.Rmd",
-    figure2e = "figure2e_P1shRNAdox/figure2e.Rmd",
-    figure3a = "figure3a_stableLineExpression/figure3a.Rmd",
-    figure3b = "figure3b_stableLineCellCycle/figure3b.Rmd",
-    figure3c = "figure3c_stableLineGrowthStarvation/figure3c.Rmd",
-    figure3d = "figure3d_stableLinePolIIChIP/figure3d.Rmd",
-    figure3e = "figure3e_survival/figure3e.Rmd",
-    suppFigure1a = "suppFigure1a_TCGAcorrelationTable/",
-    suppFigure1b = "suppFigure1b_primerWalkSchematic/",
-    suppFigure1c = "suppFigure1c_polyadenylation/",
-    suppFigure1d = "suppFigure1d_isoforms/",
-    suppFigure1e = "suppFigure1e_cellularLocalization/",
-    suppFigure1f = "suppFigure1f_transcriptStability/",
-    suppFigure1g = "suppFigure1g_codingPotentialCPC/",
-    suppFigure2a = "suppFigure2a_stableLineExpressionHEK/",
-    suppFigure2b = "suppFigure2b_stableLineCCND1exp/",
-    suppFigure2c = "suppFigure2c_stableLineCCND1prot/",
-    suppFigure2d = "suppFigure2d_lnc34aCage/",
-    suppFigure2e = "suppFigure2e_lnc34aSplJnc/"
[…]

### 2017-11-15 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
all supplementary and fig3 pdfs written

@@
 
+library(grDevices)
 ```
@@
   ) +
+  facet_grid(. ~ GOI) +
+  scale_y_continuous("\u0394\u0394Ct", breaks = c(-1,0,1,2,3,4,5))+
+  labs(x = "Treatment") +
+  guides(
+    fill = guide_legend(title = "Cell line", override.aes = list(size = 6))
+  )
+
+markdown <- p + 
   geom_point(
@@
   ) +
-  facet_grid(. ~ GOI) +
   geom_linerange(
@@
     show.legend = FALSE
-  ) +
-  scale_y_continuous("\u0394\u0394Ct", breaks = c(-1,0,1,2,3,4,5))+
-  labs(
-    x = "Treatment",
-    title = "miR34a asRNA regulation by p53 induction"
-  ) +
-  guides(
-    fill = guide_legend(title = "Cell line", override.aes = list(size = 6))
   )
 
-plotRmarkdown(p)
+plotRmarkdown(markdown)
 
+pdf <- p + 
+  geom_point(
+    data = stats,
+    aes(x = Treatment, y = mean, group = Condition), 
+    position = position_dodge(width = 0.9),
+    colour = "gray20",
+    shape = 95
+  ) +
+  geom_linerange(
+    data = stats,
+    aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = stats,
+    aes(x = Treatment, y = max + 0.28, label = pFormat),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 1,
+    family = "Arial Unicode MS",
+    position = position_dodge(width = 0.9)
+  ) +
+  geom_segment(
+    data = stats,
+    aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
+    colour="grey43",
+    size = 0.1,
+    show.legend = FALSE
+  )
+
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"
+
+#ggsave(
+#  plot = figure, 
+#  filename = path, 
+#  device = cairo_pdf, 
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+#)
 ```

### 2017-11-15 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
all supplementary and fig3 pdfs written

@@
 #format for plotting
-lev <- c("PC3\nmock", "PC3\nmiR34a asRNA", "Skov3\nmock", "Skov3\nmiR34a asRNA", "Saos2\nmock",   "Saos2\nmiR34a asRNA")
+lev <- c("mock", "miR34a asRNA", "Skov3\nmock", "Skov3\nmiR34a asRNA", "Saos2\nmock",   "Saos2\nmiR34a asRNA")
 
 data <- data %>%
-  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
-  mutate(Condition = parse_factor(Condition, levels = lev))
+  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
+  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
 
 stats <- stats %>%
-  mutate(Condition = paste(`Cell line`, `Genetic mod`, sep = "\n")) %>%
-  mutate(Condition = parse_factor(Condition, levels = lev))
+  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
+  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
 
@@
   mutate(
-    max = max + c(0.25, 1, 0.25, 1, 0.25, 1)
+    max = max + c(0.25, 1.25, 0.25, 1.25, 0.25, 1.25)
   )
@@
     aes(
-      x = Condition,
+      x = `Genetic mod`,
       y = log2fold,
-      group = interaction(Condition, GOI)
+      group = interaction(`Genetic mod`, GOI)
     ),
@@
     aes(
-      x = Condition,
+      x = `Genetic mod`,
       y = log2fold,
       fill = GOI,
-      group = interaction(Condition, GOI)
+      group = interaction(`Genetic mod`, GOI)
     ),
@@
   ) +
+  scale_y_continuous("\u0394\u0394Ct")+
+  labs(x = "Cell line") +
+  guides(
+    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
+  )
+
+markdown <- p +
   geom_linerange(
@@
     aes(
-      x = Condition,
+      x = `Genetic mod`,
       ymin = CI95l,
       ymax = CI95h,
-      group = interaction(Condition, GOI)
+      group = interaction(`Genetic mod`, GOI)
     ),
@@
     aes(
-      x = Condition,
+      x = `Genetic mod`,
       y = mean,
-      group = interaction(Condition, GOI)
+      group = interaction(`Genetic mod`, GOI)
     ),
@@
       x = 1.5, 
-      y = max + 0.25, 
+      y = max + 0.4, 
       label = pFormat, 
@@
     show.legend = FALSE
-  ) +
-  scale_y_continuous("\u0394\u0394Ct")+
-  labs(
-    x = "Cell line",
-    title = "miR34a asRNA over-expressing cell lines"
-  ) +
-  guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
   )
 
-plotRmarkdown(p)
+plotRmarkdown(markdown)
 
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = `Genetic mod`,
+      ymin = CI95l,
+      ymax = CI95h,
+      group = interaction(`Genetic mod`, GOI)
+    ),
+    position = position_dodge(width = 0.9),
+    colour = "gray20",
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = `Genetic mod`,
+      y = mean,
+      group = interaction(`Genetic mod`, GOI)
+    ),
+    colour = "gray20",
+    shape = 95,
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = vl,
+    aes(
+      x = 1.5, 
+      y = max + 0.4, 
+      label = pFormat, 
+      group = interaction(`Cell line`, GOI)
+    ),
+    fill = "white",
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE,
+    fontface = "bold",
+    family = "Arial Unicode MS",
+    size = 1
+  ) +
+  geom_segment(
+    data = vl,
+    aes(
+      x = x,
+      y = max,
+      xend = xend,
+      yend = max
+    ),
+    colour = "grey43",
+    size = 0.1,
+    show.legend = FALSE
+  )
+
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3a_stableLineExpression/figure3a_stableLineExpression.pdf"
+
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```

### 2017-11-15 inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.Rmd
all supplementary and fig3 pdfs written

@@
   ) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  labs(
+    x = "Cell cycle phase",
+    y = "",
+    title = "Cell cycle"
+  ) +
+  guides(
+    fill = guide_legend(title = "Condition", override.aes = list(size = 6))
+  )
+
+markdown <- p +
   geom_linerange(
@@
     family = "Arial Unicode MS"
+  )
+plotRmarkdown(markdown)
+
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = phase, 
+      ymin = CI95l, 
+      ymax = CI95h, 
+      group = interaction(phase, condition)
+    ),
+    position = position_dodge(width = 0.9),
+    colour = "grey25",
+    size = 0.1,
+    show.legend = FALSE
   ) +
-  scale_y_continuous(labels = scales::percent_format()) +
-  labs(
-    x = "Cell cycle phase",
-    y = "",
-    title = "Cell cycle"
+  geom_point(
+    data = stats,
+    aes(
+      x = phase, 
+      y = mean, 
+      group = condition
+    ), 
+    colour = "black",
+    position = position_dodge(width = 0.9),
+    shape = 95,
+    show.legend = FALSE
   ) +
-  guides(
-    fill = guide_legend(title = "Condition", override.aes = list(size = 6))
+  geom_segment(
+    data = stats,
+    aes(
+      x = x,
+      y = y + 0.01, 
+      xend = xend, 
+      yend = y + 0.01
+    ),
+    colour = "grey43",
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = stats,
+    aes(
+      x = phase, 
+      y = y + 0.025, 
+      label = pFormat
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS"
   )
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
 
-plotRmarkdown(p)
-
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-15 inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.Rmd
all supplementary and fig3 pdfs written

@@
   ) +
+  facet_grid(. ~ Treatment) +
+  scale_x_discrete(breaks = seq(0, 35, 5)) +
+  labs(
+    x = "Time (hours)", 
+    y = "Normalized % confluency",
+    title = "miR34a asRNA's role in growth regulation."
+  ) + 
+  guides(
+    colour = guide_legend(title = "Cell line", override.aes = list(size = 3))
+  )
+
+markdown <- p +
   geom_linerange(
@@
   ) + 
-  facet_grid(. ~ Treatment) +
-  scale_x_discrete(breaks = seq(0, 35, 5)) +
-  labs(
-    x = "Time (hours)", 
-    y = "Normalized % confluency",
-    title = "miR34a asRNA's role in growth regulation."
-  ) + 
   guides(
@@
 
-plotRmarkdown(p)
+plotRmarkdown(markdown)
 
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = Time,
+      colour = `Cell line`,
+      ymin = min,
+      ymax = max
+    ), 
+    position = position_dodge(width = 1),
+    lwd = 0.1,
+    show.legend = FALSE
+  ) + 
+  geom_point(
+    data = stats,
+    aes(
+      x = Time, 
+      y = median,
+      group = `Cell line`,
+      colour = `Cell line`
+    ), 
+    size = 0.25,
+    position = position_dodge(width = 1),
+    show.legend = TRUE
+  ) + 
+  guides(
+    colour = guide_legend(title = "Cell line", override.aes = list(size = 2))
+  )
+
+figure <- plotPDF(pdf)
+
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```
@@
 The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line.
-The points represent the mean values obtained from each independant experiment (n = 3) whereas, the shadow represents 95% confidence interval, and the vertical line represents the minimum and maximum values from the independant experiments.
+The points represent the median values obtained from each independant experiment (n = 3) whereas, the shadow represents 95% confidence interval, and the vertical line represents the minimum and maximum values from the independant experiments.
 </div>

### 2017-11-15 inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd
all supplementary and fig3 pdfs written

@@
   ) +
+  scale_y_continuous("log2(Fold)") +
+  labs(
+    x = "Cell line",
+    y = "log2(Fold polII enrichment)",
+    title = "Phosphorylated Poll II ChIP"
+  ) +
+  guides(fill = FALSE)
+
+markdown <- p +
     geom_linerange(
@@
     family = "Arial Unicode MS"
+  )
+
+plotRmarkdown(markdown)
+
+pdf <- p +
+    geom_linerange(
+    data = stats,
+    aes(x = condition, ymin = CI95l, ymax = CI95h),
+    colour = "gray20",
+    size = 0.1,
+    show.legend = FALSE
   ) +
-  scale_y_continuous("log2(Fold)") +
-  labs(
-    x = "Cell line",
-    y = "log2(Fold polII enrichment)",
-    title = "Phosphorylated Poll II ChIP"
+  geom_point(
+    data = stats,
+    aes(x = condition, y = mean),
+    colour = "gray20",
+    shape = 95,
+    show.legend = FALSE
   ) +
-  guides(fill = FALSE)
+  geom_segment(
+    data = filter(stats, condition == "PC3 miR34a asRNA"),
+    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
+    colour = "grey43",
+    size = 0.1
+  ) +
+  geom_label(
+    data = stats,
+    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS"
+  )
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.pdf"
 
+# ggsave(
+#   plot = figure, 
+#   filename = path, 
+#   device = cairo_pdf, 
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-15 inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.Rmd
all supplementary and fig3 pdfs written

@@
 p <- ggplot(data = NULL)+
+  scale_y_continuous("\u0394\u0394Ct") +
+  labs(
+    x = "Treatment (hours)",
+    title = "miR34a asRNA and HG stability"
+  ) +
+  guides(color = guide_legend(title = "Gene", override.aes = list(size = 3)))
+
+markdown <- p +
   geom_point(
@@
     size = 6
+  )
+
+plotRmarkdown(markdown)
+
+pdf <- p +
+  geom_point(
+    data = data,
+    aes(
+      x = treatment,
+      y = log2fold,
+      colour = GOI
+    ),
+    fill = "white",
+    alpha = 0.6,
+    stroke = 0,
+    position = position_dodge(width = 0.9)
   ) +
-  scale_y_continuous("\u0394\u0394Ct") +
-  labs(
-    x = "Treatment (hours)",
-    title = "miR34a asRNA and HG stability"
+  geom_linerange(
+    data = stats,
+    aes(
+      x = treatment,
+      ymin = mean - sd,
+      ymax = mean + sd,
+      group = GOI
+    ),
+    colour = "black",
+    position = position_dodge(width = 0.9),
+    size = 0.1,
+    show.legend = FALSE
   ) +
-  guides(color = guide_legend(title = "Gene", override.aes = list(size = 3)))
+  geom_point(
+    data = stats,
+    aes(
+      x = treatment,
+      y = mean,
+      group = GOI
+    ),
+    colour = "black",
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE,
+    shape = 95
+  )
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.pdf"
 
+#ggsave(
+#  plot = figure, 
+#  filename = path, 
+#  device = cairo_pdf, 
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+#)
 ```

### 2017-11-15 inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.Rmd
all supplementary and fig3 pdfs written

@@
   ) +
+  scale_y_continuous("\u0394\u0394Ct") +
+  labs(
+    x = "Cell line",
+    title = "CCND1"
+  ) +
+  guides(fill = FALSE)
+
+markdown <- p + 
   geom_linerange(
@@
     family = "Arial Unicode MS"
+  )
+
+plotRmarkdown(markdown)
+
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = condition,
+      ymin = CI95l,
+      ymax = CI95h
+    ),
+    colour = "gray20",
+    size = 0.1
   ) +
-  scale_y_continuous("\u0394\u0394Ct") +
-  labs(
-    x = "Cell line",
-    title = "CCND1"
+  geom_point(
+    data = stats,
+    aes(
+      x = condition,
+      y = mean
+    ),
+    colour = "gray20",
+    shape = 95
   ) +
-  guides(fill = FALSE)
+  geom_segment(
+    aes(
+      x = 1,
+      y = 0.175, 
+      xend = 2,
+      yend = 0.175
+    ),
+    colour = "grey43",
+    size = 0.1
+  ) +
+  geom_label(
+    data = stats,
+    aes(
+      x = 1.5,
+      y = 0.2,
+      label = pFormat
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS"
+  )
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.pdf"
 
+#ggsave(
+#  plot = figure, 
+#  filename = path, 
+#  device = cairo_pdf, 
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+#)
 ```

### 2017-11-15 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
all supplementary and fig3 pdfs written

@@
   ) +
-  geom_linerange(
-    data = stats,
-    aes(
-      x = condition,
-      ymin = CI95l,
-      ymax = CI95h
-    ),
-    colour="gray20"
+  scale_y_continuous("log2(Fold)") +
+  labs(
+    x = "Cell line",
+    title = "CCND1 protein"
   ) +
+  guides(fill = FALSE)
+
+markdown <- p +
   geom_point(
@@
       x = 1.5,
-      y = max(CI95h) + 0.5,
+      y = max(CI95h) + 0.4,
       label = pFormat
@@
   ) +
-  scale_y_continuous("log2(Fold)") +
-  labs(
-    x = "Cell line",
-    title = "CCND1 protein"
+   geom_linerange(
+    data = stats,
+    aes(
+      x = condition,
+      ymin = CI95l,
+      ymax = CI95h
+    ),
+    colour="gray20"
+  )
+
+plotRmarkdown(markdown)
+
+pdf <- p + 
+  geom_point(
+    data = stats,
+    aes(
+      x = condition,
+      y = mean
+    ),
+    colour="gray20",
+    shape = 95
   ) +
-  guides(fill = FALSE)
+  geom_segment(
+    data = stats,
+    aes(
+      x = 1,
+      y = max(CI95h) + 0.25,
+      xend = 2,
+      yend = max(CI95h) + 0.25
+    ),
+    colour="grey43",
+    size = 0.1
+  ) +
+  geom_label(
+    data = stats,
+    aes(
+      x = 1.5,
+      y = max(CI95h) + 0.4,
+      label = pFormat
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS"
+  ) +
+   geom_linerange(
+    data = stats,
+    aes(
+      x = condition,
+      ymin = CI95l,
+      ymax = CI95h
+    ),
+    colour="gray20",
+    size = 0.1
+  )
 
-plotRmarkdown(p)
-
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
+ggsave(
+  plot = figure, 
+  filename = path, 
+  device = cairo_pdf, 
+  height = 60,
+  width = 83,
+  units = "mm"
+)
 ```

### 2017-11-15 inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.Rmd
all supplementary and fig3 pdfs written

--- 2017-11-14 inst/suppFigure2e_lnc34aSplJnc/lnc34aSplJnc.Rmd
@@
 
-```{r, fig.align='center', fig.height=8, fig.width=12}
+```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
+#plot rmarkdown
 ###locus
@@
 grid.draw(resize_heights(g, unit(c(3,1), "null")))
+
+#plot pdf
+#genes
+p1 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = filter(data, feature == "exon"),
+    aes(xmin = start, xmax = stop, y = gene, fill = gene),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = grid::unit(1, "mm"),
+    colour = "gray",
+    lwd = 0.1
+  ) +
+  ggthemes::theme_few() +
+  ggthemes::scale_fill_ptol() +
+  geom_segment(
+    data = filter(data, feature == "intron"),
+    aes(x = start, xend = stop, y = gene, yend = gene),
+    linetype = "dotted",
+    colour = "gray",
+    size = 0.25
+  ) +
+  xlim(9241000, 9257900) +
+  labs(x = "Chromosome 1", y = "Genes") +
+  guides(fill = FALSE) +
+  theme(
+    axis.text = element_text(size = 3),
+    axis.title.x = element_text(size = 4),
+    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
+    axis.ticks.length = unit(0.5, "mm"),
+    axis.ticks = element_line(size = 0.15),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
+  )
+
+#splice junctions
+p2 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = splJnc,
+    aes(xmin = start, xmax = stop, y = y, fill = n),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = unit(2, "pt"),
+    colour = NA,
+    lwd = 0.1,
+    show.legend = TRUE
+  ) +
+  ggthemes::theme_few() +
+  viridis::scale_fill_viridis() +
+  theme(
+    axis.title.x = element_blank(),
+    axis.title.y = element_text(size = 4),
+    legend.position = "top",
+    legend.title = element_text(size = 4),
+    legend.text = element_text(size = 4),
+    legend.box.spacing = unit(3, "pt"),
+    axis.text = element_blank(),
+    axis.ticks = element_blank(),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
+    strip.text.y = element_text(angle = 0)
+  ) +
+  labs(y = "Cage reads") +
+  xlim(9241000, 9257900) +
+  guides(fill = guide_colourbar(
+    title = "Reads",
+    title.position = "top",
+    title.hjust = 0.5,
+    barheight = unit(4, "pt"),
+    barwidth = unit(40, "pt")
+  ))
+
+grobz <- lapply(list(p1, p2), ggplotGrob)
+g <- rbind(grobz[[2]], grobz[[1]], size = "last")
+g <- resize_heights(g, unit(c(6, 1), "null"))
+
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.pdf"
+ggsave(
+  plot = g, 
+  filename = path, 
+  device = cairo_pdf, 
+  height = 60,
+  width = 83,
+  units = "mm"
+)
+
 ```

### 2017-11-15 R/plotting.R

@@ -4,16 +4,14 @@ plotPDF <- function(plot) {
   p <- plot +
     theme_few() +
     scale_fill_ptol() +
+    scale_colour_ptol() +
     theme(
-        plot.title = element_text(
-            hjust = 0.5,
-            face = "bold",
-            size = 10,
-            margin = margin(b = 2, unit = "mm")
-        ),
+        plot.title = element_blank(),
         plot.margin = unit(rep(0.1, 4), "lines"),
         legend.position = "top",
-        legend.margin = unit(1, "mm"),
+        legend.background = element_blank(),
+        legend.box.spacing = unit(5, "pt"), #this controls the spacing between strip.text.x and the legend
+        legend.margin = margin(rep(0, 4), unit = "pt"),
         legend.key.size = unit(1/5, "cm"),
         legend.title = element_text(size = 9),
         legend.text = element_text(size = 7),
@@ -23,7 +21,10 @@ plotPDF <- function(plot) {
         axis.text.x = element_text(size = 7),
         axis.ticks = element_line(size = 0.25),
         axis.ticks.length = unit(1/15, "cm"),
-        strip.text.x = element_text(size = 8, margin = margin(0.01, 0, 0.1, 0, "cm")),
+        strip.text.x = element_text(
+          size = 8,
+          margin = margin(0.01, 0, 5, 0, "pt")
+        ),
         panel.border = element_rect(fill = NA, size = 0.15)
     )
     

### 2017-11-17 inst/figure2b_HctHekDox/figure2b_HctHekDox.Rmd
all first version pdfs done

@@
   ) +
+  facet_grid(. ~ `Cell line`) +
+  scale_y_continuous(
+    "\u0394\u0394Ct",
+    breaks=c(-1,0,1,2,3,4,5)
+  ) +
+  labs(
+    x = "Treatment",
+    title = "miR34a asRNA response to p53 induction"
+  ) +
+  guides(
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 6)
+  ))
+
+markdown <- p +
   geom_point(
@@
   ) +
-  facet_grid(. ~ `Cell line`) +
   geom_linerange(
@@
   ) +
-  scale_y_continuous(
-    "\u0394\u0394Ct",
-    breaks=c(-1,0,1,2,3,4,5)
+  guides(
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 6)
+  ))
+
+plotRmarkdown(markdown)
+
+pdf <- p + 
+    geom_point(
+    data = stats,
+    aes(
+      x = Treatment,
+      y = mean,
+      group = GOI
+    ),
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE,
+    shape = 95,
+    colour = "gray20"
   ) +
-  labs(
-    x = "Treatment",
-    title = "miR34a asRNA response to p53 induction"
+  geom_linerange(
+    data = stats,
+    aes(
+      x = Treatment,
+      ymin = CI95l,
+      ymax = CI95h,
+      group = GOI
+    ),
+    colour = "gray20",
+    size = 0.1,
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = vl,
+    aes(
+      x = labelX,
+      y = max + 0.3,
+      label = pFormat,
+      group = GOI
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS",
+    position = position_dodge(width = 0.9)
+  ) +
+  geom_segment(
+    data = vl,
+    aes(
+      x = x,
+      y = max + 0.1,
+      xend = xend,
+      yend = max + 0.1,
+      group = GOI
+    ),
+    colour="grey43",
+    size = 0.1,
+    show.legend = FALSE
   ) +
   guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
-  )
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 4)
+  ))
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure2b_HctHekDox/figure2b_HctHekDox.pdf"
 
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-17 inst/figure2d_P1-HCTandHEK/figure2d_P1-HCTandHEK.Rmd
all first version pdfs done

@@
   facet_grid(. ~ `Cell line`) +
+  labs(
+    x = "Construct",
+    y = "log2 activity (a.u.)"
+  )
+
+markdown <- p +
   geom_linerange(
@@
   ) +
-  labs(
-    x = "Construct",
-    y = "log2 activity (a.u.)",
-    title = "miR34a asRNA regulation by miR34a promoter"
+  guides(fill = guide_legend(
+    title = "Gene", 
+    override.aes = list(size = 6)
+  ))
+
+plotRmarkdown(markdown)
+
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = construct,
+      ymin = CI95l,
+      ymax = CI95h,
+      group = plotGene
+    ),
+    colour = "grey20",
+    size = 0.1,
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
   ) +
-  guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
-  )
+  geom_point(
+    data = stats,
+    aes(
+      x = construct,
+      y = mean,
+      group = plotGene
+    ),
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE,
+    colour = "gray20",
+    shape = 95
+  ) +
+  geom_label(
+    data = vl,
+    aes(
+      x = 1.5, 
+      y = max + 0.25, 
+      label = pFormat, 
+      group = gene
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS",
+    position = position_dodge(width = 0.9)
+  ) +
+  geom_segment(
+    data = vl,
+    aes(
+      x = x,
+      y = max,
+      xend = xend,
+      yend = max
+    ),
+    colour = "grey43",
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  guides(fill = guide_legend(
+    title = "Gene", 
+    override.aes = list(size = 4)
+  ))
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure2d_P1-HCTandHEK/figure2d_P1-HCTandHEK.pdf"
 
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-17 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
all first version pdfs done

@@
   facet_grid(. ~ shRNA, scale = "free") +
+  scale_y_continuous("\u0394\u0394Ct") +
+  labs(
+    x = "Doxorubicin (ng/ml)",
+    title = "HCT116"
+  )
+
+markdown <- p + 
   geom_linerange(
@@
   ) +
-  scale_y_continuous("\u0394\u0394Ct") +
-  labs(
-    x = "Doxorubicin (ng/ml)",
-    title = "HCT116"
-  ) +
   guides(
@@
 
-plotRmarkdown(p)
+plotRmarkdown(markdown)
 
+pdf <- p + 
+  geom_linerange(
+    data = stats,
+    aes(
+      x = treatment, 
+      ymin = CI95l, 
+      ymax = CI95h, 
+      group = plotGOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = treatment, 
+      y = mean, 
+      group = plotGOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    shape = 95,
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = stats,
+    aes(
+      x = treatment, 
+      y = CI95h + 0.2,
+      label = pFormat,
+      group = plotGOI
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    position = position_dodge(width = 0.9),
+    fill = "white",
+    size = 1,
+    family = "Arial Unicode MS"
+  ) +
+  guides(fill = guide_legend(
+    title = "Gene",
+    override.aes = list(size = 4)
+  ))
+
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.pdf"
+
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-17 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
added gatherFigures and clearFigures functions and ran

@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"
 
-#ggsave(
-#  plot = figure, 
-#  filename = path, 
-#  device = cairo_pdf, 
-#  height = 60,
-#  width = 83,
-#  units = "mm"
-#)
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 83,
+ units = "mm"
+)
 ```

### 2017-11-17 R/gatherFigures.R
missed adding actual script in last commit, here now

@@ -1,0 +1,194 @@
+
+gatherFigures <- function() {
+  bp <- "~/Github/miR34a_asRNA_project/inst/"
+  cmds <- list(
+    figure1a = paste(
+      "cp",
+      file.path(bp, "figure1a_miR34aLocus/figure1a_miR34aLocus_hg38.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure1b = paste(
+      "cp",
+      file.path(bp, "figure1b_miR34aASExpressionCellPanel/figure1b_miR34aASExpressionCellPanel.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure1c = paste(
+      "cp",
+      file.path(bp, "figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure1d = paste(
+      "cp",
+      file.path(bp, "figure1d_3primeRACE/figure1d_3primeRACE_hg38.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure1e = paste(
+      "cp",
+      file.path(bp, "figure1e_primerWalk/figure1e_primerWalk.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure1f = paste(
+      "cp",
+      file.path(bp, "figure1f_codingPotentialCPAT/figure1f_codingPotentialCPAT.ai"),
+      file.path(bp, "allFigures/Figure1/"),
+      sep = " "
+    ),
+    figure2a = paste(
+      "cp",
+      file.path(bp, "figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"),
+      file.path(bp, "allFigures/Figure2/"),
+      sep = " "
+    ),
+    figure2b = paste(
+      "cp",
+      file.path(bp, "figure2b_HctHekDox/figure2b_HctHekDox.pdf"),
+      file.path(bp, "allFigures/Figure2/"),
+      sep = " "
+    ),
+    figure2c1 = paste(
+      "cp",
+      file.path(bp, "figure2c_P1construct/figure2c_P1construct_locus.ai"),
+      file.path(bp, "allFigures/Figure2/"),
+      sep = " "
+    ),
+    figure2c2 = paste(
+      "cp",
[…]

### 2017-11-17 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
fixed legend point sizes to correspond

@@
   scale_y_continuous("\u0394\u0394Ct", breaks = c(-1,0,1,2,3,4,5))+
-  labs(x = "Treatment") +
-  guides(
-    fill = guide_legend(title = "Cell line", override.aes = list(size = 6))
-  )
+  labs(x = "Treatment")
 
@@
     show.legend = FALSE
+  )  +
+  guides(
+    fill = guide_legend(
+      title = "Cell line", 
+      override.aes = list(size = 6)
+    )
   )
@@
     show.legend = FALSE
+  )   +
+  guides(
+    fill = guide_legend(
+      title = "Cell line", 
+      override.aes = list(size = 4)
+    )
   )

### 2017-11-17 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
fixed legend point sizes to correspond

@@
   guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 6)
+    )
   )
@@
 
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 83,
-#    units = "mm"
-# )
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```

### 2017-11-17 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
all first version pdfs done
fixed legend point sizes to correspond

@@
   scale_y_continuous("\u0394\u0394Ct")+
-  labs(x = "Cell line") +
-  guides(
-    fill = guide_legend(title = "Gene", override.aes = list(size = 6))
-  )
+  labs(x = "Cell line")
 
@@
     show.legend = FALSE
+  ) +
+  guides(
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 6)
+    )
   )
@@
     show.legend = FALSE
+  ) +
+  guides(
+    fill = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 4)
+    )
   )

### 2017-11-17 inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.Rmd
fixed legend point sizes to correspond

--- 2017-11-14 inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.Rmd
@@
   ) +
+  scale_y_continuous(labels = scales::percent_format()) +
+  labs(
+    x = "Cell cycle phase",
+    y = "",
+    title = "Cell cycle"
+  )
+
+markdown <- p +
   geom_linerange(
@@
   ) +
-  scale_y_continuous(labels = scales::percent_format()) +
-  labs(
-    x = "Cell cycle phase",
-    y = "",
-    title = "Cell cycle"
+  guides(
+    fill = guide_legend(
+      title = "Condition", 
+      override.aes = list(size = 6)
+    )
+  )
+
+plotRmarkdown(markdown)
+
+pdf <- p +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = phase, 
+      ymin = CI95l, 
+      ymax = CI95h, 
+      group = interaction(phase, condition)
+    ),
+    position = position_dodge(width = 0.9),
+    colour = "grey25",
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = phase, 
+      y = mean, 
+      group = condition
+    ), 
+    colour = "black",
+    position = position_dodge(width = 0.9),
+    shape = 95,
+    show.legend = FALSE
+  ) +
+  geom_segment(
+    data = stats,
+    aes(
+      x = x,
+      y = y + 0.01, 
+      xend = xend, 
+      yend = y + 0.01
+    ),
+    colour = "grey43",
+    size = 0.1,
+    show.legend = FALSE
+  ) +
+  geom_label(
+    data = stats,
+    aes(
+      x = phase, 
+      y = y + 0.025, 
+      label = pFormat
+    ),
+    label.size = 0,
+    label.padding = unit(0.01, "lines"),
+    show.legend = FALSE,
+    fill = "white",
+    size = 2,
+    family = "Arial Unicode MS"
   ) +
   guides(
-    fill = guide_legend(title = "Condition", override.aes = list(size = 6))
+    fill = guide_legend(
+      title = "Condition", 
+      override.aes = list(size = 4)
+    )
   )
 
-plotRmarkdown(p)
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
 
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```

### 2017-11-17 inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.Rmd
fixed legend point sizes to correspond

@@
   facet_grid(. ~ `Cell line`, scales = "free") +
+  labs(
+    x = "Cell line",
+    y = "log2(Fold)",
+    title = "miR34a asRNA"
+  ) +
+  guides(fill = FALSE)
+
+markdown <- p +
   geom_point(
@@
     show.legend = FALSE
-  ) +
-  labs(
-    x = "Cell line",
-    y = "log2(Fold)",
-    title = "miR34a asRNA"
-  ) +
-  guides(fill = FALSE)
+  )
 
@@
 
+pdf <- p +
+  geom_point(
+    data = stats,
+    aes(
+      x = Condition, 
+      y = mean
+    ),
+    colour = "grey20",
+    show.legend = FALSE,
+    shape = 95
+  ) +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = Condition, 
+      ymin = CI95l, 
+      ymax = CI95h
+    ),
+    colour = "gray20",
+    size = 0.1,
+    show.legend = FALSE
+  )
+
+figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"
+
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 83,
+ units = "mm"
+)
 ```

### 2017-11-18 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
working on figures

@@
     fill = "white",
-    size = 1,
+    size = 1.5,
     family = "Arial Unicode MS"

### 2017-11-18 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
working on figures

@@
     family = "Arial Unicode MS",
-    size = 1
+    size = 1.5
   ) +

### 2017-11-18 inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd
added gatherFigures and clearFigures functions and ran
working on figures

@@
 
+#prepare for plotting
+data <- data %>%
+  mutate(
+    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
+    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
+  )
+
+stats <- stats %>%
+  mutate(
+    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
+    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
+  )
 ```
@@
   geom_segment(
-    data = filter(stats, condition == "PC3 miR34a asRNA"),
+    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
     aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
@@
     fill = "white",
-    size = 2,
+    size = 1.5,
     family = "Arial Unicode MS"
@@
 
-# ggsave(
-#   plot = figure, 
-#   filename = path, 
-#   device = cairo_pdf, 
-#   height = 60,
-#   width = 83,
-#   units = "mm"
-# )
+ggsave(
+  plot = figure,
+  filename = path,
+  device = cairo_pdf,
+  height = 60,
+  width = 43,
+  units = "mm",
+  dpi = 10000000
+)
 ```

### 2017-11-18 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
working on figures

@@
   height = 60,
-  width = 83,
+  width = 43,
   units = "mm"

### 2017-11-18 data-raw/saveRDA.R

@@ -304,5 +304,28 @@ read_tsv('./data-raw/suppFigure2e_lnc34aSplJnc.txt') %>%
   ) %>%
   write_rds(., path = './data/suppFigure2e_lnc34aSplJnc.rds')
 
+#HEK293t P1
+read_tsv('./data-raw/suppFigure2a_HEK293tP1.txt') %>%
+  rename(`Biological Replicate` = experiment) %>%
+  mutate(
+    shRNA = gsub("shCrtl", "shCtrl", shRNA),
+    shRNA = gsub("shRenilla1.1", "shRenilla 1.1", shRNA),
+    shRNA = gsub("shRenilla2.1", "shRenilla 2.1", shRNA),
+    shRNA = gsub("shRenillaPool", "shRenilla pool", shRNA),
+    gene = gsub("B-actin", "Actin", gene)
+  ) %>%
+  mutate(
+    shRNA = parse_factor(
+      shRNA,
+      levels = c("shCtrl", "shRenilla 1.1", "shRenilla 2.1", "shRenilla pool")
+    ),
+    gene = parse_factor(
+      gene,
+      levels = c("Renilla", "Luciferase", "Actin")
+    )
+  ) %>%
+  write_rds(., path = './data/suppFigure2a_HEK293tP1.rds')
+
+
 
 #source('./data-raw/saveRDA.R')

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "Figure 1d"
subtitle: "miR34a asRNA 3-prime RACE"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

In order to define the 3' transcription termination site for the miR34a asRNA, 3'-RACE was performed.

<br></br>

####_Methods_

<br></br>

_Cell culture and 3-prime RACE_

All cell lines were cultured at 5% CO2 and 37° C with U2OS cells grown in McCoy’s 5a (Life Technologies). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. U2OS cell RNA was polyA-tailed using yeast polyA polymerase after which cDNA was synthesized using oligo(dT) primers. Nested-PCR was performed first using a forward primer in miR34a asRNA exon 1 (miR34a_asRNA_F10) and a tailed oligo(dT) primer (polyT_T7FAM) followed by a second PCR using an alternate miR34a asRNA exon 1 primer (miR34a_asRNA_F1) and a reverse primer binding to the tail of the previously used oligo(dT) primer (FAMprimer). PCR products were gel purified and cloned the Strata Clone Kit (Agilent Technologies), and sequenced.

<br></br>

_Primers_

```{r}

primers <- data.frame(
  name = c("miR34a_asRNA_F10", "polyT_T7FAM", "miR34a_asRNA_F1", "FAMprimer"),
  sequence = c(
    "ACG CGT CTC TCC AGC CCG GGA T",
    "CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
    "AGC GGC ATC TCC TCC ACC TGA AA",
    "CCG TAG CTC GTC CAG GAC CC"
  )
)
primers

```

<br></br>

####_Results_

```{r, out.width = "850px"}

url <- "figure1d_3primeRACE/results_hg38.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class = "caption">
3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript (LINC01759) from GENCODE.
</div>

<br></br>

####_Conclusions_

Sequencing of the resulting cloned cDNA indicated the transcripts 3’ transcription termination site to be 125bp upstream of the RP3-510D11.2 transcript’s annotated termination site.

<br></br><br></br>

### 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "Figure 1f"
subtitle: "miR34a asRNA coding potential via CPAT"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We utilized a bioinformatic approach to evaluate the coding potential of the miR34a asRNA transcript. The Coding-potential assessment tool uses a linear regression model to evaluate coding-potential by examining ORF length, ORF coverage, Fickett score and hexamer score. We further confirmed these results using the Coding-potential Calculator which utilizes a support based machine-based classifier and accesses an alternate set of discriminatory features.

<br></br>

####_Methods_

Protein-coding capacity was evaluated using the [Coding-potential Assessment Tool](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3616698/) and [Coding-potential Calculator](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1933232/) with default settings. Transcript sequences for use with Coding-potential Assessment Tool were downloaded from the UCSC genome browser using the following IDs: HOTAIR (ENST00000455246.1), XIST (ENST00000429829.1), β-actin (ENST00000331789.5), Tubulin (ENST00000427480.1), and MYC (ENST00000377970). Transcript sequences for use with Coding-potential Calculator were downloaded from the UCSC genome browser using the following IDs: HOTAIR (uc031qho.1), β-actin (uc003soq.4).

<br></br>

####_Results_

_Coding Potential Assesment Tool_

```{r}

url <- "figure1f_codingPotentialCPAT/results.txt"
cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat

```

<div class = "caption">
Coding potential analysis results from the Coding-potential Assessment Tool including miR34a asRNA and two characterized non-coding transcripts (HOTAIR and XIST) and 3 known coding transcripts (β-actin, tubulin, and MYC). 
</div>

*Results for Coding-potential Calculator are located in Supplementary figure 1g.

<br></br>

####_Conclusions_

Results indicated that miR34a asRNA has a similar lack of coding capacity to the known non-coding transcripts HOTAIR and XIST and differs greatly when examining these parameters to the known coding transcripts beta-actin, tubulin, and MYC. However, to fully evaluate coding potential methods such as mass spectrometry or ribosome profiling must be used.

<br></br><br></br>

### 2017-11-20 inst/coding_potential_cpc/coding_potential_cpc.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
@@
 ---
-title: "Figure 1f"
-subtitle: "miR34a asRNA coding potential via CPAT"
+title: "Supplementary Figure 1g"
+subtitle: "miR34a asRNA coding potential via CPC"
 author: "Jason T. Serviss"
@@
 
-####_Introduction_
-
-We utilized a bioinformatic approach to evaluate the coding potential of the miR34a asRNA transcript.
-The Coding-potential assessment tool uses a linear regression model to evaluate coding-potential by examining ORF length, ORF coverage, Fickett score and hexamer score.
-We further confirmed these results using the Coding-potential Calculator which utilizes a support based machine-based classifier and accesses an alternate set of discriminatory features.
-
-<br></br>
-
-####_Methods_
-
-Protein-coding capacity was evaluated using the [Coding-potential Assessment Tool](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3616698/) and [Coding-potential Calculator](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1933232/) with default settings.
-Transcript sequences for use with Coding-potential Assessment Tool were downloaded from the UCSC genome browser using the following IDs: HOTAIR (ENST00000455246.1), XIST (ENST00000429829.1), β-actin (ENST00000331789.5), Tubulin (ENST00000427480.1), and MYC (ENST00000377970).
-Transcript sequences for use with Coding-potential Calculator were downloaded from the UCSC genome browser using the following IDs: HOTAIR (uc031qho.1), β-actin (uc003soq.4).
-
-<br></br>
-
-####_Results_
-
-_Coding Potential Assesment Tool_
-
 ```{r}
 
-url <- "figure1f_codingPotentialCPAT/results.txt"
+url <- "suppFigure1g_codingPotentialCPC/results.txt"
 cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
@@
 <div class = "caption">
-Coding potential analysis results from the Coding-potential Assessment Tool including miR34a asRNA and two characterized non-coding transcripts (HOTAIR and XIST) and 3 known coding transcripts (β-actin, tubulin, and MYC).
+Analysis of coding potential of the miR34a asRNA transcript using the Coding-potential Calculator including miR34a asRNA, the characterized non-coding transcript HOTAIR, and the known coding transcript β-actin.
 </div>
 
-*Results for Coding-potential Calculator are located in Supplementary figure 1g.
-
 <br></br>
-
-####_Conclusions_
-
-Results indicated that miR34a asRNA has a similar lack of coding capacity to the known non-coding transcripts HOTAIR and XIST and differs greatly when examining these parameters to the known coding transcripts beta-actin, tubulin, and MYC.
-However, to fully evaluate coding potential methods such as mass spectrometry or ribosome profiling must be used.
-
-<br></br><br></br>

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-17 inst/figure2b_HctHekDox/figure2b_HctHekDox.Rmd
@@
     fill = "white",
-    size = 2,
+    size = 1.5,
     family = "Arial Unicode MS",

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-17 inst/figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd
@@
     fill = "white",
-    size = 1,
+    size = 1.5,
     family = "Arial Unicode MS",

### 2017-11-20 inst/isoforms/isoforms.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

@@
 ---
-title: "miR34a asRNA isoforms"
+title: "Supplementary figure 1d"
+subtitle: "miR34a asRNA isoform cloning"
 author: "Jason T. Serviss"
-date: "01/02/2017"
+date: "31/01/2017"
 output:
@@
     theme: flatly
-    toc: no
     code_folding: hide
+vignette: >
+  %\VignetteIndexEntry{Vignette Title}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
 ---
 
-#Introduction
+<style> 
+.caption { 
+  color: Black; 
+  font-family: "Times New Roman", Times, serif;
+  font-size: 1.0em; 
+}
+</style>
+
+```{r, echo = FALSE, message = FALSE}
+
+packages <- c(
+    "tidyverse",
+    "printr",
+    "ggthemes",
+    "readr",
+    "miR34AasRNAproject",
+    "grid",
+    "gtable"
+)
+purrr::walk(packages, library, character.only = TRUE)
+rm(packages)
+
+```
+
+```{r}
+
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+
+```
+
+####_Introduction_
+
 We investigated the propensity of miR34a asRNA to be alternatively spliced, using PCR cloning and sequencing.
 
-#Methods
+<br></br>
+
+####_Methods_
+
+<br></br>
+
+_Cell culture and cloning_
+
 All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies), .
@@
 Resulting PCR products were run on a agarose gel, gel extracted with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced.
+The sequencing results were visualized in the UCSC genome browser.
 
 <br></br>
-<center>![cloning gel](cloningGel.png)</center>
-<br></br>
-Cloned isoforms of the miR34a asRNA gene.
 
-##Primers
+_Primers_
+
 ```{r}
-library(printr)
+
 primers <- data.frame(
@@
 primers
+
 ```
 
-#Results
+<br></br>
 
-Product 8 resulted in miR34a AS 1  
-Product 6 resulted in miR34a AS 2  
-Product 2 resulted in miR34a AS 3  
-Product 5 resulted in miR34a AS 4
+####_Results_
+
+```{r, out.width = "850px"}
+
+url <- "suppFigure1d_isoforms/isoforms.png"
+knitr::include_graphics(file.path(projectUrl, url))
+
+```
+
+<div class = "caption">
+Sequencing results from the analysis of miR34a asRNA isoforms in U2OS cells. miR34a AS ref. refers to the full length transcript as defined by the 3’-RACE and primer walk assay.
+</div>
 
 <br></br>
-<center>![isoforms.](isoforms.png)</center>
-<br></br>
-Cloned isoforms of the miR34a asRNA gene.
 
-#Conclusions
+####_Conclusions_
+
 Results indicate that the miR34a asRNA transcript is post-transcriptionally spliced to form several different isoforms.
+
+<br></br><br></br>

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-14 inst/suppFigure2d_lnc34aCage/lnc34aCAGE.Rmd
@@
     "gtable",
-    "miR34AasRNAproject"
+    "miR34AasRNAproject",
+    "ggthemes"
 )
@@
     arrange(desc(level)) %>%
-    mutate(y = 1:length(pull(., level)))
+    mutate(
+      y = 1:length(pull(., level)),
+      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
+    )
 
@@
 
-```{r, fig.align='center', fig.height=8, fig.width=12}
-###plot
+```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
+###plot rmarkdown
 
+#genes
 p1 <- ggplot(data = NULL) +
@@
 
+#cage
 p2 <- ggplot(data = NULL) +
@@
   xlim(9241000, 9257900) +
-  guides(fill = guide_colourbar(title = "RPKM", title.position = "top", title.hjust = 0.5))
+  guides(fill = guide_colourbar(
+    title = "RPKM", 
+    title.position = "top", 
+    title.hjust = 0.5)
+  )
 
+#density
 p3 <- ggplot(data = NULL) + 
-  geom_density(data = cage, aes(x = start)) +
+  geom_line(data = cage, aes(x = start), stat="density") +
   ggthemes::theme_few() +
@@
 grid.draw(resize_heights(g, unit(c(3,1,1), "null")))
+
+#plot pdf
+#genes
+p1 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = filter(data, feature == "exon"),
+    aes(xmin = start, xmax = stop, y = gene, fill = gene),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = grid::unit(1, "mm"),
+    colour = "gray",
+    lwd = 0.1
+  ) +
+  ggthemes::theme_few() +
+  ggthemes::scale_fill_ptol() +
+  geom_segment(
+    data = filter(data, feature == "intron"),
+    aes(x = start, xend = stop, y = gene, yend = gene),
+    linetype = "dotted",
+    colour = "gray",
+    size = 0.25
+  ) +
+  xlim(9241000, 9257900) +
+  labs(x = "Chromosome 1", y = "Genes") +
+  guides(fill = FALSE) +
+  theme(
+    axis.text = element_text(size = 3),
+    axis.title.x = element_text(size = 4),
+    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
+    axis.ticks.length = unit(0.5, "mm"),
+    axis.ticks = element_line(size = 0.15),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm")
+  )
+
+#cage
+p2 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = cage,
+    aes(xmin = start, xmax = stop, y = y, fill = level),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = unit(2, "pt"),
+    colour = NA,
+    lwd = 0.1,
+    show.legend = TRUE
+  ) +
+  ggthemes::theme_few() +
+  viridis::scale_fill_viridis() +
+  theme(
+    axis.title.x = element_blank(),
+    axis.title.y = element_text(size = 4),
+    legend.position = "top",
+    legend.title = element_text(size = 4),
+    legend.text = element_text(size = 4),
+    legend.box.spacing = unit(3, "pt"),
+    axis.text = element_blank(),
+    axis.ticks = element_blank(),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
+    strip.text.y = element_text(angle = 0)
+  ) +
+  labs(y = "Cage reads") +
+  xlim(9241000, 9257900) +
+  guides(fill = guide_colourbar(
+    title = "RPKM",
+    title.position = "top",
+    title.hjust = 0.5,
+    barheight = unit(4, "pt"),
+    barwidth = unit(40, "pt")
+  ))
+
+#density
+p3 <- ggplot(data = NULL) + 
+  geom_line(data = cage, aes(x = start), stat="density", lwd = 0.1) +
+  ggthemes::theme_few() +
+  xlim(9241000, 9257900) +
+  theme(
+    axis.text = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_text(size = 4),
+    axis.ticks = element_blank(),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0, 1, 0, 1), "mm")
+  ) +
+  labs(y = "Density")
+
+grobz <- lapply(list(p1, p2, p3), ggplotGrob)
+g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
+g <- resize_heights(g, unit(c(6, 1, 1), "null"))
+#grid.draw(g)
+
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2d_lnc34aCage/suppFigure2d_lnc34aCage.pdf"
+ggsave(
+  plot = g, 
+  filename = path, 
+  device = cairo_pdf, 
+  height = 60,
+  width = 83,
+  units = "mm"
+)
 ```

### 2017-11-20 inst/mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "Figure 1b"
subtitle: "miR34a asRNA Expression Cell Panel"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"

```

####_Introduction_

We wished to examine expression of miR34a asRNA in different cancer tissues and, therefore, utilized a panel of common cancer cell lines to detect miR34a asRNA expression, as well as, miR34a HG. We included both p53 wild type, p53 mutated, and p53 null cell lines in the cell line panel due to the fact that miR34a is a known downstream target of p53.

<br></br>

####_Methods_

<br></br>

_Cell culture and PCR_

Cells were cultured with the appropriate growth medium and seeded at a desity between 50-75% confluency. The following day, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. PCR was run for 35 or 38 or 16 cycles for miR34a asRNA, miR34a HG, and beta-actin, respectivley, with 58˚C annealing temperature. PCR products were analyzed on a 2% agarose gel.

<br></br>

_Primers_

```{r}

primers <- data.frame(
    name=c(
        "miR34a asRNA F1",
        "miR34a asRNA R1",
        "miR34aHG_F",
        "miR34aHG_R",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers

```

<br></br>

####_Results_

```{r, out.width = "850px"}

url <- "figure1b_miR34aASExpressionCellPanel/cellPanelLarge.png"
knitr::include_graphics(file.path(projectUrl, url))

```

<div class = "caption">
Semi-quantitative PCR data from the screening of a panel of cell lines. 
* Indicates that, although the cell line is p53wt, other mechanisms are present which inhibit p53 function. 
</div>

<br></br>

####_Conclusions_

We were able to detect co-expression of both miR34a HG and miR34a AS in a variety of cell lines, including HCT116 human colon cancer cells and 293T human embryonic kidney cells.

<br></br><br></br>

### 2017-11-20 inst/mir34a_locus/mir34a_locus.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-20 inst/mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd
@@
 ---
-title: "Figure 1b"
-subtitle: "miR34a asRNA Expression Cell Panel"
+title: "Figure 1a"
+subtitle: "miR34a Locus"
 author: "Jason T. Serviss"
@@
 
-We wished to examine expression of miR34a asRNA in different cancer tissues and, therefore, utilized a panel of common cancer cell lines to detect miR34a asRNA expression, as well as, miR34a HG.
-We included both p53 wild type, p53 mutated, and p53 null cell lines in the cell line panel due to the fact that miR34a is a known downstream target of p53.
+An antisense transcript to the miR34a HG was detected using the UCSC genome browser.
 
@@
 
-<br></br>
-
-_Cell culture and PCR_
-
-Cells were cultured with the appropriate growth medium and seeded at a desity between 50-75% confluency.
-The following day, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies).
-500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.
-PCR was run for 35 or 38 or 16 cycles for miR34a asRNA, miR34a HG, and beta-actin, respectivley, with 58˚C annealing temperature.
-PCR products were analyzed on a 2% agarose gel.
-
-<br></br>
-
-_Primers_
-
-```{r}
-
-primers <- data.frame(
-    name=c(
-        "miR34a asRNA F1",
-        "miR34a asRNA R1",
-        "miR34aHG_F",
-        "miR34aHG_R",
-        "B-actin_F",
-        "B-actin_R"
-    ),
-    sequence=c(
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT",
-        "TCT GCT CCA GTG GCT GAT GAG AAA",
-        "GTT CAC TGG CCT CAA AGT TGG CAT",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
-primers
-
-```
+The USCS genome browser was utilized for the bioinformatic evaluation of antisense transcription at the miR34a locus.
 
@@
 
-url <- "figure1b_miR34aASExpressionCellPanel/cellPanelLarge.png"
+url <- "figure1a_miR34aLocus/miR34aLocus_hg38.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class = "caption">
-Semi-quantitative PCR data from the screening of a panel of cell lines. 
-* Indicates that, although the cell line is p53wt, other mechanisms are present which inhibit p53 function. 
+A schematic picture of the miR34a locus from the UCSC genome browser (hg38) including miR34a HG and mature miR34a, and LINC01759. H3K4me3 ChIP-seq and conservation over the locus is also shown.
 </div>
@@
 
-####_Conclusions_
+####_Conclusion_
 
-We were able to detect co-expression of both miR34a HG and miR34a AS in a variety of cell lines, including HCT116 human colon cancer cells and 293T human embryonic kidney cells.
+GENCODE annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.
 

### 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

---
title: "P1 shRenilla HEK293t transfections"
author: "Jason T. Serviss"
date: "12/01/2017"
output:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

#Introduction
Functional characterization of individual antisense transcripts has previously shown their capability to regulate their sense gene. We therefore investigated the possibility that miR34a asRNA may regulate miR34a HG levels. We hypothesized that the overlapping regions of the sense and antisense transcripts may have a crucial role in miR34a asRNAs ability to regulate miR34a HG via RNA:DNA or RNA:RNA interaction. Accordingly, we first co-transfected the p1 construct, containing the overlapping region of the two transcripts, and an short hairpin (sh) RNA targeting renilla into HEK293T cells .

#Methods
We utilized the P1 construct where the overlapping region of miR34a HG and miR34a AS is cloned with luciferase downstream of miR34a HG and renilla downstream of miR34a AS. The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis. Mol Cell, 2007. 26(5): p. 731-43. All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone). All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin. 2.5x10^5 293T cells were seeded in a 12-well plate. After 24hrs these were co-transfected with 50 ng of the P1 construct and 250 ng shRenilla using lipo2k standard protocol. After 48 hours, RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.

```{r}
library(printr)
p1 <- data.frame(
    name="p1",
    sequence="GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
              CCT GCT C"
)
p1
```

```{r}
shRNAs <- data.frame(
    name=c(
        "shRenilla1.1",
        "shRenilla2.1"
    ),
    sequence=c(
        "AAT ACA CCG CGC TAC TGG C",
        "TAA CGG GAT TTC ACG AGG C"
    )
)
shRNAs
```

```{r}
primers <- data.frame(
    name=c(
        "Luc_set_II_F",
        "Luc_set_II_R",
        "Renilla_pBiDir_F1",
        "Renilla_pBiDir_R1",
        "B-actin_F",
        "B-actin_R"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)
primers
```

#Results
```{r}
library(reshape2)
library(ggplot2)
library(ggthemes)
library(plyr)
data <- read.table('~/GitHub/miR34aFigures/inst/HEK293tP1/QPCRdata.txt', header=TRUE, sep="\t")

goi <- subset(data, gene %in% c("Luciferase", "Renilla"))
hk <- subset(data, gene == "B-actin")
hk <- rbind(hk,hk)
hk <- hk[order(hk$belongsTo), ]

colnames(goi)[5:6] <- c("Ct1GOI", "Ct2GOI")
colnames(hk)[5:6] <- c("Ct1HK", "Ct2HK")

data <- cbind(goi, hk[,c("Ct1HK", "Ct2HK")])
data$meanGOI <- rowMeans(data[,c("Ct1GOI", "Ct2GOI")])
data$meanHK <- rowMeans(data[,c("Ct1HK", "Ct2HK")])

#ddct
data$dct <- data$meanGOI - data$meanHK
ddct <- ddply(
    data,
    c("experiment", "shRNA", "belongsTo", "gene"),
    summarize,
    ddct=dct-data[data$experiment == experiment & data$shRNA == "shCrtl" & data$belongsTo == belongsTo & data$gene == gene, "dct"]
)
data <- merge(data, ddct, by=c("experiment", "shRNA", "belongsTo", "gene"))

data$fold <- 2^-data$ddct
data$log2fold <- log2(data$fold)

#calculate stats
stats <- ddply(
    data,
    c("shRNA", "belongsTo", "gene"),
    summarize,
    mean=mean(log2fold),
    pValue=t.test(log2fold, data[data$shRNA == "shCrtl" & data$belongsTo == belongsTo & data$gene == gene ,"log2fold"], alternative="less")$p.value,
    CI95l=t.test(log2fold)$conf.int[1],
    CI95h=t.test(log2fold)$conf.int[2]
)

stats$pStars <- ifelse(
    stats$pValue < 0.05 & stats$pValue > 0.0049, 
    "\u2605", 
    ifelse(
        stats$pValue < 0.005 & stats$pValue > 0.00049, 
        "\u2605\u2605",
        ifelse(
            stats$pValue < 0.0005, 
            "\u2605\u2605\u2605",
            ""
        )
    )
)

data <- merge(data, stats, by=c("shRNA", "belongsTo", "gene"))
```

```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
#plot for rmarkdown
ggplot(data, aes(x=shRNA, y=log2fold))+
    geom_violin(
        aes(fill=gene),
        trim=TRUE,
        alpha=0.3,
        color=NA,
        scale="width",
        show.legend = FALSE
    )+
    geom_point( 
        aes(colour=gene),
        size=4,
        position=position_dodge(width=0.9)
    )+
#    geom_linerange(
#        aes(ymin=CI95l, ymax=CI95h, group=gene),
#        colour="black",
#        position=position_dodge(width=0.9),
#        show.legend = FALSE
#    )+
    geom_point(
        aes(y=mean, group=gene),
        colour="black",
        position=position_dodge(width=0.9),
        show.legend = FALSE
    )+
#    geom_label(
#        aes(y=CI95h+0.15, label=pStars, group=gene),
#        label.size=0,
#        label.padding=unit(0.01, "lines"),
#        show.legend = FALSE,
#        fill="white",
#        size=5,
#        family="Arial Unicode MS",
#        position=position_dodge(width=0.9)
#    )+
    scale_y_continuous(
        "\u0394\u0394Ct",
        sec.axis = sec_axis(
            ~2^., 
            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}),
            label=round(c(2^-6,2^-5,2^-4,2^-3,2^-2,2^-1,2^0), digits=3),
            breaks=c(2^-6,2^-5,2^-4,2^-3,2^-2,2^-1,2^0)
        )
    )+
    labs(
      x="shRNA",
      title="HEK293t",
      caption=
            "miR34a (luficerase) and miR34a asRNA (renilla) in HEK293t cells which were co-transfected with the P1 construct and the specified shRNA.\nError bars (black vertical) indicate 95% CI and means are represented by black dots."
    )+
    theme_few()+
    scale_fill_ptol()+
    scale_colour_ptol()+
    #values=c("#014d64", "#6794a7")
    theme(
        plot.title = element_text(
            hjust = 0.5,
            face="bold",
            size=20
        ),
        plot.caption = element_text(
            hjust=0, 
            margin=margin(t=15),
            family="Arial Unicode MS"
        ),
        legend.position="top",
        legend.title=element_text(size=17),
        legend.text=element_text(size=15),
        axis.title=element_text(size=17),
        axis.title.x=element_text(margin=margin(t=10)),
        axis.text=element_text(size=15),
        strip.text.x=element_text(size=17)
    )+
    guides(color = guide_legend(title = "Gene", override.aes = list(size=3)))

#plot for pdf
```

#Conclusions
Analysis of luciferase and renilla expression revealed that by decreasing levels of the renilla transcript (corresponding to miR34a asRNA) luciferase (corresponding to miR34a HG) levels were concomitantly decreased. These results indicate that miR34a asRNA is capable of regulating the miR34a HG in a concordant manner and that the overlapping region of the miR34a asRNA may be sufficient to mediate this regulation.

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-15 inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.Rmd
@@
 
-#ggsave(
-#  plot = figure, 
-#  filename = path, 
-#  device = cairo_pdf, 
-#  height = 60,
-#  width = 83,
-#  units = "mm"
-#)
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 43,
+ units = "mm"
+)
 ```

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-15 inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.Rmd
@@
   guides(
-    colour = guide_legend(title = "Cell line", override.aes = list(size = 3))
+    colour = guide_legend(
+      title = "Cell line", 
+      override.aes = list(size = 3)
+    )
   )
@@
   guides(
-    colour = guide_legend(title = "Cell line", override.aes = list(size = 2))
+    colour = guide_legend(
+      title = "Cell line", 
+      override.aes = list(size = 2)
+    )
   )
@@
 figure <- plotPDF(pdf)
+path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"
 
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"
-# ggsave(
-#   plot = figure,
-#   filename = path,
-#   device = cairo_pdf,
-#   height = 60,
-#   width = 83,
-#   units = "mm"
-# )
+ggsave(
+  plot = figure,
+  filename = path,
+  device = cairo_pdf,
+  height = 60,
+  width = 83,
+  units = "mm"
+)
 ```

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

--- 2017-11-15 inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.Rmd
@@
   ) +
-  guides(color = guide_legend(title = "Gene", override.aes = list(size = 3)))
+  guides(
+    color = guide_legend(
+      title = "Gene", 
+      override.aes = list(size = 3)
+    )
+  )
 
@@
 
-#ggsave(
-#  plot = figure, 
-#  filename = path, 
-#  device = cairo_pdf, 
-#  height = 60,
-#  width = 83,
-#  units = "mm"
-#)
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 83,
+ units = "mm"
+)
 ```

### 2017-11-20 R/gatherFigures.R

@@ -1,192 +1,25 @@
 
 gatherFigures <- function() {
-  bp <- "~/Github/miR34a_asRNA_project/inst/"
-  cmds <- list(
-    figure1a = paste(
+  bp <- "~/Github/miR34a_asRNA_project/inst"
+  rmds <- fileMap()
+  exts <- lapply(rmds, function(x) gsub("\\.Rmd$", "\\.pdf", x))
+  cmds <- lapply(1:length(exts), function(x)
+    paste(
       "cp",
-      file.path(bp, "figure1a_miR34aLocus/figure1a_miR34aLocus_hg38.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure1b = paste(
-      "cp",
-      file.path(bp, "figure1b_miR34aASExpressionCellPanel/figure1b_miR34aASExpressionCellPanel.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure1c = paste(
-      "cp",
-      file.path(bp, "figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure1d = paste(
-      "cp",
-      file.path(bp, "figure1d_3primeRACE/figure1d_3primeRACE_hg38.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure1e = paste(
-      "cp",
-      file.path(bp, "figure1e_primerWalk/figure1e_primerWalk.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure1f = paste(
-      "cp",
-      file.path(bp, "figure1f_codingPotentialCPAT/figure1f_codingPotentialCPAT.ai"),
-      file.path(bp, "allFigures/Figure1/"),
-      sep = " "
-    ),
-    figure2a = paste(
-      "cp",
-      file.path(bp, "figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"),
-      file.path(bp, "allFigures/Figure2/"),
-      sep = " "
-    ),
-    figure2b = paste(
-      "cp",
-      file.path(bp, "figure2b_HctHekDox/figure2b_HctHekDox.pdf"),
-      file.path(bp, "allFigures/Figure2/"),
-      sep = " "
-    ),
-    figure2c1 = paste(
[…]

### 2017-11-20 R/processFigures.R

@@ -31,42 +31,8 @@ plotFigure <- function(figure, ...) {
 
 #returns the path to the figure's .rmd file
 getPath <- function(figure) {
-  map <- makeMap()
+  map <- fileMap(type = "Rmd")
   map[figure][[1]]
-}
-
-#returns a map of paths to each figures .rmd file
-makeMap <- function() {
-  list(
-    figure1a = "figure1a_miR34aLocus/figure1a_miR34aLocus.Rmd",
-    figure1b = "figure1b_miR34aASExpressionCellPanel/figure1b_miR34aASExpressionCellPanel.Rmd",
-    figure1c = "figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.Rmd",
-    figure1d = "figure1d_3primeRACE/figure1d_3primeRACE.Rmd",
-    figure1e = "figure1e_primerWalk/figure1e_primerWalk.Rmd",
-    figure1f = "figure1f_codingPotentialCPAT/figure1f_codingPotentialCPAT.Rmd",
-    figure2a = "figure2a_HCT116p53null/figure2a_HCT116p53null.Rmd",
-    figure2b = "figure2b_HctHekDox/figure2b_HctHekDox.Rmd",
-    figure2c = "figure2c_P1construct/figure2c_P1construct.Rmd",
-    figure2d = "figure2d_P1-HCTandHEK/figure2d_P1-HCTandHEK.Rmd",
-    figure2e = "figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd",
-    figure3a = "figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd",
-    figure3b = "figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.Rmd",
-    figure3c = "figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.Rmd",
-    figure3d = "figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd",
-    figure3e = "figure3e_survival/figure3e_survival.Rmd",
-    suppFigure1a = "suppFigure1a_TCGAcorrelationTable/suppFigure1a_TCGAcorrelationTable.Rmd",
-    suppFigure1b = "suppFigure1b_primerWalkSchematic/suppFigure1b_primerWalkSchematic.Rmd",
[…]

### 2017-11-20 R/utils.R

@@ -1,5 +1,75 @@
 
-#used to download and filter data with map in saveRDA.R file
+#' fileMap
+#'
+#' Maps figures to various source file types.
+#'
+#' @name fileMap
+#' @rdname fileMap
+#' @aliases fileMap
+#' @param type, character; The type of source file to map. Can be Rmd, pdf, or
+#'    rds, or png.
+#' @return list.
+#' @author Jason T. Serviss
+#' @examples
+#'
+#' fileMap()
+#'
+NULL
+
+#' @rdname fileMap
+#' @export
+
+fileMap <- function(type) {
+  pList <- list(
+    figure1a = "mir34a_locus/mir34a_locus.Rmd",
+    figure1b = "mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd",
+    figure1c = "tcga_correlation/tcga_correlation.Rmd",
+    figure1d = "3_prime_race/3_prime_race.Rmd",
+    figure1e = "primer_walk/primer_walk.Rmd",
+    figure1f = "coding_potential_cpat/coding_potential_cpat.Rmd",
+    figure2a = "hct116_p53_null/hct116_p53_null.Rmd",
+    figure2b = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
+    figure2c = "p1_construct/p1_construct.Rmd",
+    figure2d = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
+    figure2e = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
+    figure3a = "stable_line_expression/stable_line_expression.Rmd",
+    figure3b = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
+    figure3c = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
+    figure3d = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
+    figure3e = "tcga_survival/tcga_survival.Rmd",
+    suppFigure1a = "tcga_correlation_table/tcga_correlation_table.Rmd",
+    suppFigure1b = "primer_walk_schematic/primer_walk_schematic.Rmd",
+    suppFigure1c = "polyadenylation/polyadenylation.Rmd",
+    suppFigure1d = "isoforms/isoforms.Rmd",
+    suppFigure1e = "cellular_localization/cellular_localization.Rmd",
[…]

### 2017-11-20 data-raw/saveRDA.R

@@ -1,331 +1,0 @@
-library(tidyverse)
-library(miR34AasRNAproject)
-
-#HCTp53null
-read_tsv('./data-raw/figure2a_HCT116p53null.txt', col_names = TRUE) %>%
-  rename(gene = Target) %>%
-  mutate(
-    Condition = case_when(
-      Condition == "WT"       ~ "HCT116 p53-wt",
-      Condition == "p53 null" ~ "HCT116 p53-null",
-      TRUE                    ~ "error in saveRDA.R"
-    ),
-    gene = case_when(
-      gene == "miR34a AS" ~ "miR34a asRNA",
-      gene == "miR34a HG" ~ "miR34a HG",
-      gene == "Actin"     ~ "Actin",
-      TRUE                ~ "error in saveRNA.R"
-    )
-  ) %>%
-  mutate(
-    Treatment = parse_factor(
-      Treatment,
-      levels = c("0", "100", "200", "500")
-    ),
-    Condition = parse_factor(
-      Condition,
-      levels = c("HCT116 p53-wt", "HCT116 p53-null")
-    ),
-    gene = parse_factor(
-      gene,
-      levels = c("miR34a HG", "miR34a asRNA", "Actin")
-    )
-  ) %>%
-  write_rds(., path = './data/figure2a_HCT116p53null.rds')
-
-#HctHekDox
-read_tsv('./data-raw/figure2b_HctHekDox.txt', col_names = TRUE) %>%
-  rename(
-    `Biological Replicate` = experiment,
-    `Cell line` = cellLine,
-    Treatment = treatment
-  ) %>%
-  mutate(Treatment = parse_factor(
-    Treatment,
-    levels = c("untreated", "doxorubicin")
-  )) %>%
-  mutate(gene = case_when(
-    gene == "B-actin" ~ "Actin",
-    TRUE              ~ gene
-  )) %>%
-  write_rds(., path = './data/figure2b_HctHekDox.rds')
-
-#P1-HCTandHEK
-read_tsv('./data-raw/figure2d_P1-HCTandHEK.txt', col_names = TRUE) %>%
-  rename(
-    `Biological Replicate` = experiment,
-    `Cell line` = cellLine
-  ) %>%
-  mutate(
-    gene = case_when(
-      gene == "renilla"    ~ "Renilla",
-      gene == "luciferase" ~ "Luciferase",
-      TRUE                 ~ "error in saveRNA.R"
-    ),
[…]

### 2017-11-20 data-raw/saveRDS.R

@@ -1,0 +1,347 @@
+library(tidyverse)
+library(miR34AasRNAproject)
+
+#hct116_p53_null
+print("processing hct116_p53_null")
+read_tsv('./data-raw/hct116_p53_null.txt', col_names = TRUE) %>%
+  rename(gene = Target) %>%
+  mutate(
+    Condition = case_when(
+      Condition == "WT"       ~ "HCT116 p53-wt",
+      Condition == "p53 null" ~ "HCT116 p53-null",
+      TRUE                    ~ "error in saveRDA.R"
+    ),
+    gene = case_when(
+      gene == "miR34a AS" ~ "miR34a asRNA",
+      gene == "miR34a HG" ~ "miR34a HG",
+      gene == "Actin"     ~ "Actin",
+      TRUE                ~ "error in saveRNA.R"
+    )
+  ) %>%
+  mutate(
+    Treatment = parse_factor(
+      Treatment,
+      levels = c("0", "100", "200", "500")
+    ),
+    Condition = parse_factor(
+      Condition,
+      levels = c("HCT116 p53-wt", "HCT116 p53-null")
+    ),
+    gene = parse_factor(
+      gene,
+      levels = c("miR34a HG", "miR34a asRNA", "Actin")
+    )
+  ) %>%
+  write_rds(., path = './data/hct116_p53_null.rds')
+
+#hct116_hek293t_dox
+print("processing hct116_hek293t_dox")
+read_tsv('./data-raw/hct116_hek293t_dox.txt', col_names = TRUE) %>%
+  rename(
+    `Biological Replicate` = experiment,
+    `Cell line` = cellLine,
+    Treatment = treatment
+  ) %>%
+  mutate(Treatment = parse_factor(
+    Treatment,
+    levels = c("untreated", "doxorubicin")
+  )) %>%
+  mutate(gene = case_when(
+    gene == "B-actin" ~ "Actin",
+    TRUE              ~ gene
+  )) %>%
+  write_rds(., path = './data/hct116_hek293t_dox.rds')
+
+#p1_hct116_hek293t
+print("processing p1_hct116_hek293t")
+read_tsv('./data-raw/p1_hct116_hek293t.txt', col_names = TRUE) %>%
+  rename(
+    `Biological Replicate` = experiment,
+    `Cell line` = cellLine
+  ) %>%
+  mutate(
+    gene = case_when(
+      gene == "renilla"    ~ "Renilla",
[…]

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
starting to change Rmds to use new fileMap function

--- 2017-11-14 inst/suppFigure1e_cellularLocalization/suppFigure1e_cellularLocalization.Rmd
@@
 projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 
@@
 
-url <- "suppFigure1e_cellularLocalization.rds"
+url <- fileMap(type = "rds")["suppFigure1e"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
+figure <- plotPDF(p)
+path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1e_cellularLocalization/suppFigure1e_cellularLocalization.pdf"
+
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 83,
+ units = "mm"
+)
 ```

### 2017-11-20 inst/mir34a_locus/mir34a_locus.Rmd
starting to change Rmds to use new fileMap function

@@
 
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
 dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
@@
 
-url <- "figure1a_miR34aLocus/miR34aLocus_hg38.png"
+url <- "mir34a_locus/mir34a_locus_hg38.png"
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
starting to change Rmds to use new fileMap function
more of the previous commit

@@
 
-url <- "figure1d_3primeRACE/results_hg38.png"
+url <- fileMap(type = "png")["figure1d"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
more of the previous commit 2

@@
   "grid",
-    "gtable"
+  "gtable",
+  "grDevices"
 )
@@
 
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
 dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
@@
 figure <- plotPDF(p)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1e_cellularLocalization/suppFigure1e_cellularLocalization.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
 

### 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
more of the previous commit 2

@@
 
-url <- "figure1f_codingPotentialCPAT/results.txt"
+#url <- "figure1f_codingPotentialCPAT/results.txt"
+url <- fileMap(type = "png")["figure1f"][[1]]
+
 cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")

### 2017-11-20 R/utils.R
more of the previous commit 2

@@ -7,7 +7,7 @@
 #' @rdname fileMap
 #' @aliases fileMap
 #' @param type, character; The type of source file to map. Can be Rmd, pdf, or
-#'    rds, or png.
+#'    rds, txt, or png.
 #' @return list.
 #' @author Jason T. Serviss
 #' @examples
@@ -57,6 +57,11 @@ fileMap <- function(type) {
     base <- lapply(pList, basename)
     dir <- lapply(base, function(x) file.path("data", x))
     ext <- lapply(dir, function(x) gsub("\\.Rmd$", "\\.rds", x))
+    return(ext)
+  } else if(type == "txt") {
+    base <- lapply(pList, basename)
+    dir <- lapply(base, function(x) file.path("data-raw", x))
+    ext <- lapply(dir, function(x) gsub("\\.Rmd$", "\\.txt", x))
     return(ext)
   } else if(type == "pdf") {
     ext <- lapply(pList, function(x) gsub("\\.Rmd$", "\\.pdf", x))

### 2017-11-20 data-raw/saveRDS.R

@@ -342,6 +342,9 @@ read_tsv('./data-raw/p1_hek293t.txt') %>%
   ) %>%
   write_rds(., path = './data/p1_hek293t.rds')
 
+#coding_potential_cpat
+read_tsv('./data-raw/coding_potential_cpat.txt') %>%
+  write_rds(., path = './data/coding_potential_cpat.rds')
 
 
 #source('./data-raw/saveRDS.R')

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
more of the previous commit 4

@@
 projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 

### 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
more of the previous commit 4

--- 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
@@
 
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 
@@
 
-url <- "figure1f_codingPotentialCPAT/results.txt"
-cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
+url <- fileMap(type = "rds")["figure1f"][[1]]
+cpat <-read_rds(url(file.path(dataUrl, url)))
 cpat

### 2017-11-20 inst/mir34a_locus/mir34a_locus.Rmd
more of the previous commit
more of the previous commit 4

@@
 
-url <- "mir34a_locus/mir34a_locus_hg38.png"
+url <- fileMap(type = "png")["figure1a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 data-raw/saveRDS.R

@@ -346,5 +346,9 @@ read_tsv('./data-raw/p1_hek293t.txt') %>%
 read_tsv('./data-raw/coding_potential_cpat.txt') %>%
   write_rds(., path = './data/coding_potential_cpat.rds')
 
+#coding_potential_cpc
+read_tsv('./data-raw/coding_potential_cpc.txt') %>%
+  write_rds(., path = './data/coding_potential_cpc.rds')
+
 
 #source('./data-raw/saveRDS.R')

### 2017-11-20 inst/coding_potential_cpc/coding_potential_cpc.Rmd
more of the previous commit 5

@@
 
-url <- "suppFigure1g_codingPotentialCPC/results.txt"
-cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
+url <- fileMap(type = "rds")["suppFigure1g"][[1]]
+cpat <- read_rds(url(file.path(dataUrl, url)))
 cpat

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
more of the previous commit 5

@@
 
-url <- "figure2b_HctHekDox.rds"
+url <- fileMap(type = "rds")["figure2b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure2b_HctHekDox/figure2b_HctHekDox.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
 

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
more of the previous commit 5

@@
 
-url <- "figure2a_HCT116p53null.rds"
+url <- fileMap(type = "rds")["figure2a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure2a_HCT116p53null/figure2a_HCT116p53null.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
 

### 2017-11-20 inst/isoforms/isoforms.Rmd
more of the previous commit 5

@@
 
-url <- "suppFigure1d_isoforms/isoforms.png"
+url <- fileMap(type = "png")["suppFigure1d"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
more of the previous commit 5

@@
 ```{r, message = FALSE}
+
 packages <- c(
@@
 rm(packages)
+
+```
+
+```{r}
+
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+
 ```
@@
 nrCellLinesDown <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
-  url <- "suppFigure2d_lnc34aCage.txt"
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "txt")["suppFigure2d"][[1]]
+
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 cellLinesInFinal <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-  url <- "suppFigure2d_lnc34aCage.rds"
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "rds")["suppFigure2d"][[1]]
+
   read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDA.R file.
+All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
 Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
@@
 
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-url <- "suppFigure2d_lnc34aCage.rds"
+url <- fileMap(type = "rds")["suppFigure2d"][[1]]
 cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2d_lnc34aCage/suppFigure2d_lnc34aCage.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])
+
 ggsave(

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
more of the previous commit 5

--- 2017-11-15 inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.Rmd
@@
 ```{r, echo = FALSE, message = FALSE}
+
 packages <- c(
@@
 nrCellLinesDown <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data-raw"
-  url <- "suppFigure2e_lnc34aSplJnc.txt"
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "txt")["suppFigure2e"][[1]]
+
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 cellLinesInFinal <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-  url <- "suppFigure2e_lnc34aSplJnc.rds"
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "rds")["suppFigure2e"][[1]]
+
   read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDA.R file.
+All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
 Of these cell lines `r cellLinesInFinal() %>% length()` cell lines had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
@@
 #splice junctions
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/data"
-url <- "suppFigure2e_lnc34aSplJnc.rds"
+url <- fileMap(type = "rds")["suppFigure2e"][[1]]
 splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2e_lnc34aSplJnc/suppFigure2e_lnc34aSplJnc.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])
+
 ggsave(

### 2017-11-20 inst/mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd
more of the previous commit 5

@@
 
-url <- "figure1b_miR34aASExpressionCellPanel/cellPanelLarge.png"
+url <- fileMap(type = "png")["figure1b"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/p1_construct/p1_construct.Rmd
more of the previous commit 6

--- 2017-11-14 inst/figure2c_P1construct/figure2c_P1construct.Rmd
@@
 
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 
@@
 
-url <- "figure2c_P1construct/locusSimple.png"
+url <- fileMap(type = "png")["figure2c"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class="caption">
-A schematic representation of the miR34a locus and the region cloned in the P1 construct including the overlapping region between miR34a host gene (purple) and miR34a asRNA (green), the region cloned into the P1 construct (red), and the P53 binding site (light blue).
-</div>
-
-<br></br>
-
-```{r, out.width = "850px"}
-
-url <- "figure2c_P1construct/constructSimple.png"
-knitr::include_graphics(file.path(projectUrl, url))
-
-```
-
-<div class="caption">
-A schematic representation of the fully cloned P1 construct including the overlapping region between miR34a host gene and miR34a asRNA (green), the reported genes, luciferase (purple) and renilla (red), the primer binding sites, and the shRNA binding site (used in Figure 2d).
+Top: A schematic representation of the miR34a locus and the region cloned in the P1 construct including the overlapping region between miR34a host gene (purple) and miR34a asRNA (green), the region cloned into the P1 construct (red), and the P53 binding site (light blue).
+Bottom: A schematic representation of the fully cloned P1 construct including the overlapping region between miR34a host gene and miR34a asRNA (green), the reported genes, luciferase (purple) and renilla (red), the primer binding sites, and the shRNA binding site (used in Figure 2d).
 </div>

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
more of the previous commit 6

@@
 
-url <- "figure2d_P1-HCTandHEK.rds"
+url <- fileMap(type = "rds")["figure2d"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure2d_P1-HCTandHEK/figure2d_P1-HCTandHEK.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
 

### 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
more of the previous commit 6

--- 2017-11-18 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
@@
 
-url <- "figure2e_P1shRNAdox.rds"
+url <- fileMap(type = "rds")["figure2e"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
 

### 2017-11-20 inst/polyadenylation/polyadenylation.Rmd
more of the previous commit 6

--- 2017-11-14 inst/suppFigure1c_polyadenylation/suppFigure1c_polyadenylation.Rmd
@@
 
-url <- "suppFigure1c_polyadenylation/polyadenylation.png"
+url <- fileMap(type = "png")["suppFigure1c"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/primer_walk/primer_walk.Rmd
more of the previous commit 6

--- 2017-11-14 inst/figure1e_primerWalk/figure1e_primerWalk.Rmd
@@
 
-url <- "figure1e_primerWalk/gel.png"
+url <- fileMap(type = "png")["figure1e"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/primer_walk_schematic/primer_walk_schematic.Rmd
more of the previous commit 6

--- 2017-11-14 inst/suppFigure1b_primerWalkSchematic/suppFigure1b_primerWalkSchematic.Rmd
@@
 
-url <- "suppFigure1b_primerWalkSchematic/schematic_hg38.png"
+#url <- "suppFigure1b_primerWalkSchematic/schematic_hg38.png"
+#knitr::include_graphics(file.path(projectUrl, url))
+
+url <- fileMap(type = "png")["suppFigure1b"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
done with changes in last commits (I hope)

@@
 
-url <- "suppFigure2b_stableLineCCND1exp.rds"
+url <- fileMap(type = "rds")["suppFigure2b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
 

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
done with changes in last commits (I hope)

--- 2017-11-18 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
@@
 
-url <- "suppFigure2c_stableLineCCND1prot/singleExp.png"
+url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot_singleExp.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 
-url <- "suppFigure2c_stableLineCCND1prot.rds"
+url <- fileMap(type = "rds")["suppFigure2c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
+
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
 ggsave(

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
done with changes in last commits (I hope)

@@
 
-url <- "figure3b_stableLineCellCycle.rds"
+#url <- "figure3b_stableLineCellCycle.rds"
+#data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+url <- fileMap(type = "rds")["figure3b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
+#path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])
 

### 2017-11-20 inst/stable_line_expression/stable_line_expression.Rmd
done with changes in last commits (I hope)

--- 2017-11-18 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
@@
 
-url <- "figure3a_stableLineExpression.rds"
+url <- fileMap(type = "rds")["figure3a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure3a_stableLineExpression/figure3a_stableLineExpression.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
 

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
done with changes in last commits (I hope)

--- 2017-11-17 inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.Rmd
@@
 
-url <- "suppFigure2a_stableLineExpressionHEK.rds"
+url <- fileMap(type = "rds")["suppFigure2a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
 
@@
  height = 60,
- width = 83,
+ width = 130,
  units = "mm"

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
done with changes in last commits (I hope)

@@
 
-url <- "figure3c_stableLineGrowthStarvation.rds"
+url <- fileMap(type = "rds")["figure3c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])
 

### 2017-11-20 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
done with changes in last commits (I hope)

--- 2017-11-18 inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd
@@
 
-url <- "figure3d_stableLinePolIIChIP.rds"
+url <- fileMap(type = "rds")["figure3d"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])
 

### 2017-11-20 inst/tcga_correlation/tcga_correlation.Rmd
done with changes in last commits (I hope)

--- 2017-11-14 inst/figure1c_TCGAcorrelation/figure1c_TCGAcorrelation.Rmd
@@
 
-url <- "figure1c_TCGAcorrelation/miR34a_RP3-510D11.2_diploid_only_edited.png"
+url <- fileMap(type = "png")["figure1c"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/tcga_correlation_table/tcga_correlation_table.Rmd
done with changes in last commits (I hope)

--- 2017-11-14 inst/suppFigure1a_TCGAcorrelationTable/suppFigure1a_TCGAcorrelationTable.Rmd
@@
 
-url <- "suppFigure1a_TCGAcorrelationTable/table.png"
+url <- fileMap(type = "png")["suppFigure1a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
done with changes in last commits (I hope)

@@
 
-url <- "suppFigure1f_transcriptStability.rds"
+url <- fileMap(type = "rds")["suppFigure1f"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 figure <- plotPDF(pdf)
-path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.pdf"
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])
 

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(p)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
 
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 83,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
+# ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+# )
 ```

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
 
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/hct116_p53_null/hct116_p53_null.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
 
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 83,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
+# ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+# )
 ```

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
commenting ggsave in Rmds

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])
-
-ggsave(
-  plot = g, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 83,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])
+# ggsave(
+#   plot = g, 
+#   filename = path, 
+#   device = cairo_pdf, 
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
commenting ggsave in Rmds

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])
-
-ggsave(
-  plot = g, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 83,
-  units = "mm"
-)
-
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])
+# ggsave(
+#   plot = g, 
+#   filename = path, 
+#   device = cairo_pdf, 
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
 
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
 
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
 
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 43,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+# ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 43,
+#  units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
commenting ggsave in Rmds

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
-ggsave(
-  plot = figure, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 43,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
+# ggsave(
+#   plot = figure, 
+#   filename = path, 
+#   device = cairo_pdf, 
+#   height = 60,
+#   width = 43,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
commenting ggsave in Rmds

@@
 ```{r, message = FALSE}
-
-#url <- "figure3b_stableLineCellCycle.rds"
-#data <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
@@
 figure <- plotPDF(pdf)
-#path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])
 
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_expression/stable_line_expression.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
 
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
 
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 130,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
+# ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 130,
+#  units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])
 
-ggsave(
-  plot = figure,
-  filename = path,
-  device = cairo_pdf,
-  height = 60,
-  width = 83,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])
 
-ggsave(
-  plot = figure,
-  filename = path,
-  device = cairo_pdf,
-  height = 60,
-  width = 43,
-  units = "mm",
-  dpi = 10000000
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 43,
+#   units = "mm",
+#   dpi = 10000000
+# )
 ```

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
commenting ggsave in Rmds

@@
 figure <- plotPDF(pdf)
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])
 
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 83,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])
+# ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 83,
+#  units = "mm"
+# )
 ```

### 2017-11-20 inst/SurvivalTCGA/processTCGA.R

@@ -1,0 +1,179 @@
+
+
+#call tcga download function 
+exp <- tcga[[1]]
+cols <- tcga[[2]]
+rows <- tcga[[3]]
+
+#calculate size factors
+sf <- lapply(exp, function(x) colSums(x))
+
+##subset AS: ENSG00000234546, HG: ENSG00000228526 and calculate cpm
+.norm.log.counts <- function(counts) {
+  norm.fact <- colSums(counts)
+  counts.norm <- t(apply(counts, 1, .norm, n = norm.fact))
+  counts.log <- log2(counts.norm)
+}
+
+.norm <- function(x, n) {
+  x / n * 1000000 + 1
+}
+
+sub <- lapply(exp, function(x)
+  x[rownames(x) %in% c("ENSG00000234546", "ENSG00000228526"), ]
+)
+
+cpm <- lapply(sub, .norm.log.counts)
+cpmTibble <- lapply(cpm, function(x)
+  tibble(
+    sample = colnames(x),
+    ENSG00000234546 = x[rownames(x) == "ENSG00000234546", ],
+    ENSG00000228526 = x[rownames(x) == "ENSG00000228526", ]
+  )
+)
+
+asDF <- bind_rows(cpmTibble)
+
+#find patients with the days_to_death variable present
+dtd <- lapply(cols, function(x)
+  tibble(
+    sample = rownames(x),
+    days_to_death = as.numeric(x[, colnames(x) == "days_to_death"]),
+    disease_type = as.character(x[, colnames(x) == "project_id"]),
+    patient = as.character(x[, colnames(x) == "patient"]),
+    days_to_last_follow_up = as.numeric(x[, colnames(x) == "days_to_last_follow_up"]),
+    vital_status = as.character(x[, colnames(x) == "vital_status"])
+  )
+)
+
+dtd <- bind_rows(dtd) %>%
+  mutate(
+    OS_time_to_event = case_when(
+      vital_status == "alive" ~ days_to_last_follow_up,
+      vital_status == "dead" ~ days_to_death
+  ))
+
+#add p53 mut status
+p53in <- rjson::fromJSON(file = "~/Github/miR34a_asRNA_project/inst/SurvivalTCGA/files.2017-11-13T13_37_07.279347_p53mut.json" )
+fileName <- sapply(p53in, `[[`, 1)
+p53mutSamp <- gsub(
[…]

### 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
adding complete p1_hek293t Rmd and figures

@@
 author: "Jason T. Serviss"
-date: "12/01/2017"
+date: "31/01/2017"
 output:
@@
     theme: flatly
-    toc: no
     code_folding: hide
+vignette: >
+  %\VignetteIndexEntry{Vignette Title}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
 ---
 
-#Introduction
+<style> 
+.caption { 
+  color: Black; 
+  font-family: "Times New Roman", Times, serif;
+  font-size: 1.0em; 
+}
+</style>
+
+```{r, echo = FALSE, message = FALSE}
+
+packages <- c(
+    "tidyverse",
+    "printr",
+    "ggthemes",
+    "readr",
+    "miR34AasRNAproject",
+    "grid",
+    "gtable"
+)
+purrr::walk(packages, library, character.only = TRUE)
+rm(packages)
+
+```
+
+```{r}
+
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+
+```
+
+####_Introduction_
+
 Functional characterization of individual antisense transcripts has previously shown their capability to regulate their sense gene.
@@
 
-#Methods
+<br></br>
+
+####_Methods_
+
 We utilized the P1 construct where the overlapping region of miR34a HG and miR34a AS is cloned with luciferase downstream of miR34a HG and renilla downstream of miR34a AS.
@@
 
+<br></br>
+
+#####_Constructs_
 ```{r}
-library(printr)
 p1 <- data.frame(
@@
 ```
+
+<br></br>
+
+#####_shRNAs_
 
@@
 ```
+
+<br></br>
+
+#####_Primers_
 
@@
 
-#Results
+####_Results_
+
 ```{r}
-library(reshape2)
-library(ggplot2)
-library(ggthemes)
-library(plyr)
-data <- read.table('~/GitHub/miR34aFigures/inst/HEK293tP1/QPCRdata.txt', header=TRUE, sep="\t")
 
-goi <- subset(data, gene %in% c("Luciferase", "Renilla"))
-hk <- subset(data, gene == "B-actin")
-hk <- rbind(hk,hk)
-hk <- hk[order(hk$belongsTo), ]
+url <- fileMap(type = "rds")["suppFigure2b"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
-colnames(goi)[5:6] <- c("Ct1GOI", "Ct2GOI")
-colnames(hk)[5:6] <- c("Ct1HK", "Ct2HK")
+#Luciferase = miR34a HG
+#Renilla = miR34a AS
 
-data <- cbind(goi, hk[,c("Ct1HK", "Ct2HK")])
-data$meanGOI <- rowMeans(data[,c("Ct1GOI", "Ct2GOI")])
-data$meanHK <- rowMeans(data[,c("Ct1HK", "Ct2HK")])
+#calculate dct
+groups <- c("shRNA", "Biological Replicate", "belongsTo", "gene")
+gois <- c("Luciferase", "Renilla")
 
-#ddct
-data$dct <- data$meanGOI - data$meanHK
-ddct <- ddply(
-    data,
-    c("experiment", "shRNA", "belongsTo", "gene"),
-    summarize,
-    ddct=dct-data[data$experiment == experiment & data$shRNA == "shCrtl" & data$belongsTo == belongsTo & data$gene == gene, "dct"]
-)
-data <- merge(data, ddct, by=c("experiment", "shRNA", "belongsTo", "gene"))
+data <- data %>%
+  technicalMeans(., groups) %>%
+  dct(., gois, Actin, groups, F)
 
-data$fold <- 2^-data$ddct
-data$log2fold <- log2(data$fold)
-
-#calculate stats
-stats <- ddply(
-    data,
-    c("shRNA", "belongsTo", "gene"),
-    summarize,
-    mean=mean(log2fold),
-    pValue=t.test(log2fold, data[data$shRNA == "shCrtl" & data$belongsTo == belongsTo & data$gene == gene ,"log2fold"], alternative="less")$p.value,
-    CI95l=t.test(log2fold)$conf.int[1],
-    CI95h=t.test(log2fold)$conf.int[2]
+#calculate ddct
+groups[groups == "gene"] <- "GOI"
+logical <- tibble(
+  `shRNA` = pull(data, shRNA) == "shCtrl"
 )
 
-stats$pStars <- ifelse(
-    stats$pValue < 0.05 & stats$pValue > 0.0049, 
-    "\u2605", 
-    ifelse(
-        stats$pValue < 0.005 & stats$pValue > 0.00049, 
-        "\u2605\u2605",
-        ifelse(
-            stats$pValue < 0.0005, 
-            "\u2605\u2605\u2605",
-            ""
-        )
-    )
+data <- data %>%
+  ddct(., logical, groups) %>%
+  folds(.)
+```
+
+```{r, fig.align='center', fig.height=8, fig.width=12}
+#plot for rmarkdown
+
+p <- ggplot(data = NULL) +
+  geom_violin(
+    data = data,
+    aes(
+      x = shRNA,
+      y = log2fold,
+      group = interaction(shRNA, GOI)
+    ),
+    trim = TRUE,
+    alpha = 0.5,
+    fill = "grey",
+    colour = NA,
+    scale = "width",
+    show.legend = FALSE
+  ) +
+  geom_dotplot(
+    data = data, 
+    aes(
+      x = shRNA,
+      y = log2fold,
+      fill = GOI,
+      group = interaction(shRNA, GOI)
+    ),
+    binwidth = 1/10,
+    colour = NA,
+    alpha = 0.5,
+    position = position_dodge(width = 0.9), 
+    binaxis = 'y', 
+    stackdir = 'center',
+    dotsize = 4,
+    show.legend = TRUE
+  ) +
+  facet_grid(. ~ belongsTo) +
+  scale_y_continuous("\u0394\u0394Ct")+
+  labs(x = "Cell line")
+
+plotRmarkdown(p) +
+  theme(
+    strip.text.x = element_blank(),
+    axis.text.x = element_text(angle = 90)
   )
 
-data <- merge(data, stats, by=c("shRNA", "belongsTo", "gene"))
+figure <- plotPDF(p) +
+  theme(
+    strip.text.x = element_blank(),
+    axis.text.x = element_text(angle = 90)
+  )
+
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```
 
-```{r, fig.align='center', fig.height=8, fig.width=12, eval=TRUE, message=FALSE, warning=FALSE}
-#plot for rmarkdown
-ggplot(data, aes(x=shRNA, y=log2fold))+
-    geom_violin(
-        aes(fill=gene),
-        trim=TRUE,
-        alpha=0.3,
-        color=NA,
-        scale="width",
-        show.legend = FALSE
-    )+
-    geom_point( 
-        aes(colour=gene),
-        size=4,
-        position=position_dodge(width=0.9)
-    )+
-#    geom_linerange(
-#        aes(ymin=CI95l, ymax=CI95h, group=gene),
-#        colour="black",
-#        position=position_dodge(width=0.9),
-#        show.legend = FALSE
-#    )+
-    geom_point(
-        aes(y=mean, group=gene),
-        colour="black",
-        position=position_dodge(width=0.9),
-        show.legend = FALSE
-    )+
-#    geom_label(
-#        aes(y=CI95h+0.15, label=pStars, group=gene),
-#        label.size=0,
-#        label.padding=unit(0.01, "lines"),
-#        show.legend = FALSE,
-#        fill="white",
-#        size=5,
-#        family="Arial Unicode MS",
-#        position=position_dodge(width=0.9)
-#    )+
-    scale_y_continuous(
-        "\u0394\u0394Ct",
-        sec.axis = sec_axis(
-            ~2^., 
-            name = expression(2^{- ~ Delta ~ Delta ~ "Ct"}),
-            label=round(c(2^-6,2^-5,2^-4,2^-3,2^-2,2^-1,2^0), digits=3),
-            breaks=c(2^-6,2^-5,2^-4,2^-3,2^-2,2^-1,2^0)
-        )
-    )+
-    labs(
-      x="shRNA",
-      title="HEK293t",
-      caption=
-            "miR34a (luficerase) and miR34a asRNA (renilla) in HEK293t cells which were co-transfected with the P1 construct and the specified shRNA.\nError bars (black vertical) indicate 95% CI and means are represented by black dots."
-    )+
-    theme_few()+
-    scale_fill_ptol()+
-    scale_colour_ptol()+
-    #values=c("#014d64", "#6794a7")
-    theme(
-        plot.title = element_text(
-            hjust = 0.5,
-            face="bold",
-            size=20
-        ),
-        plot.caption = element_text(
-            hjust=0, 
-            margin=margin(t=15),
-            family="Arial Unicode MS"
-        ),
-        legend.position="top",
-        legend.title=element_text(size=17),
-        legend.text=element_text(size=15),
-        axis.title=element_text(size=17),
-        axis.title.x=element_text(margin=margin(t=10)),
-        axis.text=element_text(size=15),
-        strip.text.x=element_text(size=17)
-    )+
-    guides(color = guide_legend(title = "Gene", override.aes = list(size=3)))
+<br></br>
 
-#plot for pdf
-```
+####_Conclusions_
 
-#Conclusions
 Analysis of luciferase and renilla expression revealed that by decreasing levels of the renilla transcript (corresponding to miR34a asRNA) luciferase (corresponding to miR34a HG) levels were concomitantly decreased.
 These results indicate that miR34a asRNA is capable of regulating the miR34a HG in a concordant manner and that the overlapping region of the miR34a asRNA may be sufficient to mediate this regulation.
+
+<br></br><br></br>

### 2017-11-20 inst/SurvivalTCGA/processTCGA.Rmd
re-running Rmds after addition of suppFig3

---
title: "TCGA"
output: html_document
---

Import data
```{r}
tcga <- readr::read_rds('~/Desktop/tcga.rds')

#call tcga download function 
exp <- tcga[[1]]
cols <- tcga[[2]]
rows <- tcga[[3]]
rm(tcga)
```

Run tsne as a sanity check
```{r}
.norm.log.counts <- function(counts) {
  norm.fact <- colSums(counts)
  counts.norm <- t(apply(counts, 1, .norm, n = norm.fact))
  counts.log <- log2(counts.norm)
}

.norm <- function(x, n) {
  x / n * 1000000 + 1
}

#caluclate log cpm
cpm <- lapply(exp, .norm.log.counts)
rm(exp)

#find genes present in all expression data
genes <- lapply(cpm, rownames)
inCommon <- Reduce(intersect, genes)

#subset expression list to only include in common genes
cpmFiltered <- lapply(cpm, function(x) as.data.frame(x[rownames(x) %in% inCommon, ]))

#bind list
cpmMat <- as.matrix(bind_cols(cpmFiltered))

#select highly variable genes
RowVar <- function(x) {
  rowSums((x - rowMeans(x))^2)/(dim(x)[2] - 1)
}
rv <- RowVar(cpmMat)
select <- order(rv, decreasing = TRUE)[1:5000]

#calculate 1-pearson's
d <- as.dist(1-cor(cpmMat[select, ], method = "p"))
```

```{r}

##subset AS: ENSG00000234546, HG: ENSG00000228526 and calculate cpm

sub <- lapply(exp, function(x)
  x[rownames(x) %in% c("ENSG00000234546", "ENSG00000228526"), ]
)

cpm <- lapply(sub, .norm.log.counts)
cpmTibble <- lapply(cpm, function(x)
  tibble(
    sample = colnames(x),
    ENSG00000234546 = x[rownames(x) == "ENSG00000234546", ],
    ENSG00000228526 = x[rownames(x) == "ENSG00000228526", ]
  )
)

asDF <- bind_rows(cpmTibble)

#find patients with the days_to_death variable present
dtd <- lapply(cols, function(x)
  tibble(
    sample = rownames(x),
    days_to_death = as.numeric(x[, colnames(x) == "days_to_death"]),
    disease_type = as.character(x[, colnames(x) == "project_id"]),
    patient = as.character(x[, colnames(x) == "patient"]),
    days_to_last_follow_up = as.numeric(x[, colnames(x) == "days_to_last_follow_up"]),
    vital_status = as.character(x[, colnames(x) == "vital_status"])
  )
)

dtd <- bind_rows(dtd) %>%
  mutate(
    OS_time_to_event = case_when(
      vital_status == "alive" ~ days_to_last_follow_up,
      vital_status == "dead" ~ days_to_death
  ))

#add p53 mut status
p53in <- rjson::fromJSON(file = "~/Github/miR34a_asRNA_project/inst/SurvivalTCGA/files.2017-11-13T13_37_07.279347_p53mut.json" )
fileName <- sapply(p53in, `[[`, 1)
p53mutSamp <- gsub(
  "nationwidechildrens\\.org_biospecimen\\.(.*)\\.xml",
  "\\1",
  fileName
)

data <- dtd %>%
  mutate(p53 = if_else(patient %in% p53mutSamp, "mut", "wt")) %>%
  right_join(asDF)

#remove normal (non-tumor) samples
data <- data %>%
  filter(as.numeric(gsub("^.{13}(..).*", "\\1", pull(data, sample))) < 10)
```

look at normal vs tumor

survival
```{r}
#HG AS corr
data %>%
  select(p53, disease_type, ENSG00000228526, ENSG00000234546) %>%
  gather(gene, cpm, -p53, -disease_type) %>%
#filter(disease_type == "TCGA-UVM") %>%
  arrange(gene, cpm, p53) %>%
  group_by(disease_type, p53, gene) %>%
  mutate(tumour = row_number()) %>%
#mutate(cpm = scale(cpm, center = TRUE, scale = FALSE)) %>%
  filter(disease_type == "TCGA-STAD") %>%
  ggplot(aes(tumour, cpm, colour = gene)) +
    geom_point(aes(shape = p53)) +
    facet_grid(.~disease_type, scales = "free", space = "free")

#p53 plot
data %>%
  mutate(p53 = if_else(patient %in% p53mutSamp, "mut", "wt")) %>%
  filter(!is.na(days_to_death)) %>%
  group_by(disease_type) %>%
  filter(n_distinct(p53) == 2) %>%
  ungroup() %>%
  add_count(p53, disease_type) %>%
  group_by(disease_type) %>%
  filter(all(n > 5)) %>%
  ungroup() %>%
  mutate(p53 = parse_factor(p53, levels = c("wt", "mut"))) %>%
  ggplot(aes(p53, days_to_death, fill = disease_type)) +
    geom_boxplot() +
#geom_jitter() +
    guides(fill = FALSE) +
    facet_wrap(~ disease_type)

#p53 cor
data %>%
  mutate(p53 = if_else(patient %in% p53mutSamp, "mut", "wt")) %>%
  filter(!is.na(days_to_death)) %>%
  group_by(disease_type) %>%
  filter(n_distinct(p53) == 2) %>%
  ungroup() %>%
  add_count(p53, disease_type) %>%
  group_by(disease_type) %>%
  filter(all(n > 5)) %>%
  select(-n) %>%
  ungroup() %>%
  mutate(p53 = parse_factor(p53, levels = c("wt", "mut"))) %>%
  group_by(disease_type) %>%
  do(tidy(lm(days_to_death ~ p53, data = .))) %>%
  print(n = nrow(.))

#HG plot
data %>%
  mutate(p53 = if_else(patient %in% p53mutSamp, "mut", "wt")) %>%
  filter(!is.na(days_to_death)) %>%
  group_by(disease_type) %>%
  filter(n_distinct(p53) == 2) %>%
  ungroup() %>%
  add_count(p53, disease_type) %>%
  group_by(disease_type) %>%
  filter(all(n > 5)) %>%
  select(-n) %>%
  ungroup() %>%
  mutate(p53 = parse_factor(p53, levels = c("wt", "mut"))) %>%
  group_by(disease_type, p53) %>%
  mutate(
    quantile = ntile(ENSG00000228526, 10),
    group = case_when(
      quantile == 1 | quantile == 2 | quantile == 3 ~ "low",
      quantile == 8 | quantile == 9 | quantile == 10 ~ "high",
      TRUE ~ "middle"
    ),
    group = parse_factor(group, levels = c("low", "middle", "high")),
    n = n()
  ) %>%
  ungroup() %>%
#group_by(p53, group, disease_type) %>%
# filter(n_distinct(sample) < 10) %>%
  select(disease_type, p53, group) %>% table
  ggplot(aes(group, days_to_death, fill = p53)) +
    geom_boxplot() +
    facet_wrap(~disease_type)

#AS
data %>%
  mutate(p53 = if_else(patient %in% p53mutSamp, "mut", "wt")) %>%
  filter(!is.na(days_to_death)) %>%
  group_by(disease_type) %>%
  filter(n_distinct(p53) == 2) %>%
  ungroup() %>%
  add_count(p53, disease_type) %>%
  group_by(disease_type) %>%
  filter(all(n > 5)) %>%
  select(-n) %>%
  ungroup() %>%
  mutate(p53 = parse_factor(p53, levels = c("wt", "mut"))) %>%
  group_by(disease_type, p53) %>%
  mutate(
    quantile = ntile(ENSG00000234546, 10),
    group = case_when(
      quantile == 1 | quantile == 2 | quantile == 3 ~ "low",
      quantile == 8 | quantile == 9 | quantile == 10 ~ "high",
      TRUE ~ "middle"
    ),
    group = parse_factor(group, levels = c("low", "middle", "high")),
    n = n()
  ) %>%
  ungroup() %>%
#select(disease_type, p53, group) %>% table
  filter(disease_type == "TCGA-BLCA") %>%
  ggplot(aes(group, days_to_death, fill = p53)) +
    geom_boxplot() +
    facet_wrap(~disease_type) +
    scale_y_continuous(trans = "log2")

```

### 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
re-running Rmds after addition of suppFig3

--- 2017-11-20 inst/lnc34a_cage/lnc34a_cage.Rmd
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure2d"][[1]]
+  url <- fileMap(type = "txt")["suppFigure3d"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure2d"][[1]]
+  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
 
@@
 
-url <- fileMap(type = "rds")["suppFigure2d"][[1]]
+url <- fileMap(type = "rds")["suppFigure3d"][[1]]
 cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2d"][[1]])
-
-ggsave(
-  plot = g, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 83,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
+# ggsave(
+#   plot = g,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
re-running Rmds after addition of suppFig3

--- 2017-11-20 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure2e"][[1]]
+  url <- fileMap(type = "txt")["suppFigure3e"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure2e"][[1]]
+  url <- fileMap(type = "rds")["suppFigure3e"][[1]]
 
@@
 #splice junctions
-url <- fileMap(type = "rds")["suppFigure2e"][[1]]
+url <- fileMap(type = "rds")["suppFigure3e"][[1]]
 splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2e"][[1]])
-
-ggsave(
-  plot = g, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 83,
-  units = "mm"
-)
-
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3e"][[1]])
+# ggsave(
+#   plot = g,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
re-running Rmds after addition of suppFig3

@@
 
-url <- fileMap(type = "rds")["figure2d"][[1]]
+url <- fileMap(type = "rds")["figure2c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2c"][[1]])
 # ggsave(

### 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
re-running Rmds after addition of suppFig3

@@
 
-url <- fileMap(type = "rds")["figure2e"][[1]]
+url <- fileMap(type = "rds")["figure2d"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2e"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
 # ggsave(

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
re-running Rmds after addition of suppFig3

@@
 
-url <- fileMap(type = "rds")["suppFigure2b"][[1]]
+url <- fileMap(type = "rds")["suppFigure3b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3b"][[1]])
 # ggsave(

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
re-running Rmds after addition of suppFig3

--- 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
@@
 
-url <- fileMap(type = "rds")["suppFigure2c"][[1]]
+url <- fileMap(type = "rds")["suppFigure3c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
-ggsave(
-  plot = figure, 
-  filename = path, 
-  device = cairo_pdf, 
-  height = 60,
-  width = 43,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3c"][[1]])
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 43,
+#   units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
re-running Rmds after addition of suppFig3

@@
 
-url <- fileMap(type = "rds")["suppFigure2a"][[1]]
+url <- fileMap(type = "rds")["suppFigure3a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3a"][[1]])
 # ggsave(

### 2017-11-20 R/utils.R

@@ -29,9 +29,8 @@ fileMap <- function(type) {
     figure1f = "coding_potential_cpat/coding_potential_cpat.Rmd",
     figure2a = "hct116_p53_null/hct116_p53_null.Rmd",
     figure2b = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
-    figure2c = "p1_construct/p1_construct.Rmd",
-    figure2d = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
-    figure2e = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
+    figure2c = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
+    figure2d = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
     figure3a = "stable_line_expression/stable_line_expression.Rmd",
     figure3b = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
     figure3c = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
@@ -44,11 +43,13 @@ fileMap <- function(type) {
     suppFigure1e = "cellular_localization/cellular_localization.Rmd",
     suppFigure1f = "transcript_stability/transcript_stability.Rmd",
     suppFigure1g = "coding_potential_cpc/coding_potential_cpc.Rmd",
-    suppFigure2a = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
-    suppFigure2b = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
-    suppFigure2c = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
-    suppFigure2d = "lnc34a_cage/lnc34a_cage.Rmd",
-    suppFigure2e = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd"
+    suppFigure2a = "p1_construct/p1_construct.Rmd",
+    suppFigure2b = "p1_hek293t/p1_hek293t.Rmd",
+    suppFigure3a = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
+    suppFigure3b = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
+    suppFigure3c = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
[…]

### 2017-11-20 R/gatherFigures.R
running gatherFigures

@@ -1,13 +1,12 @@
 
 gatherFigures <- function() {
   bp <- "~/Github/miR34a_asRNA_project/inst"
-  rmds <- fileMap()
-  exts <- lapply(rmds, function(x) gsub("\\.Rmd$", "\\.pdf", x))
-  cmds <- lapply(1:length(exts), function(x)
+  pdfs <- fileMap(type = "pdf")
+  cmds <- lapply(1:length(pdfs), function(x)
     paste(
       "cp",
-      file.path(bp, exts[[x]]),
-      file.path(bp, "allFigures", substr(names(exts)[[x]], 1, nchar(names(exts)[[x]])-1)),
+      file.path(bp, pdfs[[x]]),
+      file.path(bp, "allFigures", substr(names(pdfs)[[x]], 1, nchar(names(pdfs)[[x]])-1)),
       sep = " "
     )
   )

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
adding full WB for CCND1

@@
 
-_Representative experiment_
+_Western blot_
 ```{r, out.width = "500px"}
 
-url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot_singleExp.png"
+url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class="caption">
-A resulting western blot representative of the results from the three independant experiments.
+The resulting western blot showing the results from the three independant experiments.
 </div>

### 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
adding 3 primer race schematic

@@
 
+```{r, fig.align='center', fig.height=2, fig.width=12, warning = FALSE, message = FALSE}
+data <- tibble(
+  gene = readr::parse_factor(
+    c(rep("miR34a asRNA", 5), rep("lnc34a", 3), "miR34a asRNA F1", "miR34a asRNA F10"),
+    levels = c("miR34a asRNA", "lnc34a", "miR34a asRNA F1", "miR34a asRNA F10")
+  ),
+  feature = c(
+    "exon", "intron", "exon", "intron", "exon",
+    "exon", "intron", "exon",
+    "primer", "primer"
+  ),
+  start = c(
+    9181991, 9182316, 9183633, 9183807, 9191393,
+    9181737, 9182295, 9196912,
+    9182279, 9182223
+    ),
+  stop = c(
+    9182316, 9183633, 9183807, 9191393, 9191686,
+    9182295, 9196912, 9197043,
+    9182301, 9182244
+  )
+)
+
+p <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = filter(data, feature %in% c("exon") & gene == "miR34a asRNA"),
+    aes(xmin = start, xmax = stop, y = gene, fill = gene),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    colour = "gray"
+  )  +
+  geom_segment(
+    data = filter(data, feature == "intron" & gene == "miR34a asRNA"),
+    aes(x = start, xend = stop, y = gene, yend = gene),
+    linetype = "dotted",
+    colour = "gray",
+    size = 1
+  ) +
+  geom_segment(
+    data = filter(data, feature == "primer"),
+    aes(x = start, xend = stop, y = 1.1, yend = 1.1, colour = gene),
+    size = 5 
+  ) +
+  labs(x = "Chromosome 1") +
+  guides(fill = FALSE, colour = guide_legend(title = "Primer"))
+
+plotRmarkdown(p) +
+  theme_void() +
+  scale_fill_brewer()
+```
+
+<div class = "caption">
+3’-RACE schematic illustrating primer placement on the miR34a asRNA transcript for 3'-RACE.
+</div>
+
+<br></br>
+
 ####_Results_

### 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
work on fig2

@@
 
-#####_Constructs_
+_Constructs_
 ```{r}
@@
 
-#####_shRNAs_
+_shRNAs_
 
@@
 
-#####_Primers_
+_Primers_
 

### 2017-11-20 data-raw/saveRDS.R
adding tcga_correlation_table as .rds

@@ -350,5 +350,10 @@ read_tsv('./data-raw/coding_potential_cpat.txt') %>%
 read_tsv('./data-raw/coding_potential_cpc.txt') %>%
   write_rds(., path = './data/coding_potential_cpc.rds')
 
+#tcga_correlation_table
+read_tsv('./data-raw/tcga_correlation_table.txt') %>%
+  write_rds(., path = './data/tcga_correlation_table.rds')
+
+
 
 #source('./data-raw/saveRDS.R')

### 2017-11-20 data-raw/saveRDS.R
updating preprocessing for tcga correlation table

@@ -352,6 +352,28 @@ read_tsv('./data-raw/coding_potential_cpc.txt') %>%
 
 #tcga_correlation_table
 read_tsv('./data-raw/tcga_correlation_table.txt') %>%
+  rename(
+    r_total = r,
+    p_value_total = p,
+    p_value_mutated = p_mutated,
+    p_value_nonmut = p_nonmut
+  ) %>%
+  mutate(
+    r_total = gsub(",", ".", r_total),
+    p_value_total = gsub(",", ".", p_value_total),
+    r_mutated = gsub(",", ".", r_mutated),
+    p_value_mutated = gsub(",", ".", p_value_mutated),
+    r_nonmut = gsub(",", ".", r_nonmut),
+    p_value_nonmut = gsub(",", ".", p_value_nonmut)
+  ) %>%
+  mutate(
+    r_total = as.numeric(r_total),
+    p_value_total = as.numeric(p_value_total),
+    r_mutated = as.numeric(r_mutated),
+    p_value_mutated = as.numeric(p_value_mutated),
+    r_nonmut = as.numeric(r_nonmut),
+    p_value_nonmut = as.numeric(p_value_nonmut)
+  ) %>%
   write_rds(., path = './data/tcga_correlation_table.rds')
 
 

### 2017-11-20 R/QpcrFuns.R
added documentation for all functions and ran document

@@ -1,16 +1,66 @@
+#' technicalMeans
+#'
+#' Calculates the means of the two technical replicates.
+#'
+#' Accepts a tibble with grouping variables and ct values (typically with one
+#' column per ct value replicate). The grouping variable should include the
+#' names of all columns where the ct values are not located.
+#'
+#' @name technicalMeans
+#' @rdname technicalMeans
+#' @aliases technicalMeans
+#' @param data tibble; See function description.
+#' @param grouping character. See function description.
+#' @return A tibble including the values of the mean ct values.
+#' @author Jason T. Serviss
+#'
+NULL
+
+#' @rdname technicalMeans
 #' @export
+#' @importFrom tidyr gather
+#' @importFrom dplyr group_by summarize one_of ungroup
+#' @importFrom rlang syms !!!
+#' @importFrom magrittr "%>%"
+
 technicalMeans <- function(
     data,
     grouping
 ){
     data %>%
     gather(`Tech. Replicate`, Ct, -one_of(grouping)) %>%
-    group_by(!!! rlang::syms(grouping)) %>%
+    group_by(!!! syms(grouping)) %>%
     summarize(ctMean = mean(Ct, na.rm = TRUE)) %>%
     ungroup()
 }
 
+#' dct
+#'
+#' Calculates the delta ct value.
+#'
+#' @name dct
+#' @rdname dct
+#' @aliases dct
+#' @param data tibble; A tibble output by the \link{code{technicalMeans}}
+#'  function.
+#' @param GOIs character. The genes of interest.
+#' @param HK character. The house keeping gene.
+#' @param grouping unquoted expression(s). Column names of variables that include the
+#'  experimental conditions.
+#' @param logical. A logical indicating if the median of the house keeping genes
+#'  should be used to calculate dct; default = TRUE.
+#' @return A tibble including the dct values.
+#' @author Jason T. Serviss
+#'
+NULL
+
+#' @rdname dct
 #' @export
+#' @importFrom dplyr enquo mutate rename one_of quo_name group_by case_when ungroup select
+#' @importFrom rlang "!!" "!!!"
+#' @importFrom tidyr spread gather
+#' @importFrom magrittr "%>%"
+
 dct <- function(
     data,
     GOIs,
@@ -32,7 +82,7 @@ dct <- function(
         -one_of(names(.)[!names(.) %in% GOIs]),
[…]

### 2017-11-20 R/processFigures.R

@@ -27,8 +27,6 @@ plotFigure <- function(figure, ...) {
   runDockerAndView(path)
 }
 
-####Helpers
-
 #returns the path to the figure's .rmd file
 getPath <- function(figure) {
   map <- fileMap(type = "Rmd")

### 2017-11-20 inst/SurvivalTCGA/processTCGA.Rmd
adding processTCGA script

@@
 cpmFiltered <- lapply(cpm, function(x) as.data.frame(x[rownames(x) %in% inCommon, ]))
+rm(cpm)
 
 #bind list
-cpmMat <- as.matrix(bind_cols(cpmFiltered))
+cpmMat <- as.matrix(dplyr::bind_cols(cpmFiltered))
+rm(cpmFiltered)
 

### 2017-11-20 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
removed alpha for all points and cleared and gathered figures

@@
     colour = NA,
-    alpha = 0.5,
+    #alpha = 0.5,
     position = position_dodge(width = 0.9), 

### 2017-11-20 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
removed alpha for all points and cleared and gathered figures

@@
     binwidth = 1/10,
-    alpha = 0.5,
+    #alpha = 0.5,
     colour = NA,

### 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
removed alpha for all points and cleared and gathered figures

@@
     stackdir = 'center',
-    dotsize = 4,
+    dotsize = 2,
     show.legend = TRUE
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
addition to last commit
removed alpha for all points and cleared and gathered figures

@@
 <div class="caption">
-The resulting western blot showing the results from the three independant experiments.
+The resulting western blot showing results from the three independant experiments.
 </div>

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
adding cell cycle software to methods in Rmd
removed alpha for all points and cleared and gathered figures

@@
 _Analysis_
-Write the software used to quantify the cell cycle phases.
-
+The cell cycle phases ModFit software (Verity Software House) was used to quantify the percentage of cells in each cell cycle phase.
 Percentages were converted to log2 fractions for each sample.

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
removed alpha for all points and cleared and gathered figures

@@
     binwidth = 1/10,
-    alpha = 0.5,
+    #alpha = 0.5,
     position = position_dodge(width = 0.9), 

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
removed alpha for all points and cleared and gathered figures

@@
     size = 4,
-    alpha = 0.6,
+    alpha = 0.9,
     position = position_dodge(width = 0.9)
@@
     fill = "white",
-    alpha = 0.6,
+    alpha = 0.9,
     stroke = 0,

### 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
updated figures after last commit
nothing

@@
   html_document:
+    code_folding: hide
     theme: flatly
-    code_folding: hide
-vignette: >
-  %\VignetteIndexEntry{Vignette Title}
-  %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
+vignette: |
+  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
 ---
@@
   scale_y_continuous("\u0394\u0394Ct")+
-  labs(x = "Cell line")
+  labs(x = "shRNA")
 

### 2017-11-21 inst/stable_line_expression/stable_line_expression.Rmd
adding additional replicates for stable line exp

@@
 #remove Skov exp 1 due to variability in technical replicates
-data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")
+#data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")
 
@@
   technicalMeans(., groups) %>%
-  dct(., gois1, Actin, groups) %>%
+  dct(., gois1, Actin, groups, F) %>%
   mutate(GOI = as.character(GOI))
@@
   technicalMeans(., groups) %>%
-  dct(., gois2, RNU48, groups) %>%
+  dct(., gois2, RNU48, groups, F) %>%
   mutate(GOI = as.character(GOI))

### 2017-11-21 inst/stable_line_expression/stable_line_expression.Rmd
fixing figures after last commit

@@
   mutate(
-    max = max + c(0.25, 1.25, 0.25, 1.25, 0.25, 1.25)
+    max = max + c(0.55, 1.95, 0.25, 1.65, 0.25, 1.65)
   )
@@
       x = 1.5, 
-      y = max + 0.4, 
+      y = max + 0.6, 
       label = pFormat, 
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 83,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```

### 2017-11-21 inst/tcga_correlation/tcga_correlation.Rmd
tcga correlation plotting done

@@
 subtitle: "miR34a asRNA and miR34a TCGA correlation"
-author: "Jason T. Serviss"
+author: "Jimmy Van den Eynden and Jason T. Serviss"
 date: "31/01/2017"
@@
 ####_Results_
+```{r}
+url <- fileMap(type = "rds")["figure1c"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+#normalize expression values
+data <- mutate(
+    data,
+    RP3 = log2(RP3 / max(RP3)),
+    miR34a = log2(miR34a / max(miR34a))  
+  )
+
+#add BRCA subtypes
+data <- data %>%
+  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
+  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))
+```
+
+```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
+#plot
+data %>%
+  arrange(cancer_PAM50, TP53, RP3) %>%
+  plotTCGAcorrelation(type = "diploid only")
+
+#save to pdf
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
+pdf(path, width = 28)
+data %>%
+  arrange(cancer_PAM50, TP53, RP3) %>%
+  plotTCGAcorrelation(type = "diploid only")
+dev.off()
+
+```
 
@@
 
-```{r, out.width = "1000px"}
-
-url <- fileMap(type = "png")["figure1c"][[1]]
-knitr::include_graphics(file.path(projectUrl, url))
-
-```
-
 <br></br>

### 2017-11-21 R/plotting.R

@@ -97,14 +97,17 @@ plotTCGAcorrelation <- function(data, type = "diploid only") {
     type = "l",
     col = "red",
     frame.plot = FALSE,
-    ylim = c(-12, 1),
+    ylim = c(-16, 1),
+    yaxt = "n",
     xlab = "Tumors",
     ylab = "Relative expression level (log2)"
   )
+  axis(2, at = seq(0, -12, by = -2), las = 2)
 }
 
 .plotLabelsAndColors <- function(data, colors) {
   idx_start <- which(!duplicated(pull(data, "cancer_PAM50")))
+  names(idx_start) <- pull(data, cancer_PAM50)[idx_start]
   idx_end <- c(idx_start - 1, nrow(data))
   idx_end <- idx_end[-1]
   
@@ -114,14 +117,14 @@ plotTCGAcorrelation <- function(data, type = "diploid only") {
       -12,
       idx_end[i],
       0,
-      col = cancer_colors[correlation_matrix_sel[idx_start[i], "cancer_PAM50"]],
+      col = pull(filter(colors, cancer == names(idx_start[i])), value),
       border = NA
     )
     text(
-      idx_start[i],
-      0,
-      data[idx_start[i], "cancer_PAM50"],
-      adj = c(1, 1),
+      x = median(which(pull(data, cancer_PAM50) == names(idx_start)[[i]])),
+      y = -12.1,
+      labels = pull(data, "cancer_PAM50")[idx_start[i]],
+      adj = c(1, 0.5),
       srt = 90
     )
   }

### 2017-11-21 inst/tcga_correlation/tcga_correlation.Rmd
re-ran tcga correaltion rmd

@@
 #save to pdf
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
-pdf(path, width = 28)
-data %>%
-  arrange(cancer_PAM50, TP53, RP3) %>%
-  plotTCGAcorrelation(type = "diploid only")
-dev.off()
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
+# pdf(path, width = 28)
+# data %>%
+#   arrange(cancer_PAM50, TP53, RP3) %>%
+#   plotTCGAcorrelation(type = "diploid only")
+# dev.off()
 

### 2017-11-25 inst/SurvivalTCGA/processTCGA.Rmd
working on figures and inserting into manuscript

@@
 cpmMat <- as.matrix(dplyr::bind_cols(cpmFiltered))
+rownames(cpmMat) <- inCommon
+readr::write_rds(cpmMat, path = "~/Desktop/tcgaCPM.rds", compress = "bz2")
 rm(cpmFiltered)
+
+#coldata
+colNames <- lapply(cols, colnames)
+inCommon <- Reduce(intersect, colNames)
+colsFiltered <- lapply(cols, function(x) as.data.frame(x[, colnames(x) %in% inCommon]))
+colsMat <- dplyr::bind_rows(colsFiltered) %>%
+  as_tibble() %>%
+  readr::write_rds(path = "~/Desktop/colData.rds", compress = "bz2")
 
@@
 d <- as.dist(1-cor(cpmMat[select, ], method = "p"))
+
+#tsne
+tsne <- as.data.frame(Rtsne::Rtsne(d, is_distance = TRUE, perplexity = 50, max_iter = 5000)$Y)
+leng <- unlist(lapply(cols, function(x) nrow(x)))
+tsne$cancer <- rep(names(rows), leng)
+tsne$AS <- cpmMat[rownames(cpmMat) == "ENSG00000234546", ]
+tsne$HG <- cpmMat[rownames(cpmMat) == "ENSG00000228526", ]
+
+#plot
+col64 <- c(
+"#000000", "#FFFF00", "#1CE6FF", "#FF34FF", "#FF4A46", "#008941", "#006FA6", "#A30059",
+"#FFDBE5", "#7A4900", "#0000A6", "#63FFAC", "#B79762", "#004D43", "#8FB0FF", "#997D87",
+"#5A0007", "#809693", "#FEFFE6", "#1B4400", "#4FC601", "#3B5DFF", "#4A3B53", "#FF2F80",
+"#61615A", "#BA0900", "#6B7900", "#00C2A0", "#FFAA92", "#FF90C9", "#B903AA", "#D16100",
+"#DDEFFF", "#000035", "#7B4F4B", "#A1C299", "#300018", "#0AA6D8", "#013349", "#00846F",
+"#372101", "#FFB500", "#C2FFED", "#A079BF", "#CC0744", "#C0B9B2", "#C2FF99", "#001E09",
+"#00489C", "#6F0062", "#0CBD66", "#EEC3FF", "#456D75", "#B77B68", "#7A87A1", "#788D66",
+"#885578", "#FAD09F", "#FF8A9A", "#D157A0", "#BEC459", "#456648", "#0086ED", "#886F4C",
+"#34362D", "#B4A8BD", "#00A6AA", "#452C2C", "#636375", "#A3C8C9", "#FF913F", "#938A81",
+"#575329", "#00FECF", "#B05B6F", "#8CD0FF", "#3B9700", "#04F757", "#C8A1A1", "#1E6E00",
+"#7900D7", "#A77500", "#6367A9", "#A05837", "#6B002C", "#772600", "#D790FF", "#9B9700",
+"#549E79", "#FFF69F", "#201625", "#72418F", "#BC23FF", "#99ADC0", "#3A2465", "#922329",
+"#5B4534", "#FDE8DC", "#404E55", "#0089A3", "#CB7E98", "#A4E804", "#324E72", "#6A3A4C")
+
+ggplot(tsne, aes(V1, V2, colour = cancer)) + geom_point() + scale_colour_manual(values = col64)
+ggplot(tsne, aes(V1, V2, colour = AS), alpha = 0.5) + geom_jitter() + viridis::scale_colour_viridis()
+ggplot(tsne, aes(V1, V2, colour = HG)) + geom_point() + viridis::scale_colour_viridis()
+
+#clinical
+#find clinical in common
+clin <- lapply(cols, colnames)
+inCommon <- Reduce(intersect, clin)
+clinFiltered <- lapply(cols, function(x) as.data.frame(x[, colnames(x) %in% inCommon]))
+clinical <- dplyr::bind_rows(clinFiltered)
+
+tsne$tumor_stage <- clinical$tumor_stage
+tsne$vital_status <- clinical$vital_status
+tsne$morphology <- clinical$morphology
+tsne$days_to_death <- clinical$days_to_death
+tsne$days_to_recurrence <- clinical$days_to_recurrence
+tsne$tumor_grade <- clinical$tumor_grade
+tsne$progression_or_recurrence <- clinical$progression_or_recurrence
+
+tsne %>%
+#  filter(!is.na(days_to_recurrence)) %>%
+  ggplot(aes(V1, V2, colour = progression_or_recurrence), alpha = 0.5) + geom_jitter()
+
 ```

### 2017-11-25 inst/lnc34a_cage/lnc34a_cage.Rmd
sorting the cell lines alpha for easier reading
working on figures and inserting into manuscript

@@
 
-####Introduction
+#### _Introduction_
 
@@
 
-####Methods
+#### _Methods_
 
@@
     ) %>%
-    unique()
+    unique() %>%
+    sort()
 }
@@
 
-####Results
+#### _Results_
 
@@
 )
+
+#try to cut the data so that the CAGE reads are more visable in the figure.
+data <- filter(data, start < 9245000) %>%
+  mutate(stop = if_else(feature == "intron" & start != 9242375, 9245000, stop))
 
@@
 p1 <- ggplot(data = NULL) +
+  geom_segment(
+    data = filter(data, feature == "intron"),
+    aes(x = start, xend = stop, y = gene, yend = gene),
+    linetype = "dotted",
+    colour = "gray",
+    size = 1
+  ) +
   gggenes::geom_gene_arrow(
@@
   ggthemes::scale_fill_ptol() +
-  geom_segment(
-    data = filter(data, feature == "intron"),
-    aes(x = start, xend = stop, y = gene, yend = gene),
-    linetype = "dotted",
-    colour = "gray",
-    size = 1
-  ) +
-  xlim(9241000, 9257900) +
+  xlim(9241000, 9245000) +
   labs(x = "Chromosome 1", y = "Genes") +
@@
   labs(y = "Cage reads") +
-  xlim(9241000, 9257900) +
+  xlim(9241000, 9245000) +
   guides(fill = guide_colourbar(
@@
   ggthemes::theme_few() +
-  xlim(9241000, 9257900) +
+  xlim(9241000, 9245000) +
   theme(
@@
   ) +
-  xlim(9241000, 9257900) +
-  labs(x = "Chromosome 1", y = "Genes") +
+  xlim(9241000, 9245000) +
+  labs(x = "Chromosome 1", y = "") +
   guides(fill = FALSE) +
   theme(
-    axis.text = element_text(size = 3),
-    axis.title.x = element_text(size = 4),
-    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
+    axis.text = element_text(size = 6),
+    axis.title.x = element_text(size = 6),
+    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
     axis.ticks.length = unit(0.5, "mm"),
@@
     axis.title.x = element_blank(),
-    axis.title.y = element_text(size = 4),
+    axis.title.y = element_text(size = 6),
     legend.position = "top",
-    legend.title = element_text(size = 4),
-    legend.text = element_text(size = 4),
+    legend.title = element_text(size = 7),
+    legend.text = element_text(size = 6),
     legend.box.spacing = unit(3, "pt"),
@@
     barheight = unit(4, "pt"),
-    barwidth = unit(40, "pt")
+    barwidth = unit(50, "pt")
   ))
@@
     axis.title.x = element_blank(),
-    axis.title.y = element_text(size = 4),
+    axis.title.y = element_text(size = 6),
     axis.ticks = element_blank(),
     panel.border = element_rect(fill = NA, size = 0.1),
-    plot.margin = unit(c(0, 1, 0, 1), "mm")
+    plot.margin = unit(c(0, 1, 2, 1), "mm")
   ) +
@@
 
-####Conclusions
+#### _Conclusions_
 

### 2017-11-25 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
sorting the cell lines alpha for easier reading
working on figures and inserting into manuscript

@@
 All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
-Of these cell lines `r cellLinesInFinal() %>% length()` cell lines had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
+Of these cell lines `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
 Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`.
@@
   xlim(9241000, 9257900) +
-  labs(x = "Chromosome 1", y = "Genes") +
+  labs(x = "Chromosome 1", y = "") +
   guides(fill = FALSE) +
   theme(
-    axis.text = element_text(size = 3),
-    axis.title.x = element_text(size = 4),
-    axis.title.y = element_text(size = 4, margin = margin(r = 8, "cm")),
+    axis.text = element_text(size = 6),
+    axis.title.x = element_text(size = 6),
+    axis.title.y = element_text(size = 6, margin = margin(r = 8, "cm")),
     axis.ticks.length = unit(0.5, "mm"),
@@
   ) +
-  labs(y = "Cage reads") +
+  labs(y = "Spliced reads") +
   xlim(9241000, 9257900) +
   guides(fill = guide_colourbar(
-    title = "Reads",
+    title = "Read count",
     title.position = "top",
@@
 
-####Conclusions
+#### _Conclusions_
 Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (Supplementary figure XX) with those being the mist highly expressed corresponding to the annotated miR34a asRNA transcript.

### 2017-11-25 inst/p1_hek293t/p1_hek293t.Rmd
working on figures and inserting into manuscript

@@
 
-####_Introduction_
+#### _Introduction_
 
@@
 
-####_Methods_
+#### _Methods_
 
@@
 
-####_Results_
+#### _Results_
 
@@
   ) +
-  facet_grid(. ~ belongsTo) +
+  facet_grid(. ~ belongsTo, scales = "free") +
   scale_y_continuous("\u0394\u0394Ct")+
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 83,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```
@@
 
-####_Conclusions_
+#### _Conclusions_
 

### 2017-11-27 inst/cellular_localization_encode/cellular_localization_encode.Rmd
adding cellular_localization_encode

---
title: "miR34a asRNA cellular localization"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "grid",
    "gtable",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

#### _Introduction_

<br></br>

#### _Methods_

<br></br>

#### _Results_

```{r}

#SK-N-SH has a larger proportion of GAPDH in the nucleus than cytoplasm
#The variation in miR34a asRNA expression is way too large for SK-MEL-5
#K562, HT1080, SK-N-DZ, and NCI-H460 have no or low miR34a asRNA expression
#use GAPDH instead of ACTB for cytoplasmic fraction, seems to be a better representation.

fdata <- data %>% 
  filter(!`Biosample term name` %in% c("K562", "HT1080", "SK-N-DZ", "NCI-H460", "SK-MEL-5", "SK-N-SH")) %>% 
  filter(gene_name != "ACTB") %>%
  select(`Biosample term name`, gene_id, gene_name, fraction, `Library made from`, `Biological replicate(s)`, TPM) %>%
  group_by(`Biosample term name`, gene_id, gene_name, fraction) %>%
  mutate(tmp = n() == 2) %>%
  filter(tmp | `Library made from` == "polyadenylated mRNA") %>%
  ungroup() %>%
  select(-tmp) %>%
  group_by(`Biosample term name`, gene_id, gene_name, `Biological replicate(s)`) %>%
  mutate(frac = TPM / sum(TPM)) %>%
  ungroup()

stats <- fdata %>%
  group_by(`Biosample term name`, gene_id, gene_name, fraction) %>%
  filter(n() == 2) %>%
  summarize(
    n = n(),
    mean = mean(frac),
    sd_min = mean(frac) + sd(frac),
    sd_max = mean(frac) - sd(frac)
  )  %>%
  ungroup()
```

```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
p <- stats %>%
  ggplot(aes(gene_name, mean, color = fraction)) +
  geom_point(position = position_dodge(width = 1)) +
  facet_wrap(~`Biosample term name`, ncol = 1) +
  geom_errorbar(aes(ymax = sd_max, ymin = sd_min), width = 0, position = position_dodge(width = 1)) +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  labs(
    y = "Mean %",
    x = "Gene"
  ) +
  guides(colour = guide_legend(title = "Fraction"))

plotRmarkdown(p) +
  theme(legend.position = "top")

figure <- plotPDF(p)

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
# ggsave(
#  plot = figure,
#  filename = path,
#  device = cairo_pdf,
#  height = 60,
#  width = 83,
#  units = "mm"
# )
```

<div class="caption">
Write figure legend.
</div>

<br></br>

#### _Conclusions_

<br></br><br></br>

### 2017-11-27 R/utils.R

@@ -40,7 +40,7 @@ fileMap <- function(type) {
     suppFigure1b = "primer_walk_schematic/primer_walk_schematic.Rmd",
     suppFigure1c = "polyadenylation/polyadenylation.Rmd",
     suppFigure1d = "isoforms/isoforms.Rmd",
-    suppFigure1e = "cellular_localization/cellular_localization.Rmd",
+    suppFigure1e = "cellular_localization_encode/cellular_localization_encode.Rmd",
     suppFigure1f = "transcript_stability/transcript_stability.Rmd",
     suppFigure1g = "coding_potential_cpc/coding_potential_cpc.Rmd",
     suppFigure2a = "p1_construct/p1_construct.Rmd",

### 2017-11-27 data-raw/saveRDS.R

@@ -343,14 +343,17 @@ read_tsv('./data-raw/p1_hek293t.txt') %>%
   write_rds(., path = './data/p1_hek293t.rds')
 
 #coding_potential_cpat
+print("processing coding_potential_cpat")
 read_tsv('./data-raw/coding_potential_cpat.txt') %>%
   write_rds(., path = './data/coding_potential_cpat.rds')
 
 #coding_potential_cpc
+print("processing coding_potential_cpc")
 read_tsv('./data-raw/coding_potential_cpc.txt') %>%
   write_rds(., path = './data/coding_potential_cpc.rds')
 
 #tcga_correlation_table
+print("processing tcga_correlation_table")
 read_tsv('./data-raw/tcga_correlation_table.txt') %>%
   rename(
     r_total = r,
@@ -377,6 +380,7 @@ read_tsv('./data-raw/tcga_correlation_table.txt') %>%
   write_rds(., path = './data/tcga_correlation_table.rds')
 
 #tcga_correlation
+print("processing tcga_correlation")
 read_tsv('./data-raw/tcga_correlation.txt') %>%
   mutate(
     TP53 = as.numeric(TP53),
@@ -386,6 +390,35 @@ read_tsv('./data-raw/tcga_correlation.txt') %>%
   ) %>%
   write_rds(., path = './data/tcga_correlation.rds')
 
-
+#cellular_localization_encode
+read_tsv('https://www.encodeproject.org/metadata/type=Experiment&assay_term_name=RNA-seq&replicates.library.biosample.donor.organism.scientific_name=Homo+sapiens&biosample_type=immortalized+cell+line&files.file_type=tsv&assay_title%21=small+RNA-seq&assembly=GRCh38/metadata.tsv') %>%
+  rename(fraction = `Biosample subcellular fraction term name`) %>%
+  filter(
+    `Output type` == "gene quantifications" &
+    fraction %in% c("nucleus", "cytosol") &
+    Assembly == "GRCh38" &
+    is.na(`Audit WARNING`) &
+    is.na(`Audit INTERNAL_ACTION`) &
+    is.na(`Audit ERROR`) &
+    is.na(`Audit NOT_COMPLIANT`)
+  ) %>%
+    mutate(fileContens =
+      map(
+        `File download URL`,
+        ~ read_tsv(., col_names = TRUE)
+      )
[…]

### 2017-11-27 inst/cellular_localization_encode/cellular_localization_encode.Rmd
finished cellular localization encode

@@
     "tidyverse",
+    "printr",
+    "ggthemes",
+    "readr",
+    "miR34AasRNAproject",
     "grid",
-    "gtable",
-    "miR34AasRNAproject"
+    "gtable"
 )
@@
 ```{r}
+
+url <- fileMap(type = "rds")["suppFigure1e"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
-p <- stats %>%
-  ggplot(aes(gene_name, mean, color = fraction)) +
-  geom_point(position = position_dodge(width = 1)) +
+markdown <- ggplot(data = NULL) +
+  geom_point(
+    data = stats,
+    aes(x = gene_name, y = mean, color = fraction),
+    position = position_dodge(width = 1)
+  ) +
   facet_wrap(~`Biosample term name`, ncol = 1) +
-  geom_errorbar(aes(ymax = sd_max, ymin = sd_min), width = 0, position = position_dodge(width = 1)) +
+  geom_errorbar(
+    data = stats, 
+    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
+    width = 0,
+    position = position_dodge(width = 1)
+  ) +
   scale_y_continuous(labels = scales::percent) +
@@
   labs(
-    y = "Mean %",
+    y = "% TPM",
     x = "Gene"
@@
 
-plotRmarkdown(p) +
-  theme(legend.position = "top")
+plotRmarkdown(markdown) +
+  theme(
+    legend.position = "top",
+    axis.title.y = element_text(margin = margin(r = 20, "cm"))
+  )
 
-figure <- plotPDF(p)
+pdf <- ggplot(data = NULL) +
+  geom_point(
+    data = stats,
+    aes(x = gene_name, y = mean, color = fraction),
+    position = position_dodge(width = 1),
+    size = 0.25
+  ) +
+  facet_wrap(~`Biosample term name`, ncol = 1) +
+  geom_errorbar(
+    data = stats, 
+    aes(x = gene_name, ymax = sd_max, ymin = sd_min, colour = fraction), 
+    width = 0,
+    position = position_dodge(width = 1),
+    size = 0.1
+  ) +
+  scale_y_continuous(labels = scales::percent) +
+  coord_flip() +
+  labs(
+    y = "% TPM",
+    x = "Gene"
+  ) +
+  guides(colour = guide_legend(title = "Fraction"))
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
-# ggsave(
-#  plot = figure,
-#  filename = path,
-#  device = cairo_pdf,
-#  height = 60,
-#  width = 83,
-#  units = "mm"
-# )
+figure <- plotPDF(pdf) +
+  theme(
+    axis.text.y = element_text(size = 4),
+    strip.text.x = element_text(size = 5)
+  )
+
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
+ggsave(
+ plot = figure,
+ filename = path,
+ device = cairo_pdf,
+ height = 60,
+ width = 83,
+ units = "mm"
+)
 ```

### 2017-11-27 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
correcting text in lnc34a splice junctions .Rmd

@@
 
-All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
+All available RNAseq splice junction data from the ENCODE project originating from the Cold Spring Harbor Lab from `r nrCellLinesDown()` cell lines was downloaded from the UCSC genome browser with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
 Of these cell lines `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).

### 2017-11-27 inst/cellular_localization_encode/cellular_localization_encode.Rmd
further work on manuscript

@@
     position = position_dodge(width = 1),
-    size = 0.25
+    size = 0.5
   ) +
@@
     position = position_dodge(width = 1),
-    size = 0.1
+    size = 0.25
   ) +

### 2017-11-27 R/utils.R

@@ -27,8 +27,8 @@ fileMap <- function(type) {
     figure1d = "3_prime_race/3_prime_race.Rmd",
     figure1e = "primer_walk/primer_walk.Rmd",
     figure1f = "coding_potential_cpat/coding_potential_cpat.Rmd",
-    figure2a = "hct116_p53_null/hct116_p53_null.Rmd",
-    figure2b = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
+    figure2b = "hct116_p53_null/hct116_p53_null.Rmd",
+    figure2a = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
     figure2c = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
     figure2d = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
     figure3a = "stable_line_expression/stable_line_expression.Rmd",

### 2017-11-27 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
further modifications to manuscript and figures

@@
 
+data <- data %>%
+  mutate(Treatment = case_when(
+    Treatment == "untreated" ~ 0,
+    Treatment == "doxorubicin" ~ 200,
+    TRUE ~ NaN
+  )) %>%
+  mutate(Treatment = parse_factor(Treatment, levels = c("0", "200")))
+
+stats <- stats %>%
+  mutate(Treatment = case_when(
+    Treatment == "untreated" ~ 0,
+    Treatment == "doxorubicin" ~ 200,
+    TRUE ~ NaN
+  )) %>%
+  mutate(Treatment = parse_factor(Treatment, levels = c("0", "200")))
 ```
@@
   labs(
-    x = "Treatment",
+    x = "Doxorubicin (ng/ml)",
     title = "miR34a asRNA response to p53 induction"

### 2017-11-27 inst/hct116_p53_null/hct116_p53_null.Rmd
further modifications to manuscript and figures

@@
   ungroup()
-
 ```
@@
   scale_y_continuous("\u0394\u0394Ct", breaks = c(-1,0,1,2,3,4,5))+
-  labs(x = "Treatment")
+  labs(x = "Doxorubicin (ng/ml)")
 

### 2017-11-27 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
further modifications to manuscript and figures

@@
     CI95h = t.test(log2fold)$conf.int[2]
-  )
+  ) %>%
+  ungroup()
 
@@
 
-plotRmarkdown(p)
+plotRmarkdown(markdown)
 

### 2017-12-01 R/utils.R
adding parseUCSCfiles function

@@ -85,3 +85,67 @@ fileMap <- function(type) {
   read_tsv(x, col_names = FALSE, col_types = col_types) %>%
     filter(X1 == "chr1" & X2 >= start & X3 <= stop & X6 == "+")
 }
+
+#parse ENCODE metadata from UCSC
+parseUCSCfiles <- function(url) {
+  fileName <- "(wgEncode.*)\t[A-Za-z]*=.*"
+  objStatus <- ".*\tobjStatus=(.*)\\; p[A-Za-z]*=.*"
+  project <- ".*project=(.*)\\; grant.*"
+  grant <- ".*grant=(.*).\\s+lab=.*"
+  lab <- ".*lab=(.*)\\; composite=.*"
+  composite <- ".*composite=(.*)\\; dataType=.*"
+  dataType <- ".*dataType=(.*)\\; view=.*"
+  view <- ".*view=(.*)\\; cell=.*"
+  cell <- ".*cell=(.*)\\; localization=.*"
+  localization <- ".*localization=(.*)\\; rnaExtract=.*"
+  rnaExtract <- ".*rnaExtract=(.*)\\; replicate=.*"
+  replicate <- ".*replicate=(.*)\\; dataVersion=.*"
+  dataVersion <- ".*dataVersion=(.*)\\; dccAccession=.*"
+  dccAccession <- ".*dccAccession=(.*)\\; dateSubmitted=.*"
+  dateSubmitted <- ".*dateSubmitted=(.*)\\; dateUnrestricted=.*"
+  dateUnrestricted <- ".*dateUnrestricted=(.*)\\; subId=.*"
+  geoSampleAccession <- ".*geoSampleAccession=(.*)\\; [A-Za-z]*=.*"
+  labExpId <- ".*labExpId=(.*)\\; bioRep=.*"
+  bioRep <- ".*bioRep=(.*)\\; seqPlatform=.*"
+  seqPlatform <- ".*seqPlatform=(.*)\\; tableName=.*"
+  tableName <- ".*tableName=(.*)\\; type=.*"
+  type <- ".*type=(.*)\\; md5sum=.*"
+  md5sum <- ".*md5sum=(.*)\\; size=.*"
+  size <- ".*size=(.*)$"
+  
+  read_lines(url) %>%
+  tibble(
+    line = .,
+    `file name` = str_replace(., fileName, "\\1"),
+    `obj status` = if_else(str_detect(., objStatus), str_replace(., objStatus, "\\1"), "NA"),
[…]

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
getting lnc34a cage from UCSC again, to incorporate polyA- data

@@
 ---
-title: "lnc34a CAGE"
+title: "Lnc34a CAGE"
 author: "Jason T. Serviss"
@@
 }
+
+#add function to show polyA and total RNA table
 ```
 
-All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
-Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
-These cell lines included: `r cellLinesInFinal()`.
+All available CAGE data from r nrCellLinesDown() cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
+Of these r cellLinesInFinal() %>% length() cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
+These cell lines included: r cellLinesInFinal().
 All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance.
@@
 ```{r}
-data <- tibble(
-  gene = readr::parse_factor(
-    c(rep("miR34a asRNA", 5), rep("lnc34a", 3)),
-    levels = c("miR34a asRNA", "lnc34a")
-  ),
+#genes and primers
+gdata <- tibble(
+  gene = c(rep("miR34a asRNA", 5), rep("lnc34a", 3)),
+  fill = gene,
   feature = c(
@@
 #try to cut the data so that the CAGE reads are more visable in the figure.
-data <- filter(data, start < 9245000) %>%
+gdata <- filter(gdata, start < 9245000) %>%
   mutate(stop = if_else(feature == "intron" & start != 9242375, 9245000, stop))
 
+#add primer walk primers
 pw <- tibble(
-  gene = paste("F", 10:15, sep = ""),
+  fill = paste("F", 10:15, sep = ""),
+  gene = "Primers",
   feature = rep("primer", 6),
@@
 
+gdata <- bind_rows(gdata, pw) %>%
+  mutate(gene = readr::parse_factor(gene, levels = c("Primers", "lnc34a", "miR34a asRNA")))
+
+#cage data
 url <- fileMap(type = "rds")["suppFigure3d"][[1]]
-cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
-    arrange(desc(level)) %>%
-    mutate(
-      y = 1:length(pull(., level)),
-      cellLine = gsub("^wgEncodeRikenCage(.*)Cell.*", "\\1", filename)
-    )
+cage <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
@@
   geom_segment(
-    data = filter(data, feature == "intron"),
+    data = filter(gdata, feature == "intron"),
     aes(x = start, xend = stop, y = gene, yend = gene),
@@
   gggenes::geom_gene_arrow(
-    data = filter(data, feature == "exon"),
-    aes(xmin = start, xmax = stop, y = gene, fill = gene),
+    data = filter(gdata, feature %in% c("exon", "primer")),
+    aes(xmin = start, xmax = stop, y = gene, fill = fill),
     arrowhead_width = unit(0, "mm"),
@@
     colour = "gray"
+  ) +
+  geom_text(
+    data = filter(gdata, feature == "primer"),
+    aes(x = start + 10, y = 2.5, label = fill),
+    size = 3,
+    angle = 90,
+    colour = "grey20"
   ) +
@@
     arrowhead_height = unit(0, "mm"),
-    arrow_body_height = unit(2, "mm"),
+    arrow_body_height = unit(1, "mm"),
     colour = "gray",
@@
 p3 <- ggplot(data = NULL) + 
-  geom_line(data = cage, aes(x = start), stat="density") +
+  geom_line(data = cage, aes(x = start), stat = "density") +
   ggthemes::theme_few() +
@@
 #plot pdf
+
 #genes
 p1 <- ggplot(data = NULL) +
-  gggenes::geom_gene_arrow(
-    data = filter(data, feature == "exon"),
-    aes(xmin = start, xmax = stop, y = gene, fill = gene),
-    arrowhead_width = unit(0, "mm"),
-    arrowhead_height = unit(0, "mm"),
-    arrow_body_height = grid::unit(1, "mm"),
-    colour = "gray",
-    lwd = 0.1
-  ) +
-  ggthemes::theme_few() +
-  ggthemes::scale_fill_ptol() +
   geom_segment(
-    data = filter(data, feature == "intron"),
+    data = filter(gdata, feature == "intron"),
     aes(x = start, xend = stop, y = gene, yend = gene),
@@
   ) +
+  gggenes::geom_gene_arrow(
+    data = filter(gdata, feature %in% c("exon", "primer")),
+    aes(xmin = start, xmax = stop, y = gene, fill = fill),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = unit(1, "mm"),
+    colour = "gray",
+    lwd = 0.1
+  ) +
+  geom_text(
+    data = filter(gdata, feature == "primer"),
+    aes(x = start + 10, y = 2.65, label = fill),
+    size = 1.75,
+    angle = 90,
+    colour = "grey20"
+  ) +
+  ggthemes::theme_few() +
+  ggthemes::scale_fill_ptol() +
   xlim(9241000, 9245000) +
-  labs(x = "Chromosome 1", y = "") +
+  labs(x = "Chromosome 1", y = "Genes") +
   guides(fill = FALSE) +
@@
 #cage
+p2 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = cage,
+    aes(xmin = start, xmax = stop, y = y, fill = level),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    arrow_body_height = unit(1, "mm"),
+    colour = NA,
+    lwd = 0.1,
+    show.legend = TRUE
+  ) +
+  ggthemes::theme_few() +
+  viridis::scale_fill_viridis() +
+  theme(
+    axis.title.x = element_blank(),
+    axis.title.y = element_text(size = 6),
+    legend.position = "top",
+    legend.title = element_text(size = 5),
+    legend.text = element_text(size = 4),
+    legend.box.spacing = unit(3, "pt"),
+    axis.text = element_blank(),
+    axis.ticks = element_blank(),
+    panel.border = element_rect(fill = NA, size = 0.1),
+    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
+    strip.text.y = element_text(angle = 0)
+  ) +
+  labs(y = "Cage reads") +
+  xlim(9241000, 9245000) +
+  guides(fill = guide_colourbar(
+    title = "RPKM", 
+    title.position = "top", 
+    title.hjust = 0.5,
+    barheight = unit(2, "mm")
+  ))
+
+#density
+p3 <- ggplot(data = NULL) + 
+  geom_line(
+    data = cage, 
+    aes(x = start), 
+    stat = "density", 
+    lwd = 0.1
+  ) +
+  ggthemes::theme_few() +
+  xlim(9241000, 9245000) +
+  theme(
+    axis.text = element_blank(),
+    axis.title.x = element_blank(),
+    axis.title.y = element_text(size = 6),
+    axis.ticks = element_blank(),
+    panel.border = element_rect(fill = NA, size = 0.1)
+    #plot.margin = unit(c(0, 1, 2, 1), "mm")
+  ) +
+  labs(y = "Density")
+
+grobz <- lapply(list(p1, p2, p3), ggplotGrob)
+g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
+g <- resize_heights(g, unit(c(5, 1, 1.5), "null"))
+#grid.draw(g)
+
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
+ggsave(
+  plot = g,
+  filename = path,
+  device = cairo_pdf,
+  height = 125,
+  width = 90,
+  units = "mm"
+)
+```
+
 p2 <- ggplot(data = NULL) +
@@
 
-#density
-p3 <- ggplot(data = NULL) + 
-  geom_line(data = cage, aes(x = start), stat="density", lwd = 0.1) +
-  ggthemes::theme_few() +
-  xlim(9241000, 9245000) +
-  theme(
-    axis.text = element_blank(),
-    axis.title.x = element_blank(),
-    axis.title.y = element_text(size = 6),
-    axis.ticks = element_blank(),
-    panel.border = element_rect(fill = NA, size = 0.1),
-    plot.margin = unit(c(0, 1, 2, 1), "mm")
-  ) +
-  labs(y = "Density")
-
-grobz <- lapply(list(p1, p2, p3), ggplotGrob)
-g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
-g <- resize_heights(g, unit(c(6, 1, 1), "null"))
-#grid.draw(g)
-
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
-# ggsave(
-#   plot = g,
-#   filename = path,
-#   device = cairo_pdf,
-#   height = 60,
-#   width = 83,
-#   units = "mm"
-# )
-```
-
 <div class="caption">

### 2017-12-01 data-raw/saveRDS.R

@@ -266,13 +266,15 @@ read_tsv('./data-raw/stable_line_ccnd1_prot.txt', col_names = TRUE) %>%
 #the chromosomal regions correspond to 200 bp upstream of the lnc34a start
 #site and 200 bp downstream of the GENCODE annotated miR34a asRNA start site.
 print("processing lnc34a_cage")
-read_tsv('./data-raw/lnc34a_cage.txt', col_names = FALSE) %>%
-  pull(X1) %>%
-  read_tsv(.) %>%
+parseUCSCfiles('http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/files.txt') %>%
+  filter(type == "bedRnaElements") %>%
+  write_tsv(., path = './data-raw/lnc34a_cage.txt') %>%
+#slice(1:5) %>%
   mutate(fileContens =
     map(
-      `File download URL`,
-      ~ read_tsv(., col_names = FALSE) %>%
+      `url`,
+      ~ print(.) %>%
+        read_tsv(., col_names = FALSE, na = c("", "NA", ".")) %>%
         filter(X1 == "chr1" & X2 >= (9241796 - 200) & X3 <= (9242263 + 200) & X6 == "+")
     )
   ) %>%

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
adding updated lnc34a CAGE figures

@@
 output:
+  pdf_document: default
   html_document:
+    code_folding: hide
     theme: flatly
-    code_folding: hide
-vignette: >
-  %\VignetteIndexEntry{Vignette Title}
-  %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
+vignette: |
+  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
 ---
@@
     "miR34AasRNAproject",
-    "ggthemes"
+    "ggthemes",
+    "printr"
 )
@@
 projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
 
@@
 nrCellLinesDown <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
   url <- fileMap(type = "txt")["suppFigure3d"][[1]]
-
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
-    pull(14) %>% 
-    gsub(
-      "^http://hgdownload.cse.ucsc.edu/goldenPath/hg19/encodeDCC/wgEncodeRikenCage/wgEncodeRikenCage(.*)Cell.*", 
-      "\\1",
-      .
-    ) %>%
+    pull(cell) %>%
     unique() %>%
@@
   url <- fileMap(type = "rds")["suppFigure3d"][[1]]
+  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+    pull(cell) %>%
+    unique()
+}
 
+RNAprepTable <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
   read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
-    pull(filename) %>%
-    gsub(
-      "^wgEncodeRikenCage(.*)Cell.*",
-      "\\1",
-      .
-    ) %>%
-    unique() %>%
-    sort()
+    mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
+    select(`rna extract`) %>%
+    count(`rna extract`)
+}
+
+localizationTable <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
+  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+    select(localization) %>%
+    count(localization)
 }
@@
 
-All available CAGE data from r nrCellLinesDown() cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
-Of these r cellLinesInFinal() %>% length() cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
-These cell lines included: r cellLinesInFinal().
+All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
+Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
+These cell lines included: `r cellLinesInFinal()`.
 All CAGE reads were plotted and the RPKM of the individual reads was used to color each read to indicate their relative abundance.
-In addition, a density plot shows the distribution of the CAGE reads at in the specified interval.
+In addition, a density plot shows the distribution of the CAGE reads in the specified interval.
+Further information concerning RNA extraction and localization of the samples included is shown below:
+
+Number of samples from included RNA extraction methods:
+
+```{r}
+RNAprepTable()
+```
+
+Number of samples from included RNA localizations:
+
+```{r}
+localizationTable()
+```
 
@@
   device = cairo_pdf,
-  height = 125,
+  height = 150,
   width = 90,
@@
 
-p2 <- ggplot(data = NULL) +
-  gggenes::geom_gene_arrow(
-    data = cage,
-    aes(xmin = start, xmax = stop, y = y, fill = level),
-    arrowhead_width = unit(0, "mm"),
-    arrowhead_height = unit(0, "mm"),
-    arrow_body_height = unit(2, "pt"),
-    colour = NA,
-    lwd = 0.1,
-    show.legend = TRUE
-  ) +
-  ggthemes::theme_few() +
-  viridis::scale_fill_viridis() +
-  theme(
-    axis.title.x = element_blank(),
-    axis.title.y = element_text(size = 6),
-    legend.position = "top",
-    legend.title = element_text(size = 7),
-    legend.text = element_text(size = 6),
-    legend.box.spacing = unit(3, "pt"),
-    axis.text = element_blank(),
-    axis.ticks = element_blank(),
-    panel.border = element_rect(fill = NA, size = 0.1),
-    plot.margin = unit(c(0.01, 1, 0.01, 1), "mm"),
-    strip.text.y = element_text(angle = 0)
-  ) +
-  labs(y = "Cage reads") +
-  xlim(9241000, 9245000) +
-  guides(fill = guide_colourbar(
-    title = "RPKM",
-    title.position = "top",
-    title.hjust = 0.5,
-    barheight = unit(4, "pt"),
-    barwidth = unit(50, "pt")
-  ))
-
 <div class="caption">
-CAGE tags (top), CAGE tag density (middle), and antisense genes (bottom) at the miR34a locus. CAGE tags are colored according to their corresponding RPKM values.
+CAGE tags (top), CAGE tag density (middle), and antisense genes at the miR34a locus and primers from the primer walk assay (bottom). CAGE tags are colored according to their corresponding RPKM values.
 </div>
@@
 The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site.
-An additional peak, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site and corresponds to the upstream start site detected in our primer walk analysis (figure 1e).
+Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (figure 1e).
 Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript.
@@
 An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected.
+Finally, lnc34a may not be 5'-capped precluding its detection by CAGE.
 

### 2017-12-01 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
adding rna extraction method to lnc34a splice analysis

--- 2017-11-25 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
@@
   "gtable",
-    "miR34AasRNAproject"
+  "miR34AasRNAproject",
+  "printr"
 )
@@
 }
+
+RNAprepTable <- function() {
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "rds")["suppFigure3e"][[1]]
+  final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+    select(filename) %>%
+    distinct() %>%
+    mutate(filename = str_replace(filename, "^(.*)\\.bedRnaElements.*", "\\1"))
+
+  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+  url <- fileMap(type = "txt")["suppFigure3e"][[1]]
+  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
+    filter(X__15 %in% pull(final, filename)) %>%
+    rename(`rna extract` = X__3) %>%
+    select(`rna extract`) %>%
+    count(`rna extract`)
+}
 ```
 
-All available splice junction data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
+All available whole cell RNAseq splice junction data from the ENCODE project originating from the Cold Spring Harbor Lab from `r nrCellLinesDown()` cell lines was downloaded from the UCSC genome browser with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
 Of these cell lines `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
@@
 All splice junctions were plotted and colored according to the number of reads corresponding to each.
+Information regarding the RNA extraction is included below:
+
+Number of samples from included RNA extraction methods:
+
+```{r, message = FALSE}
+RNAprepTable()
+```
 
@@
 <div class="caption">
-Splice junctions (top) detected in RNAseq data from the ENCODE project and antisense genes (bottom) at the miR34a locus. Splice junctions are colored according to the corresponding total read count.
+Splice junctions (top) detected in RNAseq data from the ENCODE project and antisense genes (bottom) at the miR34a locus.
+Splice junctions are colored according to the corresponding total read count.
+In cases where the exact same read was detected multiple times the read count was summed.
 </div>
@@
 #### _Conclusions_
-Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (Supplementary figure XX) with those being the mist highly expressed corresponding to the annotated miR34a asRNA transcript.
+Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (**Supplementary Fig 1d.**) with those being the most highly expressed corresponding to the annotated miR34a asRNA transcript.
 Despite this, no splice junctions appear to correspond to the intron in the lnc34a transcript.
@@
 An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected.
+Finally, lnc34a may not be expressed in any of the cell lines examined.
 

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
updating rmds according to fileMap

@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
-  url <- fileMap(type = "txt")["suppFigure3d"][[1]]
+  url <- fileMap(type = "txt")["suppFigure4a"][[1]]
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure3d"][[1]]
+  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
   read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 #cage data
-url <- fileMap(type = "rds")["suppFigure3d"][[1]]
+url <- fileMap(type = "rds")["suppFigure4a"][[1]]
 cage <- read_rds(gzcon(url(file.path(dataUrl, url))))

### 2017-12-01 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
updating rmds according to fileMap

@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure3e"][[1]]
+  url <- fileMap(type = "txt")["suppFigure4b"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure3e"][[1]]
+  url <- fileMap(type = "rds")["suppFigure4b"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure3e"][[1]]
+  url <- fileMap(type = "rds")["suppFigure4b"][[1]]
   final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure3e"][[1]]
+  url <- fileMap(type = "txt")["suppFigure4b"][[1]]
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 #splice junctions
-url <- fileMap(type = "rds")["suppFigure3e"][[1]]
+url <- fileMap(type = "rds")["suppFigure4b"][[1]]
 splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))

### 2017-12-01 R/utils.R

@@ -48,8 +48,8 @@ fileMap <- function(type) {
     suppFigure3a = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
     suppFigure3b = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
     suppFigure3c = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
-    suppFigure3d = "lnc34a_cage/lnc34a_cage.Rmd",
-    suppFigure3e = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd"
+    suppFigure4a = "lnc34a_cage/lnc34a_cage.Rmd",
+    suppFigure4b = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd"
   )
   
   if(type == "Rmd") {

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
small adjustments to text in lnc34a analysis rmds

@@
 All available CAGE data from `r nrCellLinesDown()` cell lines was downloaded from UCSC with the script entitled "lnc34a CAGE" in the data-raw/saveRDS.R file.
-Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE tags mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
+Of these `r cellLinesInFinal() %>% length()` cell lines had CAGE transcription start sites mapping to the plus strand of chromosome 1 and in regions corresponding to 200 bp upstream of the lnc34a start site (9241796 - 200) and 200 bp upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
 These cell lines included: `r cellLinesInFinal()`.
@@
 The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site.
-Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (figure 1e).
+Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (**Figure 1e**).
 Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript.

### 2017-12-01 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
small adjustments to text in lnc34a analysis rmds

@@
 All available whole cell RNAseq splice junction data from the ENCODE project originating from the Cold Spring Harbor Lab from `r nrCellLinesDown()` cell lines was downloaded from the UCSC genome browser with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
-Of these cell lines `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
+Of these cell lines, `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
 Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`.

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
grouped identical reads in CAGE figure

@@
 output:
-  pdf_document: default
   html_document:
@@
     theme: flatly
+  pdf_document: default
 vignette: |
@@
 gdata <- bind_rows(gdata, pw) %>%
-  mutate(gene = readr::parse_factor(gene, levels = c("Primers", "lnc34a", "miR34a asRNA")))
+  mutate(gene = readr::parse_factor(gene, levels = c("miR34a asRNA", "lnc34a", "Primers")))
 
@@
 url <- fileMap(type = "rds")["suppFigure4a"][[1]]
-cage <- read_rds(gzcon(url(file.path(dataUrl, url))))
+cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  select(start, stop, level) %>%
+  group_by(start, stop) %>%
+  summarize(level = sum(level)) %>%
+  ungroup() %>%
+  arrange(desc(level)) %>%
+  mutate(y = 1:n())
 
@@
 p1 <- ggplot(data = NULL) +
+  gggenes::geom_gene_arrow(
+    data = filter(gdata, feature %in% c("exon", "primer")),
+    aes(xmin = start, xmax = stop, y = gene, fill = fill, group = gene),
+    arrowhead_width = unit(0, "mm"),
+    arrowhead_height = unit(0, "mm"),
+    colour = "gray"
+  ) +
   geom_segment(
     data = filter(gdata, feature == "intron"),
-    aes(x = start, xend = stop, y = gene, yend = gene),
+    aes(x = start, xend = stop, y = gene, yend = gene, group = gene),
     linetype = "dotted",
@@
     size = 1
-  ) +
-  gggenes::geom_gene_arrow(
-    data = filter(gdata, feature %in% c("exon", "primer")),
-    aes(xmin = start, xmax = stop, y = gene, fill = fill),
-    arrowhead_width = unit(0, "mm"),
-    arrowhead_height = unit(0, "mm"),
-    colour = "gray"
   ) +
@@
 p1 <- ggplot(data = NULL) +
-  geom_segment(
-    data = filter(gdata, feature == "intron"),
-    aes(x = start, xend = stop, y = gene, yend = gene),
-    linetype = "dotted",
-    colour = "gray",
-    size = 0.25
-  ) +
   gggenes::geom_gene_arrow(
@@
   ) +
+  geom_segment(
+    data = filter(gdata, feature == "intron"),
+    aes(x = start, xend = stop, y = gene, yend = gene),
+    linetype = "dotted",
+    colour = "gray",
+    size = 0.25
+  ) +
   geom_text(
     data = filter(gdata, feature == "primer"),
-    aes(x = start + 10, y = 2.65, label = fill),
+    aes(x = start + 10, y = 2.55, label = fill),
     size = 1.75,
@@
 g <- rbind(grobz[[2]], grobz[[3]], grobz[[1]], size = "last")
-g <- resize_heights(g, unit(c(5, 1, 1.5), "null"))
+g <- resize_heights(g, unit(c(5, 1, 2), "null"))
 #grid.draw(g)
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3d"][[1]])
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
 ggsave(
@@
   device = cairo_pdf,
-  height = 150,
+  height = 100,
   width = 90,

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
commented figure pdf save

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
-ggsave(
-  plot = g,
-  filename = path,
-  device = cairo_pdf,
-  height = 100,
-  width = 90,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
+# ggsave(
+#   plot = g,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 100,
+#   width = 90,
+#   units = "mm"
+# )
 ```

### 2017-12-01 inst/stable_line_expression/stable_line_expression.Rmd
fixing headers in Rmds

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```
@@
 
-####_Conclusion_
+#### _Conclusion_
 

### 2017-12-03 inst/cellular_localization_encode/cellular_localization_encode.Rmd
adding sessionInfo to all rmds

@@
 
+asRNAs are known to be capable of exerting regulatory functions on both a transcriptional and post-transcriptional level and therefore, the cellular localization of the asRNA can be informative concerning the method of regulation.
+
 <br></br>
@@
 #### _Methods_
+Quantified RNAseq data from 11 cell lines from the GRCh38 assembly was downloaded from ENCODE and quantifications for miR34a asRNA (ENSG00000234546), ACTB (ENSG00000075624), GAPDH (ENSG00000111640), and MALAT1 (ENSG00000251562) were extracted.
+Cell lines for which data was downloaded include: A549, GM12878, HeLa-S3, HepG2, HT1080, K562    MCF-7, NCI-H460, SK-MEL-5, SK-N-DZ, SK-N-SH.
+Initial exploratory analysis revealed that several cell lines should not be included in the final figure for the following reasons: The SK-N-SH has a larger proportion of GAPDH in the nucleus than cytoplasm.
+The variation of miR34a asRNA expression is too large for SK-MEL-5.
+K562, HT1080, SK-N-DZ, and NCI-H460 have no or low miR34a asRNA expression.
+In addition, both the cytoplasmic markers ACTB and GAPDH were analyzed for their ability to differentiate between the nuclear and cytoplasmic fractions, and GAPDH was choosed for the final analysis due its superior performance.
+Furthermore, only polyadenylated libraries were used in the final analysis and only samples with 2 biological replicates were retained.
+For each cell type, gene, and biological replicate the fraction of transcripts per million (TPM) in each cellular compartment was calculate as the fraction of TPM in the specific compartment by the total TPM.
+The mean and standard deviation for the fraction was subsequently calculated for each cell type and cellular compartment and this information was represented in the final figure.
 
@@
 <div class="caption">
-Write figure legend.
+RNAseq data from five fractionated cell lines in the ENCODE project showing the percentage of transcripts per million (TPM) for miR34a asRNA.
+MALAT1 (nuclear localization) and GAPDH (cytoplasmic localization) are included as fractionation controls.
+Points represent the mean and horizontal lines represent the standard deviation from two biological replicates.
 </div>
@@
 #### _Conclusions_
+The analysis revealed that the miR34a asRNA transcript localizes to both the nucleus and cytoplasm but primarily resides in the nucleus.
 
 <br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-03 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
re-ran all rmds and added sessionInfo to all

@@
 
-url <- fileMap(type = "rds")["figure2b"][[1]]
+url <- fileMap(type = "rds")["figure2a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
 # ggsave(
@@
 <br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-03 inst/hct116_p53_null/hct116_p53_null.Rmd
re-ran all rmds and added sessionInfo to all

@@
 
-url <- fileMap(type = "rds")["figure2a"][[1]]
+url <- fileMap(type = "rds")["figure2b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
 # ggsave(

### 2017-12-03 inst/cellular_localization_encode/cellular_localization_encode.Rmd
done adding the TCGA correlation TABLE, more work on manuscript (citations)

@@
     "ggthemes",
-    "readr",
     "miR34AasRNAproject",

### 2017-12-03 inst/stable_line_expression/stable_line_expression.Rmd
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

@@
   ),
-  n = c(3, 5, 4, 4, 5, 5)
+  n = c(5, 5, 4, 4, 5, 5)
 )

### 2017-12-03 inst/tcga_correlation/tcga_correlation.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

--- 2017-11-20 inst/tcga_correlation/tcga_correlation.Rmd
@@
 
-####_Introduction_
+#### _Introduction_
+We interogated RNA sequencing data from TCGA to determine in miR34a and miR34a asRNA expression was correlated in both TP53 wild type and mutated samples.
 
@@
 
-####_Results_
+#### _Results_
+```{r}
+url <- fileMap(type = "rds")["figure1c"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+#normalize expression values
+data <- mutate(
+    data,
+    RP3 = log2(RP3 / max(RP3)),
+    miR34a = log2(miR34a / max(miR34a))  
+  )
+
+#add BRCA subtypes
+data <- data %>%
+  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
+  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))
+
+#sort 
+data <- arrange(data, cancer_PAM50, TP53, RP3)
+
+#remove infinite data
+data <- filter(data, !is.infinite(RP3) & !is.infinite(miR34a))
+
+#diploid only
+data <- filter(data, abs(RP3_cna) < 0.1)
+```
+
+```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
+#plot
+plotTCGAcorrelation(data, type = "diploid only")
+
+#save to pdf
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
+# pdf(path, width = 28)
+# data %>%
+#   arrange(cancer_PAM50, TP53, RP3) %>%
+#   plotTCGAcorrelation(type = "diploid only")
+# invisible(dev.off())
+```
 
@@
 
-Insert code here from Erik and write Intro Methods etc
-
-```{r, out.width = "1000px"}
-
-url <- fileMap(type = "png")["figure1c"][[1]]
-knitr::include_graphics(file.path(projectUrl, url))
-
-```
-
 <br></br>
 
-####_Conclusions_
+#### _Conclusions_
+miR34a asRNA and miR34a tend to be highly correlated in the cancer types examined in both TP53 wild type and mutated samples.
+In addition, the results indicate that both miR34a asRNA and miR34a expression levels are decreased in the presence of TP53 mutations.
 
 <br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-03 inst/tcga_correlation_table/tcga_correlation_table.Rmd
adding tcga_correlation_table as .rds
ran tcga correlation table .rmd after last 2 commits
re-ran all rmds and added sessionInfo to all
done adding the TCGA correlation TABLE, more work on manuscript (citations)

@@
 
-```{r, out.width = "850px"}
+```{r, warning = FALSE}
+url <- fileMap(type = "rds")["figure1c"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
 
-url <- fileMap(type = "png")["suppFigure1a"][[1]]
-knitr::include_graphics(file.path(projectUrl, url))
+#normalize expression values
+data <- mutate(
+    data,
+    RP3 = log2(RP3 / max(RP3)),
+    miR34a = log2(miR34a / max(miR34a))  
+  )
 
+#add BRCA subtypes
+data <- data %>%
+  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
+  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))
+
+#sort 
+data <- arrange(data, cancer_PAM50, TP53, RP3)
+
+#remove infinite data
+data <- filter(data, !is.infinite(RP3) & !is.infinite(miR34a))
+
+#diploid only
+data <- filter(data, abs(RP3_cna) < 0.1)
+
+#rename TP53
+data <- mutate(data, TP53 = if_else(TP53 == 1, "TP53mut", "TP53wt"))
+
+#diploid only correlation analysis
+#calculate correlation for all samples per cancer type
+all <- data %>% 
+  filter(RP3_cna < 0.1) %>%
+  group_by(cancer) %>%
+  summarize(
+    n = n(),
+    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
+    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+  )
+
+#calculate correlation for p53 wt and mut samples per cancer type
+p53 <- data %>%
+  group_by(cancer, TP53) %>%
+  filter(n() > 3) %>%
+  summarize(
+    n = n(),
+    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
+    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+  ) %>%
+  ungroup() %>%
+  gather(metric, value, -(cancer:TP53)) %>%
+  unite(temp, TP53, metric) %>%
+  spread(temp, value)
+
+full_join(all, p53, by = "cancer")
 ```

### 2017-12-04 inst/tcga_correlation_table/tcga_correlation_table.Rmd
previously missed the BRCA subtypes in the table, corrected now

@@
 
+Note: in cases where less than 3 samples are in any group, r-estimates and p-values are not reported.
 ```{r, warning = FALSE}
@@
   filter(RP3_cna < 0.1) %>%
-  group_by(cancer) %>%
+  group_by(cancer_PAM50) %>%
   summarize(
@@
 p53 <- data %>%
-  group_by(cancer, TP53) %>%
+  group_by(cancer_PAM50, TP53) %>%
   filter(n() > 3) %>%
@@
   ungroup() %>%
-  gather(metric, value, -(cancer:TP53)) %>%
+  gather(metric, value, -(cancer_PAM50:TP53)) %>%
   unite(temp, TP53, metric) %>%
@@
 
-full_join(all, p53, by = "cancer")
+full_join(all, p53, by = "cancer_PAM50")
 ```

### 2017-12-04 inst/cellular_localization_encode/cellular_localization_encode.Rmd
adding to methods section for cellular localization, polyA status

@@
 In addition, both the cytoplasmic markers ACTB and GAPDH were analyzed for their ability to differentiate between the nuclear and cytoplasmic fractions, and GAPDH was choosed for the final analysis due its superior performance.
-Furthermore, only polyadenylated libraries were used in the final analysis and only samples with 2 biological replicates were retained.
+Furthermore, only polyadenylated libraries were used in the final analysis, due to the fact that the cellular compartment enrichment was seen to be improved in these samples, and all analyzed genes are reported to be polyadenylated (MALAT1: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2722846/).
+Only samples with 2 biological replicates were retained.
 For each cell type, gene, and biological replicate the fraction of transcripts per million (TPM) in each cellular compartment was calculate as the fraction of TPM in the specific compartment by the total TPM.

### 2017-12-04 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
added a silent p-value calculation in growth analysis

@@
 
+#unreported p-values per time point
+p <- data %>% 
+  filter(Time != 0) %>% 
+  unite(tmp, `Biological Replicate`, `Cell line`) %>% 
+  spread(tmp, techMean) %>% 
+  group_by(Treatment, Time) %>% 
+  summarize(
+	  p = t.test(
+	    c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`), 
+	    c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`)
+	  )$p.value,
+	  meanAS = mean(c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`)),
+	  meanMock = mean(c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`))
+  ) %>%
+  mutate(fold = meanAS / meanMock)
 ```

### 2017-12-04 inst/cellular_localization_encode/cellular_localization_encode.Rmd
lots of work on figures to improve readability

@@
   ) +
+  geom_vline(
+    mapping = NULL, 
+    xintercept=c(1.5, 2.5), 
+    color = "darkgrey", 
+    linetype = 3
+  ) +
   scale_y_continuous(labels = scales::percent) +
@@
     aes(x = gene_name, y = mean, color = fraction),
-    position = position_dodge(width = 1),
-    size = 0.5
+    position = position_dodge(width = 0.45),
+    size = 0.17
   ) +
@@
     width = 0,
-    position = position_dodge(width = 1),
+    position = position_dodge(width = 0.45),
     size = 0.25
+  ) +
+  geom_vline(
+    mapping = NULL,
+    xintercept=c(1.5, 2.5), 
+    color = "darkgrey", 
+    linetype = 3,
+    size = 0.35
   ) +
@@
     axis.text.y = element_text(size = 4),
-    strip.text.x = element_text(size = 5)
+    panel.spacing = unit(0.1, "lines"),
+    strip.text.x = element_text(size = 5, margin = margin(5.5, 5.5, 2.5, 5.5, unit = "pt"))
   )
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
-ggsave(
- plot = figure,
- filename = path,
- device = cairo_pdf,
- height = 60,
- width = 83,
- units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 83,
+#   units = "mm"
+# )
 ```

### 2017-12-04 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
lots of work on figures to improve readability

@@
   ungroup() %>%
+  mutate(max = max + c(0, 0.2, 0, 0)) %>%
   pFormat(.) %>%
@@
     shape = 95,
+    size = 4,
     colour = "gray20"
@@
     colour = "gray20",
-    size = 0.1,
+    size = 0.3,
     position = position_dodge(width = 0.9),
@@
       x = labelX,
-      y = max + 0.3,
+      y = max + 0.4,
       label = pFormat,
@@
     fill = "white",
-    size = 1.5,
+    size = 2,
     family = "Arial Unicode MS",
@@
     colour="grey43",
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE

### 2017-12-04 inst/hct116_p53_null/hct116_p53_null.Rmd
lots of work on figures to improve readability

@@
     colour = "gray20",
-    shape = 95
+    shape = 95,
+    size = 4
   ) +
@@
     position = position_dodge(width = 0.9),
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE
@@
     data = stats,
-    aes(x = Treatment, y = max + 0.28, label = pFormat),
+    aes(x = Treatment, y = max + 0.4, label = pFormat),
     label.size = 0,

### 2017-12-04 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

@@
     colour = "grey20",
-    size = 0.1,
+    size = 0.3,
     position = position_dodge(width = 0.9),
@@
     colour = "gray20",
+    size = 4,
     shape = 95
@@
       x = 1.5, 
-      y = max + 0.25, 
+      y = max + 0.35, 
       label = pFormat, 
@@
     colour = "grey43",
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE

### 2017-12-04 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
fixing headers in Rmds
adding sessionInfo to all rmds
lots of work on figures to improve readability

--- 2017-11-20 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
@@
     GOI == "Renilla" ~ "  Renilla\n(miR34a asRNA)"
-  ))
-
+  )) %>%
+  group_by(GOI, treatment) %>%
+  mutate(
+    height = if_else(treatment == 0, 0, max(CI95h, na.rm = TRUE)),
+    x = case_when(
+      treatment ==   0 ~ 1 + 0.25,
+      treatment == 300 ~ 2 + 0.25,
+      treatment == 500 ~ 3 + 0.25
+    ),
+    xend = case_when(
+      treatment ==   0 ~ 1 - 0.25,
+      treatment == 300 ~ 2 - 0.25,
+      treatment == 500 ~ 3 - 0.25
+    )
+  ) %>%
+  ungroup()
 ```
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
+
+# p <- ggplot(data = NULL) +
+#   geom_violin(
+#     data = data,
+#     aes(
+#       x = treatment, 
+#       y = log2fold, 
+#       group = interaction(plotGOI, treatment)
+#     ),
+#     trim = TRUE,
+#     scale = "width",
+#     alpha = 0.3,
+#     colour = NA,
+#     fill = "gray",
+#     show.legend = FALSE
+#   ) +
+#   geom_dotplot(
+#     data = data, 
+#     aes(
+#       x = treatment,
+#       y = log2fold,
+#       fill = plotGOI
+#     ),
+#     binwidth = 1/10,
+#     #alpha = 0.5,
+#     colour = NA,
+#     position = position_dodge(width = 0.9), 
+#     binaxis = 'y', 
+#     stackdir = 'center',
+#     dotsize = 2,
+#     show.legend = TRUE
+#   ) +
+#   facet_grid(. ~ shRNA, scale = "free") +
+#   scale_y_continuous("\u0394\u0394Ct") +
+#   labs(
+#     x = "Doxorubicin (ng/ml)",
+#     title = "HCT116"
+#   )
+
+# markdown <- p + 
+#   geom_linerange(
+#     data = stats,
+#     aes(
+#       x = treatment, 
+#       ymin = CI95l, 
+#       ymax = CI95h, 
+#       group = plotGOI
+#     ),
+#     colour = "gray20",
+#     position = position_dodge(width = 0.9),
+#     show.legend = FALSE
+#   ) +
+#   geom_point(
+#     data = stats,
+#     aes(
+#       x = treatment, 
+#       y = mean, 
+#       group = plotGOI
+#     ),
+#     colour = "gray20",
+#     position = position_dodge(width = 0.9),
+#     shape = 95,
+#     size = 6,
+#     show.legend = FALSE
+#   ) +
+#   geom_label(
+#     data = stats,
+#     aes(
+#       x = treatment, 
+#       y = CI95h + 0.2,
+#       label = pFormat,
+#       group = plotGOI
+#     ),
+#     label.size = 0,
+#     label.padding = unit(0.01, "lines"),
+#     show.legend = FALSE,
+#     position = position_dodge(width = 0.9),
+#     fill = "white",
+#     size = 5,
+#     family = "Arial Unicode MS"
+#   ) +
+#   guides(
+#     fill = guide_legend(
+#       title = "Gene", 
+#       override.aes = list(size = 6)
+#     )
+#   )
 
@@
       y = log2fold, 
-      group = interaction(plotGOI, treatment)
+      group = interaction(shRNA, treatment)
     ),
@@
       y = log2fold,
-      fill = plotGOI
+      fill = shRNA
     ),
     binwidth = 1/10,
-    alpha = 0.5,
+    #alpha = 0.5,
     colour = NA,
@@
   ) +
-  facet_grid(. ~ shRNA, scale = "free") +
+  facet_grid(. ~ plotGOI, scale = "free") +
   scale_y_continuous("\u0394\u0394Ct") +
@@
   )
-
 markdown <- p + 
@@
       ymax = CI95h, 
-      group = plotGOI
+      group = shRNA
     ),
@@
       y = mean, 
-      group = plotGOI
+      group = shRNA
     ),
@@
       x = treatment, 
-      y = CI95h + 0.2,
-      label = pFormat,
-      group = plotGOI
+      y = height + 0.5,
+      label = pFormat
     ),
@@
     show.legend = FALSE,
-    position = position_dodge(width = 0.9),
     fill = "white",
@@
     family = "Arial Unicode MS"
+  ) +
+  geom_segment(
+    data = stats,
+    aes(x = x, y = height + 0.25, xend = xend, yend = height + 0.25),
+    colour="grey43",
+    show.legend = FALSE
   )  +
@@
     shape = 95,
+    size = 4,
     show.legend = FALSE
@@
     show.legend = FALSE,
-    position = position_dodge(width = 0.9),
     fill = "white",
-    size = 1.5,
+    size = 2,
     family = "Arial Unicode MS"
+  ) +
+  geom_segment(
+    data = stats,
+    aes(x = x, y = height + 0.25, xend = xend, yend = height + 0.25),
+    colour="grey43",
+    size = 0.3,
+    show.legend = FALSE
   )  +

### 2017-12-04 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

@@
     stackdir = 'center',
-    dotsize = 0.5,
+    dotsize = 1,
     show.legend = TRUE
@@
     colour = "grey25",
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE
@@
     fill = "white",
-    size = 1.5,
+    size = 2,
     family = "Arial Unicode MS"

### 2017-12-04 inst/stable_line_expression/stable_line_expression.Rmd
lots of work on figures to improve readability

@@
   mutate(
-    max = max + c(0.55, 1.95, 0.25, 1.65, 0.25, 1.65)
+    max = max + c(0.75, 2.65, 0.45, 2.35, 0.45, 2.35)
   )
@@
     stackdir = 'center',
-    dotsize = 4,
+    dotsize = 6,
     show.legend = TRUE
@@
     colour = "gray20",
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE
@@
     shape = 95,
+    size = 4,
     position = position_dodge(width = 0.9),
@@
       x = 1.5, 
-      y = max + 0.6, 
+      y = max + 0.85, 
       label = pFormat, 
@@
     family = "Arial Unicode MS",
-    size = 1.5
+    size = 2
   ) +

### 2017-12-04 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
lots of work on figures to improve readability

@@
     position = position_dodge(width = 1),
-    lwd = 0.1,
+    lwd = 0.2,
     show.legend = FALSE

### 2017-12-04 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
lots of work on figures to improve readability

@@
     colour = "grey43",
-    size = 0.1
+    size = 0.3
   ) +

### 2017-12-04 inst/tcga_correlation/tcga_correlation.Rmd
lots of work on figures to improve readability

@@
 
-#save to pdf
+##save to pdf
 # path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
-# pdf(path, width = 28)
-# data %>%
-#   arrange(cancer_PAM50, TP53, RP3) %>%
-#   plotTCGAcorrelation(type = "diploid only")
+# pdf(path, width = 7.7, height = 4)
+# plotTCGAcorrelation(data, type = "diploid only")
 # invisible(dev.off())

### 2017-12-04 inst/tcga_correlation_table/tcga_correlation_table.Rmd
lots of work on figures to improve readability

@@
 Note: in cases where less than 3 samples are in any group, r-estimates and p-values are not reported.
+
 ```{r, warning = FALSE}
@@
     n = n(),
-    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
-    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+    `all pvalue` = cor.test(RP3, miR34a, method = "spearman")$p.value,
+    `all rho` = cor.test(RP3, miR34a, method = "spearman")$estimate
+  ) %>%
+  mutate(
+    `all pvalue` = format(`all pvalue`, scientific = TRUE, digits = 3),
+    `all rho` = format(`all rho`, scientific = TRUE, digits = 3)
   )
@@
     n = n(),
-    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
-    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+    pvalue = cor.test(RP3, miR34a, method = "spearman")$p.value,
+    rho = cor.test(RP3, miR34a, method = "spearman")$estimate
   ) %>%
   ungroup() %>%
+  mutate(
+    pvalue = format(pvalue, scientific = TRUE, digits = 3),
+    rho = format(rho, scientific = TRUE, digits = 3)
+  ) %>%
   gather(metric, value, -(cancer_PAM50:TP53)) %>%
-  unite(temp, TP53, metric) %>%
+  unite(temp, TP53, metric, sep = " ") %>%
   spread(temp, value)
 
-full_join(all, p53, by = "cancer_PAM50")
+table <- full_join(all, p53, by = "cancer_PAM50") %>%
+  rename(cancer = cancer_PAM50, `all n` = n) %>%
+  select(
+    cancer, `all n`, `all rho`, `all pvalue`, `TP53wt n`, 
+    `TP53wt rho`, `TP53wt pvalue`, `TP53mut n`, `TP53mut rho`, `TP53mut pvalue`
+  )
+
+table
+
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
+pdf(file = path, width = 14)
+gridExtra::grid.table(table, rows = NULL)
+invisible(dev.off())
 ```

### 2017-12-04 R/QpcrFuns.R

@@ -247,8 +247,14 @@ pFormat <- function(
     stats
 ){
     idx <- which(colnames(stats) == "pValue")
-    mutate(stats, pFormat = case_when(
+    mutate(stats,
+      pFormat = case_when(
         is.nan(pValue) | pValue == 1 ~ "",
-        TRUE ~ format(stats[[idx]], scientific = TRUE, digits = 2))
+        TRUE ~ gsub(
+          "([0-9]*e.)0(.*)",
+          "\\1\\2",
+          format(stats[[idx]], scientific = TRUE, digits = 2)
+        )
+      )
     )
 }

### 2017-12-05 inst/lnc34a_cage/lnc34a_cage.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

@@
     select(`rna extract`) %>%
-    count(`rna extract`)
+    dplyr::count(`rna extract`)
 }
@@
     select(localization) %>%
-    count(localization)
+    dplyr::count(localization)
 }
@@
 #try to cut the data so that the CAGE reads are more visable in the figure.
-gdata <- filter(gdata, start < 9245000) %>%
-  mutate(stop = if_else(feature == "intron" & start != 9242375, 9245000, stop))
+gdata <- filter(gdata, start < 9243000) %>%
+  mutate(stop = if_else(feature == "intron", 9243000, stop))
 
@@
   ggthemes::scale_fill_ptol() +
-  xlim(9241000, 9245000) +
+  xlim(9241596, 9243000) +
   labs(x = "Chromosome 1", y = "Genes") +
@@
   labs(y = "Cage reads") +
-  xlim(9241000, 9245000) +
+  xlim(9241596, 9243000) +
   guides(fill = guide_colourbar(
@@
   ggthemes::theme_few() +
-  xlim(9241000, 9245000) +
+  xlim(9241596, 9243000) +
   theme(
@@
     colour = "gray",
-    size = 0.25
+    size = 0.55
   ) +

### 2017-12-05 inst/p1_hek293t/p1_hek293t.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

--- 2017-11-20 inst/p1_hek293t/p1_hek293t.Rmd
@@
     colour = NA,
-    #alpha = 0.5,
+    alpha = 0.75,
     position = position_dodge(width = 0.9), 
@@
     stackdir = 'center',
-    dotsize = 2,
+    dotsize = 3,
     show.legend = TRUE
   ) +
-  facet_grid(. ~ belongsTo) +
+  facet_grid(. ~ belongsTo, scales = "free") +
   scale_y_continuous("\u0394\u0394Ct")+

### 2017-12-05 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

@@
     colour = "gray20",
-    size = 0.1
+    size = 0.3
   ) +
@@
 
-####_Conclusions_
+#### _Conclusions_
 
 CCND1 expression levels are decreased in PC3 cell lines stably over-expressing miR34a asRNA.
+
+<br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-05 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

@@
     colour="gray20",
-    shape = 95
+    shape = 95,
+    size = 4
   ) +
@@
     colour="grey43",
-    size = 0.1
+    size = 0.3
   ) +
@@
     colour="gray20",
-    size = 0.1
+    size = 0.3
   )
@@
 
-####_Conclusions_
+#### _Conclusions_
 
 Cyclin D1 protein levels are significantly reduced in PC3 cells overexpressing miR34a asRNA, consistent with increased miR34a expression levels and the reduced G1 cell cycle phase observed in PC3 cells.
+
+<br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-05 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
re-ran all rmds and added sessionInfo to all
more work on figure readability, done?

@@
     binwidth = 1/10,
-    #alpha = 0.5,
+    alpha = 0.75,
     position = position_dodge(width = 0.9), 
@@
     stackdir='center',
-    dotsize = 4,
+    dotsize = 6,
     show.legend = TRUE
@@
     show.legend = FALSE,
+    size = 4,
     shape = 95

### 2017-12-05 inst/tcga_correlation_table/tcga_correlation_table.Rmd
more work on figure readability, done?

--- 2017-12-04 inst/tcga_correlation_table/tcga_correlation_table.Rmd
@@
     n = n(),
-    all_pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
-    all_R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+    `all p` = cor.test(RP3, miR34a, method = "spearman")$p.value,
+    `all rho` = cor.test(RP3, miR34a, method = "spearman")$estimate
+  ) %>%
+  mutate(
+    `all p` = format(`all p`, scientific = TRUE, digits = 3),
+    `all rho` = format(`all rho`, scientific = TRUE, digits = 3)
   )
@@
     n = n(),
-    pvalue = signif(cor.test(RP3, miR34a, method = "spearman")$p.value, 3),
-    R_estimate = signif(cor.test(RP3, miR34a, method = "spearman")$estimate, 3)
+    p = cor.test(RP3, miR34a, method = "spearman")$p.value,
+    rho = cor.test(RP3, miR34a, method = "spearman")$estimate
   ) %>%
   ungroup() %>%
+  mutate(
+    p = format(p, scientific = TRUE, digits = 3),
+    rho = format(rho, scientific = TRUE, digits = 3)
+  ) %>%
   gather(metric, value, -(cancer_PAM50:TP53)) %>%
-  unite(temp, TP53, metric) %>%
+  unite(temp, TP53, metric, sep = " ") %>%
   spread(temp, value)
 
-full_join(all, p53, by = "cancer_PAM50")
+table <- full_join(all, p53, by = "cancer_PAM50") %>%
+  rename(cancer = cancer_PAM50, `all n` = n) %>%
+  select(
+    cancer, `all n`, `all rho`, `all p`, `TP53wt n`, 
+    `TP53wt rho`, `TP53wt p`, `TP53mut n`, `TP53mut rho`, `TP53mut p`
+  )
+
+table
+
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
+# pdf(file = path, width = 14)
+# gridExtra::grid.table(table, rows = NULL)
+# invisible(dev.off())
 ```

### 2017-12-05 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
further work on figure visability, comments katja, comments #2 felix

--- 2017-12-03 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
@@
   ungroup() %>%
+  mutate(max = max + c(0, 0.4, 0, 0)) %>%
   pFormat(.) %>%
@@
     stackdir='center',
-    dotsize = 2,
+    dotsize = 3,
     show.legend = TRUE
@@
     shape = 95,
-    colour = "gray20"
+    size = 4,
+    colour = "grey30"
   ) +
@@
     ),
-    colour = "gray20",
-    size = 0.1,
+    colour = "grey30",
+    size = 0.3,
     position = position_dodge(width = 0.9),
@@
       x = labelX,
-      y = max + 0.3,
+      y = max + 0.5,
       label = pFormat,
@@
     fill = "white",
-    size = 1.5,
+    colour = "grey30",
+    size = 2.5,
     family = "Arial Unicode MS",
@@
     ),
-    colour="grey43",
-    size = 0.1,
+    colour="grey30",
+    size = 0.3,
     show.legend = FALSE
@@
       title = "Gene", 
-      override.aes = list(size = 4)
+      override.aes = list(size = 4),
+      ncol = 1
   ))
@@
 #    height = 60,
-#    width = 83,
+#    width = 53,
 #    units = "mm"

### 2017-12-05 inst/hct116_p53_null/hct116_p53_null.Rmd
further work on figure visability, comments katja, comments #2 felix

--- 2017-12-03 inst/hct116_p53_null/hct116_p53_null.Rmd
@@
     position = position_dodge(width = 0.9),
-    colour = "gray20",
-    shape = 95
+    colour = "grey30",
+    shape = 95,
+    size = 4
   ) +
@@
     aes(x = Treatment, ymin = CI95l, ymax = CI95h, group = Condition),
-    colour = "gray20",
+    colour = "grey30",
     position = position_dodge(width = 0.9),
-    size = 0.1,
+    size = 0.3,
     show.legend = FALSE
@@
     data = stats,
-    aes(x = Treatment, y = max + 0.28, label = pFormat),
+    aes(
+      x = Treatment, 
+      y = max + 0.4, 
+      label = pFormat
+    ),
     label.size = 0,
@@
     aes(x = x, y = max + 0.1, xend = xend, yend = max + 0.1),
-    colour="grey43",
-    size = 0.1,
+    colour="grey30",
+    size = 0.3,
     show.legend = FALSE
@@
 #   height = 60,
-#  width = 83,
+#   width = 115,
 #   units = "mm"

### 2017-12-05 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
   left_join(ys) %>%
-  mutate(max = max + c(0.25, 1, 0.25, 1))
+  mutate(max = max + c(0.25, 1.2, 0.25, 1.2))
 
@@
     stackdir = 'center',
-    dotsize = 2,
+    dotsize = 3,
     show.legend = TRUE
@@
     ),
-    colour = "grey20",
+    colour = "grey30",
     size = 0.3,
@@
     show.legend = FALSE,
-    colour = "gray20",
+    colour = "grey30",
     size = 4,
@@
       x = 1.5, 
-      y = max + 0.35, 
+      y = max + 0.4, 
       label = pFormat, 
@@
     fill = "white",
-    size = 2,
+    colour = "grey30",
+    size = 2.5,
     family = "Arial Unicode MS",
@@
     ),
-    colour = "grey43",
+    colour = "grey30",
     size = 0.3,
@@
 #    height = 60,
-#    width = 83,
+#    width = 68,
 #    units = "mm"

### 2017-12-05 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
   mutate(
-    height = if_else(treatment == 0, 0, max(CI95h, na.rm = TRUE)),
+    height = if_else(treatment == 0, 0.15, max(CI95h, na.rm = TRUE)),
     x = case_when(
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
-
-# p <- ggplot(data = NULL) +
-#   geom_violin(
-#     data = data,
-#     aes(
-#       x = treatment, 
-#       y = log2fold, 
-#       group = interaction(plotGOI, treatment)
-#     ),
-#     trim = TRUE,
-#     scale = "width",
-#     alpha = 0.3,
-#     colour = NA,
-#     fill = "gray",
-#     show.legend = FALSE
-#   ) +
-#   geom_dotplot(
-#     data = data, 
-#     aes(
-#       x = treatment,
-#       y = log2fold,
-#       fill = plotGOI
-#     ),
-#     binwidth = 1/10,
-#     #alpha = 0.5,
-#     colour = NA,
-#     position = position_dodge(width = 0.9), 
-#     binaxis = 'y', 
-#     stackdir = 'center',
-#     dotsize = 2,
-#     show.legend = TRUE
-#   ) +
-#   facet_grid(. ~ shRNA, scale = "free") +
-#   scale_y_continuous("\u0394\u0394Ct") +
-#   labs(
-#     x = "Doxorubicin (ng/ml)",
-#     title = "HCT116"
-#   )
-
-# markdown <- p + 
-#   geom_linerange(
-#     data = stats,
-#     aes(
-#       x = treatment, 
-#       ymin = CI95l, 
-#       ymax = CI95h, 
-#       group = plotGOI
-#     ),
-#     colour = "gray20",
-#     position = position_dodge(width = 0.9),
-#     show.legend = FALSE
-#   ) +
-#   geom_point(
-#     data = stats,
-#     aes(
-#       x = treatment, 
-#       y = mean, 
-#       group = plotGOI
-#     ),
-#     colour = "gray20",
-#     position = position_dodge(width = 0.9),
-#     shape = 95,
-#     size = 6,
-#     show.legend = FALSE
-#   ) +
-#   geom_label(
-#     data = stats,
-#     aes(
-#       x = treatment, 
-#       y = CI95h + 0.2,
-#       label = pFormat,
-#       group = plotGOI
-#     ),
-#     label.size = 0,
-#     label.padding = unit(0.01, "lines"),
-#     show.legend = FALSE,
-#     position = position_dodge(width = 0.9),
-#     fill = "white",
-#     size = 5,
-#     family = "Arial Unicode MS"
-#   ) +
-#   guides(
-#     fill = guide_legend(
-#       title = "Gene", 
-#       override.aes = list(size = 6)
-#     )
-#   )
 
@@
     ),
-    colour = "gray20",
+    colour = "grey30",
     position = position_dodge(width = 0.9),
@@
       x = treatment, 
-      y = height + 0.5,
+      y = height + 0.6,
       label = pFormat
@@
     fill = "white",
-    size = 2,
+    colour = "grey30",
+    size = 2.5,
     family = "Arial Unicode MS"
@@
     aes(x = x, y = height + 0.25, xend = xend, yend = height + 0.25),
-    colour="grey43",
+    colour="grey30",
     size = 0.3,
@@
 #    height = 60,
-#    width = 83,
+#    width = 100,
 #    units = "mm"

### 2017-12-05 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
     ),
-    colour = "gray20",
+    colour = "grey30",
     size = 0.3
@@
     ),
-    colour = "gray20",
+    colour = "grey30",
     shape = 95,
@@
     ),
-    colour = "grey43",
+    colour = "grey30",
     size = 0.3

### 2017-12-05 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
     ),
-    colour="gray20",
+    colour="gray30",
     shape = 95,
@@
     ),
-    colour="grey43",
+    colour="gray30",
     size = 0.3
@@
     fill = "white",
-    size = 2,
+    colour = "gray30",
+    size = 2.5,
     family = "Arial Unicode MS"
@@
     ),
-    colour="gray20",
+    colour="gray30",
     size = 0.3

### 2017-12-05 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
     position = position_dodge(width = 0.9),
-    colour = "grey25",
+    colour = "grey30",
     size = 0.3,
@@
     ), 
-    colour = "black",
+    colour = "grey30",
     position = position_dodge(width = 0.9),
@@
       x = x,
-      y = y + 0.01, 
+      y = y + 0.02, 
       xend = xend, 
-      yend = y + 0.01
+      yend = y + 0.02
     ),
-    colour = "grey43",
+    colour = "grey30",
     size = 0.3,
@@
       x = phase, 
-      y = y + 0.025, 
+      y = y + 0.038, 
       label = pFormat
     ),
+    colour = "grey30",
     label.size = 0,
@@
     fill = "white",
-    size = 2,
+    size = 2.5,
     family = "Arial Unicode MS"
@@
 #    height = 60,
-#    width = 83,
+#    width = 93,
 #    units = "mm"

### 2017-12-05 inst/stable_line_expression/stable_line_expression.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
   mutate(
-    max = max + c(0.75, 2.65, 0.45, 2.35, 0.45, 2.35)
+    max = max + c(0.95, 3.35, 0.65, 3.15, 0.65, 3.15)
   )
@@
     position = position_dodge(width = 0.9),
-    colour = "gray20",
+    colour = "grey30",
     size = 0.3,
@@
       x = 1.5, 
-      y = max + 0.85, 
+      y = max + 1, 
       label = pFormat, 
@@
     fill = "white",
+    colour = "grey30",
     label.size = 0,
@@
     family = "Arial Unicode MS",
-    size = 2
+    size = 2.5
   ) +

### 2017-12-05 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
     ),
-    colour = "grey20",
+    colour = "gray30",
     show.legend = FALSE,
@@
     ),
-    colour = "gray20",
+    colour = "gray30",
     size = 0.3,

### 2017-12-05 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
further work on figure visability, comments katja, comments #2 felix

@@
     aes(x = condition, ymin = CI95l, ymax = CI95h),
-    colour = "gray20",
+    colour = "grey30",
     size = 0.3,
@@
     aes(x = condition, y = mean),
-    colour = "gray20",
+    colour = "grey30",
     shape = 95,
@@
     aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
-    colour = "grey43",
+    colour = "grey30",
     size = 0.3

### 2017-12-06 inst/primers/primers.Rmd
adding primer document

@@
 ---
-title: "Primers used in the miR34a asRNA study"
+title: "Primers"
+author: "Jason T. Serviss"
+date: "`r Sys.Date()`"
 output:
-  pdf_document:
   html_document:
     theme: flatly
-    toc: no
     code_folding: hide
+    keep_md: true
+vignette: >
+  %\VignetteIndexEntry{Vignette Title}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
 ---
 
-```{r global_options, include = FALSE}
-knitr::opts_chunk$set(message=FALSE, 
-tidy.opts=list(width.cutoff=60))
-library(pander)
+```{r, echo = FALSE, message = FALSE}
+
+library(printr)
+library(tibble)
+
 ```
 
-```{r, echo=FALSE}
-d1 <- data.frame(
-    name="miR155_asF",
-    sequence="AAG CTG GTC CAG\nGGC CAT TAT ACA",
-    figures="Supplementary Fig. 1A"
+## Figure 1b
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34a asRNA F1",
+        "miR34a asRNA R1",
+        "miR34a HG F",
+        "miR34a HG R",
+        "ß-actin Fwd",
+        "ß-actin Rev"
+    ),
+    sequence=c(
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
+    )
 )
 
-d2 <- data.frame(
-    name="miR155_asR",
-    sequence="TGA CCT CAT GAT CCA GTC ACC TCA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 1d
+
+```{r}
+
+tibble(
+  name = c(
+    "miR34a asRNA F10",
+    "polyT T7 FAM",
+    "miR34a asRNA F1",
+    "FAM primer"),
+  sequence = c(
+    "ACG CGT CTC TCC AGC CCG GGA T",
+    "CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
+    "AGC GGC ATC TCC TCC ACC TGA AA",
+    "CCG TAG CTC GTC CAG GAC CC"
+  )
 )
 
-d3 <- data.frame(
-    name="miR301a_asF2",
-    sequence="CAA CGG CAG AAG CTT CAC CAC AAA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 2a
+
+```{r}
+
+tibble(
+    name=c(
+        "ß-actin Fwd",
+        "ß-actin Rev",
+        "miR34a HG F",
+        "miR34a HG R",
+        "miR34a AS F1",
+        "miR34a AS R1"
+
+    ),
+    sequence=c(
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TCG GGA TGT CCA CGT CA",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT"
+
+    )
 )
 
-d4 <- data.frame(
-    name="miR301a_asR2",
-    sequence="CGC TGC TGG ATT CGT TTG GCA TAA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 2b
+
+```{r}
+
+tibble(
+    name=c(
+        "ß-actin Fwd",
+        "ß-actin Rev",
+        "miR34a HG F",
+        "miR34a HG R",
+        "miR34a as F1",
+        "miR34a as R1"
+
+    ),
+    sequence=c(
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TCG GGA TGT CCA CGT CA",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT"
+
+    )
 )
 
-d5 <- data.frame(
-    name="miR34bc_asF2",
-    sequence="ACA GAA GTC ACT GGC ACT CTG A",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 2c
+
+```{r}
+
+tibble(
+    name=c(
+        "Luc setII F",
+        "Luc setII R",
+        "Renilla pBiDir F1",
+        "Renilla pBiDir R1",
+        "ß-actin Fwd",
+        "ß-actin Rev"
+    ),
+    sequence=c(
+        "AAG ATT CAA AGT GCG CTG CTG",
+        "TTG CCT GAT ACC TGG CAG ATG",
+        "TAA CGC GGC CTC TTC TTA TTT",
+        "GAT TTG CCT GAT TTG CCC ATA",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
+    )
 )
 
-d6 <- data.frame(
-    name="miR34bc_asR2",
-    sequence="ACC CAT ATG GTC ATC TCC TTC GGA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 2d
+
+```{r}
+
+tibble(
+    name=c(
+        "Luc set II F",
+        "Luc set II R",
+        "Renilla pBiDir F1",
+        "Renilla pBiDir R1",
+        "ß-actin Fwd",
+        "ß-actin Rev"
+    ),
+    sequence=c(
+        "AAG ATT CAA AGT GCG CTG CTG",
+        "TTG CCT GAT ACC TGG CAG ATG",
+        "TAA CGC GGC CTC TTC TTA TTT",
+        "GAT TTG CCT GAT TTG CCC ATA",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
+    )
 )
 
-d7 <- data.frame(
-    name="miR21_asF",
-    sequence="AGT CTT ACC TGT GGT GTG CCC ATT",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 3a
+
+Cloning primers
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34aAS cloning F4",
+        "miR34aAS cloning Ex3_1"
+    ),
+    sequence=c(
+        "ACG CGT CTC TCC AGC CCG GGA T",
+        "AAT GAT GGC CGC AAC TAA TGA CGG"
+    )
 )
 
-d8 <- data.frame(
-    name="miR21_asR",
-    sequence="AGG TCC ATC TCT GCA GAA GCC ATT",
-    figures="Supplementary Fig. 1A"
+```
+
+QPCR primers
+
+```{r}
+
+tibble(
+    name=c(
+        "ß-actin Fwd",
+        "ß-actin Rev",
+        "miR34a AS F1",
+        "miR34a AS R1"
+
+    ),
+    sequence=c(
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TCG GGA TGT CCA CGT CA",
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT"
+
+    )
 )
 
-d9 <- data.frame(
-    name="miR29b_asF",
-    sequence="TGT AAT AAG AAG GGC GGT GCT CGT",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 3d
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34a ChIP F1",
+        "miR34a ChIP R1"
+    ),
+    sequence=c(
+       "AAA GTT TGC AAA GAA GGA GGC GGG",
+       "AGG GAA GAA AGA ACT AGC CGA GCA"
+    )
 )
 
-d10 <- data.frame(
-    name="miR29b_asR",
-    sequence="AAC CTG TCT TTG TCG CAG GTC TCA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 1 Supplement 2a
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34a AS F10",
+        "miR34a AS F11",
+        "miR34a AS F12",
+        "miR34a AS F13",
+        "miR34a AS F14",
+        "miR34a AS F15",
+        "miR34a AS R1"
+    ),
+    sequence=c(
+        "ACG CGT CTC TCC AGC CCG GGA T",
+        "ATC TGC GTG GTC ACC GAG AAG CA",
+        "CGC ACG GAC TGA GAA ACA CAA G",
+        "ACG GAG GCT ACA CAA TTG AAC AGG",
+        "AGG GAA GAA AGA ACT AGC CGA GCA",
+        "CAT TTG CTG CAA TAT CAC CGT GGC",
+        "TTG CCT CGT GAG TCC AAG GAG AAT"
+    )
 )
 
-d11 <- data.frame(
-    name="miR142_asRNA_F",
-    sequence="TTG ATC GTC ATG CTG ACC CAG TGA",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 1 Supplement 2b
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34a AS F1",
+        "miR34a AS R1",
+        "miR34a AS int1 R1",
+        "miR34a HG F",
+        "miR34a HG R",
+        "ß-actin Fwd",
+        "ß-actin Rev",
+        "U48 F",
+        "U48 R"
+    ),
+    sequence=c(
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "TGC GCA AAC TAC GCG CTC T",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA",
+        "AGT GAT GAT GAC CCC AGG TA",
+        "GGT CAG AGC GCT GCG GTG AT"
+    )
 )
 
-d12 <- data.frame(
-    name="miR142_asRNA_R",
-    sequence="GGG CGG TCT TAC ATG CCT TTG AAT",
-    figures="Supplementary Fig. 1A"
+```
+
+## Figure 1 Supplement 2c
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34a AS F12",
+        "miR34a AS R1",
+        "miR34a AS R2",
+        "miR34a AS R3",
+        "miR34a AS Ex3 R1"
+    ),
+    sequence=c(
+        "AAA CAC AAG CGT TTA CCT GGG TGC",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "ATA GGT TCA TTT GCC CGA TGT GCC",
+        "CCA CAG CTG TTG CTT CTG AAT GCT",
+        "TGA TGG CCG CAA CTA ATG ACG GAT"
+    )
 )
 
-d13 <- data.frame(
-    name="miR34a_asF10",
-    sequence="ACG CGT CTC TCC AGC CCG GGA T",
-    figures="Fig. 1C, Fig. 1E"
+```
+
+## Figure 2 Supplement 2a
+
+```{r}
+
+ tibble(
+    name=c(
+        "Luc setII F",
+        "Luc setII R",
+        "Renilla pBiDir F1",
+        "Renilla pBiDir R1",
+        "ß-actin Fwd",
+        "ß-actin Rev"
+    ),
+    sequence=c(
+        "AAG ATT CAA AGT GCG CTG CTG",
+        "TTG CCT GAT ACC TGG CAG ATG",
+        "TAA CGC GGC CTC TTC TTA TTT",
+        "GAT TTG CCT GAT TTG CCC ATA",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
+    )
 )
 
-d14 <- data.frame(
-    name="miR34a_asF11",
-    sequence="ATC TGC GTG GTC ACC GAG AAG CA",
-    figures="Fig. 1E"
+```
+
+## Figure 3 Supplement 1a
+
+Cloning primers
+
+```{r}
+
+tibble(
+    name=c(
+        "miR34aAS cloning F4",
+        "miR34aAS cloning Ex3_1"
+    ),
+    sequence=c(
+        "ACG CGT CTC TCC AGC CCG GGA T",
+        "AAT GAT GGC CGC AAC TAA TGA CGG"
+    )
 )
 
-d15 <- data.frame(
-    name="miR34a_asF12",
-    sequence="AAA CAC AAG CGT TTA CCT GGG TGC",
-    figures="Fig. 1E, Supplementary Fig. 1C"
+```
+
+QPCR primers
+
+```{r}
+
+tibble(
+    name=c(
+        "ß-actin Fwd",
+        "ß-actin Rev",
+        "miR34a AS F1",
+        "miR34a AS R1"
+
+    ),
+    sequence=c(
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TCG GGA TGT CCA CGT CA",
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT"
+
+    )
+)
+```
+
+## Figure 3 Supplement 2a
+
+```{r}
+
+tibble(
+    name=c(
+        "CCND1 Fwd",	
+        "CCND1 Rev",
+        "ß-actin Fwd",
+        "ß-actin Rev"
+    ),
+    sequence=c(
+        "CGT GGC CTC TAA GAT GAA GG",
+        "CTG GCA TTT TGG AGA GGA AG",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
+    )
 )
 
-d16 <- data.frame(
-    name="miR34a_asF13",
-    sequence="ACG GAG GCT ACA CAA TTG AAC AGG",
-    figures="Fig. 1E"
-)
-
-d17 <- data.frame(
-    name="miR34a_asF14",
-    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
-    figures="Fig. 1E"
-)
-
-d18 <- data.frame(
-    name="miR34a_asF15",
-    sequence="CAT TTG CTG CAA TAT CAC CGT GGC",
-    figures="Fig. 1E"
-)
-
-d19 <- data.frame(
-    name="miR34a_as_int1R1",
-    sequence="TGC GCA AAC TAC GCG CTC T",
-    figures="Fig. 1F"
-)
-
-d20 <- data.frame(
-    name="miR34a_asR2",
-    sequence="ATA GGT TCA TTT GCC CGA TGT GCC",
-    figures="Supplementary Fig. 1C"
-)
-
-d21 <- data.frame(
-    name="miR34a_asR3",
-    sequence="CCA CAG CTG TTG CTT CTG AAT GCT",
-    figures="Supplementary Fig. 1C"
-)
-
-d22 <- data.frame(
-    name="miR34a_asEx3_R1",
-    sequence="GTT GCC TTC TTC GCA ACT CCT TGT",
-    figures="Supplementary Fig. 1C"
-)
-
-d23 <- data.frame(
-    name="miR34a_asF1",
-    sequence="AGC GGC ATC TCC TCC ACC TGA AA",
-    figures="Fig. 1B, Fig. 1C, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1E"
-)
-
-d24 <- data.frame(
-    name="miR34a_asR1",
-    sequence="TTG CCT CGT GAG TCC AAG GAG AAT",
-    figures="Fig. 1B, Fig. 1E, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1C, Supplementary Fig. 1E"
-)
-
-d25 <- data.frame(
-    name="miR34a_HG_F",
-    sequence="TCT GCT CCA GTG GCT GAT GAG AAA",
-    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
-)
-
-d26 <- data.frame(
-    name="miR34a_HG_R",
-    sequence="GTT CAC TGG CCT CAA AGT TGG CAT",
-    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
-)
-
-d27 <- data.frame(
-    name="miR34a_mature_F",
-    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
-    figures="Fig. 3B"
-)
-
-d28 <- data.frame(
-    name="miR34a_mature_R",
-    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
-    figures="Fig. 3B"
-)
-
-d29 <- data.frame(
-    name="B-actin_F",
-    sequence="AGG TCA TCA CCA TTG GCA ATG AG",
-    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
-)
-
-d30 <- data.frame(
-    name="B-actin_R",
-    sequence="CTT TGC GGA TGT CCA CGT CA",
-    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
-)
-
-d31 <- data.frame(
-    name="T7_long_reverse",
-    sequence="CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
-    figures="Fig. 1C"
-)
-
-d32 <- data.frame(
-    name="FAM_primer",
-    sequence="CCG TAG CTC GTC CAG GAC CC",
-    figures="Fig. 1C"
-)
-
-d33 <- data.frame(
-    name="U48_F (sybr)",
-    sequence="AGT GAT GAT GAC CCC AGG TA",
-    figures="Fig. 1F, Fig. 1G"
-)
-
-d34 <- data.frame(
-    name="U48_R (sybr)",
-    sequence="GGT CAG AGC GCT GCG GTG AT",
-    figures="Fig. 1F, Fig. 1G"
-)
-
-d35 <- data.frame(
-    name="U48_F (taqman)",
-    sequence="Control miRNA Assay, RNU48, human",
-    figures="Fig. 3B"
-)
-
-d36 <- data.frame(
-    name="U48_R (taqman)",
-    sequence="Control miRNA Assay, RNU48, human",
-    figures="Fig. 3B"
-)
-
-d37 <- data.frame(
-    name="Renilla_pBiDir_F1",
-    sequence="TAA CGC GGC CTC TTC TTA TTT",
-    figures="Fig. 3A"
-)
-
-d38 <- data.frame(
-    name="Renilla_pBiDir_R1",
-    sequence="GAT TTG CCT GAT TTG CCC ATA",
-    figures="Fig. 3A"
-)
-
-d39 <- data.frame(
-    name="Luc_set_II_F",
-    sequence="AAG ATT CAA AGT GCG CTG CTG",
-    figures="Fig. 3A"
-)
-
-d40 <- data.frame(
-    name="Luc_set_II_R",
-    sequence="TTG CCT GAT ACC TGG CAG ATG",
-    figures="Fig. 3A"
-)
-
-d41 <- data.frame(
-    name="CCND1 Fwd",
-    sequence="CGT GGC CTC TAA GAT GAA GG",
-    figures="Fig. 3D"
-)
-
-d42 <- data.frame(
-    name="CCND1 Rev",
-    sequence="CTG GCA TTT TGG AGA GGA AG",
-    figures="Fig. 3D"
-)
-
-d43 <- data.frame(
-    name="miR34a ChIP_F1",
-    sequence="AAA GTT TGC AAA GAA GGA GGC GGG",
-    figures="Fig. 3F"
-)
-
-d44 <- data.frame(
-    name="miR34aChIP_R1",
-    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
-    figures="Fig. 3F"
-)
-
-primers <- rbind(
-    d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18, d19, d20,
-    d21, d22, d23, d24, d25, d26, d27, d28, d29, d30, d31, d32, d33, d34, d35, d36, d37, d38, d39, d40,
-    d41, d42, d43, d44
-)
-
-primers$primerType <- c(
-    rep("Other asRNA", 12),
-    rep("miR34a asRNA", 12),
-    rep("miR34a HG", 2),
-    rep("miR34a mature", 2),
-    rep("Other primers", 14),
-    rep("miR34a asRNA", 2)
-)
-primers <- primers[order(as.character(primers$primerType)),]
-
-primers$primerType <- c(
-    "miR34a asRNA", rep("", 13),
-    "miR34a HG", "",
-    "miR34a mature", "",
-    "Other asRNA", rep("", 11),
-    "Other primers", rep("", 13)
-)
-
-colnames(primers) <- c("Name", "Sequence", "Figure", "Primer type")
-rownames(primers) <- 1:nrow(primers)
-primers <- primers[,c("Primer type", "Name", "Sequence", "Figure")]
 ```
 
-```{r, results='asis', echo=FALSE}
-panderOptions('table.split.table', Inf)
-pandoc.table(primers, keep.line.breaks = TRUE)
+```{r}
+
 ```

### 2017-12-06 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
added linear model for growth exp.

@@
     "grid",
-    "gtable"
+    "gtable",
+    "broom"
 )
@@
 
-#unreported p-values per time point
-p <- data %>% 
-  filter(Time != 0) %>% 
-  unite(tmp, `Biological Replicate`, `Cell line`) %>% 
-  spread(tmp, techMean) %>% 
-  group_by(Treatment, Time) %>% 
-  summarize(
-	  p = t.test(
-	    c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`), 
-	    c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`)
-	  )$p.value,
-	  meanAS = mean(c(`1_PC3 miR34a asRNA`, `2_PC3 miR34a asRNA`, `3_PC3 miR34a asRNA`)),
-	  meanMock = mean(c(`1_PC3 Mock`, `2_PC3 Mock`, `3_PC3 Mock`))
-  ) %>%
-  mutate(fold = meanAS / meanMock)
+#linear model
+model.data <-  data %>%
+  mutate(Time = as.numeric(Time)) %>%
+  group_by(Treatment) %>%
+  mutate(rank = rank(techMean)) %>%
+  do(glance(lm(rank ~ Time +`Cell line`, data = .))) %>%
+  ungroup() %>%
+  rename(pValue = p.value) %>%
+  pFormat(.) %>%
+  select(-pValue) %>%
+  rename(p.value = pFormat)
+
+as.data.frame(model.data)
+
+growth.lm <- data %>%
+  mutate(Time = as.numeric(Time)) %>%
+  group_by(Treatment) %>%
+  mutate(rank = rank(techMean)) %>%
+  do(tidy(lm(rank ~ Time +`Cell line`, data = .))) %>%
+  ungroup() %>%
+  rename(pValue = p.value) %>%
+  pFormat(.) %>%
+  select(-pValue) %>%
+  rename(p.value = pFormat)
+
+as.data.frame(growth.lm)
+
 ```

### 2017-12-06 inst/lnc34a/lnc34a.Rmd
manuscript polishing and adding final lnc34a document

---
title: "lnc34a analysis"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}
packages <- c(
    "tidyverse",
    "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

library(miR34AasRNAproject)
```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

An unannotated transcript, Lnc34a, arising from the antisense orientation of the miR34a locus and with a transcription start site >250 bp upstream of the annotated miR34a asRNAs start site, has been previously reported in a study examining colorectal cancer (Wang et al. 2016). Among the findings in Wang et al. the authors discover that Lnc34a negatively regulates miR34a expression via recruitment of DNMT3a, PHB2, and HDAC1 to the miR34a promoter. Although the Lnc34a and miR34a asRNA transcripts share some sequence similarity, we believe them to be separate RNAs transcripts. Furthermore, Lnc34a may be highly context dependent and potentially only expressed at biologically significant levels in colon cancer stem cells, or other stem-like cells, in agreement with the conclusions drawn in the paper.

Several lines of evidence point to the fact that miR34a asRNA and lnc34a are not the same transcript and, in addition, that lnc34a expression may be confined to a highly specific subset of colorectal cancer stem cells. First, we were unable to detect transcription upstream of the 5' start site that was defined in the primer walk assay (**Fig. 1E** and **Supplementary Fig. 1B**) although the reported lnc34a start site is >250 base pairs upstream of the F12 primer used in this assay. This could simply be due to the fact that lnc34a is not expressed in HEK293t cells in which the assay was performed. To further investigate the existence of transcription start sites in the antisense orientation of the miR34a locus, we interrogated CAGE data from 28 cell lines.

```{r, out.height = "100px", dpi = 500}

url <- fileMap(type = "png")["suppFigure4a"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

```

<div class="caption">
All available CAGE data from the ENCODE project for 36 cell lines was downloaded from the UCSC genome browser for genome version hg19. Of these, 28 cell lines had CAGE transcription start sites mapping to the plus strand of chromosome 1 and in regions corresponding to 200 base pairs upstream of the lnc34a start site (9241796 - 200) and 200 base pairs upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200). These cell lines included: HFDPC, H1-hESC, HMEpC, HAoEC, HPIEpC, HSaVEC, GM12878, hMSC-BM, HUVEC, AG04450, hMSC-UC, IMR90, NHDF, SK-N-SH_RA, BJ, HOB, HPC-PL, HAoAF, NHEK, HVMF, HWP, MCF-7, HepG2, hMSC-AT, NHEM.f_M2, SkMC, NHEM_M2, and HCH. In total 74 samples were included. 17 samples were polyA-, 47 samples were polyA+, and 10 samples were total RNA. In addition, 34 samples were whole cell, 15 enriched for the cytosolic fraction, 15 enriched for the nucleolus, and 15 enriched for the nucleus. All CAGE reads were plotted and the RPKM of the individual reads was used to colour each read to indicate their relative abundance (top panel). In addition, a density plot (middle panel) shows the distribution of the CAGE reads in the specified interval and the transcription start regions for lnc34a and miR34a asRNA as well as primer positions from the primer walk assay (bottom panel).
</div>

The results show a high density of CAGE tags aligning to the region corresponding to the annotated miR34a asRNA start site. Several additional peaks, albeit with a much lower average expression, aligns slightly upstream of the annotated miR34a asRNA start site, one of which, corresponds to the upstream start site detected in our primer walk analysis (**Figure 1e**). Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript. This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors. An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected. Finally, lnc34a may not be 5'-capped precluding its detection by CAGE.

In order to lnc34a expression in a manner that is not dependant on 5'-capping, we proceeded to examine spliced RNA sequencing reads from 36 cell lines, taking advantage of the fact that lnc34a has an exon which is not present in any miR34a asRNA isoforms.

```{r, fig.align='center', fig.height=8, fig.width=12}

url <- fileMap(type = "png")["suppFigure4b"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

```

<div class="caption">
All available whole cell (i.e. non-fractionated) spliced read data originating from the Cold Spring Harbor Lab in the ENCODE  project for 38 cell lines was downloaded from the UCSC genome browser. Of these cell lines, 36 had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region). Splice junctions from the following cell lines were included in the final figure: A549, Ag04450, Bj, CD20, CD34 mobilized, Gm12878, H1hesc, Haoaf, Haoec, Hch, Helas3, Hepg2, Hfdpc, Hmec, Hmepc, Hmscat, Hmscbm, Hmscuc, Hob, Hpcpl, Hpiepc, Hsavec, Hsmm, Huvec, Hvmf, Hwp, Imr90, Mcf7, Monocd14, Nhdf, Nhek, Nhemfm2, Nhemm2, Nhlf, Skmc, and Sknsh. All splice junctions were included in the figure and coloured according to the number of reads corresponding to each (top panel). In cases where the exact same read was detected multiple times the read count was summed and represented as one read in the figure. miR34a asRNA and lnc34a transcripts are represented for reference (bottom panel).
</div>

These results indicate that, although splice junctions corresponding to multiple isoforms detected by PCR cloning of the miR34a asRNA were detected, the data give no support for the presence of the splice junction between the first and second exon of lnc34a. In summary, these results indicate that lnc34a expression may be confined to colon cancer stem cells as evidence for its expression in the examined cell lines is not forthcomming.

In addition, we note several comments in the public review that was published in conjunction with the work by Wang et al. The authors mention, and provide data, indicating that lnc34a expression is not changed upon ectopic expression of TP53. In contrast, miR34a asRNA is strongly regulated by TP53 as the evidence shows in this and others (Léveillé 2015, Rashi-Elkeles 2014, Hünten 2015, Ashouri 2016, Kim 2017) findings.

Furthermore, Wang et al. also mention in the public review that lnc34a has a low expression level in HCT116 cells although we detect robust expression of miR34a asRNA in this cell type (**Figure 1b**).

In summary, these results indicate that lnc34a expression is not present in the cell types examined where there exists strong evidence for the presence miR34a asRNA. For these reasons, we believe miR34a asRNA and lnc34a to be individual antisense RNA transcripts.

### 2017-12-09 inst/tcga_expression/tcga_expression.Rmd
work on supplement1b

---
title: "Figure 1c"
subtitle: "miR34a asRNA and miR34a TCGA correlation"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

#### _Introduction_
We interogated RNA sequencing data from TCGA to determine in miR34a and miR34a asRNA expression was correlated in both TP53 wild type and mutated samples.

<br></br>

#### _Methods_

<br></br>

#### _Results_
```{r}
url <- fileMap(type = "rds")["Figure 1c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

#normalize expression values
data <- mutate(
    data,
    RP3 = log2(RP3 / max(RP3)),
    miR34a = log2(miR34a / max(miR34a))  
  )

#add BRCA subtypes
data <- data %>%
  mutate(PAM50 = if_else(is.na(PAM50), "", PAM50)) %>%
  mutate(cancer_PAM50 = gsub("BRCA", "BRCA ", paste(cancer, PAM50, sep = "")))

#sort 
data <- arrange(data, cancer_PAM50, TP53, RP3)

#remove infinite data
data <- filter(data, !is.infinite(RP3) & !is.infinite(miR34a))

#diploid only
data <- filter(data, abs(RP3_cna) < 0.1)

##prepare for plotting
data <- data %>%
  mutate(TP53 = if_else(TP53 == 0, "TP53 wt", "TP53 mut")) %>%
  select(TCGA_cancer_id, TP53, cancer_PAM50, RP3, miR34a) %>%
  gather(gene, value, -(TCGA_cancer_id:cancer_PAM50)) %>%
  mutate(gene = if_else(gene == "RP3", "miR34a asRNA", "miR34a"))

#remove cancers that don't have at least 5 patients in both TP53 wt and mutated
data <- data %>%
  group_by(cancer_PAM50, TP53, gene) %>%
  filter(n() > 5) %>%
  group_by(cancer_PAM50, gene) %>%
  filter(length(unique(TP53)) == 2) %>%
  ungroup()

#calculate stats
stats <- data %>%
  group_by(cancer_PAM50, gene, TP53) %>%
  summarize(value = list(value)) %>%
  spread(TP53, value) %>%
  mutate(
    mean_wt = mean(unlist(`TP53 wt`)),
    mean_mut = mean(unlist(`TP53 mut`)),
    CI95l_wt = t.test(unlist(`TP53 wt`))$conf.int[1],
    CI95l_mut = t.test(unlist(`TP53 mut`))$conf.int[1],
    CI95h_wt = t.test(unlist(`TP53 wt`))$conf.int[2],
    CI95h_mut = t.test(unlist(`TP53 mut`))$conf.int[2],
    pValue = t.test(unlist(`TP53 wt`), unlist(`TP53 mut`))$p.value
  ) %>%
  ungroup() %>%
  gather(metric, value, -(cancer_PAM50:`TP53 wt`), -pValue) %>%
  separate(col = metric, into = c("metric", "TP53"), sep = "_") %>%
  spread(metric, value) %>%
  mutate(TP53 = if_else(TP53 == "wt", "TP53 wt", "TP53 mut")) %>%
  pFormat(.)

#add fake data where p53 mut is missing (will be hidden in plot) to keep empty space
data <- data %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = unique(cancer_PAM50)))

stats <- stats %>%
  mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
  mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = unique(cancer_PAM50)))
```

```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    )
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(legend.position = "top") +
  guides(colour = guide_legend(title = "TP53 status"))

#plot pdf
figure <- ggplot(data = NULL) + 
  geom_jitter(
    data = data,
    aes(
      x = cancer_PAM50,
      y = value,
      colour = TP53
    ),
    position = position_dodge(width = 0.75),
    alpha = 0.5,
    size = 1
  ) +
  geom_text(
    data = stats, 
    aes(
      x = cancer_PAM50, 
      y = 1, 
      label = pFormat
    ),
    size = 3.25
  ) +
  geom_point(
    data = stats,
    aes(
      x = cancer_PAM50,
      y = mean,
      group = TP53
    ),
    colour = "grey30",
    shape = 124,
    size = 4,
    lwd = 1,
    position = position_dodge(width = 0.75)
  ) +
  facet_wrap(~gene, ncol = 2) +
  coord_flip(ylim = c(-12, 2.05)) +
  labs(
    x = "Cancer",
    y = "Expression"
  ) +
  theme_few() +
  scale_colour_economist() +
  theme(
    plot.margin = unit(rep(0.1, 4), "lines"),
    legend.position = "top",
    legend.background = element_blank(),
    legend.box.spacing = unit(5, "pt"), #this controls the spacing between strip.text.x and the legend
    legend.margin = margin(rep(0, 4), unit = "pt"),
    legend.key.size = unit(1/5, "cm"),
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 7),
    axis.title = element_text(size = 9),
    axis.title.x = element_text(margin = margin(t = 5)),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10),
    axis.ticks = element_line(size = 0.25),
    axis.ticks.length = unit(1/15, "cm"),
    panel.border = element_rect(fill = NA, size = 0.15)
  ) +
  guides(colour = guide_legend(title = "TP53 status", override.aes = list(size = 3, alpha = 1)))

##save to pdf
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1b"][[1]])
ggsave(
   plot = figure,
   filename = path,
   device = cairo_pdf,
   height = 135,
   width = 205,
   units = "mm"
)
```

<div class="caption">
A graphical depiction of the TCGA expression analysis. Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
</div>

<br></br>

#### _Conclusions_
miR34a asRNA and miR34a tend to be highly correlated in the cancer types examined in both TP53 wild type and mutated samples. In addition, the results indicate that both miR34a asRNA and miR34a expression levels are decreased in the presence of TP53 mutations.

<br></br><br></br>

```{r}
sessionInfo()
```

### 2017-12-09 R/utils.R

@@ -21,35 +21,36 @@ NULL
 
 fileMap <- function(type) {
   pList <- list(
-    figure1a = "mir34a_locus/mir34a_locus.Rmd",
-    figure1b = "mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd",
-    figure1c = "tcga_correlation/tcga_correlation.Rmd",
-    figure1d = "3_prime_race/3_prime_race.Rmd",
-    figure1e = "primer_walk/primer_walk.Rmd",
-    figure1f = "coding_potential_cpat/coding_potential_cpat.Rmd",
-    figure2b = "hct116_p53_null/hct116_p53_null.Rmd",
-    figure2a = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
-    figure2c = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
-    figure2d = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
-    figure3a = "stable_line_expression/stable_line_expression.Rmd",
-    figure3b = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
-    figure3c = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
-    figure3d = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
-    figure3e = "tcga_survival/tcga_survival.Rmd",
-    suppFigure1a = "tcga_correlation_table/tcga_correlation_table.Rmd",
-    suppFigure1b = "primer_walk_schematic/primer_walk_schematic.Rmd",
-    suppFigure1c = "polyadenylation/polyadenylation.Rmd",
-    suppFigure1d = "isoforms/isoforms.Rmd",
-    suppFigure1e = "cellular_localization_encode/cellular_localization_encode.Rmd",
-    suppFigure1f = "transcript_stability/transcript_stability.Rmd",
-    suppFigure1g = "coding_potential_cpc/coding_potential_cpc.Rmd",
-    suppFigure2a = "p1_construct/p1_construct.Rmd",
-    suppFigure2b = "p1_hek293t/p1_hek293t.Rmd",
-    suppFigure3a = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
[…]

### 2017-12-09 inst/SurvivalTCGA/processTCGA.R

@@ -1,179 +1,0 @@
-
-
-#call tcga download function 
-exp <- tcga[[1]]
-cols <- tcga[[2]]
-rows <- tcga[[3]]
-
-#calculate size factors
-sf <- lapply(exp, function(x) colSums(x))
-
-##subset AS: ENSG00000234546, HG: ENSG00000228526 and calculate cpm
-.norm.log.counts <- function(counts) {
-  norm.fact <- colSums(counts)
-  counts.norm <- t(apply(counts, 1, .norm, n = norm.fact))
-  counts.log <- log2(counts.norm)
-}
-
-.norm <- function(x, n) {
-  x / n * 1000000 + 1
-}
-
-sub <- lapply(exp, function(x)
-  x[rownames(x) %in% c("ENSG00000234546", "ENSG00000228526"), ]
-)
-
-cpm <- lapply(sub, .norm.log.counts)
-cpmTibble <- lapply(cpm, function(x)
-  tibble(
-    sample = colnames(x),
-    ENSG00000234546 = x[rownames(x) == "ENSG00000234546", ],
-    ENSG00000228526 = x[rownames(x) == "ENSG00000228526", ]
-  )
-)
-
-asDF <- bind_rows(cpmTibble)
-
-#find patients with the days_to_death variable present
-dtd <- lapply(cols, function(x)
-  tibble(
-    sample = rownames(x),
-    days_to_death = as.numeric(x[, colnames(x) == "days_to_death"]),
-    disease_type = as.character(x[, colnames(x) == "project_id"]),
-    patient = as.character(x[, colnames(x) == "patient"]),
-    days_to_last_follow_up = as.numeric(x[, colnames(x) == "days_to_last_follow_up"]),
-    vital_status = as.character(x[, colnames(x) == "vital_status"])
-  )
-)
-
-dtd <- bind_rows(dtd) %>%
-  mutate(
-    OS_time_to_event = case_when(
-      vital_status == "alive" ~ days_to_last_follow_up,
-      vital_status == "dead" ~ days_to_death
-  ))
-
-#add p53 mut status
-p53in <- rjson::fromJSON(file = "~/Github/miR34a_asRNA_project/inst/SurvivalTCGA/files.2017-11-13T13_37_07.279347_p53mut.json" )
-fileName <- sapply(p53in, `[[`, 1)
-p53mutSamp <- gsub(
[…]

### 2017-12-09 inst/cellular_localization_encode/cellular_localization_encode.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "miR34a asRNA cellular localization"
+title: "Figure 1-Supplement 2e"
+subtitle: "miR34a asRNA cellular localization"
 author: "Jason T. Serviss"
@@
 
-url <- fileMap(type = "rds")["suppFigure1e"][[1]]
+url <- fileMap(type = "rds")["Figure 1-Supplement 2e"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 2e"][[1]])
 # ggsave(

### 2017-12-09 inst/coding_potential_cpc/coding_potential_cpc.Rmd
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 1g"
+title: "Figure 1-Supplement 2d"
 subtitle: "miR34a asRNA coding potential via CPC"
@@
 
-url <- fileMap(type = "rds")["suppFigure1g"][[1]]
+url <- fileMap(type = "rds")["Figure 1-Supplement 2d"][[1]]
 cpat <- read_rds(url(file.path(dataUrl, url)))
@@
 <br></br>
+
+```{r}
+sessionInfo()
+```

### 2017-12-09 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 2b"
+title: "Figure 2a"
 subtitle: "miR34a asRNA expression in HCT116 and HEK293t upon doxorubicin treatment"
@@
 
-url <- fileMap(type = "rds")["figure2a"][[1]]
+url <- fileMap(type = "rds")["Figure 2a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
 # ggsave(

### 2017-12-09 inst/hct116_p53_null/hct116_p53_null.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 2a"
+title: "Figure 2b"
 subtitle: "miR34a asRNA doxorubicin treatment of HCT116 p53 wt and null"
@@
 
-url <- fileMap(type = "rds")["figure2b"][[1]]
+url <- fileMap(type = "rds")["Figure 2b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2b"][[1]])
 # ggsave(

### 2017-12-09 inst/isoforms/isoforms.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary figure 1d"
+title: "Figure 1-Supplement 2c"
 subtitle: "miR34a asRNA isoform cloning"
@@
 
-url <- fileMap(type = "png")["suppFigure1d"][[1]]
+url <- fileMap(type = "png")["Figure 1-Supplement 2c"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-12-09 inst/lnc34a/lnc34a.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "lnc34a analysis"
+title: "Supplementary Document 1"
+subtitle: "lnc34a analysis"
 author: "Jason T. Serviss"
@@
 
-url <- fileMap(type = "png")["suppFigure4a"][[1]]
+url <- fileMap(type = "png")["Supplementary Document 1a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class="caption">
-All available CAGE data from the ENCODE project for 36 cell lines was downloaded from the UCSC genome browser for genome version hg19.
+<strong>Supplementary Document 1a:</strong> All available CAGE data from the ENCODE project for 36 cell lines was downloaded from the UCSC genome browser for genome version hg19.
 Of these, 28 cell lines had CAGE transcription start sites mapping to the plus strand of chromosome 1 and in regions corresponding to 200 base pairs upstream of the lnc34a start site (9241796 - 200) and 200 base pairs upstream of the GENCODE annotated miR34a asRNA start site (9242263 + 200).
@@
 
-url <- fileMap(type = "png")["suppFigure4b"][[1]]
+url <- fileMap(type = "png")["Supplementary Document 1b"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class="caption">
-All available whole cell (i.e.
+<strong>Supplementary Document 1b:</strong> All available whole cell (i.e.
 non-fractionated) spliced read data originating from the Cold Spring Harbor Lab in the ENCODE  project for 38 cell lines was downloaded from the UCSC genome browser.

### 2017-12-09 inst/p1_construct/p1_construct.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 2c"
+title: "Figure 2-Supplement 1a-b"
 subtitle: "Schematic representation of the P1 construct"
@@
 
-url <- fileMap(type = "png")["figure2c"][[1]]
+url <- fileMap(type = "png")["Figure 2-Supplement 1a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 *For all results and conclusions please see Figure 2d.
+
+```{r}
+sessionInfo()
+```

### 2017-12-09 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 2d"
+title: "Figure 2c"
 subtitle: "P1 transfections in HCT116 and HEK293t cells"
@@
 
-url <- fileMap(type = "rds")["figure2c"][[1]]
+url <- fileMap(type = "rds")["Figure 2c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2c"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2c"][[1]])
 # ggsave(

### 2017-12-09 inst/p1_hek293t/p1_hek293t.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "P1 shRenilla HEK293t transfections"
+title: "Figure 2-Supplement 2"
+subtitle: "P1 shRenilla HEK293t transfections"
 author: "Jason T. Serviss"
@@
 
-url <- fileMap(type = "rds")["suppFigure2b"][[1]]
+url <- fileMap(type = "rds")["Figure 2-Supplement 2"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2-Supplement 2"][[1]])
 # ggsave(

### 2017-12-09 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 2e"
+title: "Figure 2d"
 subtitle: "P1 transfections with shRNA Renilla and doxorubicin treatment"
@@
 
-url <- fileMap(type = "rds")["figure2d"][[1]]
+url <- fileMap(type = "rds")["Figure 2d"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure2d"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
 # ggsave(

### 2017-12-09 inst/polyadenylation/polyadenylation.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary figure 1c"
+title: "Figure 1-Supplement 2b"
 subtitle: "miR34a asRNA polyadenylation"
@@
 
-url <- fileMap(type = "png")["suppFigure1c"][[1]]
+url <- fileMap(type = "png")["Figure 1-Supplement 2b"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-12-09 inst/primer_walk_schematic/primer_walk_schematic.Rmd
done with changes in last commits (I hope)
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 1b"
+title: "Figure 1-Supplement 2a"
 subtitle: "Primer walk schematic"
@@
 
-#url <- "suppFigure1b_primerWalkSchematic/schematic_hg38.png"
-#knitr::include_graphics(file.path(projectUrl, url))
-
-url <- fileMap(type = "png")["suppFigure1b"][[1]]
+url <- fileMap(type = "png")["Figure 1-Supplement 2a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2017-12-09 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 2b"
+title: "Figure 3-Supplement 2a"
 subtitle: "CCND1 expression in PC3 stable cell lines"
@@
 
-url <- fileMap(type = "rds")["suppFigure3b"][[1]]
+url <- fileMap(type = "rds")["Figure 3-Supplement 2a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 2c"
+title: "Figure 3-Supplement 2b"
 subtitle: "CCND1 protein expression in PC3 stable lines"
@@
 
-url <- fileMap(type = "rds")["suppFigure3c"][[1]]
+url <- fileMap(type = "rds")["Figure 3-Supplement 2b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3c"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2b"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
all paths updated to match article inc. Rmd titles

@@
 
-url <- fileMap(type = "rds")["figure3b"][[1]]
+url <- fileMap(type = "rds")["Figure 3b"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3b"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_expression/stable_line_expression.Rmd
all paths updated to match article inc. Rmd titles

@@
 
-url <- fileMap(type = "rds")["figure3a"][[1]]
+url <- fileMap(type = "rds")["Figure 3a"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
-
-#remove Skov exp 1 due to variability in technical replicates
-#data <- filter(data, `Biological Replicate` != 1 | `Cell line` != "Skov3")
 
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3a"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 2a"
+title: "Figure 3-Supplement 1"
 subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293t"
@@
 
-url <- fileMap(type = "rds")["suppFigure3a"][[1]]
+url <- fileMap(type = "rds")["Figure 3-Supplement 1"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 1"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
all paths updated to match article inc. Rmd titles

@@
 
-url <- fileMap(type = "rds")["figure3c"][[1]]
+url <- fileMap(type = "rds")["Figure 3c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3c"][[1]])
 # ggsave(

### 2017-12-09 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
all paths updated to match article inc. Rmd titles

@@
 
-url <- fileMap(type = "rds")["figure3d"][[1]]
+url <- fileMap(type = "rds")["Figure 3d"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3d"][[1]])
 # ggsave(

### 2017-12-09 inst/tcga_correlation/tcga_correlation.Rmd
all paths updated to match article inc. Rmd titles

@@
 ```{r}
-url <- fileMap(type = "rds")["figure1c"][[1]]
+url <- fileMap(type = "rds")["Figure 1c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 ##save to pdf
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure1c"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1c"][[1]])
 # pdf(path, width = 7.7, height = 4)

### 2017-12-09 inst/tcga_correlation_table/tcga_correlation_table.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Supplementary Figure 1a"
+title: "Figure 1-Supplement 1a"
 subtitle: "TCGA correlation table"
@@
 ```{r, warning = FALSE}
-url <- fileMap(type = "rds")["figure1c"][[1]]
+url <- fileMap(type = "rds")["Figure 1c"][[1]]
 data <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1a"][[1]])
 # pdf(file = path, width = 14)

### 2017-12-09 inst/tcga_expression/tcga_expression.Rmd
all paths updated to match article inc. Rmd titles

@@
 ---
-title: "Figure 1c"
-subtitle: "miR34a asRNA and miR34a TCGA correlation"
+title: "Figure 1-Supplement 1b"
+subtitle: "miR34a asRNA and miR34a TCGA expression"
 author: "Jimmy Van den Eynden and Jason T. Serviss"
@@
     CI95h_mut = t.test(unlist(`TP53 mut`))$conf.int[2],
-    pValue = t.test(unlist(`TP53 wt`), unlist(`TP53 mut`))$p.value
+    pValue = wilcox.test(unlist(`TP53 wt`), unlist(`TP53 mut`), alternative = "two.sided")$p.value
   ) %>%
@@
 
-```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE}
+```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE, warning = FALSE}
 ggplot(data = NULL) + 
@@
     legend.text = element_text(size = 7),
-    axis.title = element_text(size = 9),
-    axis.title.x = element_text(margin = margin(t = 5)),
+    axis.title.y = element_blank(),
+    axis.title.x = element_text(size = 9, margin = margin(t = 5)),
     axis.text.y = element_text(size = 10),
@@
 ##save to pdf
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1b"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 135,
-   width = 205,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1b"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 135,
+#    width = 205,
+#    units = "mm"
+# )
 ```

### 2017-12-09 R/utils.R

@@ -27,8 +27,8 @@ fileMap <- function(type) {
     `Figure 1d` = "3_prime_race/3_prime_race.Rmd",
     `Figure 1e` = "primer_walk/primer_walk.Rmd",
     `Figure 1f` = "coding_potential_cpat/coding_potential_cpat.Rmd",
-    `Figure 2b` = "hct116_p53_null/hct116_p53_null.Rmd",
     `Figure 2a` = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
+    `Figure 2b` = "hct116_p53_null/hct116_p53_null.Rmd",
     `Figure 2c` = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
     `Figure 2d` = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
     `Figure 3a` = "stable_line_expression/stable_line_expression.Rmd",
@@ -50,7 +50,9 @@ fileMap <- function(type) {
     `Figure 3-Supplement 2a` = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
     `Figure 3-Supplement 2b` = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
     `Supplementary Document 1a` = "lnc34a_cage/lnc34a_cage.Rmd",
-    `Supplementary Document 1b` = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd"
+    `Supplementary Document 1b` = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd",
+    `Supplementary Document 1` = "lnc34a/lnc34a.Rmd",
+    `Supplementary Document 2` = "primers/primers.Rmd"
   )
   
   if(type == "Rmd") {

### 2017-12-10 inst/lnc34a_cage/lnc34a_cage.Rmd
some manuscript stuff and adding recreate_all_figures

@@
     theme: flatly
-  pdf_document: default
 vignette: |
   %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
+editor_options: 
+  chunk_output_type: console
 ---
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
-  url <- fileMap(type = "txt")["suppFigure4a"][[1]]
+  url <- fileMap(type = "txt")["Supplementary Document 1a"][[1]]
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure4a"][[1]]
+  url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
   read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 #cage data
-url <- fileMap(type = "rds")["suppFigure4a"][[1]]
+url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
 cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Document 1a"][[1]])
 # ggsave(

### 2017-12-10 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
re-ran all rmds and added sessionInfo to all
some manuscript stuff and adding recreate_all_figures

@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure4b"][[1]]
+  url <- fileMap(type = "txt")["Supplementary Document 1b"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure4b"][[1]]
+  url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["suppFigure4b"][[1]]
+  url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
   final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["suppFigure4b"][[1]]
+  url <- fileMap(type = "txt")["Supplementary Document 1b"][[1]]
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 #splice junctions
-url <- fileMap(type = "rds")["suppFigure4b"][[1]]
+url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
 splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure3e"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Document 1b"][[1]])
 # ggsave(

### 2017-12-10 R/utils.R

@@ -21,6 +21,7 @@ NULL
 
 fileMap <- function(type) {
   pList <- list(
+    `All figures` = "recreate_all_figures/recreate_all_figures.Rmd",
     `Figure 1a` = "mir34a_locus/mir34a_locus.Rmd",
     `Figure 1b` = "mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd",
     `Figure 1c` = "tcga_correlation/tcga_correlation.Rmd",

### 2017-12-10 inst/lnc34a_cage/lnc34a_cage.Rmd
trying to fix str_replace missing error in lnc34a_cage

@@
     "ggthemes",
-    "printr"
+    "printr",
+    "stringr"
 )

### 2017-12-10 inst/tcga_expression/tcga_expression.Rmd
fixing some rmd typos

@@
 A graphical depiction of the TCGA expression analysis.
+P-values are shown on the right side of each panel and compare TP53 wild type samples with nonsynonymous TP53 muated samples.
+The small vertical line indicated the mean.
 Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).
@@
 #### _Conclusions_
-miR34a asRNA and miR34a tend to be highly correlated in the cancer types examined in both TP53 wild type and mutated samples.
-In addition, the results indicate that both miR34a asRNA and miR34a expression levels are decreased in the presence of TP53 mutations.
+
+miR34a asRNA and miR34a tend to exhibit a decreased expression in cancer types examined in patients with TP53 mutations.
 

### 2017-12-10 inst/isoforms/isoforms.Rmd
added primer combos and annealing info to isoforms

@@
 500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.
-PCR was performed with the specified primer sets with annealing temperature 60˚C unless otherwise indicated.
+PCR was performed with the specified primer sets with annealing temperature 60˚C unless otherwise indicated (see below).
 PCR was run for 35 cycles for those primer sets with annealing temperature 60˚C and 40 cycles in other cases.
-Resulting PCR products were run on a agarose gel, gel extracted with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced.
+Resulting PCR products were run on a agarose gel, gel extracted (8 in total) with the QIAquick gel extraction kit (Qiagen), cloned using the Strata Cloning kit (Agilent), and sequenced.
 The sequencing results were visualized in the UCSC genome browser.
+Results aligning to the opposite strand and spurious results (several small 24bp alignments) were removed from the final figure.
 
@@
     name=c(
-        "F12",
-        "R1",
-        "R2",
-        "R3",
-        "Ex3R1"
+        "miR34a AS F12",
+        "miR34a AS R1",
+        "miR34a AS R2",
+        "miR34a AS R3",
+        "miR34a AS Ex3 R1"
     ),
@@
 ```
+
+Primer combinations:
+miR34a AS F12 + miR34a AS R1
+miR34a AS F12 + miR34a AS R2
+miR34a AS F12 + miR34a AS R3
+miR34a AS F12 + miR34a AS Ex3 R1 (56 degrees annealing)
+miR34a AS F12 + miR34a AS Ex3 R1 (58 degrees annealing)
 

### 2017-12-11 inst/lnc34a/lnc34a.Rmd
adding prelim data documentation

@@
 Despite this, we find no CAGE tags aligning at the transcription start site or upstream of the transcription start site of the lnc34a transcript.
-This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as claimed by the authors.
+This potentially indicates that lnc34a is tightly regulated and specifically expressed in the CCSC context, as suggested by the authors.
 An alternative intrepretation could be that lnc34a expression is present in a subset of the examined cell lines although at too low levels to be detected.
@@
 
-In order to lnc34a expression in a manner that is not dependant on 5'-capping, we proceeded to examine spliced RNA sequencing reads from 36 cell lines, taking advantage of the fact that lnc34a has an exon which is not present in any miR34a asRNA isoforms.
+In order to lnc34a expression in a manner that is not dependant on 5'-capping, we proceeded to examine spliced RNA sequencing reads from 36 cell lines, taking advantage of the fact that lnc34a has an exon which is not present in any annotated or PCR cloned miR34a asRNA isoforms.
 
@@
 These results indicate that, although splice junctions corresponding to multiple isoforms detected by PCR cloning of the miR34a asRNA were detected, the data give no support for the presence of the splice junction between the first and second exon of lnc34a.
-In summary, these results indicate that lnc34a expression may be confined to colon cancer stem cells as evidence for its expression in the examined cell lines is not forthcomming.
+In summary, these results indicate that lnc34a is unlikely to represent the same asRNA transcript as miR34a asRNA and that its expression may be confined to colon cancer stem cells.
 
-In addition, we note several comments in the public review that was published in conjunction with the work by Wang et al.
-The authors mention, and provide data, indicating that lnc34a expression is not changed upon ectopic expression of TP53.
-In contrast, miR34a asRNA is strongly regulated by TP53 as the evidence shows in this and others (Léveillé 2015, Rashi-Elkeles 2014, Hünten 2015, Ashouri 2016, Kim 2017) findings.
-
+In addition, there are several other lines of evidence indicating that the asRNA described in our paper is distinct from lnc34a.
+We noted several comments in the public review that was published in conjunction with the work by Wang et al.
+that the authors mention, and provide data, indicating that lnc34a expression is not changed upon ectopic expression of TP53.
+In contrast, miR34a asRNA is strongly regulated by TP53 as the evidence shows in this and others findings (Léveillé 2015, Rashi-Elkeles 2014, Hünten 2015, Ashouri 2016, Kim 2017).
 Furthermore, Wang et al.
@@
 
-In summary, these results indicate that lnc34a expression is not present in the cell types examined where there exists strong evidence for the presence miR34a asRNA.
-For these reasons, we believe miR34a asRNA and lnc34a to be individual antisense RNA transcripts.
+In summary, these results indicate that lnc34a expression is not present in the cell types examined where there exists strong evidence for the presence miR34a asRNA and, for these reasons, we believe miR34a asRNA and lnc34a to be individual antisense RNA transcripts.

### 2017-12-11 inst/stable_line_expression/stable_line_expression.Rmd
adding prelim data documentation

@@
 delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples.
-At least three independant experiments (biological replicates) were performed in total (see more below).
+Five independant experiments were performed in total.
 The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.
-
-<br></br>
-
-The sample numbers for each group are as follows:
-```{r}
-
-n <- data.frame(
-  name = c(
-    "PC3 mock",
-    "PC3 miR34a asRNA",
-    "Skov3 mock",
-    "Skov3 miR34a asRNA",
-    "Saos2 mock",
-    "Saos2 miR34a asRNA"
-  ),
-  n = c(5, 5, 4, 4, 5, 5)
-)
-n
-
-```
 

### 2017-12-11 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
adding prelim data documentation

@@
 title: "Figure 3-Supplement 1"
-subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293t"
+subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293T"
 author: "Jason T. Serviss"
@@
 Delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding untreated samples.
-Five independant experiments were performed in total for all cell lines with the exception of PC3.
-Six independant experiments were preformed for the PC3 cell lines although, one experiment was removed due to excessivley high ct values (>30) in the house keeping gene, indicating an insufficient amount of RNA to sucessfully detect the genes of interest.
+Five independant experiments were performed in total for all cell lines.
 

### 2017-12-11 R/data.R

@@ -91,3 +91,462 @@ NULL
 #' @examples
 #' getData('Figure 1-Supplement 2d')
 NULL
+
+#' miR34a asRNA expression in HCT116 and HEK293t upon doxorubicin treatment.
+#'
+#' All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured
+#' in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a
+#' (Life Technologies). All growth mediums were supplemented with 10%
+#' heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin.
+#' Cells were plated at 300,000 cells per well in a 6-well plate and cultured
+#' overnight. The following day cells were treated with 0, 100, 200, or
+#' 500 ng/ml doxorubicin for 24hrs. RNA was extracted using the RNeasy mini kit
+#' (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life
+#' Technologies). 500ng RNA was used for cDNA synthesis using MuMLV (Life
+#' Technologies) and a 1:1 mix of oligo(dT) and random nanomers. QPCR was
+#' carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied
+#' Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min,
+#' 95 °C for 3 s, 60 °C for 30 s.
+#' @name hct116_hek293t_dox
+#' @format A tibble with 48 rows and 6 variables:
+#'\describe{
+#'   \item{'Biological Replicate'}{Numeric; Indicates the biological replicate of the sample.}
+#'   \item{'Cell line'}{Character; Indicating the cell line the data corresponds to.}
+#'   \item{Treatment}{Character; Indicates the treatment type.}
+#'   \item{gene}{Character; indicates the gene that the Ct values correspond to.}
+#'   \item{Ct1}{Numeric; Ct value corresponding to the first technical replicate.}
+#'   \item{Ct2}{Numeric; Ct value corresponding to the 2nd technical replicate.}
+#'   ...
+#' }
+#' @examples
+#' getData('Figure 2a')
+NULL
+
+#' miR34a asRNA doxorubicin treatment of HCT116 p53 wt and null.
+#'
+#' HCT116 cells were cultured in DMEM high modified (Hyclone, GE healthcare)
+#' supplemented with supplemented with 2mM L-glutamine, 50ug/ml
[…]

### 2017-12-11 R/utils.R

@@ -200,7 +200,14 @@ NULL
 getData <- function(figure) {
   #check that there is data for the figure
   figsWithData <- c(
-    'Figure 1-Supplement 2e', 'Figure 1f', 'Figure 1-Supplement 2d'
+    'Figure 1-Supplement 2e', 'Figure 1f', 'Figure 1-Supplement 2d',
+    'Figure 2a', 'Figure 2b', 'Supplementary Document 1a',
+    'Supplementary Document 1b', 'Figure 2c', 'Figure 2-Supplement 2',
+    'Figure 2d', 'Figure 3-Supplement 2a', 'Figure 3-Supplement 2b',
+    'Figure 3b', 'Figure 3-Supplement 1', 'Figure 3a',
+    'Figure 3c', 'Figure 3d', 'Figure 1-Supplement 1a',
+    'Figure 1c'
+    
   )
   if(!figure %in% figsWithData) {
     stop("There is no data for the figure you specified")

### 2017-12-12 inst/coding_potential_geiger/coding_potential_geiger.Rmd
lots of changes, pray you never need to return before this point

---
title: "Coding Potential with Geiger et al. dataset"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

#### _Introduction_

We desired to complement the bioinformatics-based coding potential analyses by scanning the publically available proteomics dataset for peptides matching miR34a asRNA.

<br></br>

#### _Methods_

Orbitrap raw MS/MS files for 11 human cell lines (A549, GAMG, HEK293, HeLa, HepG2, K562, MCF7, RKO, U2OS, LnCap and Jurkat) were downloaded from the PRIDE repository (PXD002395, (Geiger et al., 2012)) converted to mzML format using msConvert from the ProteoWizard tool suite (Holman et al., 2014). Spectra were then searched using MSGF+ (v10072) (Kim and Pevzner, 2014)  and Percolator (v2.08) (Granholm et al., 2014). All searches were done against the human protein subset of Ensembl 75 in the Galaxy platform (Boekel et al., 2015) supplemented with the 6 frame translation of uc057cap.1 and the PCR cloned sequence of miRNA34a asRNA (see below). MSGF+ settings included precursor mass tolerance of 10 ppm, fully-tryptic peptides, maximum peptide length of 50 amino acids and a maximum charge of 6. Fixed modification was carbamidomethylation on cysteine residues, a variable modification was used for oxidation on methionine residues. PSMs found at 1% FDR (false discovery rate) were used to infer peptide identities. The output from all searches are available in coding_potential_geiger.rds.

<br></br>

_RNA sequences used for translation_

```{r}
tibble(
  name = c("miR34AasRNA_cloned", "uc057cap.1"),
  sequence = c(
    "AAACACAAGCGTTTACCTGGGTGCATGCTGGGACGGGGCGAGCAGGTAGTGCAGGCTTCCAGGCCTCTCCTGCCCCGGAGCTTGGCTGCAGGACTCCCGCAAAATCTCCAAATGCCCCCGATCTGCGTGGTCACCGAGAAGCAGCCCGGCTCGGAACAAGCCCAGGCAAGCCCAGGCAGAGCCCGCCGCCGGGTCCTCCTTCCTGCTCGTGCCACCAGGCCCCGGGGCCGCGACGCGTCTCTCCAGCCCGGGATCCGGGGAGCTGGGCTGTCCCCAGACCGACGGGACAGCGGCATCTCCTCCACCTGAAAAGGAAAGAGGACCAGTTTGCAGGACTCCGAACTGGGCCCGCGAGATCTCCACCTGCGCAAAACGAAAGGGCGGATTCTCCTTGGACTCACGAGGCAACCGCTCCCCGGGGTGAGAACGGGGGACTCATTCCTCCGGCACTGGGAGAAGACGATTCTTTAGGAGGAGGACAGGGAAGCGAATGCTACCCAGATGTCTCAGTATACTGGCTCGCGGCACATCGGGCAAATGAACCTATCAGATAACAACGGCAGATCAGATGCCTGAGCATTCAGAAGCAACAGCTGTGGAGCCCCCGTGGGTTCAGAAGGCCTGGTTCCCGTCTCCAGAAGCCTGGCTCTCCTCCCTCCTGGGCCCACTACTTTGGCTTCTTGTTCCTACGTACAAGGAGTTGCGAAGAAGGCAACTCTTCCCCTCCCTGAAGCCAAAGGAATGAAACAGACTAGGGCGGGAGAGGTGGCCATCCGTCATTAGTTGCGGCCATCA",
    "ACCAGGCCCCGGGGCCGCGACGCGTCTCTCCAGCCCGGGATCCGGGGAGCTGGGCTGTCCCCAGACCGACGGGACAGCGGCATCTCCTCCACCTGAAAAGGAAAGAGGACCAGTTTGCAGGACTCCGAACTGGGCCCGCGAGATCTCCACCTGCGCAAAACGAAAGGGCGGATTCTCCTTGGACTCACGAGGCAACCGCTCCCCGGGGTGAGAACGGGGGACTCATTCCTCCGGCACTGGGAGAAGACGATTCTTTAGGAGGAGGACAGGGAAGCGAATGCTACCCAGGATAACAACGGCAGATCAGATGCCTGAGCATTCAGAAGCAACAGCTGTGGAGCCCCCGTGGGTTCAGAAGGCCTGGTTCCCGTCTCCAGAAGCCTGGCTCTCCTCCCTCCTGGGCCCACTACTTTGGCTTCTTGTTCCTACGTACAAGGAGTTGCGAAGAAGGCAACTCTTCCCCTCCCTGAAGCCAAAGGAATGAAACAGACTAGGGCGGGAGAGGTGGCCATCCGTCATTAGTTGCGGCCATCAGTAACAGCAACAGGACACGGAACCTAAGGCTGTATCCATCCTGGGCCCCCAGGGAAACATCAGCGGGAGCGGTACTAAGGAAGTGCTCATCTCTTAGAGACAAAGGCCCATGGAGGGGAACAGTAACCATCCCCTCCCAATTCAGAAAATGTTAACATAAGCACTTCATTTCTCATGCAGATAACCACATAAGTCTATTAATTCCATGCCAGCAGGGTATAGGAATTGGTCTATAGGAGAAAGGGTCACCCACTGAAAGGTGGGCTGAATAGAATTCCTTGCCTGGGCTTTGAGGTCCTGGCATGGAGAAGGCTGTAGAAATGCTGGCATCAGTGGAACCCTCAATAAACAGAATTCTTGTTAAAGAA"
  )
) %>% 
  mutate(sequence = str_replace_all(sequence, "(.{3})", "\\1 "))
```

_6 frame translations_

```{r}
tibble(
  name = c(
    "miR34AasRNA_cloned_5_3_Frame_1", "miR34AasRNA_cloned_5_3_Frame_2", "miR34AasRNA_cloned_5_3_Frame_3",
    "miR34AasRNA_cloned_3_5_Frame_1", "miR34AasRNA_cloned_3_5_Frame_2", "miR34AasRNA_cloned_3_5_Frame_3",
    "uc057cap.1_5_3_Frame_1", "uc057cap.1_5_3_Frame_2", "uc057cap.1_5_3_Frame_3",
    "uc057cap.1_3_5_Frame_1", "uc057cap.1_3_5_Frame_2", "uc057cap.1_3_5_Frame_3"
  ),
  sequence = c(
    "KHKRLPGCMLGRGEQVVQASRPLLPRSLAAGLPQNLQMPPICVVTEKQPGSEQAQASPGRARRRVLLPARATRPRGRDASLQPGIRGAGLSPDRRDSGISST*KGKRTSLQDSELGPRDLHLRKTKGRILLGLTRQPLPGVRTGDSFLRHWEKTIL*EEDREANATQMSQYTGSRHIGQMNLSDNNGRSDA*AFRSNSCGAPVGSEGLVPVSRSLALLPPGPTTLASCSYVQGVAKKATLPLPEAKGMKQTRAGEVAIRH*LRPS",
    "NTSVYLGACWDGASR*CRLPGLSCPGAWLQDSRKISKCPRSAWSPRSSPARNKPRQAQAEPAAGSSFLLVPPGPGAATRLSSPGSGELGCPQTDGTAASPPPEKERGPVCRTPNWAREISTCAKRKGGFSLDSRGNRSPG*ERGTHSSGTGRRRFFRRRTGKRMLPRCLSILARGTSGK*TYQITTADQMPEHSEATAVEPPWVQKAWFPSPEAWLSSLLGPLLWLLVPTYKELRRRQLFPSLKPKE*NRLGRERWPSVISCGH",
    "TQAFTWVHAGTGRAGSAGFQASPAPELGCRTPAKSPNAPDLRGHREAARLGTSPGKPRQSPPPGPPSCSCHQAPGPRRVSPARDPGSWAVPRPTGQRHLLHLKRKEDQFAGLRTGPARSPPAQNERADSPWTHEATAPRGENGGLIPPALGEDDSLGGGQGSECYPDVSVYWLAAHRANEPIR*QRQIRCLSIQKQQLWSPRGFRRPGSRLQKPGSPPSWAHYFGFLFLRTRSCEEGNSSPP*SQRNETD*GGRGGHPSLVAAI",
    "*WPQLMTDGHLSRPSLFHSFGFREGKSCLLRNSLYVGTRSQSSGPRREESQASGDGNQAF*THGGSTAVASECSGI*SAVVI**VHLPDVPRASILRHLGSIRFPVLLLKNRLLPVPEE*VPRSHPGERLPRESKENPPFRFAQVEISRAQFGVLQTGPLSFSGGGDAAVPSVWGQPSSPDPGLERRVAAPGPGGTSRKEDPAAGSAWACLGLFRAGLLLGDHADRGHLEILRESCSQAPGQERPGSLHYLLAPSQHAPR*TLVF", 
    "DGRN**RMATSPALVCFIPLASGRGRVAFFATPCT*EQEAKVVGPGGRRARLLETGTRPSEPTGAPQLLLLNAQASDLPLLSDRFICPMCREPVY*DIWVAFASLSSS*RIVFSQCRRNESPVLTPGSGCLVSPRRIRPFVLRRWRSRGPSSESCKLVLFPFQVEEMPLSRRSGDSPAPRIPGWRDASRPRGLVARAGRRTRRRALPGLAWACSEPGCFSVTTQIGGIWRFCGSPAAKLRGRRGLEACTTCSPRPSMHPGKRLC",
    "MAATNDGWPPLPP*SVSFLWLQGGEELPSSQLLVRRNKKPK*WAQEGGEPGFWRREPGLLNPRGLHSCCF*MLRHLICRCYLIGSFARCAASQYTETSG*HSLPCPPPKESSSPSAGGMSPPFSPRGAVAS*VQGESALSFCAGGDLAGPVRSPANWSSFLFRWRRCRCPVGLGTAQLPGSRAGETRRGPGAWWHEQEGGPGGGLCLGLPGLVPSRAASR*PRRSGAFGDFAGVLQPSSGAGEAWKPALPARPVPACTQVNACV",
    "PGPGAATRLSSPGSGELGCPQTDGTAASPPPEKERGPVCRTPNWAREISTCAKRKGGFSLDSRGNRSPG*ERGTHSSGTGRRRFFRRRTGKRMLPRITTADQMPEHSEATAVEPPWVQKAWFPSPEAWLSSLLGPLLWLLVPTYKELRRRQLFPSLKPKE*NRLGRERWPSVISCGHQ*QQQDTEPKAVSILGPQGNISGSGTKEVLIS*RQRPMEGNSNHPLPIQKMLT*ALHFSCR*PHKSINSMPAGYRNWSIGERVTH*KVG*IEFLAWALRSWHGEGCRNAGISGTLNKQNSC*R",
    "QAPGPRRVSPARDPGSWAVPRPTGQRHLLHLKRKEDQFAGLRTGPARSPPAQNERADSPWTHEATAPRGENGGLIPPALGEDDSLGGGQGSECYPG*QRQIRCLSIQKQQLWSPRGFRRPGSRLQKPGSPPSWAHYFGFLFLRTRSCEEGNSSPP*SQRNETD*GGRGGHPSLVAAISNSNRTRNLRLYPSWAPRETSAGAVLRKCSSLRDKGPWRGTVTIPSQFRKC*HKHFISHADNHISLLIPCQQGIGIGL*EKGSPTERWAE*NSLPGL*GPGMEKAVEMLASVEPSINRILVKE",
    "TRPRGRDASLQPGIRGAGLSPDRRDSGISST*KGKRTSLQDSELGPRDLHLRKTKGRILLGLTRQPLPGVRTGDSFLRHWEKTIL*EEDREANATQDNNGRSDA*AFRSNSCGAPVGSEGLVPVSRSLALLPPGPTTLASCSYVQGVAKKATLPLPEAKGMKQTRAGEVAIRH*LRPSVTATGHGT*GCIHPGPPGKHQRERY*GSAHLLETKAHGGEQ*PSPPNSENVNISTSFLMQITT*VY*FHASRV*ELVYRRKGHPLKGGLNRIPCLGFEVLAWRRL*KCWHQWNPQ*TEFLLK",
    "FFNKNSVY*GFH*CQHFYSLLHARTSKPRQGILFSPPFSG*PFLL*TNSYTLLAWN**TYVVICMRNEVLMLTFSELGGDGYCSPPWAFVSKR*ALP*YRSR*CFPGGPGWIQP*VPCPVAVTDGRN**RMATSPALVCFIPLASGRGRVAFFATPCT*EQEAKVVGPGGRRARLLETGTRPSEPTGAPQLLLLNAQASDLPLLSWVAFASLSSS*RIVFSQCRRNESPVLTPGSGCLVSPRRIRPFVLRRWRSRGPSSESCKLVLFPFQVEEMPLSRRSGDSPAPRIPGWRDASRPRGL",
    "SLTRILFIEGSTDASISTAFSMPGPQSPGKEFYSAHLSVGDPFSYRPIPIPCWHGINRLMWLSA*EMKCLC*HFLNWEGMVTVPLHGPLSLRDEHFLSTAPADVSLGAQDGYSLRFRVLLLLLMAATNDGWPPLPP*SVSFLWLQGGEELPSSQLLVRRNKKPK*WAQEGGEPGFWRREPGLLNPRGLHSCCF*MLRHLICRCYPG*HSLPCPPPKESSSPSAGGMSPPFSPRGAVAS*VQGESALSFCAGGDLAGPVRSPANWSSFLFRWRRCRCPVGLGTAQLPGSRAGETRRGPGAW",
    "L*QEFCLLRVPLMPAFLQPSPCQDLKAQARNSIQPTFQWVTLSPIDQFLYPAGMELIDLCGYLHEK*SAYVNIF*IGRGWLLFPSMGLCL*EMSTSLVPLPLMFPWGPRMDTALGSVSCCCY*WPQLMTDGHLSRPSLFHSFGFREGKSCLLRNSLYVGTRSQSSGPRREESQASGDGNQAF*THGGSTAVASECSGI*SAVVILGSIRFPVLLLKNRLLPVPEE*VPRSHPGERLPRESKENPPFRFAQVEISRAQFGVLQTGPLSFSGGGDAAVPSVWGQPSSPDPGLERRVAAPGPG"
  )
) %>% 
  mutate(sequence = str_replace_all(sequence, "(.{3})", "\\1 "))

```

#### _Conclusions_

No peptides were identified that reliably mapped to either sequence. Therefore, it doesn’t seem to be a highly abundant protein or peptide that is ubiquitiously present in cancer at the very least. The results should not be intrepreted such that there are no matching peptides, but the likelihood is lower. It is nigh on impossible to prove that the sequence is never  translated but given the search results it seems likelier that miR34a asRNA is non-coding.

### 2017-12-12 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
lots of changes, pray you never need to return before this point

@@
 Cell pellets were frozen down at -80°C before lysed for Western Blot analysis.
-Western Blot analysis was performed following Lottes’ protocol.
 Cells were lysed in RIPA Buffer and run on a 4-12% Bis-Tris-SDS Gel using MOPS running buffer.
@@
 Membranes were blocked for 1 hour at room temperature in 5% milk.
-Membranes were incubated with a cyclin D1 antibody (92G2 Rabbit mAb, Cell Signalling) overnight at 4°C.
+Membranes were incubated with a cyclin D1 antibody (92G2 Rabbit mAb, Cell Signalling, 1:1000) overnight at 4°C.
 The membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature.
@@
 After the picture was taken, the membrane was stripped using 0.4M NaOH solution for 20min.
-Blocking step was repeated and primary antibody against GAPDH was incubated for overnight at 4°C.
+Blocking step was repeated and primary antibody against GAPDH (Abcam #ab9485, 1:5000) was incubated for overnight at 4°C.
 Consequently, the membrane was incubated using a goat anti-rabbit antibody conjugated to HRP for 1 hour at room temperature.

### 2017-12-12 inst/tcga_correlation/tcga_correlation.Rmd
lots of changes, pray you never need to return before this point

@@
 #### _Methods_
+
+RNA-Seq data and copy number data were downloaded from TCGA and processed as described previously (Ashouri et al.
+2016).
+Briefly, RNA-Seq data were aligned to the human hg19 assembly and quantified using GENCODE (v19) annotated HTSeq-counts and FPKM normalizations.
+Expression data from miR34a and miR34 asRNA (identified as RP3-510D11.2) were used for further analysis.
+Copy number amplitudes for GENCODE genes were determined from segmented copy-number data.
+Samples that were diploid for miR34 asRNA were identified as those samples that had copy number amplitudes between -0.1 and 0.1.
+
+Somatic mutation data were downloaded from the Genomics Data Commons data portal (GDC) as mutation annotation format (maf) files, called using Mutect2 on 30/10/2017 (v7) (Grossman et al. 2016).
 

### 2017-12-12 inst/tcga_correlation_table/tcga_correlation_table.Rmd
lots of changes, pray you never need to return before this point

@@
   %\VignetteIndexEntry{Vignette Title}
+  %\VignetteEncoding{UTF-8}
   %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
+editor_options: 
+  chunk_output_type: console
 ---
@@
     `all p` = format(`all p`, scientific = TRUE, digits = 3),
-    `all rho` = format(`all rho`, scientific = TRUE, digits = 3)
+    `all rho` = format(`all rho`, scientific = FALSE, digits = 2)
   )
@@
     p = format(p, scientific = TRUE, digits = 3),
-    rho = format(rho, scientific = TRUE, digits = 3)
+    rho = format(rho, scientific = FALSE, digits = 1)
   ) %>%
@@
 
+#add abbreviation definitions
+def <- tibble(
+  fullName = c(
+    "Adrenocortical carcinoma", "Bladder Urothelial Carcinoma", "Breast invasive carcinoma", 
+    "Breast invasive carcinoma", "Breast invasive carcinoma", "Breast invasive carcinoma",
+    "Cervical squamous cell carcinoma and\nendocervical adenocarcinoma", "Head and Neck squamous cell carcinoma", "Kidney Chromophobe",
+    "Kidney renal clear cell carcinoma", "Kidney renal papillary cell carcinoma", "Brain Lower Grade Glioma",
+    "Liver hepatocellular carcinoma", "Lung adenocarcinoma", "Lung squamous cell carcinoma",
+    "Ovarian serous cystadenocarcinoma", "Prostate adenocarcinoma", "Skin Cutaneous Melanoma",
+    "Stomach adenocarcinoma", "Thyroid carcinoma"
+  ),
+  cancer = c(
+    "ACC", "BLCA", "BRCA Basal", 
+    "BRCA Her2", "BRCA LumA", "BRCA LumB",
+    "CESC", "HNSC", "KICH",
+    "KIRC", "KIRP", "LGG",
+    "LIHC", "LUAD", "LUSC",
+    "OV", "PRAD", "SKCM", 
+    "STAD", "THCA"
+  )
+)
+
+table <- def %>%
+  full_join(table, by = "cancer") %>%
+  mutate(finalName = case_when(
+    fullName == "Breast invasive carcinoma" ~ paste(fullName, gsub("BRCA", "(BRCA)", cancer), sep = " "),
+    TRUE ~ paste(fullName, "(", cancer, ")", sep = " ")
+  )) %>%
+  select(-fullName, -cancer) %>%
+  rename(cancer = finalName) %>%
+  select(cancer, `all n`, `all rho`, `all p`, `TP53wt n`, `TP53wt rho`, `TP53wt p`, `TP53mut n`, `TP53mut rho`, `TP53mut p`)
+
+#save figure
 # path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 1-Supplement 1a"][[1]])
-# pdf(file = path, width = 14)
+# pdf(file = path, width = 13, height = 6.1)
 # gridExtra::grid.table(table, rows = NULL)

### 2017-12-12 inst/tcga_expression/tcga_expression.Rmd
lots of changes, pray you never need to return before this point

@@
 
+RNA-Seq data and copy number data were downloaded from TCGA and processed as described previously (Ashouri et al.
+2016).
+Briefly, RNA-Seq data were aligned to the human hg19 assembly and quantified using GENCODE (v19) annotated HTSeq-counts and FPKM normalizations.
+Expression data from miR34a and miR34 asRNA (identified as RP3-510D11.2) were used for further analysis.
+Copy number amplitudes for GENCODE genes were determined from segmented copy-number data.
+Samples that were diploid for miR34 asRNA were identified as those samples that had copy number amplitudes between -0.1 and 0.1.
+
+Somatic mutation data were downloaded from the Genomics Data Commons data portal (GDC) as mutation annotation format (maf) files, called using Mutect2 on 30/10/2017 (v7) (Grossman et al. 2016).
+
 <br></br>
@@
   mutate(
-    mean_wt = mean(unlist(`TP53 wt`)),
-    mean_mut = mean(unlist(`TP53 mut`)),
+    median_wt = median(unlist(`TP53 wt`)),
+    median_mut = median(unlist(`TP53 mut`)),
     CI95l_wt = t.test(unlist(`TP53 wt`))$conf.int[1],
@@
   mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
-  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = unique(cancer_PAM50)))
+  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))
 
@@
   mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
-  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = unique(cancer_PAM50)))
+  mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))
 ```
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12, message = FALSE, warning = FALSE}
+
 ggplot(data = NULL) + 
@@
       x = cancer_PAM50,
-      y = mean,
+      y = median,
       group = TP53
@@
 P-values are shown on the right side of each panel and compare TP53 wild type samples with nonsynonymous TP53 muated samples.
-The small vertical line indicated the mean.
+The small vertical line indicated the median.
 Bladder Urothelial Carcinoma (BLCA), Breast invasive carcinoma (BRCA), Head and Neck squamous cell carcinoma (HNSC), Lower Grade Glioma (LGG), Liver hepatocellular carcinoma (LIHC), Lung adenocarcinoma (LUAD), Lung squamous cell carcinoma (LUSC), Ovarian serous cystadenocarcinoma (OV), Prostate adenocarcinoma (PRAD), Skin Cutaneous Melanoma (SKCM), Stomach adenocarcinoma (STAD).

### 2017-12-12 data-raw/saveRDS.R

@@ -328,6 +328,11 @@ print("processing coding_potential_cpc")
 read_tsv('./data-raw/coding_potential_cpc.txt') %>%
   write_rds(., path = './data/coding_potential_cpc.rds')
 
+#coding potential Geiger
+print("processing coding_potential_geiger")
+read_tsv('./data-raw/coding_potential_geiger.txt') %>%
+  write_rds(., path = './data/coding_potential_geiger.rds')
+
 #tcga_correlation_table
 print("processing tcga_correlation_table")
 read_tsv('./data-raw/tcga_correlation_table.txt') %>%

### 2017-12-14 inst/tcga_survival_total/tcga_survival_total.Rmd
many rushed last minute changes

---
title: "Figure 4a-4b"
subtitle: "lncTAM34a survival analysis in TCGA cancers"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

#library(grDevices)
```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

**_Please note that the following script has not yet been fully integrated into the package and, therefore, is included here to facilitate transparency although re-running the script in real-time is not yet supported. This will be resolved before publication._**

Data were derived from TCGA:

* **data/lncRNA_cancer_id.rds**: Matrix containing for each TCGA barcode information regarding cancer type.
* **data/lncRNA_clin.rds**: Matrix containing for each TCGA barcode information regarding vital state (first column) and date of last follow-up (second column). Data were downloaded from TCGA on 20171027.
* **data/lncRNA_TCGA_TP53_hasNonsynMut.rds**: Named vector containing for each TCGA barcode information regarding TP53 nonSynonymous mutation state: FALSE if no mutation or synonymous mutations, TRUE if mutated. Mutect2 v7 called data were downloaded from TCGA on 20171030.
* **data/lncRNA_expr_RP3.rds**: Named numeric vector containing for each TCGA barcode information regarding RP3-510D11.2 expression. For details on RNA-Seq processing, see *Ashouri A et al. Nat Commun. 2016;7*
* **data/lncRNA_cna_RP3.rds**: Named numeric vector containing for each TCGA barcode information regarding RP3-510D11.2 copy number alteration (gene-based segmentation values). For details on processing, see *Ashouri A et al. Nat Commun. 2016;7*
* **data/lncRNA_expr_miR34a.rds**: Named numeric vector containing for each TCGA barcode information regarding miR34a expression. For details on RNA-Seq processing, see *Ashouri A et al. Nat Commun. 2016;7*
* **data/lncRNA_TCGA_BRCA_PAM50.rds**: Named character vector containing for each TCGA barcode from the breast cancer dataset information regarding PAM50 classification: LumA, LumB, Basal or Her2. For details on PAM50 classification, see *Ashouri A et al. Nat Commun. 2016;7*

```{r, eval = FALSE}
TCGA_cancer_id<- readRDS("data/lncRNA_cancer_id.rds") # TCGA Subtype IDs
TCGA_clin_surv<- readRDS("data/lncRNA_clin.rds") # Survival data
TCGA_TP53_hasNonsynMut<- readRDS("data/lncRNA_TCGA_TP53_hasNonsynMut.rds") # Survival data
RP3_expr<- readRDS(file = "data/lncRNA_expr_RP3.rds")
RP3_cna<- readRDS(file = "data/lncRNA_cna_RP3.rds")
miR34a_expr<- readRDS(file = "data/lncRNA_expr_miR34a.rds")
TCGA_PAM50<- readRDS(file = "data/lncRNA_TCGA_BRCA_PAM50.rds")
```

## Functions

```{r, eval = FALSE}
source("functions/create_survival_plot.R") # Function used to create survival plots
source("functions/create_expression_groups.R") # Function used to divide samples based on expression percentile thresholds
source("functions/get_survival.R") # Function used to calculate survival probabilities
```

## Libraries
```{r, eval = FALSE}
  library(survival)
  library(KMsurv)
  library(svglite)
  library(WriteXLS)
```

# Survival analysis per cancer type

## Kaplan-Meier

```{r, message=F, warning=F, eval = FALSE}

    # Get cancers for which all expression data available: 17 in total
    cancers<- sort(names(table(TCGA_cancer_id[names(RP3_expr),1])))

    # Set expression th
    th1<- 0.1
    th2<- 1-th1

    p_vals<- NULL      
    # Create plots
  for(plot_format in 1:2){
    if(plot_format==1) pdf("figs/lncRNA_survival_KM.pdf",width = 17,height = 24)
    else svglite("figs/lncRNA_survival_KM.svg",width = 17,height = 24)
    par(mfrow=c(9,6))
    for(cancer in cancers){
      samples_cancer<- rownames(TCGA_cancer_id)[TCGA_cancer_id[,1]==cancer]

      # Mutation only for TP53
      TCGA_TP53_hasNonsynMut_temp<- TCGA_TP53_hasNonsynMut[names(TCGA_TP53_hasNonsynMut)%in%samples_cancer]
      names(TCGA_TP53_hasNonsynMut_temp)<- substr(names(TCGA_TP53_hasNonsynMut_temp),1,12)
      clin_class<- cbind(TCGA_clin_surv,TCGA_TP53_hasNonsynMut_temp[rownames(TCGA_clin_surv)])
      n1<- sum(clin_class[,3]==FALSE,na.rm=T)
      n2<- sum(clin_class[,3]==TRUE,na.rm=T)
      if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0) plot.new() # No use if no motation information
      else p1<- create_survival_plot(clinical_data = clin_class,classes_to_compare = c(FALSE,TRUE),classnames=c(paste("TP53 WT (n=",n1,")",sep=""),paste("TP53 MUT (n=",n2,")",sep="")),plot_title =  cancer,save_plot = TRUE,add_to_existing_plot = TRUE, plot_cols = c("black","black"), plot_lty = 1:2,return_p = TRUE)

    # Expr + Mutation
    for(i in 1:2){
      expr<- list(RP3_expr,miR34a_expr)[[i]]
      gene<- c("miR34a asRNA","miR34a")[i]
      # for(isMut in c(F,T)){
      isMut=FALSE
        samples_cancer_sel<- intersect(names(TCGA_TP53_hasNonsynMut)[TCGA_TP53_hasNonsynMut==isMut],samples_cancer)
        expr_temp<- expr[names(expr)%in%samples_cancer_sel]
        class<- create_expression_groups(expr_temp,gene,th=c(th1,th2))
        names(class)<- substr(names(class),1,12)
        class[class==3]<- 2
        clin_class<- cbind(TCGA_clin_surv[names(class),],class)
        if(sum(!is.na(clin_class[,3]))==0) next
        n1<- sum(clin_class[,3]==1,na.rm=T)
        n2<- sum(clin_class[,3]==2,na.rm=T)
        n3<- sum(clin_class[,3]==3,na.rm=T)
        # if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0|n1==0|n2==0|n3==0) plot.new()
        if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0|n1==0|n2==0) plot.new()
        else px<- create_survival_plot(clinical_data = clin_class,classes_to_compare = c(1,2),classnames=c(paste("Low expression (<P",100*th1," - n=",n1,")",sep=""),paste( "Normal expression (>P",100*th1," - n=",n2,")",sep="")),plot_title = paste(cancer,gene,sep=" "),save_plot = TRUE,add_to_existing_plot = TRUE,plot_cols = c("black","red"), plot_lty=rep(1+isMut,2),return_p = TRUE)
      # }
        if(i==1) p2<- px
        if(i==2) p3<- px
    }
      p_vals<- cbind(p_vals,c(p1,p2,p3))
    }
    dev.off()
  }

  p_vals<- p_vals[,1:17]
  colnames(p_vals)<- cancers
  rownames(p_vals)<- c("TP53","miR34a_asRNA","miR34a")
```

## 5y survival probabilities

```{r, message=F, warning=F, eval = FALSE}

# Create correlation matrix
common_samples<- intersect(names(TCGA_TP53_hasNonsynMut),names(RP3_expr))
correlation_matrix<- cbind(RP3=RP3_expr[common_samples],miR34a=miR34a_expr[common_samples],TP53=TCGA_TP53_hasNonsynMut[common_samples],cancer=TCGA_cancer_id[common_samples,1])

n_years<- 5

# Get surv probs
cancers<- sort(unique(correlation_matrix[,"cancer"]))
survProb_ls<- list()

# Independent
for(gene in c("RP3","miR34a","TP53")){
  cat(gene,"\n")
  surv_matrix<- matrix(NA,3,length(cancers),dimnames = list(1:3,cancers))
  for(cancer in cancers){
    correlation_matrix_temp<- correlation_matrix[correlation_matrix[,"cancer"]==cancer,]
    if(gene!="TP53") correlation_matrix_temp<- cbind(correlation_matrix_temp,class=create_expression_groups(t(correlation_matrix_temp),gene,th=c(0.1,0.9)))
    else correlation_matrix_temp<- cbind(correlation_matrix_temp,class=as.numeric(correlation_matrix_temp[,gene]=="TRUE")+1) 
    for(i in 1:2){
      if(i==1) samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]==i]
      else samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]%in%c(2,3)]
      if(length(samples_sel)<=1) next
      surv_data<- TCGA_clin_surv[rownames(TCGA_clin_surv)%in%substr(samples_sel,1,12),]
      survProb<- get_survival(surv_data,n_years)
      if(length(survProb)==0) next
      surv_matrix[i,cancer]<- survProb
    }
  }
  survProb_ls[gene]<- list(surv_matrix)
}

# TP53 status dependent
for(gene in c("RP3","miR34a")){
  cat(gene,"\n")
  for(mut in c(0,1)){
    surv_matrix<- matrix(NA,3,length(cancers),dimnames = list(1:3,cancers))
    for(cancer in cancers){
      correlation_matrix_temp<- correlation_matrix[correlation_matrix[,"cancer"]==cancer&as.numeric(correlation_matrix[,"TP53"]=="TRUE")==mut,,drop=F]
      if(nrow(correlation_matrix_temp)<=1) next
      correlation_matrix_temp<- cbind(correlation_matrix_temp,class=create_expression_groups(t(correlation_matrix_temp),gene,th=c(0.1,0.9)))
      for(i in 1:2){
        if(i==1) samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]==i]
        else samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]%in%c(2,3)]
        if(length(samples_sel)<=1) next
        surv_data<- TCGA_clin_surv[rownames(TCGA_clin_surv)%in%substr(samples_sel,1,12),]
        survProb<- get_survival(surv_data,n_years)
        if(length(survProb)==0) next
        surv_matrix[i,cancer]<- survProb
      }
    }
    survProb_ls[paste(gene,mut,sep="_")]<- list(surv_matrix)
  }
}

# Remove NA!
survProb_ls[["RP3"]]<- survProb_ls[["RP3"]][,!is.na(survProb_ls[["RP3"]][1,])&!is.na(survProb_ls[["RP3"]][2,])]
survProb_ls[["miR34a"]]<- survProb_ls[["miR34a"]][,!is.na(survProb_ls[["miR34a"]][1,])&!is.na(survProb_ls[["miR34a"]][2,])]
survProb_ls[["TP53"]]<- survProb_ls[["TP53"]][,!is.na(survProb_ls[["TP53"]][1,])&!is.na(survProb_ls[["TP53"]][2,])]
survProb_ls[["RP3_0"]]<- survProb_ls[["RP3_0"]][,!is.na(survProb_ls[["RP3_0"]][1,])&!is.na(survProb_ls[["RP3_0"]][2,])]
survProb_ls[["RP3_1"]]<- survProb_ls[["RP3_1"]][,!is.na(survProb_ls[["RP3_1"]][1,])&!is.na(survProb_ls[["RP3_1"]][2,])]
survProb_ls[["miR34a_0"]]<- survProb_ls[["miR34a_0"]][,!is.na(survProb_ls[["miR34a_0"]][1,])&!is.na(survProb_ls[["miR34a_0"]][2,])]
survProb_ls[["miR34a_1"]]<- survProb_ls[["miR34a_1"]][,!is.na(survProb_ls[["miR34a_1"]][1,])&!is.na(survProb_ls[["miR34a_1"]][2,])]
# 
# for(plot_format in 1:2){
#   if(plot_format==1) pdf("figs/lncRNA_5ySurv_expr.pdf",width = 14, height = 14)
#   else svglite("figs/lncRNA_5ySurv_expr.svg",width = 14, height = 14)
# 
#   par(mfrow=c(2,1))
# 
#   boxplot(list(
#     survProb_ls[["RP3"]][1,],survProb_ls[["RP3"]][2,],NA,
#     survProb_ls[["miR34a"]][1,],survProb_ls[["miR34a"]][2,],NA,
#     survProb_ls[["TP53"]][2,],survProb_ls[["TP53"]][1,]),
#     outline=F,ylab=paste(n_years,"y survival probability",sep=""),frame.plot=F,axes=F,col=c("lightgrey",NA,NA,"lightgrey",NA,NA,"darkgrey",NA)
#   )
#   axis(2)
#   text(1.5,1,paste("P=",signif(wilcox.test(survProb_ls[["RP3"]][1,],survProb_ls[["RP3"]][2,],paired=T)$p.value,3),sep=""))
#   text(4.5,1,paste("P=",signif(wilcox.test(survProb_ls[["miR34a"]][1,],survProb_ls[["miR34a"]][2,],paired=T)$p.value,3),sep=""))
#   text(7.5,1,paste("P=",signif(wilcox.test(survProb_ls[["TP53"]][1,],survProb_ls[["TP53"]][2,],paired=T)$p.value,3),sep=""))
#   text(1.5,1.05,"miR34a asRNA",xpd=NA)
#   text(4.5,1.05,"miR34a",xpd=NA)
#   text(7.5,1.05,"TP53",xpd=NA)
#   legend("bottom",horiz = T,legend = c("Control","Low expression (<P10)","Mutated"),fill = c("white","lightgrey","darkgrey"),bty="n")
#   
#   boxplot(list(
#     survProb_ls[["RP3_0"]][1,],survProb_ls[["RP3_0"]][2,],NA,
#     survProb_ls[["RP3_1"]][1,],survProb_ls[["RP3_1"]][2,],NA,
#     survProb_ls[["miR34a_0"]][1,],survProb_ls[["miR34a_0"]][2,],NA,
#     survProb_ls[["miR34a_1"]][1,],survProb_ls[["miR34a_1"]][2,]),
#     outline=F,ylab=paste(n_years,"y survival probability",sep=""),frame.plot=F,axes=F,col=c("lightgrey",NA,NA,"lightgrey",NA,NA,"lightgrey",NA,NA,"lightgrey",NA)
#   )
#   axis(2)
#   text(1.5,1,signif(wilcox.test(survProb_ls[["RP3_0"]][1,],survProb_ls[["RP3_0"]][2,],paired=T)$p.value,3))
#   text(4.5,1,signif(wilcox.test(survProb_ls[["RP3_1"]][1,],survProb_ls[["RP3_1"]][2,],paired=T)$p.value,3))
#   text(7.5,1,signif(wilcox.test(survProb_ls[["miR34a_0"]][1,],survProb_ls[["miR34a_0"]][2,],paired=T)$p.value,3))
#   text(10.5,1,signif(wilcox.test(survProb_ls[["miR34a_1"]][1,],survProb_ls[["miR34a_1"]][2,],paired=T)$p.value,3))
#   text(3,1.1,"miR34a asRNA",xpd=NA)
#   text(1.5,1.05,"TP53 wt",xpd=NA)
#   text(4.5,1.05,"TP53 mut",xpd=NA)
#   text(9,1.1,"miR34a",xpd=NA)
#   text(7.5,1.05,"TP53 wt",xpd=NA)
#   text(10.5,1.05,"TP53 mut",xpd=NA)
#   legend("bottom",horiz = T,legend = c("Control","Low expression (<P10)"),fill = c("white","lightgrey"),bty="n")
#   
#   dev.off()
# }

# Correlation between survival
 cancer_colors<- c(
  rgb(0.498,0.498,0.498),
  rgb(0.7804,0.7804,0.7804),
  rgb(0.1216,0.4667,0.7059),
  rgb(0.1216,0.4667,0.7059),
  rgb(0.6824,0.7804,0.9098),
  rgb(0.0902,0.7451,0.8118),
  rgb(0.6196,0.8941,0.898),
  rgb(1,0.498,0.0549),
  rgb(1,0.7333,0.4706),
  rgb(0.8392,0.1529,0.1569),
  rgb(1,0.5961,0.5882),
  rgb(0.5804,0.4039,0.7412),
  rgb(0.7725,0.6118,0.7961),
  rgb(0.8902,0.4667,0.7608),
  rgb(0.9686,0.7137,0.8235),
  rgb(0.549,0.3373,0.2941),
  rgb(0.7686,0.6118,0.5804),
  rgb(0.1725,0.6275,0.1725),
  rgb(0.5961,0.8745,0.5412),
  rgb(0.7373,0.7412,0.1333),
  rgb(0.8588,0.8824,0.5529),
  rgb(0.9294,0.8,0.0588),
  rgb(1,0.9255,0)
)
  names(cancer_colors)<- c('ACC','BLCA','BRCA','BRCA Basal','BRCA Her2','BRCA LumA','BRCA LumB','CESC','GBM','HNSC','KICH','KIRC','KIRP','LGG','LIHC','LUAD','LUSC','OV','PRAD','SKCM','STAD','THCA','UCS')

for(plot_format in 1:2){
  if(plot_format==1) pdf("figs/lncRNA_5ySurv_expr_corr.pdf",width = 14, height = 7)
  else svglite("figs/lncRNA_5ySurv_expr_corr.svg",width = 21, height = 7)

  par(mfrow=c(1,3))

  # Focus on WT group only!
  survProb_rel_RP3<- survProb_ls[["RP3_0"]][1,]-survProb_ls[["RP3_0"]][2,]
  survProb_rel_miR34a<- survProb_ls[["miR34a_0"]][1,]-survProb_ls[["miR34a_0"]][2,]
  survProb_rel_TP53<- survProb_ls[["TP53"]][2,]-survProb_ls[["TP53"]][1,]

  for(i in 1:3){
    x_param_name<- c("TP53","miR34a_asRNA","miR34a")[i]
    x_param<- list(survProb_rel_TP53,survProb_rel_RP3,survProb_rel_miR34a)[[i]]
    y_param_name<- c("miR34a_asRNA","miR34a","TP53")[i]
    y_param<- list(survProb_rel_RP3,survProb_rel_miR34a,survProb_rel_TP53)[[i]]
    common_cancers<- intersect(names(x_param),names(y_param))
    x_param<- x_param[common_cancers]
    y_param<- y_param[common_cancers]
    plot(x_param,y_param,frame.plot=F,xlim=c(-1,+1),ylim=c(-1,+1),xlab=x_param_name,ylab=y_param_name)  
    boxplot(y_param,at = 0.75,add=T,frame.plot=F,outline=F,boxwex=0.2)
    boxplot(x_param,at = 0.75,add=T,frame.plot=F,outline=F,horizontal = T,boxwex=0.2)
    p_temp<- signif(cor.test(x_param,y_param,method = "spearman")$p.value,3)
    r_temp<- signif(cor.test(x_param,y_param,method = "spearman")$estimate,3)
    legend("topleft",legend = c(paste("P=",p_temp,sep=""),paste("r=",r_temp,sep="")),bty="n")
    for(cancer in common_cancers){
      points(x_param[cancer],y_param[cancer],col=cancer_colors[cancer],pch=16,cex=2)
    }
    # abline(h=0,v=0,lty=2)
  }
  dev.off()
}

  # Survival effects
  median(survProb_rel_RP3) # -0.096
  median(survProb_rel_miR34a) # -0.068
  median(survProb_rel_TP53) # -0.064
  wilcox.test(survProb_rel_RP3) # p=0.083
  wilcox.test(survProb_rel_miR34a) # p=0.17
  wilcox.test(survProb_rel_TP53) # p=0.04

```

### 2017-12-14 R/utils.R

@@ -36,7 +36,9 @@ fileMap <- function(type) {
     `Figure 3b` = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
     `Figure 3c` = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
     `Figure 3d` = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
-    `Figure 3e` = "tcga_survival/tcga_survival.Rmd",
+    `Figure 4a` = "tcga_survival/tcga_survival.Rmd",
+    `Figure 4b` = "tcga_survival/tcga_survival.Rmd",
+    `Figure 5` = "model/model.Rmd",
     `Figure 1-Supplement 1a` = "tcga_correlation_table/tcga_correlation_table.Rmd",
     `Figure 1-Supplement 1b` = "tcga_expression/tcga_expression.Rmd",
     `Figure 1-Supplement 2a` = "primer_walk_schematic/primer_walk_schematic.Rmd",
@@ -50,6 +52,7 @@ fileMap <- function(type) {
     `Figure 3-Supplement 1` = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
     `Figure 3-Supplement 2a` = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
     `Figure 3-Supplement 2b` = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
+    `Figure 4-Supplement 1` = "tcga_survival_total/tcga_survival_total.Rmd",
     `Supplementary Document 1a` = "lnc34a_cage/lnc34a_cage.Rmd",
     `Supplementary Document 1b` = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd",
     `Supplementary Document 1` = "lnc34a/lnc34a.Rmd",

### 2017-12-14 R/survival.R
adding jimmy's survival functions

@@ -1,0 +1,84 @@
+create_survival_plot<- function(clinical_data,classes_to_compare=NULL,classnames=NULL,filename="survival.pdf",save_plot=FALSE,add_to_existing_plot=FALSE,plot_title=NULL,plot_cols=NULL,plot_lty=NULL,return_p=FALSE){
+  
+  # Check
+  if(length(classes_to_compare)!=length(classnames)) stop("Lengths of classes to compare different from classnames")
+  
+  # Load libraries
+  library(survival)
+  library(KMsurv)
+  
+  # Rename colnames
+  colnames(clinical_data)<- c("vital_state","FU","class")
+  if(is.null(classes_to_compare)){
+    classes_to_compare<- na.omit(unique(clinical_data[,"class"]))
+    classnames<- paste("class ",classes_to_compare,sep="")
+  }
+  classnames<- classnames[order(classes_to_compare)]
+  classes_to_compare<- sort(classes_to_compare)
+  
+  # Select classes
+  clin_sel<- clinical_data[clinical_data[,"class"]%in%classes_to_compare,]
+  
+  # Survival parameters
+  Death<- as.numeric(clin_sel[,"vital_state"]=="dead")
+  FU<- as.numeric(clin_sel[,"FU"])
+  FU[is.infinite(FU)]<-NA
+  FU<- FU/365.25
+  class<- clin_sel[,"class"]
+  
+  # Survival tables
+  surv_table<-cbind(FU,Death,class)
+  surv_table<-na.omit(surv_table[!is.infinite(surv_table[,1]),])
+  attach(as.data.frame(surv_table))
+  my.surv.object<-Surv(FU, Death) # Create survival object
+  my.fit<-survfit(my.surv.object ~ class) # Fit
+  
+  # Plot
+  classes_with_data<- which(classes_to_compare%in%gsub("class=","",names(my.fit$strata))) # Otherwise problems if no data
+  if(save_plot==FALSE) x11()
+  else if(add_to_existing_plot==FALSE) pdf(file=filename)
+  else NA
+  if(is.null(plot_cols)){
+    plot(my.fit,col=classes_with_data,xlim=c(0,5),xlab="time (years)",ylab="Survival Probability",main=plot_title,frame=FALSE) # Plot
[…]

### 2018-02-12 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
removing violin and updating for lncTAM34a name change for hct116_hek293t_dox

@@
 groups <- c("Treatment", "Biological Replicate", "Cell line", "gene")
-gois <- c("miR34a asRNA", "miR34a HG")
+gois <- c("lncTAM34a", "miR34a HG")
 
@@
     x = case_when(
-      GOI == "miR34a asRNA" ~ 1 - 0.25,
+      GOI == "lncTAM34a" ~ 1 - 0.25,
       GOI ==    "miR34a HG" ~ 1 + 0.25
@@
     xend = case_when(
-      GOI == "miR34a asRNA" ~ 2 - 0.25,
+      GOI == "lncTAM34a" ~ 2 - 0.25,
       GOI ==    "miR34a HG" ~ 2 + 0.25
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = Treatment,
-      y = log2fold,
-      group = interaction(GOI, Treatment)
-    ),
-    trim = TRUE,
-    fill = "gray",
-    alpha = 0.3,
-    color = NA,
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 53,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 53,
+   units = "mm"
+)
 ```

### 2018-02-12 inst/hct116_p53_null/hct116_p53_null.Rmd
many rushed last minute changes
removing violin and updating for lncTAM34a name change for hct116_p53_null

@@
 
-library(grDevices)
+#library(grDevices)
 ```
@@
 groups <- c("Condition", "Treatment", "Biological Replicate", "Cell line", "gene")
-gois <- c("miR34a asRNA", "miR34a HG")
+gois <- c("lncTAM34a", "miR34a HG")
 
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = Treatment, 
-      y = log2fold,
-      group = interaction(Condition, Treatment)
-    ),
-    trim = TRUE,
-    alpha = 0.3,
-    fill = "gray",
-    colour = NA,
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(

### 2018-02-12 data-raw/saveRDS.R
updating raw data and data for p1_hct116_hek293t with lncTAM34a name

@@ -68,6 +68,7 @@ read_tsv('./data-raw/p1_hct116_hek293t.txt', col_names = TRUE) %>%
     ),
     construct = gsub("empty", "Empty", .data$construct)
   ) %>%
+  mutate(alias = if_else(alias == "miR34a asRNA", "lncTAM34a", alias)) %>%
   write_rds(., path = './data/p1_hct116_hek293t.rds')
 
 #p1_shrna_renilla_dox

### 2018-02-12 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
fixing some rmd typos
removing violin and updating name to lncTAM34a for p1_hct116_hek293t

@@
 
-*For a schematic representation of the P1 construct please see Figure 2c.
+*For a schematic representation of the P1 construct please see Figure 2-Supplement 1a-b.
 
@@
     gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
-    gene == "Renilla"    ~ "        Renilla\n(miR34a asRNA)",
+    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
     TRUE ~ "somehow missed a gene"
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = construct,
-      y = logValue,
-      group = interaction(construct, plotGene)
-    ),
-    trim = TRUE,
-    alpha = 0.3,
-    fill = "gray",
-    color = NA,
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(

### 2018-02-12 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
removing violin and name change to lncTAM34a for p1_shrna_renilla_dox

@@
     GOI == "Luciferase" ~ " Luciferase\n(miR34a HG)",
-    GOI == "Renilla" ~ "  Renilla\n(miR34a asRNA)"
+    GOI == "Renilla" ~ "Renilla\n(lncTAM34a)"
+  )) %>%
+  mutate(plotGOI = factor(
+    plotGOI, 
+    levels = c("Renilla\n(lncTAM34a)", " Luciferase\n(miR34a HG)")
   ))
@@
     GOI == "Luciferase" ~ " Luciferase\n(miR34a HG)",
-    GOI == "Renilla" ~ "  Renilla\n(miR34a asRNA)"
+    GOI == "Renilla" ~ "Renilla\n(lncTAM34a)"
+  )) %>%
+  mutate(plotGOI = factor(
+    plotGOI, 
+    levels = c("Renilla\n(lncTAM34a)", " Luciferase\n(miR34a HG)")
   )) %>%
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
-
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = treatment, 
-      y = log2fold, 
-      group = interaction(shRNA, treatment)
-    ),
-    trim = TRUE,
-    scale = "width",
-    alpha = 0.3,
-    colour = NA,
-    fill = "gray",
-    show.legend = FALSE
-  ) +
   geom_dotplot(
@@
   )
+
 markdown <- p + 
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 100,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 100,
+   units = "mm"
+)
 ```

### 2018-02-12 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
missed one on last commit

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 100,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 100,
+#    units = "mm"
+# )
 ```

### 2018-02-12 data-raw/saveRDS.R
fixing lncTAM34a name in data-raw and data for stable_line_cell_cycle

@@ -122,10 +122,10 @@ read_tsv('./data-raw/stable_line_cell_cycle.txt', col_names = TRUE) %>%
     `Cell line` = cellLine
   ) %>%
   mutate(
-    condition = gsub("miR34a AS", "miR34a asRNA", .data$condition)
+    condition = gsub("miR34a AS", "lncTAM34a", .data$condition)
   ) %>%
   mutate(
-    condition = parse_factor(condition, levels = c("mock", "miR34a asRNA")),
+    condition = parse_factor(condition, levels = c("mock", "lncTAM34a")),
     phase = parse_factor(phase, levels = c("G1", "S", "G2"))
   ) %>%
   write_rds(., path = './data/stable_line_cell_cycle.rds')

### 2018-02-12 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
removing violin and fixing names for stable_line_cell_cycle

@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = phase, 
-      y = value,
-      group = interaction(phase, condition)
-    ),
-    scale = "width",
-    alpha = 0.3,
-    fill = "gray",
-    weight = 10,
-    trim = TRUE,
-    color = NA,
-    show.legend = FALSE
-  ) +
   geom_dotplot(

### 2018-02-12 data-raw/saveRDS.R
fixing name lncTAM34a in stable_line_expression data and raw data

@@ -94,8 +94,8 @@ read_tsv('./data-raw/stable_line_expression.txt', col_names = TRUE) %>%
     `Genetic mod` = `Sample Name`
   ) %>%
   mutate(
-    `Genetic mod` = gsub("miR34a AS", "miR34a asRNA", .data$`Genetic mod`),
-    gene = gsub("miR34a asRNA F1R1", "miR34a asRNA", .data$gene),
+    `Genetic mod` = gsub("miR34a AS", "lncTAM34a", .data$`Genetic mod`),
+    gene = gsub("miR34a asRNA F1R1", "lncTAM34a", .data$gene),
     gene = gsub("B-actin", "Actin", .data$gene)
   ) %>%
   mutate(
@@ -105,11 +105,11 @@ read_tsv('./data-raw/stable_line_expression.txt', col_names = TRUE) %>%
     ),
     `Genetic mod` = parse_factor(
       `Genetic mod`,
-      levels = c("mock", "miR34a asRNA")
+      levels = c("mock", "lncTAM34a")
     ),
     gene = parse_factor(
       gene,
-      levels = c("miR34a asRNA", "miR34a", "Actin", "RNU48")
+      levels = c("lncTAM34a", "miR34a", "Actin", "RNU48")
     )
   ) %>%
   write_rds(., path = './data/stable_line_expression.rds')
@@ -199,9 +199,9 @@ read_tsv('./data-raw/stable_line_expression_hek293t.txt', col_names = TRUE) %>%
     gene = Gene
   ) %>%
   mutate(
-    Condition = gsub("F4", "miR34a\nasRNA", Condition),
+    Condition = gsub("F4", "lncTAM34a", Condition),
     gene = gsub("B-actin", "Actin", gene),
-    gene = gsub("miR34a asRNA F1R1", "miR34a asRNA", gene)
+    gene = gsub("miR34a asRNA F1R1", "lncTAM34a", gene)
   ) %>%
   mutate(
     `Cell line` = parse_factor(
@@ -210,7 +210,7 @@ read_tsv('./data-raw/stable_line_expression_hek293t.txt', col_names = TRUE) %>%
     ),
     Condition = parse_factor(
       Condition,
-      levels = c("wt", "mock", "miR34a\nasRNA")
+      levels = c("wt", "mock", "lncTAM34a")
     )
   ) %>%
   write_rds(., path = './data/stable_line_expression_hek293t.rds')

### 2018-02-12 inst/stable_line_expression/stable_line_expression.Rmd
removing violin and changing name to lncTAM34a for stable_line_expression

@@
 #keeping genes.
-gois1 <- c("miR34a asRNA", "Actin")
+gois1 <- c("lncTAM34a", "Actin")
 gois2 <- c("miR34a", "RNU48")
@@
 data <- bind_rows(data1, data2) %>%
-  mutate(GOI = parse_factor(GOI, levels = c("miR34a asRNA", "miR34a")))
+  mutate(GOI = parse_factor(GOI, levels = c("lncTAM34a", "miR34a")))
 
@@
 #format for plotting
-lev <- c("mock", "miR34a asRNA", "Skov3\nmock", "Skov3\nmiR34a asRNA", "Saos2\nmock",   "Saos2\nmiR34a asRNA")
+lev <- c("mock", "lncTAM34a", "Skov3\nmock", "Skov3\nlncTAM34a", "Saos2\nmock",   "Saos2\nlncTAM34a")
 
-data <- data %>%
-  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
-  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
+#data <- data %>%
+#  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
+#  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
 
-stats <- stats %>%
-  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
-  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
+#stats <- stats %>%
+#  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
+#  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
 
@@
       GOI ==    "miR34a" ~ 1 + 0.25,
-      GOI == "miR34a asRNA" ~ 1 - 0.25
+      GOI == "lncTAM34a" ~ 1 - 0.25
     ),
@@
       GOI ==    "miR34a" ~ 2 + 0.25,
-      GOI == "miR34a asRNA" ~ 2 - 0.25
+      GOI == "lncTAM34a" ~ 2 - 0.25
     )
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = `Genetic mod`,
-      y = log2fold,
-      group = interaction(`Genetic mod`, GOI)
-    ),
-    trim = TRUE,
-    alpha = 0.5,
-    fill = "grey",
-    colour = NA,
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(

### 2018-02-12 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
fixing name change to lncTAM34a and removing violin for stable_line_expression_hek293t

@@
 groups <- c("Condition", "Biological Replicate", "Cell line", "gene")
-gois <- c("miR34a asRNA")
+gois <- c("lncTAM34a")
 
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12}
-
 p <- ggplot(data = NULL)+
-  geom_violin(
-    data = data,
-    aes(
-      x = Condition,
-      y = log2fold
-    ),
-    scale = "width",
-    trim = TRUE,
-    alpha = 0.3,
-    color = NA,
-    fill = "gray",
-    show.legend = FALSE
-  ) +
   geom_dotplot(
@@
 #   height = 60,
-#   width = 130,
+#   width = 160,
 #   units = "mm"

### 2018-02-12 data-raw/saveRDS.R
fixing data and raw data with new name for stable_line_pol2_chip

@@ -167,14 +167,14 @@ read_tsv('./data-raw/stable_line_pol2_chip.txt', col_names = TRUE) %>%
     `Cell line` = cellLine
   ) %>%
   mutate(
-    condition = gsub("miR34a AS", "PC3 miR34a asRNA", .data$condition),
+    condition = gsub("miR34a AS", "PC3 lncTAM34a", .data$condition),
     condition = gsub("mock", "PC3 mock", .data$condition),
-    gene = gsub("miR34a AS", "miR34a asRNA", .data$gene)
+    gene = gsub("miR34a AS", "lncTAM34a", .data$gene)
   ) %>%
   mutate(
     condition = parse_factor(
       condition,
-      levels = c("PC3 mock", "PC3 miR34a asRNA")
+      levels = c("PC3 mock", "PC3 lncTAM34a")
     )
   ) %>%
   write_rds(., path = './data/stable_line_pol2_chip.rds')

### 2018-02-12 data-raw/saveRDS.R
fixing data and raw data with new name for stable_line_pol2_chip again

@@ -167,14 +167,14 @@ read_tsv('./data-raw/stable_line_pol2_chip.txt', col_names = TRUE) %>%
     `Cell line` = cellLine
   ) %>%
   mutate(
-    condition = gsub("miR34a AS", "PC3 lncTAM34a", .data$condition),
-    condition = gsub("mock", "PC3 mock", .data$condition),
+    condition = gsub("miR34a AS", "lncTAM34a", .data$condition),
+    condition = gsub("mock", "mock", .data$condition),
     gene = gsub("miR34a AS", "lncTAM34a", .data$gene)
   ) %>%
   mutate(
     condition = parse_factor(
       condition,
-      levels = c("PC3 mock", "PC3 lncTAM34a")
+      levels = c("mock", "lncTAM34a")
     )
   ) %>%
   write_rds(., path = './data/stable_line_pol2_chip.rds')

### 2018-02-12 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
fixing lncTAM34a and violin in analysis for stable_line_pol2_chip

@@
 ```{r, message = FALSE}
-
 url <- fileMap(type = "rds")["Figure 3d"][[1]]
@@
   bool1 <- data$`Biological Replicate` == 3
-  bool2 <- data$condition == "PC3 mock"
+  bool2 <- data$condition == "mock"
   bool <- bool1 & bool2
@@
   mutate(pFormat = case_when(
-    condition == "PC3 mock" ~ "", 
+    condition == "mock" ~ "", 
     TRUE ~ pFormat
   ))
-
-#prepare for plotting
-data <- data %>%
-  mutate(
-    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
-    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
-  )
-
-stats <- stats %>%
-  mutate(
-    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
-    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
-  )
 ```
@@
 ```{r, fig.align='center', fig.height=8, fig.width=12}
-
-p <- ggplot(data = NULL)+
-  geom_violin(
-    data = data,
-    aes(
-      x = condition,
-      y = logfoldOverControl,
-      group = condition
-    ),
-    trim = TRUE,
-    alpha = 0.3,
-    colour = NA,
-    fill = "gray",
-    show.legend = FALSE
-  ) +
+p <- ggplot(data = NULL) +
   geom_dotplot(
@@
   geom_segment(
-    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
+    data = filter(stats, condition == "lncTAM34a"),
     aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),

### 2018-02-12 inst/p1_hek293t/p1_hek293t.Rmd
fixing analysis with lncTAM34a name, removing violin, adding CI and mean, for p1_hek293t

@@
   %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
+editor_options: 
+  chunk_output_type: console
 ---
@@
   folds(.)
+
+#calculate stats
+stats <- data %>%
+  group_by(shRNA, belongsTo, GOI) %>%
+  summarize(
+    mean = mean(log2fold),
+    CI95l = t.test(log2fold)$conf.int[1],
+    CI95h =  t.test(log2fold)$conf.int[2]
+  )
 ```
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = shRNA,
-      y = log2fold,
-      group = interaction(shRNA, GOI)
-    ),
-    trim = TRUE,
-    alpha = 0.5,
-    fill = "grey",
-    colour = NA,
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(
@@
 plotRmarkdown(p) +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = shRNA, 
+      ymin = CI95l, 
+      ymax = CI95h, 
+      group = GOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = shRNA, 
+      y = mean, 
+      group = GOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    shape = 95,
+    size = 6,
+    show.legend = FALSE
+  ) +
   theme(
@@
 figure <- plotPDF(p) +
+  geom_linerange(
+    data = stats,
+    aes(
+      x = shRNA, 
+      ymin = CI95l, 
+      ymax = CI95h, 
+      group = GOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    show.legend = FALSE
+  ) +
+  geom_point(
+    data = stats,
+    aes(
+      x = shRNA, 
+      y = mean, 
+      group = GOI
+    ),
+    colour = "gray20",
+    position = position_dodge(width = 0.9),
+    shape = 95,
+    size = 6,
+    show.legend = FALSE
+  ) +
   theme(
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2-Supplement 2"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 83,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2-Supplement 2"][[1]])
+ggsave(
+   plot = figure,
+   filename = path,
+   device = cairo_pdf,
+   height = 60,
+   width = 83,
+   units = "mm"
+)
 ```

### 2018-02-12 inst/p1_hek293t/p1_hek293t.Rmd
fixing analysis with lncTAM34a name, removing violin, adding CI and mean, for p1_hek293t, again

@@
     ),
-    colour = "gray20",
+    colour = "grey30",
     position = position_dodge(width = 0.9),
+    size = 0.3,
     show.legend = FALSE
@@
     ),
-    colour = "gray20",
+    colour = "grey30",
     position = position_dodge(width = 0.9),
     shape = 95,
-    size = 6,
+    size = 4,
     show.legend = FALSE

### 2018-02-14 data-raw/saveRDS.R
data and raw-data name change for stable_line_ccnd1_exp

@@ -223,14 +223,14 @@ read_tsv('./data-raw/stable_line_ccnd1_exp.txt', col_names = TRUE) %>%
     `Cell line` = cellLine
   ) %>%
   mutate(
-    condition = gsub("miR34a AS", "PC3 miR34a\nasRNA", condition),
-    condition = gsub("mock", "PC3 mock", condition),
+    condition = gsub("miR34a AS", "lncTAM34a ", condition),
+    condition = gsub("mock", "mock", condition),
     gene = gsub("B-actin", "Actin", gene)
   ) %>%
   mutate(
     condition = parse_factor(
       condition,
-      levels = c("PC3 mock", "PC3 miR34a\nasRNA")
+      levels = c("mock", "lncTAM34a")
     )
   ) %>%
   write_rds(., path = './data/stable_line_ccnd1_exp.rds')

### 2018-02-14 inst/p1_hek293t/p1_hek293t.Rmd
removing violin and name change for stable_line_ccnd1_exp

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2-Supplement 2"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 83,
-   units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2-Supplement 2"][[1]])
+# ggsave(
+#    plot = figure,
+#    filename = path,
+#    device = cairo_pdf,
+#    height = 60,
+#    width = 83,
+#    units = "mm"
+# )
 ```

### 2018-02-14 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
removing violin and name change for stable_line_ccnd1_exp

@@
 logical <- tibble(
-  condition = pull(data, condition) == "PC3 mock"
+  condition = pull(data, condition) == "mock"
 )
@@
 #calculate stats
-stats <- calcStats(data, condition, "PC3 mock", groups) %>%
+stats <- calcStats(data, condition, "mock", groups) %>%
   pFormat(.)
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = condition,
-      y = log2fold
-    ),
-    trim = TRUE,
-    alpha = 0.3,
-    color = NA,
-    fill = "gray",
-    scale = "width"
-  ) +
   geom_dotplot(
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
-# ggsave(
-#   plot = figure,
-#   filename = path,
-#   device = cairo_pdf,
-#   height = 60,
-#   width = 43,
-#   units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
+ggsave(
+  plot = figure,
+  filename = path,
+  device = cairo_pdf,
+  height = 60,
+  width = 43,
+  units = "mm"
+)
 ```

### 2018-02-14 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
removing violin and name change for stable_line_ccnd1_exp2

@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
-ggsave(
-  plot = figure,
-  filename = path,
-  device = cairo_pdf,
-  height = 60,
-  width = 43,
-  units = "mm"
-)
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3-Supplement 2a"][[1]])
+# ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 43,
+#   units = "mm"
+# )
 ```

### 2018-02-14 data-raw/saveRDS.R
name change in data and raw data for stable_line_ccnd1_prot

@@ -240,12 +240,12 @@ print("processing stable_line_ccnd1_prot")
 read_tsv('./data-raw/stable_line_ccnd1_prot.txt', col_names = TRUE) %>%
   rename(`Biological Replicate` = experiment) %>%
   mutate(
-    condition = gsub("miR34a AS", "PC3 miR34a\nasRNA", condition),
-    condition = gsub("mock", "PC3 mock", condition)
+    condition = gsub("miR34a AS", "lncTAM34a", condition),
+    condition = gsub("mock", "mock", condition)
   ) %>%
   mutate(condition = parse_factor(
     condition,
-    levels = c("PC3 mock", "PC3 miR34a\nasRNA")
+    levels = c("mock", "lncTAM34a")
   )) %>%
   write_rds(., path = './data/stable_line_ccnd1_prot.rds')
 

### 2018-02-14 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
name change and remove violin for stable_line_ccnd1_prot

@@
 #normalize to mock
-cnt <- filter(data, condition == "PC3 mock") %>% 
+cnt <- filter(data, condition == "mock") %>% 
   pull(normHK) %>% 
@@
     CI95h = t.test(log2fold)$conf.int[2],
-    pValue = t.test(log2fold, pull(filter(data, condition == "PC3 mock"), log2fold))$p.value
+    pValue = t.test(log2fold, pull(filter(data, condition == "mock"), log2fold))$p.value
   ) %>%
@@
 p <- ggplot(data = NULL) +
-  geom_violin(
-    data = data,
-    aes(
-      x = condition,
-      y = log2fold
-    ),
-    trim = TRUE,
-    alpha = 0.3,
-    color = NA,
-    fill = "gray",
-    scale = "width",
-    show.legend = FALSE
-  ) +
   geom_dotplot(

### 2018-02-14 data-raw/saveRDS.R
fixing name in data and raw data for cellular_localization_encode and stable_line_growth_starvation

@@ -140,7 +140,8 @@ read_tsv('./data-raw/stable_line_growth_starvation.txt', col_names = TRUE)  %>%
   ) %>%
   mutate(
     `Cell line` = paste(`Cell line`, Condition, sep = " "),
-    `Cell line` = gsub("PC3 F4", "PC3 miR34a asRNA", `Cell line`)
+    `Cell line` = gsub("PC3 F4", "lncTAM34a", `Cell line`),
+    `Cell line` = gsub("PC3 Mock", "mock", `Cell line`)
   ) %>%
   mutate(
     Time = parse_factor(
@@ -153,7 +154,7 @@ read_tsv('./data-raw/stable_line_growth_starvation.txt', col_names = TRUE)  %>%
     ),
     `Cell line` = parse_factor(
       `Cell line`,
-      levels = c("PC3 Mock", "PC3 miR34a asRNA")
+      levels = c("mock", "lncTAM34a")
     )
   ) %>%
   select(-Condition) %>%
@@ -396,7 +397,7 @@ read_tsv('https://www.encodeproject.org/metadata/type=Experiment&assay_term_name
   mutate(gene_id = gsub("(.*)\\.[0-9]*$", "\\1", gene_id)) %>%
   filter(gene_id %in% c("ENSG00000234546", "ENSG00000075624", "ENSG00000111640", "ENSG00000251562")) %>%
   mutate(gene_name = case_when(
-    gene_id == "ENSG00000234546" ~ "miR34a asRNA",
+    gene_id == "ENSG00000234546" ~ "lncTAM34a",
     gene_id == "ENSG00000075624" ~ "ACTB",
     gene_id == "ENSG00000251562" ~ "MALAT1",
     gene_id == "ENSG00000111640" ~ "GAPDH",

### 2018-02-14 inst/cellular_localization_encode/cellular_localization_encode.Rmd
name change for cellular_localization_encode

@@
   ungroup()
+
+#prepare for plotting 
+stats <- mutate(stats, gene_name = parse_factor(gene_name, levels = c("GAPDH", "MALAT1", "lncTAM34a")))
 ```

### 2018-02-14 inst/tcga_expression/tcga_expression.Rmd
name change for tcga_expression

@@
   gather(gene, value, -(TCGA_cancer_id:cancer_PAM50)) %>%
-  mutate(gene = if_else(gene == "RP3", "miR34a asRNA", "miR34a"))
+  mutate(gene = if_else(gene == "RP3", "lncTAM34a", "miR34a"))
 
@@
   mutate(TP53 = parse_factor(TP53, levels = c("TP53 wt", "TP53 mut"))) %>%
-  mutate(gene = parse_factor(gene, levels = c("miR34a asRNA", "miR34a"))) %>%
+  mutate(gene = parse_factor(gene, levels = c("lncTAM34a", "miR34a"))) %>%
   mutate(cancer_PAM50 = parse_factor(cancer_PAM50, levels = rev(unique(cancer_PAM50))))

### 2018-02-26 inst/tcga_survival/fiveYR.Rmd
adding tidy functions for 5yr survival analysis

---
title: "Figure 1-Supplement 1b"
subtitle: "miR34a asRNA and miR34a TCGA expression"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}
packages <- c(
  "tidyverse",
  "printr",
  "ggthemes",
  "readr",
  "miR34AasRNAproject",
  "grid",
  "gtable",
  "survival",
  "KMsurv"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

#### _Introduction_

#### _Methods_

<br></br>

#### _Results_
```{r}

url <- fileMap(type = "rds")["Figure 4b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

```

```{r}
correlation_matrix <- filter(data, !is.na(TP53) & !is.na(lncTAM34a))
cancers <- sort(unique(correlation_matrix$Cancer))

#TP53 status independant
#Set up all combinations of variables to calcualte survival probability for
independant <- expand.grid(
  gene = c("lncTAM34a", "miR34a", "TP53"),
  cancer = cancers,
  geneLevel = c("low", "others")
) %>% 
  as_tibble() %>%
  arrange(cancer, gene, geneLevel) %>%
  mutate_if(is.factor, as.character) %>%
  group_by(gene, cancer, geneLevel) %>%
  #add data of the corresponding cancer
  mutate(data = map(cancer, function(c, cm = correlation_matrix) {
    filter(cm, Cancer == c)
  })) %>%
  #select the gene to be examined
  mutate(data = pmap(list(gene, data), function(g, d) {
      select(d, g, vitalStatus, FU)
  })) %>%
  #calculate the percentile for the gene's expression for each sample
  mutate(data = map2(gene, data, function(g, d) {
    if(any(grepl("TP53", colnames(d)))) {
      mutate(d, percentile = NA)
    } else {
      mutate(d, percentile = ntile(x = d[[1]], n = 10))
    }
  })) %>%
  #classify 10th percentile and under as "low" and the rest as "others"
  #classify TP53 mutated as low and WT as others
  mutate(data = map(data, function(d) {
    if(any(grepl("TP53", colnames(d)))) {
      mutate(d, class = if_else(TP53, "low", "others"))
    } else {
     mutate(d, class = if_else(percentile == 1, "low", "others")) 
    }
  })) %>%
  #filter data class to correspond to expected geneLevel
  mutate(data = map2(geneLevel, data, function(gl, d) {
    filter(d, class == gl)
  })) %>%
  #calculate survival probability
  mutate(surv.prob = map_dbl(data, ~get_survival(.x, 5))) %>%
  ungroup() %>%
  select(-data) %>%
  mutate(type = "independant")

# TP53 status dependent
#Set up all combinations of variables to calcualte survival probability for
dependant <- expand.grid(
  gene = c("lncTAM34a", "miR34a"),
  mutation = c(TRUE, FALSE),
  cancer = cancers,
  geneLevel = c("low", "others")
) %>% 
  as_tibble() %>%
  arrange(cancer, mutation, gene, geneLevel) %>%
  mutate_if(is.factor, as.character) %>%
  group_by(gene, mutation, cancer, geneLevel) %>%
  #add data of the corresponding cancer and TP53 status
  mutate(data = pmap(list(cancer, mutation), function(c, m, cm = correlation_matrix) {
    filter(cm, Cancer == c & TP53 == m)
  })) %>%
  #select the gene to be examined
  mutate(data = pmap(list(gene, data), function(g, d) {
      select(d, g, vitalStatus, FU)
  })) %>%
  #calculate the percentile for the gene's expression for each sample
  mutate(data = map2(gene, data, function(g, d) {
    mutate(d, percentile = ntile(x = d[[1]], n = 10))
  })) %>%
  #classify 10th percentile and under as "low" and the rest as "others"
  mutate(data = map(data, function(d) {
    mutate(d, class = if_else(percentile == 1, "low", "others"))
  })) %>%
  #filter data class to correspond to expected geneLevel
  mutate(data = map2(geneLevel, data, function(gl, d) {
    filter(d, class == gl)
  })) %>%
  #remove comparisons where there is not enough data
  mutate(bool = map_lgl(data, function(d) {
    !nrow(d) <= 1
  })) %>%
  filter(bool) %>%
  #calculate survival probability
  mutate(surv.prob = map_dbl(data, ~get_survival(.x, 5))) %>%
  ungroup() %>%
  select(-(data:bool)) %>%
  mutate(type = "dependent")

#combine the analyses and filter those to be included in the figure
survData <- bind_rows(dependant, independant) %>%
  filter(!is.na(surv.prob)) %>%
  filter((type == "dependent") | (type == "independant" & gene == "TP53")) %>%
  filter(is.na(mutation) | mutation == FALSE) %>%
  group_by(gene, mutation, cancer, type) %>%
  mutate(n = n()) %>%
  filter(n == 2) %>%
  summarize(relSurv = surv.prob[geneLevel == "low"] - surv.prob[geneLevel == "others"]) %>%
  ungroup() %>%
  select(-mutation, -type) %>%
  spread(gene, relSurv)
```

```{r, warning = FALSE}
#Add the colors for the plot to the data
colors <- getCancerColors()
survData <- full_join(survData, colors, by = "cancer")

#add ggplot theme
theme_remove_all <- theme_remove_all()

#plot 1
p1 <- mainPlot(survData, "TP53", "lncTAM34a", tRA = theme_remove_all)
p2 <- hPlot(survData, "TP53", tRA = theme_remove_all)
renderPlots(p1, p2)

#plot 2
p1 <- mainPlot(survData, "lncTAM34a", "miR34a", tRA = theme_remove_all)
p2 <- hPlot(survData, "lncTAM34a", tRA = theme_remove_all)
renderPlots(p1, p2)

#plot 3
p1 <- mainPlot(survData, "miR34a", "TP53", tRA = theme_remove_all)
p2 <- hPlot(survData, "miR34a", tRA = theme_remove_all)
renderPlots(p1, p2)
```

### 2018-02-26 R/data.R

@@ -550,3 +550,22 @@ NULL
 #' @examples
 #' getData('Figure 1-Supplement 1a')
 NULL
+
+#' TCGA survival analysis
+#'
+#'
+#' @name tcga_survival
+#' @format A tibble with 22,769 rows and 8 variables:
+#'\describe{
+#'   \item{TCGA_id}{Character; TCGA sample ID.}
+#'   \item{Cancer}{Character; Indicates cancer type.}
+#'   \item{TP53}{Numeric; Indicates TP53 nonsynonymous mutation. FALSE is wild type, TRUE is mutated. Mutect2 v7 called data were downloaded from TCGA on 20171030.}
+#'   \item{lncTAM34a}{Numeric; Expression for lncTAM34a. For details on RNA-Seq processing, see Ashouri A et al. Nat Commun. 2016;7}
+#'   \item{miR34a}{Numeric; Expression for miR34a. For details on RNA-Seq processing, see Ashouri A et al. Nat Commun. 2016;7}
+#'   \item{vitalStatus}{Character; Vital state. Data were downloaded from TCGA on 20171027.}
+#'   \item{FU}{Numeric; Date of last follow-up. Data were downloaded from TCGA on 20171027.}
+#'   ...
+#' }
+#' @examples
+#' getData('Figure 4a')
+NULL

### 2018-02-26 R/survival.R

@@ -15,7 +15,7 @@ NULL
 
 #' @rdname get_survival
 #' @export
-#' @importFrom dplyr select mutate if_else summary bind_cols filter arrange pull
+#' @importFrom dplyr select mutate if_else bind_cols filter arrange pull
 #' @importFrom survival Surv survfit
 #' @importFrom purrr map
 #' @importFrom magrittr "%>%"
@@ -251,15 +251,41 @@ renderPlots <- function(p1, p2) {
   p1 + annotation_custom(gt2, xmin = -1.1, xmax = 1.1, ymin = -1.1, ymax = -0.91)
 }
 
-#A theme removing unnecessary elements from the plots
-theme_remove_all <- theme(
-  panel.grid.minor = element_blank(),
-  panel.grid.major = element_blank(),
-  panel.background = element_blank(),
-  plot.background = element_blank()
-)
+#' Theme for survival plot.
+#'
+#' @name theme_remove_all
+#' @rdname theme_remove_all
+#' @aliases theme_remove_all
+#' @author Jason T. Serviss
+#'
+NULL
 
-#Returns the colors for the plot
+#' @rdname theme_remove_all
+#' @export
+#' @import ggplot2
+
+theme_remove_all <- function() {
+  theme(
+    panel.grid.minor = element_blank(),
+    panel.grid.major = element_blank(),
+    panel.background = element_blank(),
+    plot.background = element_blank()
+  )
+}
+
+#' Colors for survival plot.
+#'
+#' @name getCancerColors
+#' @rdname getCancerColors
+#' @aliases getCancerColors
+#' @author Jason T. Serviss
+#'
+NULL
+
+#' @rdname getCancerColors
+#' @export
+#' @importFrom tibble tibble
+
 getCancerColors <- function() {
   cancer_colors<- c(
   rgb(0.498,0.498,0.498), rgb(0.7804,0.7804,0.7804),

### 2018-02-26 data-raw/saveRDS.R

@@ -407,7 +407,7 @@ read_tsv('https://www.encodeproject.org/metadata/type=Experiment&assay_term_name
 
 #tcga_survival
 read_tsv('data-raw/tcga_survival.txt') %>%
-  select(-PAM50) %>%
+  select(-PAM50, -lncTAM34a_cna) %>%
   write_rds(., path = './data/tcga_survival.rds')
 
 #source('./data-raw/saveRDS.R')

### 2018-02-27 inst/tcga_survival/fiveYR.Rmd
adding further survival functions and survivalKM analysis

@@
 ---
-title: "Figure 1-Supplement 1b"
-subtitle: "miR34a asRNA and miR34a TCGA expression"
+title: "Figure 4b"
+subtitle: "5 year survival analysis"
 author: "Jimmy Van den Eynden and Jason T. Serviss"
@@
 
+### 5 year survival analysis
+
 ```{r}
@@
   #calculate survival probability
-  mutate(surv.prob = map_dbl(data, ~get_survival(.x, 5))) %>%
+  mutate(surv.obj = map(data, ~get_survival(.x))) %>%
+  mutate(surv.fit = map(surv.obj, ~survival_fit(.x))) %>%
+  mutate(surv.prob = map_dbl(surv.fit, ~calcSurvProb(.x))) %>%
   ungroup() %>%
-  select(-data) %>%
+  select(-data, -surv.fit) %>%
   mutate(type = "independant")
@@
   #calculate survival probability
-  mutate(surv.prob = map_dbl(data, ~get_survival(.x, 5))) %>%
+  mutate(surv.obj = map(data, ~get_survival(.x))) %>%
+  mutate(surv.fit = map(surv.obj, ~survival_fit(.x))) %>%
+  mutate(surv.prob = map_dbl(surv.fit, ~calcSurvProb(.x))) %>%
   ungroup() %>%
-  select(-(data:bool)) %>%
+  select(-(data:surv.fit)) %>%
   mutate(type = "dependent")

### 2018-02-27 inst/tcga_survival/survivalKM.Rmd
adding further survival functions and survivalKM analysis

---
title: "Figure 4a and Supplementary Figure 5"
subtitle: "Survival curves"
author: "Jimmy Van den Eynden and Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

<style>
.col2 { 
    columns: 2 200px; /* number of columns and width in pixels*/ 
    -webkit-columns: 2 200px; /* chrome, safari */ 
    -moz-columns: 2 200px; /* firefox */ 
}
</style>

```{r, echo = FALSE, message = FALSE}
packages <- c(
  "tidyverse",
  "printr",
  "ggthemes",
  "readr",
  "miR34AasRNAproject"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

#### _Introduction_

#### _Methods_

<br></br>

#### _Results_
```{r}

url <- fileMap(type = "rds")["Figure 4b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

```

```{r}
#TP53 status independant
#Set up all combinations of variables to calcualte survival probability for
independant <- expand.grid(
  gene = c("lncTAM34a", "miR34a", "TP53"),
  cancer = sort(unique(data$Cancer))
) %>% 
  as_tibble() %>%
  mutate_if(is.factor, as.character) %>%
  group_by(gene, cancer) %>%
  #add data of the corresponding cancer and, for gene expression, filter WT TP53
  mutate(data = map2(cancer, gene, function(c, g, cm = data) {
    if(g == "TP53") {
      filter(cm, Cancer == c)
    } else {
      filter(cm, Cancer == c & TP53 == FALSE)
    }
  })) %>%
  #select the gene to be examined
  mutate(data = pmap(list(gene, data), function(g, d) {
      select(d, g, vitalStatus, FU)
  })) %>%
  #remove samples where gene expression/mutation status is na
  mutate(data = map(data, function(x) filter(x, is.na(x[[1]]) == FALSE))) %>%
  #remove cancers where comparisons without data exist
  mutate(bool = map_lgl(data, function(x) nrow(x) == 0)) %>%
  group_by(cancer) %>%
  filter(!any(bool)) %>%
  #calculate the percentile for the gene's expression for each sample
  mutate(data = map2(gene, data, function(g, d) {
    if(any(grepl("TP53", colnames(d)))) {
      mutate(d, percentile = NA)
    } else {
      mutate(d, percentile = ntile(x = d[[1]], n = 10))
    }
  })) %>%
  #classify 10th percentile and under as "low" and the rest as "others"
  #classify TP53 mutated as low and WT as others
  mutate(data = map(data, function(d) {
    if(any(grepl("TP53", colnames(d)))) {
      mutate(d, class = if_else(TP53, "low", "others"))
    } else {
     mutate(d, class = if_else(percentile == 1, "low", "others")) 
    }
  })) %>%
  #calculate survival probability
  mutate(surv.obj = map(data, ~get_survival(.x))) %>%
  mutate(surv.fit = map2(data, surv.obj, function(x, y) survival_fit(y, x$class))) %>%
  mutate(p.value = map2_dbl(data, surv.obj, function(x, y) survival_p(y, x$class))) %>%
  ungroup()
```

<div class="col2">
```{r}
trash <- pmap(
  list(independant$data, independant$surv.fit, independant$gene, independant$cancer, independant$p.value), 
  function(v, w, x, y, z) {
    plotKM(v, w, x, y, z)
  }
)
```
</div>

### 2018-02-27 R/survival.R

@@ -1,28 +1,27 @@
 #SURVIVAL ANALYSIS
 
-#' Calculate survival probability
+#' Calculate survival object
 #'
 #' @name get_survival
 #' @rdname get_survival
 #' @aliases get_survival
 #' @param surv_data tibble; Includes columns vitalStatus and FU, date of last
 #'  follow-up.
-#' @param n_years; numeric Years to examine survival.
-#' @return The survival probability.
+#' @return The survival fit.
 #' @author Jason T. Serviss
 #'
 NULL
 
 #' @rdname get_survival
 #' @export
-#' @importFrom dplyr select mutate if_else bind_cols filter arrange pull
+#' @importFrom dplyr select mutate
+#' @importFrom tibble add_column
 #' @importFrom survival Surv survfit
-#' @importFrom purrr map
 #' @importFrom magrittr "%>%"
 
-get_survival <- function(surv_data, n_years = 5){
-  
-  survival <- surv_data %>%
+get_survival <- function(surv_data){
+  #Survival table
+  surv_data %>%
   #extract data and rename colnames
   select(vitalStatus, FU) %>%
   setNames(c("vital_state", "FU")) %>%
@@ -31,19 +30,85 @@ get_survival <- function(surv_data, n_years = 5){
   select(-vital_state) %>%
   mutate(FU = replace(FU, is.infinite(FU), NA)) %>%
   mutate(FU = FU / 365.25) %>%
-  # Survival tables
+  # Survival object
   {Surv(.$FU, .$Death)}
-  
-  #fit data
-  fit <- survfit(survival ~ 1) %>%
-  summary()
-  
+}
+
+#' Calculate survival fit
+#'
+#' @name survival_fit
+#' @rdname survival_fit
+#' @aliases survival_fit
+#' @param surv_obj Surv; Object of class Surv.
+#' @param class character; The classes if the survival should be a function of
+#' class. Otherwise a function of 1.
+#' @return The survival fit.
+#' @author Jason T. Serviss
+#'
+NULL
+
+#' @rdname get_survival
+#' @export
+#' @importFrom survival survfit
+
+survival_fit <- function(surv_obj, class = NULL) {
+  if(is.null(class)) {
+    fit <- survfit(surv_obj ~ 1)
+  } else {
+    fit <- survfit(surv_obj ~ class)
+  }
+}
+
+#' Calculate survival p-value
+#'
+#' @name survival_p
[…]

### 2018-02-27 inst/tcga_survival/fiveYR.Rmd
survival analysis now fully incorporated

@@
 #### _Introduction_
+Correlation analysis between the effects on the 5-year survival
+probability of TP53-mutated samples, low lncTAM34a expression, and low
+miR34a expression as indicated. For each variable the 5-year survival
+probability was compared to the control group (negative values indicate lower
+survival, positive values indicate higher survival). Spearman correlation
+coefficients are given on top left of each plot. Each dot indicates one cancer
+type. Boxplots on the bottom summarize the effects for
+the parameter on the x-axis, with indication of P values, as calculated using
+paired Wilcoxon signed rank test. Low expression was defined as TP53 non-
+mutated samples having expression values in the bottom 10th percentile.
 
 #### _Methods_
+RNAseq data was downloaded from TCGA and processed as described previously. 
+Briefly, RNAseq data were aligned to the human hg19 assembly and quantified 
+using GENCODE (v19) annotated HTSeq-counts and FPKM normalizations. Expression 
+data from miR34a and lncTAM34a (identified as RP3-510D11.2) were used for 
+further analysis.
+
+Survival analysis was performed on TCGA vital state and follow-up data,
+downloaded from GDC on 27/10/2017 using the R survival package.
 
@@
 ```
-
-### 5 year survival analysis
 

### 2018-02-28 inst/tcga_survival_total/tcga_survival_total.Rmd
last updates before CDD submission

@@
 ---
-title: "Figure 4a-4b"
-subtitle: "lncTAM34a survival analysis in TCGA cancers"
+title: "Figure 4a and Supplementary Figure 5"
+subtitle: "Survival curves"
 author: "Jimmy Van den Eynden and Jason T. Serviss"
@@
 <style>
-.caption { 
-  color: Black; 
-  font-family: "Times New Roman", Times, serif;
-  font-size: 1.0em; 
+.col2 { 
+    columns: 2 200px; /* number of columns and width in pixels*/ 
+    -webkit-columns: 2 200px; /* chrome, safari */ 
+    -moz-columns: 2 200px; /* firefox */ 
 }
@@
 ```{r, echo = FALSE, message = FALSE}
-
 packages <- c(
@@
   "readr",
-    "miR34AasRNAproject",
-    "grid",
-    "gtable"
+  "miR34AasRNAproject"
 )
@@
 
-#library(grDevices)
 ```
@@
 
-**_Please note that the following script has not yet been fully integrated into the package and, therefore, is included here to facilitate transparency although re-running the script in real-time is not yet supported.
-This will be resolved before publication._**
+#### _Introduction_
+Kaplan-Meier survival curves comparing the effects of TP53-mutated samples,
+low lncTAM34a expression and low miR34a expression to control samples in
+17 cancers from TCGA. Panels showing survival curves based on gene expression
+include only TP53 wild type patients where RNAseq data exists.
 
-Data were derived from TCGA:
+#### _Methods_
+RNAseq data was downloaded from TCGA and processed as described previously. 
+Briefly, RNAseq data were aligned to the human hg19 assembly and quantified 
+using GENCODE (v19) annotated HTSeq-counts and FPKM normalizations. Expression 
+data from miR34a and lncTAM34a (identified as RP3-510D11.2) were used for 
+further analysis.
 
-* **data/lncRNA_cancer_id.rds**: Matrix containing for each TCGA barcode information regarding cancer type.
-* **data/lncRNA_clin.rds**: Matrix containing for each TCGA barcode information regarding vital state (first column) and date of last follow-up (second column).
-Data were downloaded from TCGA on 20171027.
-* **data/lncRNA_TCGA_TP53_hasNonsynMut.rds**: Named vector containing for each TCGA barcode information regarding TP53 nonSynonymous mutation state: FALSE if no mutation or synonymous mutations, TRUE if mutated.
-Mutect2 v7 called data were downloaded from TCGA on 20171030.
-* **data/lncRNA_expr_RP3.rds**: Named numeric vector containing for each TCGA barcode information regarding RP3-510D11.2 expression.
-For details on RNA-Seq processing, see *Ashouri A et al.
-Nat Commun.
-2016;7*
-* **data/lncRNA_cna_RP3.rds**: Named numeric vector containing for each TCGA barcode information regarding RP3-510D11.2 copy number alteration (gene-based segmentation values).
-For details on processing, see *Ashouri A et al.
-Nat Commun.
-2016;7*
-* **data/lncRNA_expr_miR34a.rds**: Named numeric vector containing for each TCGA barcode information regarding miR34a expression.
-For details on RNA-Seq processing, see *Ashouri A et al.
-Nat Commun.
-2016;7*
-* **data/lncRNA_TCGA_BRCA_PAM50.rds**: Named character vector containing for each TCGA barcode from the breast cancer dataset information regarding PAM50 classification: LumA, LumB, Basal or Her2.
-For details on PAM50 classification, see *Ashouri A et al.
-Nat Commun.
-2016;7*
+Survival analysis was performed on TCGA vital state and follow-up data,
+downloaded from GDC on 27/10/2017 using the R survival package.
 
-```{r, eval = FALSE}
-TCGA_cancer_id<- readRDS("data/lncRNA_cancer_id.rds") # TCGA Subtype IDs
-TCGA_clin_surv<- readRDS("data/lncRNA_clin.rds") # Survival data
-TCGA_TP53_hasNonsynMut<- readRDS("data/lncRNA_TCGA_TP53_hasNonsynMut.rds") # Survival data
-RP3_expr<- readRDS(file = "data/lncRNA_expr_RP3.rds")
-RP3_cna<- readRDS(file = "data/lncRNA_cna_RP3.rds")
-miR34a_expr<- readRDS(file = "data/lncRNA_expr_miR34a.rds")
-TCGA_PAM50<- readRDS(file = "data/lncRNA_TCGA_BRCA_PAM50.rds")
+<br></br>
+
+#### _Results_
+```{r}
+
+url <- fileMap(type = "rds")["Figure 4b"][[1]]
+data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
 ```
 
-## Functions
-
-```{r, eval = FALSE}
-source("functions/create_survival_plot.R") # Function used to create survival plots
-source("functions/create_expression_groups.R") # Function used to divide samples based on expression percentile thresholds
-source("functions/get_survival.R") # Function used to calculate survival probabilities
+```{r}
+#TP53 status independant
+#Set up all combinations of variables to calcualte survival probability for
+independant <- expand.grid(
+  gene = c("lncTAM34a", "miR34a", "TP53"),
+  cancer = sort(unique(data$Cancer))
+) %>% 
+  as_tibble() %>%
+  mutate_if(is.factor, as.character) %>%
+  group_by(gene, cancer) %>%
+  #add data of the corresponding cancer and, for gene expression, filter WT TP53
+  mutate(data = map2(cancer, gene, function(c, g, cm = data) {
+    if(g == "TP53") {
+      filter(cm, Cancer == c)
+    } else {
+      filter(cm, Cancer == c & TP53 == FALSE)
+    }
+  })) %>%
+  #select the gene to be examined
+  mutate(data = pmap(list(gene, data), function(g, d) {
+      select(d, g, vitalStatus, FU)
+  })) %>%
+  #remove samples where gene expression/mutation status is na
+  mutate(data = map(data, function(x) filter(x, is.na(x[[1]]) == FALSE))) %>%
+  #remove cancers where comparisons without data exist
+  mutate(bool = map_lgl(data, function(x) nrow(x) == 0)) %>%
+  group_by(cancer) %>%
+  filter(!any(bool)) %>%
+  #calculate the percentile for the gene's expression for each sample
+  mutate(data = map2(gene, data, function(g, d) {
+    if(any(grepl("TP53", colnames(d)))) {
+      mutate(d, percentile = NA)
+    } else {
+      mutate(d, percentile = ntile(x = d[[1]], n = 10))
+    }
+  })) %>%
+  #classify 10th percentile and under as "low" and the rest as "others"
+  #classify TP53 mutated as low and WT as others
+  mutate(data = map(data, function(d) {
+    if(any(grepl("TP53", colnames(d)))) {
+      mutate(d, class = if_else(TP53, "low", "others"))
+    } else {
+     mutate(d, class = if_else(percentile == 1, "low", "others")) 
+    }
+  })) %>%
+  #calculate survival probability
+  mutate(surv.obj = map(data, ~get_survival(.x))) %>%
+  mutate(surv.fit = map2(data, surv.obj, function(x, y) survival_fit(y, x$class))) %>%
+  mutate(p.value = map2_dbl(data, surv.obj, function(x, y) survival_p(y, x$class))) %>%
+  ungroup()
 ```
 
-## Libraries
-```{r, eval = FALSE}
-  library(survival)
-  library(KMsurv)
-  library(svglite)
-  library(WriteXLS)
+<div class="col2">
+```{r}
+trash <- pmap(
+  list(independant$data, independant$surv.fit, independant$gene, independant$cancer, independant$p.value), 
+  function(v, w, x, y, z) {
+    plotKM(v, w, x, y, z)
+  }
+)
 ```
-
-# Survival analysis per cancer type
-
-## Kaplan-Meier
-
-```{r, message=F, warning=F, eval = FALSE}
-
-    # Get cancers for which all expression data available: 17 in total
-    cancers<- sort(names(table(TCGA_cancer_id[names(RP3_expr),1])))
-
-    # Set expression th
-    th1<- 0.1
-    th2<- 1-th1
-
-    p_vals<- NULL      
-    # Create plots
-  for(plot_format in 1:2){
-    if(plot_format==1) pdf("figs/lncRNA_survival_KM.pdf",width = 17,height = 24)
-    else svglite("figs/lncRNA_survival_KM.svg",width = 17,height = 24)
-    par(mfrow=c(9,6))
-    for(cancer in cancers){
-      samples_cancer<- rownames(TCGA_cancer_id)[TCGA_cancer_id[,1]==cancer]
-
-      # Mutation only for TP53
-      TCGA_TP53_hasNonsynMut_temp<- TCGA_TP53_hasNonsynMut[names(TCGA_TP53_hasNonsynMut)%in%samples_cancer]
-      names(TCGA_TP53_hasNonsynMut_temp)<- substr(names(TCGA_TP53_hasNonsynMut_temp),1,12)
-      clin_class<- cbind(TCGA_clin_surv,TCGA_TP53_hasNonsynMut_temp[rownames(TCGA_clin_surv)])
-      n1<- sum(clin_class[,3]==FALSE,na.rm=T)
-      n2<- sum(clin_class[,3]==TRUE,na.rm=T)
-      if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0) plot.new() # No use if no motation information
-      else p1<- create_survival_plot(clinical_data = clin_class,classes_to_compare = c(FALSE,TRUE),classnames=c(paste("TP53 WT (n=",n1,")",sep=""),paste("TP53 MUT (n=",n2,")",sep="")),plot_title =  cancer,save_plot = TRUE,add_to_existing_plot = TRUE, plot_cols = c("black","black"), plot_lty = 1:2,return_p = TRUE)
-
-    # Expr + Mutation
-    for(i in 1:2){
-      expr<- list(RP3_expr,miR34a_expr)[[i]]
-      gene<- c("miR34a asRNA","miR34a")[i]
-      # for(isMut in c(F,T)){
-      isMut=FALSE
-        samples_cancer_sel<- intersect(names(TCGA_TP53_hasNonsynMut)[TCGA_TP53_hasNonsynMut==isMut],samples_cancer)
-        expr_temp<- expr[names(expr)%in%samples_cancer_sel]
-        class<- create_expression_groups(expr_temp,gene,th=c(th1,th2))
-        names(class)<- substr(names(class),1,12)
-        class[class==3]<- 2
-        clin_class<- cbind(TCGA_clin_surv[names(class),],class)
-        if(sum(!is.na(clin_class[,3]))==0) next
-        n1<- sum(clin_class[,3]==1,na.rm=T)
-        n2<- sum(clin_class[,3]==2,na.rm=T)
-        n3<- sum(clin_class[,3]==3,na.rm=T)
-        # if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0|n1==0|n2==0|n3==0) plot.new()
-        if(nrow(clin_class)==0|sum(!is.na(clin_class[,3]))==0|n1==0|n2==0) plot.new()
-        else px<- create_survival_plot(clinical_data = clin_class,classes_to_compare = c(1,2),classnames=c(paste("Low expression (<P",100*th1," - n=",n1,")",sep=""),paste( "Normal expression (>P",100*th1," - n=",n2,")",sep="")),plot_title = paste(cancer,gene,sep=" "),save_plot = TRUE,add_to_existing_plot = TRUE,plot_cols = c("black","red"), plot_lty=rep(1+isMut,2),return_p = TRUE)
-      # }
-        if(i==1) p2<- px
-        if(i==2) p3<- px
-    }
-      p_vals<- cbind(p_vals,c(p1,p2,p3))
-    }
-    dev.off()
-  }
-
-  p_vals<- p_vals[,1:17]
-  colnames(p_vals)<- cancers
-  rownames(p_vals)<- c("TP53","miR34a_asRNA","miR34a")
-```
-
-## 5y survival probabilities
-
-```{r, message=F, warning=F, eval = FALSE}
-
-# Create correlation matrix
-common_samples<- intersect(names(TCGA_TP53_hasNonsynMut),names(RP3_expr))
-correlation_matrix<- cbind(RP3=RP3_expr[common_samples],miR34a=miR34a_expr[common_samples],TP53=TCGA_TP53_hasNonsynMut[common_samples],cancer=TCGA_cancer_id[common_samples,1])
-
-n_years<- 5
-
-# Get surv probs
-cancers<- sort(unique(correlation_matrix[,"cancer"]))
-survProb_ls<- list()
-
-# Independent
-for(gene in c("RP3","miR34a","TP53")){
-  cat(gene,"\n")
-  surv_matrix<- matrix(NA,3,length(cancers),dimnames = list(1:3,cancers))
-  for(cancer in cancers){
-    correlation_matrix_temp<- correlation_matrix[correlation_matrix[,"cancer"]==cancer,]
-    if(gene!="TP53") correlation_matrix_temp<- cbind(correlation_matrix_temp,class=create_expression_groups(t(correlation_matrix_temp),gene,th=c(0.1,0.9)))
-    else correlation_matrix_temp<- cbind(correlation_matrix_temp,class=as.numeric(correlation_matrix_temp[,gene]=="TRUE")+1) 
-    for(i in 1:2){
-      if(i==1) samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]==i]
-      else samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]%in%c(2,3)]
-      if(length(samples_sel)<=1) next
-      surv_data<- TCGA_clin_surv[rownames(TCGA_clin_surv)%in%substr(samples_sel,1,12),]
-      survProb<- get_survival(surv_data,n_years)
-      if(length(survProb)==0) next
-      surv_matrix[i,cancer]<- survProb
-    }
-  }
-  survProb_ls[gene]<- list(surv_matrix)
-}
-
-# TP53 status dependent
-for(gene in c("RP3","miR34a")){
-  cat(gene,"\n")
-  for(mut in c(0,1)){
-    surv_matrix<- matrix(NA,3,length(cancers),dimnames = list(1:3,cancers))
-    for(cancer in cancers){
-      correlation_matrix_temp<- correlation_matrix[correlation_matrix[,"cancer"]==cancer&as.numeric(correlation_matrix[,"TP53"]=="TRUE")==mut,,drop=F]
-      if(nrow(correlation_matrix_temp)<=1) next
-      correlation_matrix_temp<- cbind(correlation_matrix_temp,class=create_expression_groups(t(correlation_matrix_temp),gene,th=c(0.1,0.9)))
-      for(i in 1:2){
-        if(i==1) samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]==i]
-        else samples_sel<- rownames(correlation_matrix_temp)[correlation_matrix_temp[,"class"]%in%c(2,3)]
-        if(length(samples_sel)<=1) next
-        surv_data<- TCGA_clin_surv[rownames(TCGA_clin_surv)%in%substr(samples_sel,1,12),]
-        survProb<- get_survival(surv_data,n_years)
-        if(length(survProb)==0) next
-        surv_matrix[i,cancer]<- survProb
-      }
-    }
-    survProb_ls[paste(gene,mut,sep="_")]<- list(surv_matrix)
-  }
-}
-
-# Remove NA!
-survProb_ls[["RP3"]]<- survProb_ls[["RP3"]][,!is.na(survProb_ls[["RP3"]][1,])&!is.na(survProb_ls[["RP3"]][2,])]
-survProb_ls[["miR34a"]]<- survProb_ls[["miR34a"]][,!is.na(survProb_ls[["miR34a"]][1,])&!is.na(survProb_ls[["miR34a"]][2,])]
-survProb_ls[["TP53"]]<- survProb_ls[["TP53"]][,!is.na(survProb_ls[["TP53"]][1,])&!is.na(survProb_ls[["TP53"]][2,])]
-survProb_ls[["RP3_0"]]<- survProb_ls[["RP3_0"]][,!is.na(survProb_ls[["RP3_0"]][1,])&!is.na(survProb_ls[["RP3_0"]][2,])]
-survProb_ls[["RP3_1"]]<- survProb_ls[["RP3_1"]][,!is.na(survProb_ls[["RP3_1"]][1,])&!is.na(survProb_ls[["RP3_1"]][2,])]
-survProb_ls[["miR34a_0"]]<- survProb_ls[["miR34a_0"]][,!is.na(survProb_ls[["miR34a_0"]][1,])&!is.na(survProb_ls[["miR34a_0"]][2,])]
-survProb_ls[["miR34a_1"]]<- survProb_ls[["miR34a_1"]][,!is.na(survProb_ls[["miR34a_1"]][1,])&!is.na(survProb_ls[["miR34a_1"]][2,])]
-# 
-# for(plot_format in 1:2){
-#   if(plot_format==1) pdf("figs/lncRNA_5ySurv_expr.pdf",width = 14, height = 14)
-#   else svglite("figs/lncRNA_5ySurv_expr.svg",width = 14, height = 14)
-# 
-#   par(mfrow=c(2,1))
-# 
-#   boxplot(list(
-#     survProb_ls[["RP3"]][1,],survProb_ls[["RP3"]][2,],NA,
-#     survProb_ls[["miR34a"]][1,],survProb_ls[["miR34a"]][2,],NA,
-#     survProb_ls[["TP53"]][2,],survProb_ls[["TP53"]][1,]),
-#     outline=F,ylab=paste(n_years,"y survival probability",sep=""),frame.plot=F,axes=F,col=c("lightgrey",NA,NA,"lightgrey",NA,NA,"darkgrey",NA)
-#   )
-#   axis(2)
-#   text(1.5,1,paste("P=",signif(wilcox.test(survProb_ls[["RP3"]][1,],survProb_ls[["RP3"]][2,],paired=T)$p.value,3),sep=""))
-#   text(4.5,1,paste("P=",signif(wilcox.test(survProb_ls[["miR34a"]][1,],survProb_ls[["miR34a"]][2,],paired=T)$p.value,3),sep=""))
-#   text(7.5,1,paste("P=",signif(wilcox.test(survProb_ls[["TP53"]][1,],survProb_ls[["TP53"]][2,],paired=T)$p.value,3),sep=""))
-#   text(1.5,1.05,"miR34a asRNA",xpd=NA)
-#   text(4.5,1.05,"miR34a",xpd=NA)
-#   text(7.5,1.05,"TP53",xpd=NA)
-#   legend("bottom",horiz = T,legend = c("Control","Low expression (<P10)","Mutated"),fill = c("white","lightgrey","darkgrey"),bty="n")
-#   
-#   boxplot(list(
-#     survProb_ls[["RP3_0"]][1,],survProb_ls[["RP3_0"]][2,],NA,
-#     survProb_ls[["RP3_1"]][1,],survProb_ls[["RP3_1"]][2,],NA,
-#     survProb_ls[["miR34a_0"]][1,],survProb_ls[["miR34a_0"]][2,],NA,
-#     survProb_ls[["miR34a_1"]][1,],survProb_ls[["miR34a_1"]][2,]),
-#     outline=F,ylab=paste(n_years,"y survival probability",sep=""),frame.plot=F,axes=F,col=c("lightgrey",NA,NA,"lightgrey",NA,NA,"lightgrey",NA,NA,"lightgrey",NA)
-#   )
-#   axis(2)
-#   text(1.5,1,signif(wilcox.test(survProb_ls[["RP3_0"]][1,],survProb_ls[["RP3_0"]][2,],paired=T)$p.value,3))
-#   text(4.5,1,signif(wilcox.test(survProb_ls[["RP3_1"]][1,],survProb_ls[["RP3_1"]][2,],paired=T)$p.value,3))
-#   text(7.5,1,signif(wilcox.test(survProb_ls[["miR34a_0"]][1,],survProb_ls[["miR34a_0"]][2,],paired=T)$p.value,3))
-#   text(10.5,1,signif(wilcox.test(survProb_ls[["miR34a_1"]][1,],survProb_ls[["miR34a_1"]][2,],paired=T)$p.value,3))
-#   text(3,1.1,"miR34a asRNA",xpd=NA)
-#   text(1.5,1.05,"TP53 wt",xpd=NA)
-#   text(4.5,1.05,"TP53 mut",xpd=NA)
-#   text(9,1.1,"miR34a",xpd=NA)
-#   text(7.5,1.05,"TP53 wt",xpd=NA)
-#   text(10.5,1.05,"TP53 mut",xpd=NA)
-#   legend("bottom",horiz = T,legend = c("Control","Low expression (<P10)"),fill = c("white","lightgrey"),bty="n")
-#   
-#   dev.off()
-# }
-
-# Correlation between survival
- cancer_colors<- c(
-  rgb(0.498,0.498,0.498),
-  rgb(0.7804,0.7804,0.7804),
-  rgb(0.1216,0.4667,0.7059),
-  rgb(0.1216,0.4667,0.7059),
-  rgb(0.6824,0.7804,0.9098),
-  rgb(0.0902,0.7451,0.8118),
-  rgb(0.6196,0.8941,0.898),
-  rgb(1,0.498,0.0549),
-  rgb(1,0.7333,0.4706),
-  rgb(0.8392,0.1529,0.1569),
-  rgb(1,0.5961,0.5882),
-  rgb(0.5804,0.4039,0.7412),
-  rgb(0.7725,0.6118,0.7961),
-  rgb(0.8902,0.4667,0.7608),
-  rgb(0.9686,0.7137,0.8235),
-  rgb(0.549,0.3373,0.2941),
-  rgb(0.7686,0.6118,0.5804),
-  rgb(0.1725,0.6275,0.1725),
-  rgb(0.5961,0.8745,0.5412),
-  rgb(0.7373,0.7412,0.1333),
-  rgb(0.8588,0.8824,0.5529),
-  rgb(0.9294,0.8,0.0588),
-  rgb(1,0.9255,0)
-)
-  names(cancer_colors)<- c('ACC','BLCA','BRCA','BRCA Basal','BRCA Her2','BRCA LumA','BRCA LumB','CESC','GBM','HNSC','KICH','KIRC','KIRP','LGG','LIHC','LUAD','LUSC','OV','PRAD','SKCM','STAD','THCA','UCS')
-
-for(plot_format in 1:2){
-  if(plot_format==1) pdf("figs/lncRNA_5ySurv_expr_corr.pdf",width = 14, height = 7)
-  else svglite("figs/lncRNA_5ySurv_expr_corr.svg",width = 21, height = 7)
-
-  par(mfrow=c(1,3))
-
-  # Focus on WT group only!
-  survProb_rel_RP3<- survProb_ls[["RP3_0"]][1,]-survProb_ls[["RP3_0"]][2,]
-  survProb_rel_miR34a<- survProb_ls[["miR34a_0"]][1,]-survProb_ls[["miR34a_0"]][2,]
-  survProb_rel_TP53<- survProb_ls[["TP53"]][2,]-survProb_ls[["TP53"]][1,]
-
-  for(i in 1:3){
-    x_param_name<- c("TP53","miR34a_asRNA","miR34a")[i]
-    x_param<- list(survProb_rel_TP53,survProb_rel_RP3,survProb_rel_miR34a)[[i]]
-    y_param_name<- c("miR34a_asRNA","miR34a","TP53")[i]
-    y_param<- list(survProb_rel_RP3,survProb_rel_miR34a,survProb_rel_TP53)[[i]]
-    common_cancers<- intersect(names(x_param),names(y_param))
-    x_param<- x_param[common_cancers]
-    y_param<- y_param[common_cancers]
-    plot(x_param,y_param,frame.plot=F,xlim=c(-1,+1),ylim=c(-1,+1),xlab=x_param_name,ylab=y_param_name)  
-    boxplot(y_param,at = 0.75,add=T,frame.plot=F,outline=F,boxwex=0.2)
-    boxplot(x_param,at = 0.75,add=T,frame.plot=F,outline=F,horizontal = T,boxwex=0.2)
-    p_temp<- signif(cor.test(x_param,y_param,method = "spearman")$p.value,3)
-    r_temp<- signif(cor.test(x_param,y_param,method = "spearman")$estimate,3)
-    legend("topleft",legend = c(paste("P=",p_temp,sep=""),paste("r=",r_temp,sep="")),bty="n")
-    for(cancer in common_cancers){
-      points(x_param[cancer],y_param[cancer],col=cancer_colors[cancer],pch=16,cex=2)
-    }
-    # abline(h=0,v=0,lty=2)
-  }
-  dev.off()
-}
-
-  # Survival effects
-  median(survProb_rel_RP3) # -0.096
-  median(survProb_rel_miR34a) # -0.068
-  median(survProb_rel_TP53) # -0.064
-  wilcox.test(survProb_rel_RP3) # p=0.083
-  wilcox.test(survProb_rel_miR34a) # p=0.17
-  wilcox.test(survProb_rel_TP53) # p=0.04
-
-```
+</div>

### 2018-02-28 R/utils.R

@@ -36,26 +36,25 @@ fileMap <- function(type) {
     `Figure 3b` = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
     `Figure 3c` = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
     `Figure 3d` = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
-    `Figure 4a` = "tcga_survival/tcga_survival.Rmd",
+    `Figure 4a` = "tcga_survival_total/tcga_survival_total.Rmd",
     `Figure 4b` = "tcga_survival/tcga_survival.Rmd",
     `Figure 5` = "model/model.Rmd",
-    `Figure 1-Supplement 1a` = "tcga_correlation_table/tcga_correlation_table.Rmd",
-    `Figure 1-Supplement 1b` = "tcga_expression/tcga_expression.Rmd",
-    `Figure 1-Supplement 2a` = "primer_walk_schematic/primer_walk_schematic.Rmd",
-    `Figure 1-Supplement 2b` = "polyadenylation/polyadenylation.Rmd",
-    `Figure 1-Supplement 2c` = "isoforms/isoforms.Rmd",
-    `Figure 1-Supplement 2d` = "coding_potential_cpc/coding_potential_cpc.Rmd",
-    `Figure 1-Supplement 2e` = "cellular_localization_encode/cellular_localization_encode.Rmd",
-    `Figure 2-Supplement 1a` = "p1_construct/p1_construct.Rmd",
-    `Figure 2-Supplement 1b` = "p1_construct/p1_construct.Rmd",
-    `Figure 2-Supplement 2` = "p1_hek293t/p1_hek293t.Rmd",
-    `Figure 3-Supplement 1` = "stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd",
-    `Figure 3-Supplement 2a` = "stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd",
-    `Figure 3-Supplement 2b` = "stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd",
-    `Figure 4-Supplement 1` = "tcga_survival_total/tcga_survival_total.Rmd",
-    `Supplementary Document 1a` = "lnc34a_cage/lnc34a_cage.Rmd",
-    `Supplementary Document 1b` = "lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd",
[…]

### 2018-02-28 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
fixing supplementary names in file map and Rmds

@@
 rm(packages)
-
-```
-
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 
@@
 
-url <- fileMap(type = "rds")["Figure 2a"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 2a")
 

### 2018-02-28 inst/lnc34a_cage/lnc34a_cage.Rmd
adding prelim data documentation
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Lnc34a CAGE"
+title: "Supplementary Figure 6"
+subtitle: "Lnc34a CAGE"
 author: "Jason T. Serviss"
@@
 
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
-
-```
+<br></br>
 
@@
 nrCellLinesDown <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
-  url <- fileMap(type = "txt")["Supplementary Document 1a"][[1]]
-  read_tsv(gzcon(url(file.path(dataUrl, url)))) %>% 
+  getData("Supplementary Figure 6") %>% 
     pull(cell) %>%
@@
 cellLinesInFinal <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
-  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  getData("Supplementary Figure 6") %>%
     pull(cell) %>%
@@
 RNAprepTable <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
-  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  getData("Supplementary Figure 6") %>%
     mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
@@
 localizationTable <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
-  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  getData("Supplementary Figure 6") %>%
     select(localization) %>%
@@
 #cage data
-url <- fileMap(type = "rds")["Supplementary Document 1a"][[1]]
-cage <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+cage <- getData("Supplementary Figure 6") %>%
   select(start, stop, level) %>%

### 2018-02-28 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
adding prelim data documentation
fixing supplementary names in file map and Rmds

@@
 ---
-title: "lnc34a splice junctions"
+title: "Supplementary Figure 7"
+subtitle: "lnc34a splice junctions"
 author: "Jason T. Serviss"
@@
 
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-
-```
+<br></br>
 
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["Supplementary Document 1b"][[1]]
+  url <- fileMap(type = "txt")["Supplementary Figure 7"][[1]]
 
@@
 cellLinesInFinal <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
-
-  read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  getData("Supplementary Figure 7") %>%
     pull(filename) %>%
@@
 RNAprepTable <- function() {
-  dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
-  final <- read_rds(gzcon(url(file.path(dataUrl, url)))) %>%
+  final <- getData("Supplementary Figure 7") %>%
     select(filename) %>%
@@
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-  url <- fileMap(type = "txt")["Supplementary Document 1b"][[1]]
+  url <- fileMap(type = "txt")["Supplementary Figure 7"][[1]]
   read_tsv(gzcon(url(file.path(dataUrl, url)))) %>%
@@
 
-All available whole cell RNAseq splice junction data from the ENCODE project originating from the Cold Spring Harbor Lab from `r nrCellLinesDown()` cell lines was downloaded from the UCSC genome browser with the script entitled "lnc34a splice junctions" in the data-raw/saveRDS.R file.
-Of these cell lines, `r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand of chromosome 1 and in the region between the lnc34a start (9241796) and transcription termination (9257102) site (note that miR34a asRNA resides totally within this region).
-Splice junctions from the following cell lines were included in the final figure: `r cellLinesInFinal()`.
-All splice junctions were plotted and colored according to the number of reads corresponding to each.
+All available whole cell RNAseq splice junction data from the ENCODE project 
+originating from the Cold Spring Harbor Lab from `r nrCellLinesDown()` cell 
+lines was downloaded from the UCSC genome browser with the script entitled 
+"lnc34a splice junctions" in the data-raw/saveRDS.R file. Of these cell lines, 
+`r cellLinesInFinal() %>% length()` had spliced reads mapping to the plus strand
+of chromosome 1 and in the region between the lnc34a start (9241796) and 
+transcription termination (9257102) site (note that miR34a asRNA resides totally
+within this region). Splice junctions from the following cell lines were 
+included in the final figure: `r cellLinesInFinal()`. All splice junctions were 
+plotted and colored according to the number of reads corresponding to each. 
 Information regarding the RNA extraction is included below:
@@
 #splice junctions
-url <- fileMap(type = "rds")["Supplementary Document 1b"][[1]]
-splJnc <- read_rds(gzcon(url(file.path(dataUrl, url))))
-
-splJnc <- splJnc %>%
+splJnc <- getData("Supplementary Figure 7") %>%
   mutate(cellline = gsub(".*LongRnaSeq(.*)Cell.*", "\\1", filename)) %>%

### 2018-02-28 inst/p1_construct/p1_construct.Rmd
fixing some rmd typos
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Figure 2-Supplement 1a-b"
+title: "Supplementary Figure 3a-b"
 subtitle: "Schematic representation of the P1 construct"
@@
 
-url <- fileMap(type = "png")["Figure 2-Supplement 1a"][[1]]
+url <- fileMap(type = "png")["Supplementary Figure 3a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 
-*For all results and conclusions please see Figure 2d.
+*For all results and conclusions please see Figure 2c.
 

### 2018-02-28 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
fixing supplementary names in file map and Rmds

@@
 
-url <- fileMap(type = "rds")["Figure 2c"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 2c")
 

### 2018-02-28 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
fixing supplementary names in file map and Rmds

@@
 
-url <- fileMap(type = "rds")["Figure 2d"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 2d")
 

### 2018-02-28 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Figure 3-Supplement 2a"
+title: "Supplementary Figure 4b"
 subtitle: "CCND1 expression in PC3 stable cell lines"
@@
 
-url <- fileMap(type = "rds")["Figure 3-Supplement 2a"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Supplementary Figure 4b")
 

### 2018-02-28 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Figure 3-Supplement 2b"
+title: "Supplementary Figure 4c"
 subtitle: "CCND1 protein expression in PC3 stable lines"
@@
 ```
+
+<br></br>
 
@@
 
-url <- fileMap(type = "rds")["Figure 3-Supplement 2b"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Supplementary Figure 4c")
 

### 2018-02-28 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
fixing supplementary names in file map and Rmds

@@
 
+<br></br>
+
 #### _Results_
@@
 
-url <- fileMap(type = "rds")["Figure 3b"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 3b")
 

### 2018-02-28 inst/stable_line_expression/stable_line_expression.Rmd
fixing supplementary names in file map and Rmds

@@
 
-url <- fileMap(type = "rds")["Figure 3a"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 3a")
 

### 2018-02-28 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Figure 3-Supplement 1"
+title: "Supplementary Figure 4a"
 subtitle: "miR34a asRNA stable over-expression cell lines compared to HEK293T"
@@
 
-url <- fileMap(type = "rds")["Figure 3-Supplement 1"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Supplementary Figure 4a")
 

### 2018-02-28 inst/tcga_expression/tcga_expression.Rmd
fixing supplementary names in file map and Rmds

@@
 ---
-title: "Figure 1-Supplement 1b"
+title: "Supplementary Figure 1b"
 subtitle: "miR34a asRNA and miR34a TCGA expression"
@@
 ```{r}
-url <- fileMap(type = "rds")["Figure 1c"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+data <- getData("Supplementary Figure 1b")
 

### 2018-02-28 inst/tcga_survival/tcga_survival.Rmd
fixing supplementary names in file map and Rmds

--- 2018-02-27 inst/tcga_survival/fiveYR.Rmd
@@
 mutated samples having expression values in the bottom 10th percentile.
+
+<br></br>
 
@@
 #### _Results_
+
 ```{r}
 
-url <- fileMap(type = "rds")["Figure 4b"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
-
-```
-
-```{r}
+data <- getData("Figure 4b")
 correlation_matrix <- filter(data, !is.na(TP53) & !is.na(lncTAM34a))

### 2018-02-28 inst/tcga_survival_total/tcga_survival_total.Rmd
fixing supplementary names in file map and Rmds

@@
 include only TP53 wild type patients where RNAseq data exists.
+
+<br></br>
 
@@
 #### _Results_
+
 ```{r}
 
-url <- fileMap(type = "rds")["Figure 4b"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 4a")
 
-```
-
-```{r}
 #TP53 status independant

### 2018-02-28 R/utils.R

@@ -202,18 +202,22 @@ NULL
 getData <- function(figure) {
   #check that there is data for the figure
   figsWithData <- c(
-    'Figure 1-Supplement 2e', 'Figure 1f', 'Figure 1-Supplement 2d',
-    'Figure 2a', 'Figure 2b', 'Supplementary Document 1a',
-    'Supplementary Document 1b', 'Figure 2c', 'Figure 2-Supplement 2',
-    'Figure 2d', 'Figure 3-Supplement 2a', 'Figure 3-Supplement 2b',
-    'Figure 3b', 'Figure 3-Supplement 1', 'Figure 3a',
-    'Figure 3c', 'Figure 3d', 'Figure 1-Supplement 1a',
-    'Figure 1c'
-    
+    'Figure 1c', 'Figure 1f', 'Figure 2a', 'Figure 2b', 'Figure 2c',
+    'Figure 2d', 'Figure 3a', 'Figure 3b', 'Figure 3c', 'Figure 3d',
+    'Figure 4a', 'Figure 4b', 'Supplementary Figure 1a',
+    'Supplementary Figure 1b', 'Supplementary Figure 2d',
+    'Supplementary Figure 2e', 'Supplementary Figure 3c',
+    'Supplementary Figure 4a', 'Supplementary Figure 4b',
+    'Supplementary Figure 4c', 'Supplementary Figure 5',
+    'Supplementary Figure 6', 'Supplementary Figure 7'
   )
   if(!figure %in% figsWithData) {
     stop("There is no data for the figure you specified")
   }
+  if(figure == "Figure 4a") figure <- "Figure 4b"
+  if(figure == "Supplementary Figure 1a") figure <- "Figure 1c"
+  if(figure == "Supplementary Figure 1b") figure <- "Figure 1c"
+
   dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
   path <- fileMap('rds')[[figure]][[1]]
   read_rds(gzcon(url(file.path(dataUrl, path))))

### 2018-03-05 inst/coding_potential_cpat/coding_potential_cpat.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles
fixing supplementary names in file map and Rmds
all verbose changes finished before review

@@
 
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-
-```
-
-####_Introduction_
+#### _Introduction_
 
@@
 
-url <- fileMap(type = "rds")["figure1f"][[1]]
-cpat <-read_rds(url(file.path(dataUrl, url)))
+cpat <- getData("Figure 1f")
 cpat
@@
 
-*Results for Coding-potential Calculator are located in Supplementary figure 1g.
+*Results for Coding-potential Calculator are located in Supplementary Figure 2e.
 

### 2018-03-05 inst/hct116_p53_null/hct116_p53_null.Rmd
fixing supplementary names in file map and Rmds
all verbose changes finished before review

@@
 rm(packages)
-
-#library(grDevices)
-```
-
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
 
@@
 
-url <- fileMap(type = "rds")["Figure 2b"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 2b")
 
@@
 Monitoring the effects of 24 hours doxorubicin treatment on miR34a asRNA and HG in P53+/+ and p53-/- HCT116 cells.
-The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-03-05 inst/isoforms/isoforms.Rmd
fixing supplementary names in file map and Rmds
all verbose changes finished before review

@@
 ---
-title: "Figure 1-Supplement 2c"
+title: "Supplementary Figure 2c"
 subtitle: "miR34a asRNA isoform cloning"
@@
 Primer combinations:
+
 miR34a AS F12 + miR34a AS R1  
@@
 
-url <- fileMap(type = "png")["Figure 1-Supplement 2c"][[1]]
+url <- fileMap(type = "png")["Supplementary Figure 2c"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2018-03-05 inst/mir34a_locus/mir34a_locus.Rmd
fixing headers in Rmds
all paths updated to match article inc. Rmd titles
all verbose changes finished before review

@@
 
-url <- fileMap(type = "png")["figure1a"][[1]]
+url <- fileMap(type = "png")["Figure 1a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 
-####_Conclusion_
+#### _Conclusion_
 
-GENCODE annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.
+Refseq annotation supports the presence of a transcript orininating in the antisense orientation from the miR34a gene.
 

### 2018-03-05 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
all verbose changes finished before review

@@
 
-*For a schematic representation of the P1 construct please see Figure 2-Supplement 1a-b.
+*For a schematic representation of the P1 construct please see Supplementary Figure 3a-b.
 
@@
 Luciferase represents miR34a HG and renilla represents miR34a asRNA.
-The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-03-05 inst/p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd
all verbose changes finished before review

@@
 
-See Figure 2c for a schematic representation of the P1 construct.
+See Supplementary Figure 3a-b for a schematic representation of the P1 construct.
 
@@
 Statistical testing compared the shRNA control with shRNA renilla transfected cells using the respective treatment condition.
-The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown.

### 2018-03-05 inst/primer_walk/primer_walk.Rmd
fixing headers in Rmds
re-ran all rmds and added sessionInfo to all
all paths updated to match article inc. Rmd titles
all verbose changes finished before review

@@
 
-####_Results_
+#### _Results_
 
-Primer placement at the locus can be viewed in Supplementary Figure 1b.
+Primer placement at the locus can be viewed in Supplementary Figure 2a.
 
@@
 
-url <- fileMap(type = "png")["figure1e"][[1]]
+url <- fileMap(type = "png")["Figure 1e"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 Although there is some product present for the F12 primer, the majority of transcription seems to be originating from the F11 primer.
-This indicates that the start site is between 71-224bp upstream of the annotated start site.
+This indicates that the start site is between 90-224bp upstream of the annotated start site.
 
 <br></br><br></br>
+
+```{r}
+sessionInfo()
+```

### 2018-03-05 inst/tcga_survival/tcga_survival.Rmd
all verbose changes finished before review

@@
 
-```{r, warning = FALSE}
+```{r, warning = FALSE, fig.align='center', fig.height=8, fig.width=12}
 #Add the colors for the plot to the data

### 2018-03-05 inst/tcga_survival_short/tcga_survival_short.Rmd
all verbose changes finished before review

--- 2018-02-28 inst/tcga_survival_total/tcga_survival_total.Rmd
@@
 ---
-title: "Figure 4a and Supplementary Figure 5"
+title: "Figure 4a"
 subtitle: "Survival curves"
@@
 
-<div class="col2">
-```{r}
+```{r, fig.align='center', fig.height=8, fig.width=12}
+independant <- filter(independant, cancer == "KIRP")
 trash <- pmap(
@@
 ```
-</div>

### 2018-03-05 R/survival.R

@@ -421,7 +421,7 @@ plotKM <- function(data, fit, gene, cancer, p.value) {
     xlab = "Time (years)", ylab = "Survival Probability",
     main = cancer, frame = FALSE
   )
-  mtext(signif(p.value, digits = 3))
+  mtext(paste0("P= ", signif(p.value, digits = 3)))
   legend(
     "bottomleft", legend = ll, bty = "n", text.col = col,
     lty = lty, y.intersp = 1, cex = 0.8

### 2018-03-05 R/utils.R

@@ -36,7 +36,7 @@ fileMap <- function(type) {
     `Figure 3b` = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
     `Figure 3c` = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
     `Figure 3d` = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
-    `Figure 4a` = "tcga_survival_total/tcga_survival_total.Rmd",
+    `Figure 4a` = "tcga_survival_short/tcga_survival_short.Rmd",
     `Figure 4b` = "tcga_survival/tcga_survival.Rmd",
     `Figure 5` = "model/model.Rmd",
     `Supplementary Figure 1a` = "tcga_correlation_table/tcga_correlation_table.Rmd",

### 2018-04-27 inst/lncTAM34a_KD/lncTAM34a_KD.Rmd
adding lncTAM34a KD analysis

--- 2018-02-28 inst/stable_line_expression/stable_line_expression.Rmd
@@
 ---
-
-<style> 
-.caption { 
-  color: Black; 
-  font-family: "Times New Roman", Times, serif;
-  font-size: 1.0em; 
-}
-</style>
 
@@
 
-_Sequencing results_
-
-```{r}
-
-construct <- data.frame(
-    name="miR34a_asRNA",
-    sequence="ACG CGT CTC TCC AGC CCG GGA TCC GGG GAG CTG GGC TGT CCC CAG ACC GAC GGG ACA GCG GCA
-                TCT CCT CCA CCT GAA AAG GAA AGA GGA CCA GTT TGC AGG ACT CCG AAC TGG GCC CGC GAG ATC 
-                TCC ACC TGC GCA AAA CGA AAG GGC GGA TTC TCC TTG GAC TCA CGA GGC AAC CGC TCC CCG GGG 
-                TGA GAA CGG GGG ACT CAT TCC TCC GGC ACT GGG AGA AGA CGA TTC TTC AGG AGG AGG ACA GGG 
-                AAG CGA ATG CTA CCC AGA TGT CTC AGT ATA CTG GCT CGC GGC ACA TCG GGC AAA TGA ACC TAT 
-                CAG ATA ACA ACG GCA GAT CAG ATG CCT GAG CAT TCA GAA GCA ACA GCT GTG GAG CCC CCG TGG 
-                GTT CAG AAG GCC TGG TTC CCG TCT CCA GAA GCC TGG CTC TCC TCC CTC CTG GGC CCA CTA CTT 
-                TGG CTT CTT GTT CCT ACG TAC AAG GAG TTG CGA AGA AGG CAA CTC TTC CCC TCC CTG AAG CCA
-                AAG GAA TGA AAC AGA CTA GGG CGG GAG AGG TGG CCA TCC GTC ATT AGT TGC GGC CAT CA"
-)
-construct
-
-```
-
-<br></br>
-
-_Lentivirus production and infection_
-
-HEK293T cells were transfected with viral and expression constructs using Lipofectamine 2000 (Life Technologies), after which viral supernatants were harvested 48 and 72 hours post-transfection.
-Viral particles were concentrated using PEG-IT solution (Systems Biosciences) according to the manufacturer’s recommendations.
-HEK293T cells were used for virus titration and GFP expression was evaluated 72hrs post-infection via flow cytometry after which TU/ml was calculated.
-Cell lines were subsequently infected with the lentiviral particals using a multuplicity of infection = 1.
-After 48 hours, cells were placed under mycophenolic acid selection and the selection process was monitored using GFP expression via flow cytometry.
-When GFP expression was present in >90% of the cells, cells were frozen for downstream analysis.
-
-<br></br>
-
 _QPCR_
@@
 
-data <- getData("Figure 3a")
-
-#Have to divide the analysis due to the presence of several house 
-#keeping genes.
-gois1 <- c("lncTAM34a", "Actin")
-gois2 <- c("miR34a", "RNU48")
-data1 <- filter(data, gene %in% gois1)
-data2 <- filter(data, gene %in% gois2)
+#data <- getData("Figure 3a")
+data <- read_tsv('~/Github/miR34a_asRNA_project/data-raw/lncTAM34a_KD.txt')
 
 #calculate dct
-groups <- c("Genetic mod", "Biological Replicate", "Cell line", "gene")
+groups <- c("siRNA", "Biological Replicate", "gene")
+gois <- c("miR34a HG", "lncTAM34a")
 
-data1 <- data1 %>%
+data <- data %>%
   technicalMeans(., groups) %>%
-  dct(., gois1, Actin, groups, F) %>%
-  mutate(GOI = as.character(GOI))
-
-data2 <- data2 %>%
-  technicalMeans(., groups) %>%
-  dct(., gois2, RNU48, groups, F) %>%
-  mutate(GOI = as.character(GOI))
-
-data <- bind_rows(data1, data2) %>%
-  mutate(GOI = parse_factor(GOI, levels = c("lncTAM34a", "miR34a")))
+  dct(., gois, Actin, groups, F)
 
@@
 logical <- tibble(
-  `Biological Replicate` = pull(data, `Biological Replicate`) == 2,
-  `Genetic mod` = pull(data, `Genetic mod`) == "mock"
+  siRNA = pull(data, siRNA) == "si-Ctl"
 )
@@
 data <- data %>%
-  ddct(., logical, groups) %>%
+  ddct(., logical, groups, F) %>%
   folds(.)
@@
 #calculate stats
-stats <- calcStats(data, `Genetic mod`, "mock", groups) %>%
+stats <- calcStats(data, siRNA, "si-Ctl", groups) %>%
   pFormat(.)
 
-#format for plotting
-lev <- c("mock", "lncTAM34a", "Skov3\nmock", "Skov3\nlncTAM34a", "Saos2\nmock",   "Saos2\nlncTAM34a")
+#calculate 95% CI and mean on linear scale
+stats <- data %>%
+  filter(siRNA == "si-lncTAM34a") %>%
+  group_by(GOI, siRNA) %>%
+  summarize(
+    CI95l.linear = t.test(fold)$conf.int[1], 
+    CI95h.linear = t.test(fold)$conf.int[2]
+  ) %>%
+  ungroup() %>%
+  full_join(stats, by = c("siRNA", "GOI"))
 
-#data <- data %>%
-#  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
-#  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
-
-#stats <- stats %>%
-#  mutate(`Genetic mod` = gsub("miR34a asRNA", "miR34a\nasRNA", `Genetic mod`)) %>%
-#  mutate(`Genetic mod` = parse_factor(`Genetic mod`, levels = c("mock", "miR34a\nasRNA")))
+stats <- data %>%
+  group_by(GOI, siRNA) %>%
+  summarize(mean.linear = mean(fold)) %>%
+  ungroup() %>%
+  full_join(stats, by = c("siRNA", "GOI"))
 
 #vertical lines and labels in plot
-ys <- stats %>%
-  group_by(`Cell line`) %>%
-  summarize(max = max(CI95h))
-
 vl <- stats %>%
-  group_by(`Cell line`, GOI) %>%
-  summarize(
-    pValue = as.numeric(min(pValue))
-  ) %>%
-  ungroup() %>%
-  pFormat(.) %>%
   mutate(
     x = case_when(
-      GOI ==    "miR34a" ~ 1 + 0.25,
+      GOI == "miR34a HG" ~ 2 - 0.25,
       GOI == "lncTAM34a" ~ 1 - 0.25
@@
     xend = case_when(
-      GOI ==    "miR34a" ~ 2 + 0.25,
-      GOI == "lncTAM34a" ~ 2 - 0.25
-    )
-  ) %>%
-  inner_join(ys) %>%
-  mutate(
-    max = max + c(0.95, 3.35, 0.65, 3.15, 0.65, 3.15)
+      GOI ==  "miR34a HG" ~ 2 + 0.25,
+      GOI == "lncTAM34a" ~ 1 + 0.25
+    ),
+    label = if_else(GOI == "miR34a HG", 2, 1), 
+    max = 1
   )
@@
 
-```{r, fig.align='center', fig.height=8, fig.width=12}
+```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
 
@@
     aes(
-      x = `Genetic mod`,
-      y = log2fold,
-      fill = GOI,
-      group = interaction(`Genetic mod`, GOI)
+      x = `GOI`,
+      y = fold,
+      fill = siRNA
     ),
-    binwidth = 1/10,
+    binwidth = 0.01,
     colour = NA,
@@
     stackdir = 'center',
-    dotsize = 6,
+    dotsize = 1,
     show.legend = TRUE
   ) +
-  facet_grid(
-    . ~ `Cell line`, 
-    scales = "free", 
-    space = "free"
-  ) +
-  scale_y_continuous("\u0394\u0394Ct")+
-  labs(x = "Cell line")
+  scale_y_continuous("Fold")+
+  labs(x = "Gene")
 
@@
     aes(
-      x = `Genetic mod`,
-      ymin = CI95l,
-      ymax = CI95h,
-      group = interaction(`Genetic mod`, GOI)
+      x = GOI,
+      ymin = CI95l.linear,
+      ymax = CI95h.linear,
+      group = interaction(siRNA, GOI)
     ),
@@
     aes(
-      x = `Genetic mod`,
-      y = mean,
-      group = interaction(`Genetic mod`, GOI)
+      x = GOI,
+      y = mean.linear,
+      group = interaction(siRNA, GOI)
     ),
@@
     aes(
-      x = 1.5, 
-      y = max + 0.4, 
+      x = label, 
+      y = max + 0.075, 
       label = pFormat, 
-      group = interaction(`Cell line`, GOI)
+      group = interaction(siRNA, GOI)
     ),
@@
     label.padding = unit(0.01, "lines"),
-    position = position_dodge(width = 0.9),
     show.legend = FALSE,
@@
       x = x,
-      y = max,
+      y = max + 0.05,
       xend = xend,
-      yend = max
+      yend = max + 0.05
     ),
@@
     aes(
-      x = 1.5, 
-      y = max + 1, 
+      x = label, 
+      y = max + 0.075, 
       label = pFormat, 
-      group = interaction(`Cell line`, GOI)
+      group = interaction(siRNA, GOI)
     ),
@@
 miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control.
-The points represent the values obtained from each independant experiment (n >= 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n >= 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-04-27 R/QpcrFuns.R

@@ -201,7 +201,8 @@ calcStats <- function(
     data,
     cnt.group,
     cnt.value,
-    grouping
+    grouping,
+    ...
 ){
     quo.cnt.group <- enquo(cnt.group)
     cnt <- filter(data, (!!quo.cnt.group) == cnt.value) %>%

### 2018-04-27 data-raw/saveRDS.R

@@ -410,4 +410,11 @@ read_tsv('data-raw/tcga_survival.txt') %>%
   select(-PAM50, -lncTAM34a_cna) %>%
   write_rds(., path = './data/tcga_survival.rds')
 
+#lncTAM34a KD
+read_tsv('data-raw/lncTAM34a_KD.txt') %>%
+  mutate(gene = parse_factor(gene, levels = c("lncTAM34a", "miR34a HG", "Actin"))) %>%
+  mutate(siRNA = parse_factor(siRNA, levels = c("si-Ctl", "si-lncTAM34a"))) %>%
+  write_rds(., path = './data/lncTAM34a_KD.rds')
+
+
 #source('./data-raw/saveRDS.R')

### 2018-05-01 inst/lncTAM34a_KD/lncTAM34a_KD.Rmd

@@
 
-We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a.
-To this end, we stably over-expressed miR34a asRNA, using lentiviral transduction, in 3 different p53-null cell lines and monitored the effects on miR34a.
+We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a. To this end, we utilized
+siRNA targeting exon 2 of the miR34a asRNA transcript to lower its expression levels and observe possible effects on 
+miR34a HG in U2OS cells.
 
@@
 
-_miR34a asRNA cloning_
+_Cell culture, transfection and luminescence quantification_
 
-RNA was harvested from U2OS cells using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies).
-500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.
-PCR was run using the miR34aAS_cloning_F4 and miR34aAS_cloning_Ex3_1 primers for 40 cycles at annealing temperature 58˚C and run on an agarose gel.
-Bands were excised and extracted using the QIAquick gel extraction kit (Qiagen).
-PCR products were cloned using the Strata Clone kit (Aligent) and sequenced (results below).
-The insert for the lentiviral construct (p-HIV-I2AG-U6) was subsequently sub-cloned from the sequenced plasmid using primers with PacI and NheI cleavage sites.
-The cloned transcript largley mirrors the GENCODE annotated transcript.
+All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies).
+Growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin.
+Cells were plated at 25,000 cells per well in a 12-well plate and cultured overnight.
+The following day cells were transfected with 10nM si-Ctl or si-lncTAM34a using the standard lipofektamine 2000 (Life Technologies) protocol.
+si-Ctl was purchased from Qiagen (cat.
+nr.
+1027310) and si-lncTAM34a was purchased from Eurofins.
+The sequence for si-Ctl is not available from the manufacturer although the sequence for si-lncTAM34a is shown below.
+Cells were harvested for RNA extraction 48 hours after transfection.
 
@@
 
-_Cloning primers_
+_siRNA_
 
@@
 
-primers <- data.frame(
-    name=c(
-        "miR34aAS_cloning_F4",
-        "miR34aAS_cloning_Ex3_1"
-    ),
-    sequence=c(
-        "ACGCGTCTCTCCAGCCCGGGAT",
-        "AATGATGGCCGCAACTAATGACGG"
+siRNA <- data.frame(
+  name = c("si-lncTAM34a"),
+  sequence = c("GGG AGA AGA CGA UUC UUU")
 )
-)
-primers
+siRNA
 
@@
 QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.
-QPCR for miRNA expression analysis was performed according to the protocol for the TaqMan microRNA Assay kit (Life Technologies) with primer/probe sets purchased from the same company (TaqMan® MicroRNA Assay, hsa-miR-34a, human and Control miRNA Assay, RNU48, human) and the same cycling scheme as above.
 QPCR primers are shown below.
@@
 
-_Analysis_
-
-Two experimental (technical) replicates were included in each QPCR run and delta ct was calculated for each sample using the mean of the gene of interest's technical replicates and the house keeping gene's technical replicates.
-delta-delta ct was calculated for each sample by subtracting the median dct value for the corresponding mock samples.
-Five independant experiments were performed in total.
-The Student's t-test was used to compare the mock vs miR34a asRNA overexpressing group's delta-delta ct values for both genes.
-
-<br></br>
-
-_QPCR primers_
+_QPCR Primers_
 
@@
     name=c(
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "miR34a_asF1",
-        "miR34a_asR1"
-
+        "miR34a asRNA F1",
+        "miR34a asRNA R1",
+        "miR34aHG_F",
+        "miR34aHG_R",
+        "B-actin_F",
+        "B-actin_R"
     ),
     sequence=c(
-        "AGGTCATCACCATTGGCAATGAG",
-        "CTTTCGGGATGTCCACGTCA",
-        "AGCGGCATCTCCTCCACCTGAAA",
-        "TTGCCTCGTGAGTCCAAGGAGAAT"
-
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
+        "AGG TCA TCA CCA TTG GCA ATG AG",
+        "CTT TGC GGA TGT CCA CGT CA"
     )
@@
 
+_Analysis_
+
+Three independant experiments (biological replicates) were performed in total measuring miR34a HG whereas miR34a asRNA was measured in 4 biological replicates.
+The Student's t-test was used to compare the si-Ctl and si-lncTAM34a conditions log2 fold change for both genes.
+
+<br></br>
+
 #### _Results_
@@
 
-#data <- getData("Figure 3a")
-data <- read_tsv('~/Github/miR34a_asRNA_project/data-raw/lncTAM34a_KD.txt')
+data <- getData("Figure 2c")
+#data <- read_tsv('~/Github/miR34a_asRNA_project/data-raw/lncTAM34a_KD.txt')
 
@@
 data <- data %>%
-  technicalMeans(., groups) %>%
-  dct(., gois, Actin, groups, F)
+  gather(Ct, ctMean, -(gene:`Biological Replicate`)) %>%
+  group_by_at(groups) %>%
+  mutate(`Technical Replicate` = 1:n()) %>%
+  dct(., gois, Actin, c(groups, 'Technical Replicate'), F)
 
@@
 data <- data %>%
-  ddct(., logical, groups, F) %>%
+  mutate(br = `Biological Replicate`) %>%
+  ddct(., logical, c(groups, "br")) %>%
+  filter(`Technical Replicate` == 1) %>%
+  select(-`Technical Replicate`) %>%
+  distinct() %>%
+  na.omit() %>%
   folds(.)
@@
 stats <- data %>%
-  filter(siRNA == "si-lncTAM34a") %>%
+  #filter(siRNA == "si-lncTAM34a") %>%
   group_by(GOI, siRNA) %>%
@@
     label = if_else(GOI == "miR34a HG", 2, 1), 
-    max = 1
+    max = max(CI95h.linear)
   )
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3a"][[1]])
-# ggsave(
-#    plot = figure,
-#    filename = path,
-#    device = cairo_pdf,
-#    height = 60,
-#    width = 83,
-#    units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2c"][[1]])
+ggsave(
+  plot = figure,
+  filename = path,
+  device = cairo_pdf,
+  height = 60,
+  width = 83,
+  units = "mm"
+)
 ```
@@
 <div class="caption">
-miR34a asRNA and miR34a levels in PC3, Skov3, and Saos2 cell lines stably over-expressing miR34a asRNA compared to mock over-expressing control.
-The points represent the values obtained from each independant experiment (n >= 3).
-95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
+lncTAM34a (n = 4) and miR34a HG (n = 3) levels after 48 hour siRNA-mediated knock down of lncTAM34a in U2OS cells.
 </div>
@@
 
-miR34a asRNA over-expression causes a concominant up-regulation of miR34a in all 3 cell lines. This indicates that miR34a asRNA concordantly regulates miR34a.
+miR34a asRNA KD gives rise to a ~20% decrease in miR34a HG expression levels.
 

### 2018-05-12 inst/lncTAM34a_KD/lncTAM34a_KD.Rmd
lncTAM34a KD analysis and figure

@@
 ---
-title: "Figure 3a"
-subtitle: "miR34a asRNA stable over-expression cell lines"
+title: "Figure 2c"
+subtitle: "miR34a asRNA knock down in U2Os cells"
 author: "Jason T. Serviss"
@@
 data <- getData("Figure 2c")
-#data <- read_tsv('~/Github/miR34a_asRNA_project/data-raw/lncTAM34a_KD.txt')
 
@@
     stackdir = 'center',
-    dotsize = 1,
+    dotsize = 4,
     show.legend = TRUE
@@
       x = label, 
-      y = max + 0.075, 
+      y = max + 0.1, 
       label = pFormat, 
@@
   height = 60,
-  width = 83,
+  width = 68,
   units = "mm"

### 2018-05-12 inst/stable_line_proliferation/stable_line_proliferation.Rmd
adding stable line proliferation rds and raw processing script

--- 2017-12-09 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
@@
 ---
-title: "Figure 3c"
-subtitle: "Monitoring growth of miR34a asRNA overexpressings cells under conditions of starvation"
+title: "???"
+subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
 author: "Jason T. Serviss"
@@
 
-url <- fileMap(type = "rds")["Figure 3c"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Figure 3c")
 

### 2018-05-12 data-raw/saveRDS.R

@@ -416,5 +416,69 @@ read_tsv('data-raw/lncTAM34a_KD.txt') %>%
   mutate(siRNA = parse_factor(siRNA, levels = c("si-Ctl", "si-lncTAM34a"))) %>%
   write_rds(., path = './data/lncTAM34a_KD.rds')
 
+#Stable line proliferation
+##process day0 data
+f <- list.files(
+  'data-raw/stable_line_proliferation', pattern = ".*day0.*",
+  recursive = TRUE, full.names = TRUE
+)
+
+data0 <- f %>%
+  map(read_tsv) %>%
+  setNames(str_replace(f, ".*(day.)_(.*)_.*$", "\\2_\\1")) %>%
+  bind_rows(.id = "id") %>%
+  bind_rows(., ., .) %>%
+  separate(id, c("sample", "day"), sep = "_") %>%
+  mutate(condition = c(
+      rep("normal", nrow(.) / 3),
+      rep("0.1", nrow(.) / 3),
+      rep("HBSS", nrow(.) / 3)
+  )) %>%
+  unite(tmp, sample, condition, sep = "") %>%
+  unite(id, tmp, day)
+
+##process other files
+f <- list.files(
+  'data-raw/stable_line_proliferation', pattern = ".*day[1-3].*",
+  recursive = TRUE, full.names = TRUE
+)
+
+f %>%
+  map(read_tsv) %>%
+  setNames(str_replace(f, ".*(day.)_(.*)_.*$", "\\2_\\1")) %>%
+  bind_rows(.id = "id") %>%
+  bind_rows(data0) %>%
+  separate(id, c("Sample", "Time"), sep = "_", remove = FALSE) %>%
+  mutate(
+    Time = case_when(
+      Time == "day0" ~ "0",
+      Time == "day1" ~ "24",
+      Time == "day2" ~ "48",
+      Time == "day3" ~ "72"
+    ),
+    `Cell line` = case_when(
+      str_detect(Sample, "^m") ~ "Mock",
+      str_detect(Sample, "^[f | F]") ~ "lncTAM34a",
+      TRUE ~ Sample
+    ),
+    Condition = case_when(
+      str_detect(Sample, "0.1") ~ "0.1% FBS",
+      str_detect(Sample, "HBSS") ~ "HBSS",
+      str_detect(Sample, "normal") ~ "Normal"
+    ),
+    `Technical replicate` = case_when(
+      str_detect(Sample, "t1") ~ 1,
[…]

### 2018-05-12 data-raw/saveRDS.R
new data now sucessfully added

@@ -417,27 +417,6 @@ read_tsv('data-raw/lncTAM34a_KD.txt') %>%
   write_rds(., path = './data/lncTAM34a_KD.rds')
 
 #Stable line proliferation
-##process day0 data
-f <- list.files(
-  'data-raw/stable_line_proliferation', pattern = ".*day0.*",
-  recursive = TRUE, full.names = TRUE
-)
-
-data0 <- f %>%
-  map(read_tsv) %>%
-  setNames(str_replace(f, ".*(day.)_(.*)_.*$", "\\2_\\1")) %>%
-  bind_rows(.id = "id") %>%
-  bind_rows(., ., .) %>%
-  separate(id, c("sample", "day"), sep = "_") %>%
-  mutate(condition = c(
-      rep("normal", nrow(.) / 3),
-      rep("0.1", nrow(.) / 3),
-      rep("HBSS", nrow(.) / 3)
-  )) %>%
-  unite(tmp, sample, condition, sep = "") %>%
-  unite(id, tmp, day)
-
-##process other files
 f <- list.files(
   'data-raw/stable_line_proliferation', pattern = "\\.csv$",
   recursive = TRUE, full.names = TRUE

### 2018-05-12 inst/stable_line_proliferation/stable_line_proliferation.Rmd
adding stable line proliferation analysis

@@
     "ggthemes",
-    "readr",
     "miR34AasRNAproject",
-    "grid",
-    "gtable",
     "broom"
@@
 
-_Cell culture and confluency quantification_
+_Cell culture and proliferation assay_
 
-10^4 PC3 cells, either miR34a asRNA overexpressing or WT, were seeded in 96 well plates.
-After attachment (3-4h) media was replaced with either RPMI (Gibco, life technology) (supplemented with 2mM L-glutamine, 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum) or HBSS.
-Cells were incubated in Spark Multimode Microplate reader for 48 hours at 37°C with 5% CO2 in a humidity chamber.
-Confluency was measured every hour.
+20^4 PC3 cells, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet (!!!!) for 5min and subsequently seeded in 12 well plates.
+Time 0 measurements were taken once cells had attatched and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaniously initiated in the remaining cells.
+RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum.
+Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter).
+Time 0 was performed in biological triplicate and technical duplicate whereas all other time points were performed in biological triplicates with one technical replicate.
 
@@
 
-data <- getData("Figure 3c")
+#data <- getData("Figure 3c")
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master"
+path <- "data/stable_line_proliferation.rds"
+data <- read_rds(gzcon(url(file.path(dataUrl, path))))
 
-#normalize to first time point for control (Mock)
-.normFun <- function(
-  data,
-  Confluency,
-  Treatment,
-  Biological.Replicate,
-  Technical.Replicate,
-  Cell.line
-){
-  bool1 <- data$Treatment == Treatment
-  bool2 <- data$`Biological Replicate` == Biological.Replicate
-  bool3 <- data$`Technical Replicate` == Technical.Replicate
-  bool4 <- data$Time == 0
-  bool5 <- data$`Cell line` == Cell.line
-  bool <- bool1 & bool2 & bool3 & bool4 & bool5
-  Confluency / pull(data, Confluency)[bool]
-}
+#remove cells with negative fluorescence. Consider these 1224 cells artifacts 
+data <- filter(data, Violet > 0)
 
-data <- data %>%
-  group_by(Treatment, `Biological Replicate`, `Technical Replicate`, Time, `Cell line`) %>%
+##fix day0 data
+#Since there are no treatments at time 0 and we want a corresponding Time 0 for 
+#each of the treated samples, here we expand the Time 0 sample 3 times, one for 
+#each treatment condition at later time points.
+dataExpandT0 <- data %>% 
+  filter(Time == 0) %>%
+  bind_rows(., ., .) %>%
+  mutate(Condition = c(
+      rep("Normal", nrow(.) / 3),
+      rep("0.1% FBS", nrow(.) / 3),
+      rep("HBSS", nrow(.) / 3)
+  )) %>%
+  bind_rows(filter(data, Time != 0))
+
+#calculate means of technical replicates in day0
+#need to subsample first so that each condition has the same number of cells
+set.seed(2387723)
+data0 <- dataExpandT0 %>%
+  filter(Time == "0" & Type == "stained") %>%
+  select(-`FSC-A`, -`BSC-A`) %>%
+  group_by(`Biological replicate`, `Technical replicate`, Condition, `Cell line`, Type) %>%
+  sample_n(size = 5000) %>%
+  ungroup() %>%
+  arrange(`Cell line`, Condition, `Biological replicate`, `Technical replicate`, Violet) %>%
   mutate(
-    normConfluency = .normFun(
-      data,
-      Confluency,
-      Treatment,
-      `Biological Replicate`,
-      `Technical Replicate`,
-      `Cell line`
-    )
+    `Technical replicate` = rep(c("Tr1", "Tr2"), nrow(.)/2),
+    row = rep(1:(nrow(.) / 2), each = 2)
   ) %>%
+  spread(`Technical replicate`, Violet) %>%
+  rowwise() %>%
+  mutate(Violet = mean(c(Tr1, Tr2))) %>%
+  ungroup() %>%
+  select(-(row:Tr2)) %>%
+  bind_rows(., ., ., .) %>%
+  mutate(Time = rep(c("0", "24", "48", "72"), each = nrow(.) / 4)) %>%
+  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet)
+
+#Randomly sample 5000 cells from each condition so that all samples have the 
+#same number of cells
+set.seed(2387723)
+subData <- dataExpandT0 %>%
+  select(-`FSC-A`, -`BSC-A`, -`Technical replicate`) %>%
+  filter(Type == "stained" & Time != "0") %>%
+  group_by(`Biological replicate`, Condition, `Cell line`, Type, Time) %>%
+  sample_n(size = 5000) %>%
   ungroup()
 
-#calculate mean for each technical replicate
-data <- data %>%
-  group_by(Treatment, `Biological Replicate`, Time, `Cell line`) %>%
+#add back data from time point 0 with mean technical replicates calculated
+#in addition, add a time point 0 corresponding to each cell and condition and
+##calculate the difference for each cell from time 0
+subData <- subData %>%
+  bind_rows(filter(data0, Time == "0")) %>%
+  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet) %>%
+  add_column(day0Violet = data0$Violet) %>%
+  mutate(violetNorm = Violet - day0Violet)
+
+means <- subData %>%
+  group_by(Time, `Cell line`, Condition) %>%
   summarize(
-    techMean = mean(normConfluency)
-  ) %>%
-  ungroup()
+    mean = mean(violetNorm),
+    CI95l = t.test(violetNorm)$conf.int[1],
+    CI95h = t.test(violetNorm)$conf.int[2]
+  )
 
-#calculate stats
-stats <- data %>%
-  filter(Time != 0) %>%
-  group_by(`Cell line`, Treatment, Time) %>%
-  summarize(
-    min = min(techMean),
-    max = max(techMean),
-    mean = mean(techMean),
-    median = median(techMean),
-    CI95l = t.test(techMean)$conf.int[1],
-    CI95h = t.test(techMean)$conf.int[2]
-  )
+subData %>%
+  ggplot() +
+  geom_smooth(aes(Time, violetNorm, colour = `Cell line`, group = `Cell line`), method = "lm") +
+  geom_point(data = means, aes(Time, mean, colour = `Cell line`, group = `Cell line`)) +
+  facet_wrap(~Condition) + 
+  scale_y_continuous(breaks = c(0, -5000, -10000, -15000, -20000)) +
+  theme_few()
 

### 2018-05-15 inst/figure1d/figure1d.Rmd
updating all paths to figure numbers

--- 2017-11-20 inst/3_prime_race/3_prime_race.Rmd
@@
 
-url <- fileMap(type = "png")["figure1d"][[1]]
+url <- fileMap(type = "png")["Figure 1d"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))
@@
 <div class = "caption">
-3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript (LINC01759) from GENCODE.
+3’-RACE sequencing results displayed in the UCSC genome browser together with the annotated miR34a asRNA transcript (LINC01759) from Refseq
 </div>

### 2018-05-15 inst/figure2a/figure2a.Rmd
updating all paths to figure numbers

--- 2018-02-28 inst/hct116_hek293t_dox/hct116_hek293t_dox.Rmd
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
-ggsave(
-   plot = figure,
-   filename = path,
-   device = cairo_pdf,
-   height = 60,
-   width = 53,
-   units = "mm"
-)
+#path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2a"][[1]])
+#ggsave(
+#   plot = figure,
+#   filename = path,
+#   device = cairo_pdf,
+#   height = 60,
+#   width = 53,
+#   units = "mm"
+#)
 ```
@@
 Q-PCR showing miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after treatment with 200 ng/ml doxorubicin for 24hrs.
-The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-05-15 inst/figure3b/figure3b.Rmd
updating all paths to figure numbers

--- 2018-02-28 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
@@
 _Analysis_
+
 The cell cycle phases ModFit software (Verity Software House) was used to quantify the percentage of cells in each cell cycle phase.
@@
 Cell cycle analysis in miR34a asRNA over-expressing PC3, Skov3, and Saos2 stable cell lines compared to their respective mock control.
-The points represent the values obtained from each independant experiment (PC3 n = 5; Skov3 n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (PC3 n = 5; Skov3 n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-05-15 inst/figure3d/figure3d.Rmd
updating all paths to figure numbers

--- 2018-02-12 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
@@
 ```{r, message = FALSE}
-url <- fileMap(type = "rds")["Figure 3d"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+data <- getData("Figure 3d")
 
@@
 Phosphorylated Poll II ChIP in miR34a asRNA over-expressing PC3 stable cell lines compared to their respective mock control.
-The points represent the values obtained from each independant experiment (n = 4) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 4).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-05-15 inst/figure5/figure5.Rmd
updating all paths to figure numbers

---
title: "Figure 5"
subtitle: "A graphical summary of the proposed lncTAM34a function"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

#library(grDevices)
```

```{r}

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

```

```{r, out.width = "850px"}

url <- fileMap(type = "png")["Figure 5"][[1]]
knitr::include_graphics(file.path(projectUrl, url))

```

<div class = "caption">
<strong>Figure 5: A graphical summary of the proposed lncTAM34a function.</strong> Stress stimuli, originating in the cytoplasm or nucleus, activate TP53 as well as additional factors. These factors then bind to the miR34a promoter and drive baseline transcription levels of the sense and antisense strands. lncTAM34a serves to further increases miR34a HG transcription levels resulting in enrichment of polymerase II at the miR34a promoter and a positive feed-forward loop. lncTAM34a-mediated increases in miR34a HG potentially occur via direct DNA binding alone, by direct DNA binding and recruitment of additional factors, or through a yet unknown mechanism. miR34a HG then, in turn, is spliced and processed before being exported to the cytoplasm. The miR34a pre-miRNA then undergoes further processing before the mature miR34a binds to the RISC complex allowing it to bind and repress its targets and exert its tumor suppressive effects.
</div>

### 2018-05-15 inst/supp_figure1a/supp_figure1a.Rmd
updating all paths to figure numbers

--- 2017-12-12 inst/tcga_correlation_table/tcga_correlation_table.Rmd
@@
 ---
-title: "Figure 1-Supplement 1a"
+title: "Supplementary Figure 1a"
 subtitle: "TCGA correlation table"
@@
 
-```{r}
-
-projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
-dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
-
-```
-
 <br></br>
@@
 ```{r, warning = FALSE}
-url <- fileMap(type = "rds")["Figure 1c"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+
+data <- getData("Supplementary Figure 1a")
 

### 2018-05-15 inst/supp_figure2a/supp_figure2a.Rmd
updating all paths to figure numbers

--- 2017-12-09 inst/primer_walk_schematic/primer_walk_schematic.Rmd
@@
 ---
-title: "Figure 1-Supplement 2a"
+title: "Supplementary Figure 2a"
 subtitle: "Primer walk schematic"
@@
 
-url <- fileMap(type = "png")["Figure 1-Supplement 2a"][[1]]
+url <- fileMap(type = "png")["Supplementary Figure 2a"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2018-05-15 inst/supp_figure2b/supp_figure2b.Rmd
updating all paths to figure numbers

--- 2017-12-09 inst/polyadenylation/polyadenylation.Rmd
@@
 ---
-title: "Figure 1-Supplement 2b"
+title: "Supplementary Figure 2b"
 subtitle: "miR34a asRNA polyadenylation"
@@
 
-url <- fileMap(type = "png")["Figure 1-Supplement 2b"][[1]]
+url <- fileMap(type = "png")["Supplementary Figure 2b"][[1]]
 knitr::include_graphics(file.path(projectUrl, url))

### 2018-05-15 inst/supp_figure2d/supp_figure2d.Rmd
updating all paths to figure numbers

--- 2018-02-14 inst/cellular_localization_encode/cellular_localization_encode.Rmd
@@
 ---
-title: "Figure 1-Supplement 2e"
+title: "Supplementary Figure 2d"
 subtitle: "miR34a asRNA cellular localization"
@@
 
-url <- fileMap(type = "rds")["Figure 1-Supplement 2e"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Supplementary Figure 2d")
 

### 2018-05-15 inst/supp_figure2e/supp_figure2e.Rmd
updating all paths to figure numbers

--- 2017-12-09 inst/coding_potential_cpc/coding_potential_cpc.Rmd
@@
 ---
-title: "Figure 1-Supplement 2d"
+title: "Supplementary Figure 2e"
 subtitle: "miR34a asRNA coding potential via CPC"
@@
 
-url <- fileMap(type = "rds")["Figure 1-Supplement 2d"][[1]]
-cpat <- read_rds(url(file.path(dataUrl, url)))
+cpat <- getData("Supplementary Figure 2e")
 cpat

### 2018-05-15 inst/supp_figure3c/supp_figure3c.Rmd
updating all paths to figure numbers

--- 2018-02-14 inst/p1_hek293t/p1_hek293t.Rmd
@@
 ---
-title: "Figure 2-Supplement 2"
+title: "Supplementary Figure 3c"
 subtitle: "P1 shRenilla HEK293t transfections"
@@
 vignette: |
-  %\VignetteIndexEntry{Vignette Title} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
+  %\VignetteIndexEntry{Vignette Title} 
+  %\VignetteEngine{knitr::rmarkdown} 
+  %\VignetteEncoding{UTF-8}
 editor_options: 
@@
 
-url <- fileMap(type = "rds")["Figure 2-Supplement 2"][[1]]
-data <- read_rds(gzcon(url(file.path(dataUrl, url))))
+data <- getData("Supplementary Figure 3c")
 

### 2018-05-15 inst/supp_figure5c/supp_figure5c.Rmd
updating all paths to figure numbers

---
title: "Supplementary Figure 6"
subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
author: "Jason T. Serviss"
date: "31/01/2017"
output:
  html_document:
    theme: flatly
    code_folding: hide
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

<style> 
.caption { 
  color: Black; 
  font-family: "Times New Roman", Times, serif;
  font-size: 1.0em; 
}
</style>

```{r, echo = FALSE, message = FALSE}

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "miR34AasRNAproject",
    "broom"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

```

<br></br>

#### _Introduction_

As p53 is a well-known regulator of senescence, growth, and apoptosis and has been shown to specifically important under conditions of cellular stress, such as starvation. Therefore, we investigated whether overexpression of miR34a AS affects proliferation rate under normal and starvation conditions.

<br></br>

#### _Methods_

<br></br>

_Cell culture and proliferation assay_

20^4 PC3 cells, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet (Invitrogen) for 5min and subsequently seeded in 12 well plates. Time 0 measurements were taken once cells had attatched and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaniously initiated in the remaining cells. RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum. Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter). Time 0 was performed in biological triplicate and technical duplicate whereas all other time points were performed in biological triplicates with one technical replicate.

<br></br>

_Analysis_

Each replicate and condition were subsampled so that each had a total of 10000 cells. The mean of each technical replicate for time point 0 was calculated and, subsequently, the time 0 flouresence intensity was subtracted from each sample. The mean difference in flouresence intensity was then calculated for each biological replicate and condition and used to build a polynomial model per condition (i.e. RPMI, 0.1% FBS, and HBSS).

<br></br>

#### _Results_

```{r, message = FALSE}

data <- getData("Supplementary Figure 5c")

#remove cells with negative fluorescence. Consider these 1224 cells artifacts 
data <- filter(data, Violet > 0)

##fix day0 data
#Since there are no treatments at time 0 and we want a corresponding Time 0 for 
#each of the treated samples, here we expand the Time 0 sample 3 times, one for 
#each treatment condition at later time points.
dataExpandT0 <- data %>% 
  filter(Time == 0) %>%
  bind_rows(., ., .) %>%
  mutate(Condition = c(
      rep("RPMI", nrow(.) / 3),
      rep("0.1% FBS", nrow(.) / 3),
      rep("HBSS", nrow(.) / 3)
  )) %>%
  bind_rows(filter(data, Time != 0))

#calculate means of technical replicates in day0
#need to subsample first so that each condition has the same number of cells
sampleN <- 10000

set.seed(2387723)
data0 <- dataExpandT0 %>%
  filter(Time == "0" & Type == "stained") %>%
  select(-`FSC-A`, -`BSC-A`) %>%
  group_by(`Biological replicate`, `Technical replicate`, Condition, `Cell line`, Type) %>%
  sample_n(size = sampleN) %>%
  ungroup() %>%
  arrange(`Cell line`, Condition, `Biological replicate`, `Technical replicate`, Violet) %>%
  mutate(
    `Technical replicate` = rep(c("Tr1", "Tr2"), nrow(.)/2),
    row = rep(1:(nrow(.) / 2), each = 2)
  ) %>%
  spread(`Technical replicate`, Violet) %>%
  rowwise() %>%
  mutate(Violet = mean(c(Tr1, Tr2))) %>%
  ungroup() %>%
  select(-(row:Tr2)) %>%
  bind_rows(., ., ., .) %>%
  mutate(Time = rep(c("0", "24", "48", "72"), each = nrow(.) / 4)) %>%
  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet)

#Randomly sample 10000 cells from each condition so that all samples have the 
#same number of cells
set.seed(2387723)
subData <- dataExpandT0 %>%
  select(-`FSC-A`, -`BSC-A`, -`Technical replicate`) %>%
  filter(Type == "stained" & Time != "0") %>%
  group_by(`Biological replicate`, Condition, `Cell line`, Type, Time) %>%
  sample_n(size = sampleN) %>%
  ungroup()

#add back data from time point 0 with mean technical replicates calculated
#in addition, add a time point 0 corresponding to each cell and condition and
##calculate the difference for each cell from time 0
subData <- subData %>%
  bind_rows(filter(data0, Time == "0")) %>%
  arrange(Time, `Cell line`, Condition, `Biological replicate`, Violet) %>%
  add_column(day0Violet = data0$Violet) %>%
  mutate(violetNorm = Violet - day0Violet) %>%
  mutate(
    Time = as.numeric(Time), 
    cellLine = parse_factor(`Cell line`, levels = c("mock", "lncTAM34a"))
  ) %>% 
  select(-`Cell line`)

#calculate mean normalized flouresence for each condition and biological replicate
subDataMeans <- subData %>%
  group_by(cellLine, Time, Condition, `Biological replicate`) %>%
  summarize(mean = mean(violetNorm)) %>%
  ungroup()

#model each condition using the mean of all biological replicates using a lm
model.info <- subDataMeans %>%
  group_by(Condition) %>%
  do(glance(lm(mean ~ poly(Time, 3) + cellLine, data = .))) %>%
  ungroup()

as.data.frame(model.info)

proliferation.lm <- subDataMeans %>%
  group_by(Condition) %>%
  do(tidy(lm(mean ~ poly(Time, 3) + cellLine, data = .))) %>%
  ungroup()

as.data.frame(proliferation.lm)

#extract model components to plot
model.data <- proliferation.lm %>%
  filter(term == "cellLinelncTAM34a") %>%
  mutate(Condition = parse_factor(
    Condition, levels = c("RPMI", "0.1% FBS", "HBSS")
  )) %>% 
  rename(pValue = p.value) %>%
  pFormat(.)
```

```{r, fig.align='center', fig.height=8, fig.width=12}
p <- subDataMeans %>% 
  mutate(Condition = parse_factor(Condition, levels = c("RPMI", "0.1% FBS", "HBSS"))) %>% 
  ggplot() + 
  geom_smooth(
    aes(Time, mean, colour = cellLine, group = cellLine), colour = "lightgrey",
    method = "lm", formula = y ~ poly(x, 3), size = 0.5, alpha = 0.1
  ) +
  geom_boxplot(
    aes(Time, mean, colour = cellLine, group = interaction(Time, cellLine)),
    fatten = 2, lwd = 0.2
  ) +
  facet_wrap(~Condition) + 
  scale_x_continuous(breaks = c(0, 24, 48, 72)) +
  labs(
    x = "Time (hours)", 
    y = "Mean \U0394 fluorescence intensity"
  ) + 
  guides(colour = guide_legend(title = "Cell line"))

markdown <- p +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 2000, label = paste0("estimate=", round(estimate))),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
  ) +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 1500, label = paste0("std.error=", round(std.error))),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
  ) +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 1000, label = paste0("p=", pFormat)),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
  )

plotRmarkdown(markdown)

pdf <- p +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 3000, label = paste0("estimate=", round(estimate))),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
  ) +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 2000, label = paste0("std.error=", round(std.error))),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
  ) +
  geom_label(
    data = model.data, 
    aes(x = 0, y = 1000, label = paste0("p=", pFormat)),
    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9), show.legend = FALSE,
    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
  )

figure <- plotPDF(pdf)

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 5c"][[1]])
ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 100,
  units = "mm"
)
```

<div class="caption">
The effects of miR34a asRNA overexpression on proliferation in normal and starvation conditions in the PC3 prostate cancer cell line. The y-axis illustrates the mean difference (&Delta;; Time - Time 0) in flouresence intensity for each biological replicate and condition where decreased flouresence intensity indicates increased proliferation. Boxplots show the distribution of the mean differences from each of the biological replicates (n = 3). Grey lines indicate the polynomial regression model with the shadows indicating the 95% confidence intervals. Estimates, standard error (std.error), and P values for the cell line covariate for each model are indicated in the upper left hand corner.
</div>

<br></br>

#### _Conclusions_

miR34a asRNA overexpression causes a decrease in cell growth under all examined conditions.

<br></br><br></br>

```{r}
sessionInfo()
```

### 2018-05-15 inst/supp_figure7/supp_figure7.Rmd
updating all paths to figure numbers

--- 2018-02-28 inst/lnc34a_splice_jnc/lnc34a_splice_jnc.Rmd
@@
 #### _Conclusions_
-Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (**Supplementary Fig 1d.**) with those being the most highly expressed corresponding to the annotated miR34a asRNA transcript.
+Multiple splice junctions correspond to the miR34a asRNA transcrips and its isoforms (**Supplementary Fig 2c.**) with those being the most highly expressed corresponding to the annotated miR34a asRNA transcript.
 Despite this, no splice junctions appear to correspond to the intron in the lnc34a transcript.

### 2018-05-15 R/utils.R

@@ -22,42 +22,42 @@ NULL
 fileMap <- function(type) {
   pList <- list(
     `All figures` = "recreate_all_figures/recreate_all_figures.Rmd",
-    `Figure 1a` = "mir34a_locus/mir34a_locus.Rmd",
-    `Figure 1b` = "mir34a_asRNA_cell_panel/mir34a_asRNA_cell_panel.Rmd",
-    `Figure 1c` = "tcga_correlation/tcga_correlation.Rmd",
-    `Figure 1d` = "3_prime_race/3_prime_race.Rmd",
-    `Figure 1e` = "primer_walk/primer_walk.Rmd",
-    `Figure 1f` = "coding_potential_cpat/coding_potential_cpat.Rmd",
-    `Figure 2a` = "hct116_hek293t_dox/hct116_hek293t_dox.Rmd",
-    `Figure 2b` = "hct116_p53_null/hct116_p53_null.Rmd",
-    `Figure 2c` = "lncTAM34a_KD/lncTAM34a_KD.Rmd",
-    `Figure 2d` = "p1_hct116_hek293t/p1_hct116_hek293t.Rmd",
-    `Figure 2e` = "p1_shrna_renilla_dox/p1_shrna_renilla_dox.Rmd",
-    `Figure 3a` = "stable_line_expression/stable_line_expression.Rmd",
-    `Figure 3b` = "stable_line_cell_cycle/stable_line_cell_cycle.Rmd",
-    `Figure 3c` = "stable_line_growth_starvation/stable_line_growth_starvation.Rmd",
-    `Figure 3d` = "stable_line_pol2_chip/stable_line_pol2_chip.Rmd",
-    `Figure 4a` = "tcga_survival_short/tcga_survival_short.Rmd",
-    `Figure 4b` = "tcga_survival/tcga_survival.Rmd",
-    `Figure 5` = "model/model.Rmd",
-    `Supplementary Figure 1a` = "tcga_correlation_table/tcga_correlation_table.Rmd",
-    `Supplementary Figure 1b` = "tcga_expression/tcga_expression.Rmd",
-    `Supplementary Figure 2a` = "primer_walk_schematic/primer_walk_schematic.Rmd",
-    `Supplementary Figure 2b` = "polyadenylation/polyadenylation.Rmd",
-    `Supplementary Figure 2c` = "isoforms/isoforms.Rmd",
[…]

### 2018-05-15 data-raw/saveRDS.R

@@ -1,9 +1,44 @@
 library(tidyverse)
 library(miR34AasRNAproject)
 
-#hct116_p53_null
+#Figure 1c, tcga_correlation
+print("processing tcga_correlation")
+read_tsv('./data-raw/figure1c.txt') %>%
+  mutate(
+    TP53 = as.numeric(TP53),
+    RP3 = as.numeric(RP3),
+    RP3_cna = as.numeric(RP3_cna),
+    miR34a = as.numeric(miR34a)
+  ) %>%
+  write_rds(., path = './data/figure1c.rds')
+
+#Figure 1f, coding_potential_cpat
+print("processing coding_potential_cpat")
+  read_tsv('./data-raw/figure1f.txt') %>%
+  write_rds(., path = './data/figure1f.rds')
+
+#Figure 2a, hct116_hek293t_dox
+print("processing hct116_hek293t_dox")
+read_tsv('./data-raw/figure2a.txt', col_names = TRUE) %>%
+  rename(
+    `Biological Replicate` = experiment,
+    `Cell line` = cellLine,
+    Treatment = treatment
+  ) %>%
+  mutate(Treatment = parse_factor(
+    Treatment,
+    levels = c("untreated", "doxorubicin")
+  )) %>%
+  mutate(gene = case_when(
+    gene == "B-actin" ~ "Actin",
+    gene == "miR34a asRNA" ~ "lncTAM34a",
+    TRUE              ~ gene
+  )) %>%
+  write_rds(., path = './data/figure2a.rds')
+
+#Figure 2b, hct116_p53_null
 print("processing hct116_p53_null")
-read_tsv('./data-raw/hct116_p53_null.txt', col_names = TRUE) %>%
+read_tsv('./data-raw/figure2b.txt', col_names = TRUE) %>%
   rename(gene = Target) %>%
   mutate(
     Condition = case_when(
@@ -32,30 +67,17 @@ read_tsv('./data-raw/hct116_p53_null.txt', col_names = TRUE) %>%
       levels = c("miR34a HG", "lncTAM34a", "Actin")
     )
   ) %>%
-  write_rds(., path = './data/hct116_p53_null.rds')
+  write_rds(., path = './data/figure2b.rds')
 
-#hct116_hek293t_dox
-print("processing hct116_hek293t_dox")
-read_tsv('./data-raw/hct116_hek293t_dox.txt', col_names = TRUE) %>%
-  rename(
-    `Biological Replicate` = experiment,
-    `Cell line` = cellLine,
[…]

### 2018-05-15 inst/supp_figure4c/supp_figure4c.Rmd
updating all paths to figure numbers
fixing figure labels in Rmds

--- 2018-02-28 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
@@
 ---
-title: "Supplementary Figure 4b"
+title: "Supplementary Figure 4c"
 subtitle: "CCND1 expression in PC3 stable cell lines"
@@
 
-data <- getData("Supplementary Figure 4b")
+data <- getData("Supplementary Figure 4c")
 
@@
 Q-PCR showing cyclin D1 levels in PC3 miR34a asRNA over-expressing stable lines.
-The points represent the values obtained from each independant experiment (n = 6) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 6).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-05-15 inst/supp_figure4d/supp_figure4d.Rmd
updating all paths to figure numbers
fixing figure labels in Rmds

--- 2018-02-28 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
@@
 ---
-title: "Supplementary Figure 4c"
+title: "Supplementary Figure 4d"
 subtitle: "CCND1 protein expression in PC3 stable lines"
@@
 
-url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot.png"
+url <- "supp_figure4d/supp_figure4d_gel.png"
 knitr::include_graphics(file.path(projectUrl, url))
@@
 
-data <- getData("Supplementary Figure 4c")
+data <- getData("Supplementary Figure 4d")
 
@@
 <div class="caption">
+
 Western blot quantification showing cyclin D1 protein levels in PC3 miR34a asRNA over-expressing stable lines compared to mock.
-The points represent the values obtained from each independant experiment (n = 3) whereas, the gray shadow represents the distribution of those points.
+The points represent the values obtained from each independant experiment (n = 3).
 95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.

### 2018-05-15 inst/supp_figure5c/supp_figure5c.Rmd
fixing figure labels in Rmds

@@
 ---
-title: "Supplementary Figure 6"
+title: "Supplementary Figure 5c"
 subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"

### 2018-05-15 inst/supp_figure8/supp_figure8.Rmd
fixing figure labels in Rmds

--- 2018-02-28 inst/lnc34a_cage/lnc34a_cage.Rmd
@@
 ---
-title: "Supplementary Figure 6"
+title: "Supplementary Figure 8"
 subtitle: "Lnc34a CAGE"
@@
 nrCellLinesDown <- function() {
-  getData("Supplementary Figure 6") %>% 
+  getData("Supplementary Figure 8") %>% 
     pull(cell) %>%
@@
 cellLinesInFinal <- function() {
-  getData("Supplementary Figure 6") %>%
+  getData("Supplementary Figure 8") %>%
     pull(cell) %>%
@@
 RNAprepTable <- function() {
-  getData("Supplementary Figure 6") %>%
+  getData("Supplementary Figure 8") %>%
     mutate(`rna extract` = str_replace(`rna extract`, "total", "total RNA")) %>%
@@
 localizationTable <- function() {
-  getData("Supplementary Figure 6") %>%
+  getData("Supplementary Figure 8") %>%
     select(localization) %>%
@@
 #cage data
-cage <- getData("Supplementary Figure 6") %>%
+cage <- getData("Supplementary Figure 8") %>%
   select(start, stop, level) %>%
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Document 1a"][[1]])
+# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 8"][[1]])
 # ggsave(

### 2018-05-15 R/utils.R

@@ -217,7 +217,7 @@ getData <- function(figure) {
   if(!figure %in% figsWithData) {
     stop("There is no data for the figure you specified")
   }
-  if(figure == "Figure 4a") figure <- "Figure 4b"
+  if(figure == "Figure 4b") figure <- "Figure 4a"
   if(figure == "Supplementary Figure 1a") figure <- "Figure 1c"
   if(figure == "Supplementary Figure 1b") figure <- "Figure 1c"
   if(figure == "Supplementary Figure 6") figure <- "Figure 4a"

### 2018-05-16 inst/supp_figure4b/supp_fig4b.Rmd
adding supp fig 4b

--- 2018-05-15 inst/figure3b/figure3b.Rmd
@@
 
+```{r}
+
+projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
+dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"
+
+```
+
 <br></br>
@@
 #### _Results_
+
+_Representative result_
+
+```{r, out.width = "850px"}
+
+url <- fileMap(type = "png")["Supplementary Figure 4b"][[1]]
+knitr::include_graphics(file.path(projectUrl, url))
+
+```
+
+<div class = "caption">
+Representative flow cytometry analysis from the cell cycle analysis in Figure 3B.
+</div>
+
+<br></br>
 

### 2018-05-16 R/utils.R
adding supp fig 4b

@@ -51,6 +51,7 @@ fileMap <- function(type) {
     `Supplementary Figure 3b` = "supp_figure3b/supp_figure3b.Rmd",
     `Supplementary Figure 3c` = "supp_figure3c/supp_figure3c.Rmd",
     `Supplementary Figure 4a` = "supp_figure4a/supp_figure4a.Rmd",
+    `Supplementary Figure 4b` = "supp_figure4b/supp_figure4b.Rmd",
     `Supplementary Figure 4c` = "supp_figure4c/supp_figure4c.Rmd",
     `Supplementary Figure 4d` = "supp_figure4d/supp_figure4d.Rmd",
     `Supplementary Figure 5c` = "supp_figure5c/supp_figure5c.Rmd",

### 2018-05-16 inst/figure3c/figure3c.Rmd
adding supp 5a-b Rmds and photos

@@
 #### _Results_
+
+_Example confluence measurment_
+
+```{r, out.width = "850px"}
+
+url <- fileMap(type = "png")["Supplementary Figure 5a"][[1]]
+knitr::include_graphics(file.path(projectUrl, url))
+
+```
+
+<div class = "caption">
+Representative pictures from the growth analysis shown in Figure 3C. The green color indicates the surface covered by cells as detected by the analysis software.
+</div>
+
+<br></br>
+
+_Example phase contrast_
+
+```{r, out.width = "850px"}
+
+url <- fileMap(type = "png")["Supplementary Figure 5b"][[1]]
+knitr::include_graphics(file.path(projectUrl, url))
+
+```
+
+<div class = "caption">
+A representative phase contrast picture from the 12 hour time point of the growth analysis in Figure 3C.
+</div>
+
+<br></br>
 

### 2018-05-16 R/utils.R

@@ -54,6 +54,8 @@ fileMap <- function(type) {
     `Supplementary Figure 4b` = "supp_figure4b/supp_figure4b.Rmd",
     `Supplementary Figure 4c` = "supp_figure4c/supp_figure4c.Rmd",
     `Supplementary Figure 4d` = "supp_figure4d/supp_figure4d.Rmd",
+    `Supplementary Figure 5a` = "supp_figure5a/supp_figure5a.Rmd",
+    `Supplementary Figure 5b` = "supp_figure5b/supp_figure5b.Rmd",
     `Supplementary Figure 5c` = "supp_figure5c/supp_figure5c.Rmd",
     `Supplementary Figure 6` = "supp_figure6/supp_figure6.Rmd",
     `Supplementary Figure 7` = "supp_figure7/supp_figure7.Rmd",

### 2018-05-16 inst/supp_doc2/supp_doc2.Rmd
updating all paths to figure numbers
adding rmd for supp doc 2

--- 2017-12-06 inst/primers/primers.Rmd
@@
 ---
-title: "Primers"
-author: "Jason T. Serviss"
-date: "`r Sys.Date()`"
-output:
-  html_document:
-    theme: flatly
-    code_folding: hide
-    keep_md: true
-vignette: >
-  %\VignetteIndexEntry{Vignette Title}
-  %\VignetteEngine{knitr::rmarkdown}
-  %\VignetteEncoding{UTF-8}
+title: "Supplementary Document 2"
+output: html_document
 ---
 
-```{r, echo = FALSE, message = FALSE}
+## Figure 1b
+###
 
-library(printr)
-library(tibble)
-
-```
-
-## Figure 1b
-
-```{r}
-
-tibble(
-    name=c(
-        "miR34a asRNA F1",
-        "miR34a asRNA R1",
-        "miR34a HG F",
-        "miR34a HG R",
-        "ß-actin Fwd",
-        "ß-actin Rev"
-    ),
-    sequence=c(
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT",
-        "TCT GCT CCA GTG GCT GAT GAG AAA",
-        "GTT CAC TGG CCT CAA AGT TGG CAT",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
-
-```
+| name             | sequence                         |
+| ---------------- |:--------------------------------:|
+| miR34a asRNA F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a asRNA R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
+| miR34a HG F      | TCT GCT CCA GTG GCT GAT GAG AAA  |
+| miR34a HG R      | GTT CAC TGG CCT CAA AGT TGG CAT  |
+| ß-actin Fwd      | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev      | CTT TGC GGA TGT CCA CGT CA       |
 
@@
 
-```{r}
-
-tibble(
-  name = c(
-    "miR34a asRNA F10",
-    "polyT T7 FAM",
-    "miR34a asRNA F1",
-    "FAM primer"),
-  sequence = c(
-    "ACG CGT CTC TCC AGC CCG GGA T",
-    "CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
-    "AGC GGC ATC TCC TCC ACC TGA AA",
-    "CCG TAG CTC GTC CAG GAC CC"
-  )
-)
-
-```
+| name              | sequence                                                                                            |
+| ----------------- |:---------------------------------------------------------------------------------------------------:|
+| miR34a asRNA F10  | ACG CGT CTC TCC AGC CCG GGA T                                                                       |
+| polyT T7 FAM      | CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN  |
+| miR34a asRNA F1   | AGC GGC ATC TCC TCC ACC TGA AA                                                                      |
+| FAM primer        | CCG TAG CTC GTC CAG GAC CC                                                                          |
 
@@
 
-```{r}
-
-tibble(
-    name=c(
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "miR34a HG F",
-        "miR34a HG R",
-        "miR34a AS F1",
-        "miR34a AS R1"
-
-    ),
-    sequence=c(
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TCG GGA TGT CCA CGT CA",
-        "TCT GCT CCA GTG GCT GAT GAG AAA",
-        "GTT CAC TGG CCT CAA AGT TGG CAT",
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
-
-    )
-)
-
-```
+| name          | sequence                         |
+| ------------- |:--------------------------------:|
+| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
+| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
+| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
+| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
 
@@
 
-```{r}
-
-tibble(
-    name=c(
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "miR34a HG F",
-        "miR34a HG R",
-        "miR34a as F1",
-        "miR34a as R1"
-
-    ),
-    sequence=c(
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TCG GGA TGT CCA CGT CA",
-        "TCT GCT CCA GTG GCT GAT GAG AAA",
-        "GTT CAC TGG CCT CAA AGT TGG CAT",
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
-
-    )
-)
-
-```
+| name          | sequence                         |
+| ------------- |:--------------------------------:|
+| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
+| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
+| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
+| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
 
@@
 
-```{r}
+**QPCR primers**
 
-tibble(
-    name=c(
-        "Luc setII F",
-        "Luc setII R",
-        "Renilla pBiDir F1",
-        "Renilla pBiDir R1",
-        "ß-actin Fwd",
-        "ß-actin Rev"
-    ),
-    sequence=c(
-        "AAG ATT CAA AGT GCG CTG CTG",
-        "TTG CCT GAT ACC TGG CAG ATG",
-        "TAA CGC GGC CTC TTC TTA TTT",
-        "GAT TTG CCT GAT TTG CCC ATA",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
-
-```
+| name          | sequence                         |
+| ------------- |:--------------------------------:|
+| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
+| miR34a HG F   | TCT GCT CCA GTG GCT GAT GAG AAA  |
+| miR34a HG R   | GTT CAC TGG CCT CAA AGT TGG CAT  |
+| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
 
@@
 
-```{r}
+| name               | sequence                        |
+| ------------------ |:-------------------------------:|
+| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
+| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
+| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
+| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
+| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
+| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |
 
-tibble(
-    name=c(
-        "Luc set II F",
-        "Luc set II R",
-        "Renilla pBiDir F1",
-        "Renilla pBiDir R1",
-        "ß-actin Fwd",
-        "ß-actin Rev"
-    ),
-    sequence=c(
-        "AAG ATT CAA AGT GCG CTG CTG",
-        "TTG CCT GAT ACC TGG CAG ATG",
-        "TAA CGC GGC CTC TTC TTA TTT",
-        "GAT TTG CCT GAT TTG CCC ATA",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
+## Figure 2e
 
-```
+| name               | sequence                        |
+| ------------------ |:-------------------------------:|
+| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
+| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
+| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
+| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
+| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
+| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |
 
@@
 
-Cloning primers
+**Cloning primers**
 
-```{r}
+| name                    | sequence                         |
+| ----------------------- |:--------------------------------:|
+| miR34aAS cloning F4     | ACG CGT CTC TCC AGC CCG GGA T    |
+| miR34aAS cloning Ex3_1  | AAT GAT GGC CGC AAC TAA TGA CGG  |
 
-tibble(
-    name=c(
-        "miR34aAS cloning F4",
-        "miR34aAS cloning Ex3_1"
-    ),
-    sequence=c(
-        "ACG CGT CTC TCC AGC CCG GGA T",
-        "AAT GAT GGC CGC AAC TAA TGA CGG"
-    )
-)
+**QPCR primers**
 
-```
-
-QPCR primers
-
-```{r}
-
-tibble(
-    name=c(
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "miR34a AS F1",
-        "miR34a AS R1"
-
-    ),
-    sequence=c(
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TCG GGA TGT CCA CGT CA",
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
-
-    )
-)
-
-```
+| name         | sequence                         |
+| ------------ |:--------------------------------:|
+| ß-actin Fwd  | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev  | CTT TCG GGA TGT CCA CGT CA       |
+| miR34a AS F1 |  AGC GGC ATC TCC TCC ACC TGA AA  |
+| miR34a AS R1 |  TTG CCT CGT GAG TCC AAG GAG AAT |
 
@@
 
-```{r}
+| name            | sequence                         |
+| --------------- |:--------------------------------:|
+| miR34a ChIP F1  | AAA GTT TGC AAA GAA GGA GGC GGG  |
+| miR34a ChIP R1  | AGG GAA GAA AGA ACT AGC CGA GCA  |
 
-tibble(
-    name=c(
-        "miR34a ChIP F1",
-        "miR34a ChIP R1"
-    ),
-    sequence=c(
-       "AAA GTT TGC AAA GAA GGA GGC GGG",
-       "AGG GAA GAA AGA ACT AGC CGA GCA"
-    )
-)
+## Supplementary Figure 2a
 
-```
+| name           | sequence                         |
+| -------------- |:--------------------------------:|
+| miR34a AS F10  | ACG CGT CTC TCC AGC CCG GGA T    |
+| miR34a AS F11  | ATC TGC GTG GTC ACC GAG AAG CA   |
+| miR34a AS F12  | CGC ACG GAC TGA GAA ACA CAA G    |
+| miR34a AS F13  | ACG GAG GCT ACA CAA TTG AAC AGG  |
+| miR34a AS F14  | AGG GAA GAA AGA ACT AGC CGA GCA  |
+| miR34a AS F15  | CAT TTG CTG CAA TAT CAC CGT GGC  |
+| miR34a AS R1   | TTG CCT CGT GAG TCC AAG GAG AAT  |
 
-## Figure 1 Supplement 2a
+## Supplementary Figure 2b
 
-```{r}
+| name               | sequence                         |
+| ------------------ |:--------------------------------:|
+| miR34a AS F1       | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a AS R1       | TTG CCT CGT GAG TCC AAG GAG AAT  |
+| miR34a AS int1 R1  | TGC GCA AAC TAC GCG CTC T        |
+| miR34a HG F        | TCT GCT CCA GTG GCT GAT GAG AAA  |
+| miR34a HG R        | GTT CAC TGG CCT CAA AGT TGG CAT  |
+| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA       |
+| U48 F              | AGT GAT GAT GAC CCC AGG TA       |
+| U48 R              | GGT CAG AGC GCT GCG GTG AT       |
 
-tibble(
-    name=c(
-        "miR34a AS F10",
-        "miR34a AS F11",
-        "miR34a AS F12",
-        "miR34a AS F13",
-        "miR34a AS F14",
-        "miR34a AS F15",
-        "miR34a AS R1"
-    ),
-    sequence=c(
-        "ACG CGT CTC TCC AGC CCG GGA T",
-        "ATC TGC GTG GTC ACC GAG AAG CA",
-        "CGC ACG GAC TGA GAA ACA CAA G",
-        "ACG GAG GCT ACA CAA TTG AAC AGG",
-        "AGG GAA GAA AGA ACT AGC CGA GCA",
-        "CAT TTG CTG CAA TAT CAC CGT GGC",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
-    )
-)
+## Supplementary Figure 2c
 
-```
+| name              | sequence                         |
+| ----------------- |:--------------------------------:|
+| miR34a AS F12     | AAA CAC AAG CGT TTA CCT GGG TGC  |
+| miR34a AS R1      | TTG CCT CGT GAG TCC AAG GAG AAT  |
+| miR34a AS R2      | ATA GGT TCA TTT GCC CGA TGT GCC  |
+| miR34a AS R3      | CCA CAG CTG TTG CTT CTG AAT GCT  |
+| miR34a AS Ex3 R1  | TGA TGG CCG CAA CTA ATG ACG GAT  |
 
-## Figure 1 Supplement 2b
+## Supplementary Figure 3c
 
-```{r}
+| name               | sequence                        |
+| ------------------ |:-------------------------------:|
+| Luc setII F        | AAG ATT CAA AGT GCG CTG CTG     |
+| Luc setII R        | TTG CCT GAT ACC TGG CAG ATG     |
+| Renilla pBiDir F1  | TAA CGC GGC CTC TTC TTA TTT     |
+| Renilla pBiDir R1  | GAT TTG CCT GAT TTG CCC ATA     |
+| ß-actin Fwd        | AGG TCA TCA CCA TTG GCA ATG AG  |
+| ß-actin Rev        | CTT TGC GGA TGT CCA CGT CA      |
 
-tibble(
-    name=c(
-        "miR34a AS F1",
-        "miR34a AS R1",
-        "miR34a AS int1 R1",
-        "miR34a HG F",
-        "miR34a HG R",
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "U48 F",
-        "U48 R"
-    ),
-    sequence=c(
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT",
-        "TGC GCA AAC TAC GCG CTC T",
-        "TCT GCT CCA GTG GCT GAT GAG AAA",
-        "GTT CAC TGG CCT CAA AGT TGG CAT",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA",
-        "AGT GAT GAT GAC CCC AGG TA",
-        "GGT CAG AGC GCT GCG GTG AT"
-    )
-)
+## Supplementary Figure 4a
 
-```
+**Cloning primers**
 
-## Figure 1 Supplement 2c
+| name                    | sequence                         |
+| ----------------------- |:--------------------------------:|
+| miR34aAS cloning F4     | ACG CGT CTC TCC AGC CCG GGA T    |
+| miR34aAS cloning Ex3_1  | AAT GAT GGC CGC AAC TAA TGA CGG  |
 
-```{r}
+**QPCR primers**
 
-tibble(
-    name=c(
-        "miR34a AS F12",
-        "miR34a AS R1",
-        "miR34a AS R2",
-        "miR34a AS R3",
-        "miR34a AS Ex3 R1"
-    ),
-    sequence=c(
-        "AAA CAC AAG CGT TTA CCT GGG TGC",
-        "TTG CCT CGT GAG TCC AAG GAG AAT",
-        "ATA GGT TCA TTT GCC CGA TGT GCC",
-        "CCA CAG CTG TTG CTT CTG AAT GCT",
-        "TGA TGG CCG CAA CTA ATG ACG GAT"
-    )
-)
+| name          | sequence                         |
+| ------------- |:--------------------------------:|
+| ß-actin Fwd   | AGG TCA TCA CCA TTG GCA ATG AG   |
+| ß-actin Rev   | CTT TCG GGA TGT CCA CGT CA       |
+| miR34a AS F1  | AGC GGC ATC TCC TCC ACC TGA AA   |
+| miR34a AS R1  | TTG CCT CGT GAG TCC AAG GAG AAT  |
 
-```
+## Supplementary Figure 4c
 
-## Figure 2 Supplement 2a
-
-```{r}
-
- tibble(
-    name=c(
-        "Luc setII F",
-        "Luc setII R",
-        "Renilla pBiDir F1",
-        "Renilla pBiDir R1",
-        "ß-actin Fwd",
-        "ß-actin Rev"
-    ),
-    sequence=c(
-        "AAG ATT CAA AGT GCG CTG CTG",
-        "TTG CCT GAT ACC TGG CAG ATG",
-        "TAA CGC GGC CTC TTC TTA TTT",
-        "GAT TTG CCT GAT TTG CCC ATA",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
-
-```
-
-## Figure 3 Supplement 1a
-
-Cloning primers
-
-```{r}
-
-tibble(
-    name=c(
-        "miR34aAS cloning F4",
-        "miR34aAS cloning Ex3_1"
-    ),
-    sequence=c(
-        "ACG CGT CTC TCC AGC CCG GGA T",
-        "AAT GAT GGC CGC AAC TAA TGA CGG"
-    )
-)
-
-```
-
-QPCR primers
-
-```{r}
-
-tibble(
-    name=c(
-        "ß-actin Fwd",
-        "ß-actin Rev",
-        "miR34a AS F1",
-        "miR34a AS R1"
-
-    ),
-    sequence=c(
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TCG GGA TGT CCA CGT CA",
-        "AGC GGC ATC TCC TCC ACC TGA AA",
-        "TTG CCT CGT GAG TCC AAG GAG AAT"
-
-    )
-)
-```
-
-## Figure 3 Supplement 2a
-
-```{r}
-
-tibble(
-    name=c(
-        "CCND1 Fwd",	
-        "CCND1 Rev",
-        "ß-actin Fwd",
-        "ß-actin Rev"
-    ),
-    sequence=c(
-        "CGT GGC CTC TAA GAT GAA GG",
-        "CTG GCA TTT TGG AGA GGA AG",
-        "AGG TCA TCA CCA TTG GCA ATG AG",
-        "CTT TGC GGA TGT CCA CGT CA"
-    )
-)
-
-```
-
-```{r}
-
-```
+| name         | sequence                        |
+| ------------ |:-------------------------------:|
+| CCND1 Fwd    | CGT GGC CTC TAA GAT GAA GG      |
+| CCND1 Rev    | CTG GCA TTT TGG AGA GGA AG      |
+| ß-actin Fwd  | AGG TCA TCA CCA TTG GCA ATG AG  |
+| ß-actin Rev  | CTT TGC GGA TGT CCA CGT CA      |

### 2018-05-16 inst/figure2d/figure2d.Rmd
updating all paths to figure numbers
fixing figure labels in Rmds
updating data.R with new names

--- 2018-03-05 inst/p1_hct116_hek293t/p1_hct116_hek293t.Rmd
@@
 ---
-title: "Figure 2c"
-subtitle: "P1 transfections in HCT116 and HEK293t cells"
+title: "Figure 2d"
+subtitle: "miR34a asRNA knock down in U2OS cells"
 author: "Jason T. Serviss"
@@
 
-It is likely, due to the head-to head orientation of miR34a HG and asRNA, that transcription initiation may be activated from a single promoter in a bi-directional manner.
-To investigate whether miR34a HG and asRNA are transcribed from the same promoter as convergent transcripts, we cloned the miR34a HG promoter, including the p53 binding site, into a luciferase/renilla dual reporter vector which we hereafter refer to as p1.
-The p1 sequence was previously published in Raver-Shapira, N., et al., Transcriptional activation of miR-34a contributes to p53-mediated apoptosis.
-Mol Cell, 2007.
-26(5): p.
-731-43.
+We hypothesized that miR34a asRNA may function to mediate the levels of its sense gene, miR34a. To this end, we utilized
+siRNA targeting exon 2 of the miR34a asRNA transcript to lower its expression levels and observe possible effects on 
+miR34a HG in U2OS cells.
 
@@
 
-All cell lines were cultured at 5% CO2 and 37° C with HEK293T cells cultured in DMEM high glucose (Hyclone) and HCT116 cells in McCoy’s 5a (Life Technologies).
-All growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin.
-Cells were plated at 10,000 cells per well in a 96-well plate with a white bottom and cultured overnight.
-The following day cells were co-transfected with 10ng of empty, p1, or p2 plasmid and GFP using the standard lipofektamine 2000 (Life Technologies) protocol.
-The expression of GFP and luminescence was measured 24 h post transfection by using the Dual-Glo Luciferase Assay System (Promega) and detected by the GloMax-Multi+ Detection System (Promega).
-The expression of luminescence was normalized to GFP.
+All cell lines were cultured at 5% CO2 and 37° C with U2OS cells cultured in McCoy’s 5a (Life Technologies).
+Growth mediums were supplemented with 10% heat-inactivated FBS and 50 μg/ml of streptomycin and 50 μg/ml of penicillin.
+Cells were plated at 25,000 cells per well in a 12-well plate and cultured overnight.
+The following day cells were transfected with 10nM si-Ctl or si-lncTAM34a using the standard lipofektamine 2000 (Life Technologies) protocol.
+si-Ctl was purchased from Qiagen (cat.
+nr.
+1027310) and si-lncTAM34a was purchased from Eurofins.
+The sequence for si-Ctl is not available from the manufacturer although the sequence for si-lncTAM34a is shown below.
+Cells were harvested for RNA extraction 48 hours after transfection.
 
@@
 
-_Analysis_
-
-Three independant experiments (biological replicates) were performed in total. The Student's t-test was used to compare the empty vs p1 group's log2 activity for both genes.
-
-<br></br>
-
-_Constructs_
+_siRNA_
 
@@
 
-ps <- data.frame(
-  name = c("p1"),
-  sequence = c("GCG CCC TGC CTG GCC CCC ACC TGG TCC TCT TTC CTT TTC AGG TGG AGG AGA TGC CGC TGT
-              CCC GTC GGT CTG GGG ACA GCC CAG CTC CCC GGA TCC CGG GCT GGA GAG ACG CGT CGC GGC   
-              CCC GGG GCC TGG TGG CAC GAG CAG GAA GGA GGA CCC GGC GGC GGG CTC TGC CTG GGC TTG 
-              CCT GGG CTT GTT CCG AGC CGG GCT GCT TCT CGG TGA CCA CGC AGA TCG GGG GCA TTT GGA
-              GAT TTT GCG GGA GTC CTG CAG CCA AGC TCC GGG GCA GGA GAG GCC TGG AAG CCT GCA CTA
-              CCT GCT C"
+siRNA <- data.frame(
+  name = c("si-lncTAM34a"),
+  sequence = c("GGG AGA AGA CGA UUC UUU")
 )
-)
-ps
+siRNA
 
@@
 
-_Primers_
+_QPCR_
+
+RNA was extracted using the RNeasy mini kit (Qiagen) and subsequently treated with DNase (Ambion Turbo DNA-free, Life Technologies).
+500ng RNA was used for cDNA synthesis using MuMLV (Life Technologies) and a 1:1 mix of oligo(dT) and random nanomers.
+QPCR was carried out using KAPA 2G SYBRGreen (Kapa Biosystems) using the Applied Biosystems 7900HT machine with the cycling conditions: 95 °C for 3 min, 95 °C for 3 s, 60 °C for 30 s.
+QPCR primers are shown below.
+
+<br></br>
+
+_QPCR Primers_
 
@@
     name=c(
-        "Luc_set_II_F",
-        "Luc_set_II_R",
-        "Renilla_pBiDir_F1",
-        "Renilla_pBiDir_R1",
+        "miR34a asRNA F1",
+        "miR34a asRNA R1",
+        "miR34aHG_F",
+        "miR34aHG_R",
         "B-actin_F",
@@
     sequence=c(
-        "AAG ATT CAA AGT GCG CTG CTG",
-        "TTG CCT GAT ACC TGG CAG ATG",
-        "TAA CGC GGC CTC TTC TTA TTT",
-        "GAT TTG CCT GAT TTG CCC ATA",
+        "AGC GGC ATC TCC TCC ACC TGA AA",
+        "TTG CCT CGT GAG TCC AAG GAG AAT",
+        "TCT GCT CCA GTG GCT GAT GAG AAA",
+        "GTT CAC TGG CCT CAA AGT TGG CAT",
         "AGG TCA TCA CCA TTG GCA ATG AG",
@@
 
+_Analysis_
+
+Three independant experiments (biological replicates) were performed in total measuring miR34a HG whereas miR34a asRNA was measured in 4 biological replicates.
+The Student's t-test was used to compare the si-Ctl and si-lncTAM34a conditions log2 fold change for both genes.
+
+<br></br>
+
 #### _Results_
-
-*For a schematic representation of the P1 construct please see Supplementary Figure 3a-b.
 
@@
 
-data <- getData("Figure 2c")
+data <- getData("Figure 2d")
 
-.calcP <- function(`Cell line`, gene, logValue, data) {
-  bool1 <- pull(data, `Cell line`) == `Cell line`
-  bool2 <- pull(data, gene) == gene
-  bool3 <- pull(data, construct) == "Empty"
-  bool <- bool1 & bool2 & bool3
-  t.test(logValue, pull(data, logValue)[bool])$p.value
-}
+#calculate dct
+groups <- c("siRNA", "Biological Replicate", "gene")
+gois <- c("miR34a HG", "lncTAM34a")
 
 data <- data %>%
-    mutate(logValue = log2(value))
+  gather(Ct, ctMean, -(gene:`Biological Replicate`)) %>%
+  group_by_at(groups) %>%
+  mutate(`Technical Replicate` = 1:n()) %>%
+  dct(., gois, Actin, c(groups, 'Technical Replicate'), F)
+
+#calculate ddct
+groups[groups == "gene"] <- "GOI"
+logical <- tibble(
+  siRNA = pull(data, siRNA) == "si-Ctl"
+)
+
+data <- data %>%
+  mutate(br = `Biological Replicate`) %>%
+  ddct(., logical, c(groups, "br")) %>%
+  filter(`Technical Replicate` == 1) %>%
+  select(-`Technical Replicate`) %>%
+  distinct() %>%
+  na.omit() %>%
+  folds(.)
+
+#calculate stats
+stats <- calcStats(data, siRNA, "si-Ctl", groups) %>%
+  pFormat(.)
+
+#calculate 95% CI and mean on linear scale
+stats <- data %>%
+  #filter(siRNA == "si-lncTAM34a") %>%
+  group_by(GOI, siRNA) %>%
+  summarize(
+    CI95l.linear = t.test(fold)$conf.int[1], 
+    CI95h.linear = t.test(fold)$conf.int[2]
+  ) %>%
+  ungroup() %>%
+  full_join(stats, by = c("siRNA", "GOI"))
 
 stats <- data %>%
-  group_by(`construct`, `Cell line`, gene) %>%
-  summarize(
-    n = n(),
-    mean = mean(logValue),
-    CI95l = t.test(logValue)$conf.int[1],
-    CI95h = t.test(logValue)$conf.int[2],
-    pValue = .calcP(`Cell line`, gene, logValue, data)
-  ) %>%
+  group_by(GOI, siRNA) %>%
+  summarize(mean.linear = mean(fold)) %>%
   ungroup() %>%
-  pFormat(.)
+  full_join(stats, by = c("siRNA", "GOI"))
 
 #vertical lines and labels in plot
-ys <- stats %>%
-  group_by(`Cell line`) %>%
-  summarize(max = max(CI95h))
-
 vl <- stats %>%
-  group_by(`Cell line`, gene) %>%
-  summarize(
-    pValue = as.numeric(min(pValue))
-  ) %>%
-  ungroup() %>%
-  pFormat(.) %>%
   mutate(
     x = case_when(
-      gene == "Renilla" ~ 1 + 0.25,
-      gene == "Luciferase" ~ 1 - 0.25
+      GOI == "miR34a HG" ~ 2 - 0.25,
+      GOI == "lncTAM34a" ~ 1 - 0.25
     ),
     xend = case_when(
-      gene == "Renilla" ~ 2 + 0.25,
-      gene == "Luciferase" ~ 2 - 0.25
+      GOI ==  "miR34a HG" ~ 2 + 0.25,
+      GOI == "lncTAM34a" ~ 1 + 0.25
     ),
-    pFormat = pFormat
-  ) %>%
-  left_join(ys) %>%
-  mutate(max = max + c(0.25, 1.2, 0.25, 1.2))
-
-#fix gene labels
-data <- data %>%
-  mutate(plotGene = case_when(
-    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
-    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
-    TRUE ~ "somehow missed a gene"
-  ))
-
-stats <- stats %>%
-  mutate(plotGene = case_when(
-    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
-    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
-    TRUE ~ "somehow missed a gene"
-  ))
-
-vl <- vl %>%
-  mutate(plotGene = case_when(
-    gene == "Luciferase" ~ "  Luciferase\n(miR34a HG)",
-    gene == "Renilla"    ~ "    Renilla\n(lncTAM34a)",
-    TRUE ~ "somehow missed a gene"
-  ))
-
+    label = if_else(GOI == "miR34a HG", 2, 1), 
+    max = max(CI95h.linear)
+  )
 ```
 
-```{r, fig.align='center', fig.height=8, fig.width=12}
-
-data <- filter(data, construct %in% c("p1", "Empty"))
-stats <- filter(stats, construct %in% c("p1", "Empty"))
+```{r, fig.align='center', fig.height=8, fig.width=12, warning = FALSE}
 
@@
     aes(
-      x = construct,
-      y = logValue,
-      fill = plotGene
+      x = `GOI`,
+      y = fold,
+      fill = siRNA
     ),
-    binwidth = 1/10,
+    binwidth = 0.01,
+    colour = NA,
     #alpha = 0.5,
-    colour = NA,
     position = position_dodge(width = 0.9), 
@@
     stackdir = 'center',
-    dotsize = 3,
+    dotsize = 4,
     show.legend = TRUE
   ) +
-  facet_grid(. ~ `Cell line`) +
-  labs(
-    x = "Construct",
-    y = "log2 activity (a.u.)"
-  )
+  scale_y_continuous("Fold")+
+  labs(x = "Gene")
 
@@
     aes(
-      x = construct,
-      ymin = CI95l,
-      ymax = CI95h,
-      group = plotGene
+      x = GOI,
+      ymin = CI95l.linear,
+      ymax = CI95h.linear,
+      group = interaction(siRNA, GOI)
     ),
-    colour = "grey20",
     position = position_dodge(width = 0.9),
+    colour = "gray20",
     show.legend = FALSE
@@
     aes(
-      x = construct,
-      y = mean,
-      group = plotGene
+      x = GOI,
+      y = mean.linear,
+      group = interaction(siRNA, GOI)
     ),
+    colour = "gray20",
+    shape = 95,
+    size = 6,
     position = position_dodge(width = 0.9),
-    show.legend = FALSE,
-    colour = "gray20",
-    size = 6,
-    shape = 95
+    show.legend = FALSE
   ) +
@@
     aes(
-      x = 1.5, 
-      y = max + 0.25, 
+      x = label, 
+      y = max + 0.075, 
       label = pFormat, 
-      group = gene
+      group = interaction(siRNA, GOI)
     ),
+    fill = "white",
     label.size = 0,
@@
     show.legend = FALSE,
-    fill = "white",
-    size = 5,
+    fontface = "bold",
     family = "Arial Unicode MS",
-    position = position_dodge(width = 0.9)
+    size = 3
   ) +
@@
   ) +
-  guides(fill = guide_legend(
+  guides(
+    fill = guide_legend(
       title = "Gene", 
       override.aes = list(size = 6)
-  ))
+    )
+  )
 
@@
     aes(
-      x = construct,
-      ymin = CI95l,
-      ymax = CI95h,
-      group = plotGene
+      x = GOI,
+      ymin = CI95l.linear,
+      ymax = CI95h.linear,
+      group = interaction(siRNA, GOI)
     ),
+    position = position_dodge(width = 0.9),
     colour = "grey30",
     size = 0.3,
-    position = position_dodge(width = 0.9),
     show.legend = FALSE
@@
     aes(
-      x = construct,
-      y = mean,
-      group = plotGene
+      x = GOI,
+      y = mean.linear,
+      group = interaction(siRNA, GOI)
     ),
+    colour = "grey30",
+    shape = 95,
+    size = 4,
     position = position_dodge(width = 0.9),
-    show.legend = FALSE,
-    colour = "grey30",
-    size = 4,
-    shape = 95
+    show.legend = FALSE
   ) +
@@
     aes(
-      x = 1.5, 
-      y = max + 0.4, 
+      x = label, 
+      y = max + 0.1, 
       label = pFormat, 
-      group = gene
+      group = interaction(siRNA, GOI)
     ),
+    fill = "white",
+    colour = "grey30",
     label.size = 0,
@@
     show.legend = FALSE,
-    fill = "white",
-    colour = "grey30",
-    size = 2.5,
+    fontface = "bold",
     family = "Arial Unicode MS",
-    position = position_dodge(width = 0.9)
+    size = 2.5
   ) +
@@
   ) +
-  guides(fill = guide_legend(
+  guides(
+    fill = guide_legend(
       title = "Gene", 
       override.aes = list(size = 4)
-  ))
+    )
+  )
 
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2c"][[1]])
-# ggsave(
+#path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 2d"][[1]])
+#ggsave(
 #  plot = figure,
@@
 #  units = "mm"
-# )
+#)
 ```
@@
 <div class="caption">
-miR34a asRNA and miR34a HG levels in HCT116 and HEK293t cells after transfection with P1 or empty constructs.
-Luciferase represents miR34a HG and renilla represents miR34a asRNA.
-The points represent the values obtained from each independant experiment (n = 3).
-95% confidence interval (vertical black lines), mean (horizontal black lines), and p-values are shown with the horizontal line under the p-value indicating the comparison that was tested.
+lncTAM34a (n = 4) and miR34a HG (n = 3) levels after 48 hour siRNA-mediated knock down of lncTAM34a in U2OS cells.
 </div>
@@
 
-Upon transfection of this construct in two separate cell lines we observed increases in both luciferase and renilla indicating that miR34a HG and asRNA expression is regulated by a single promoter contained within the p1 construct.
+miR34a asRNA KD gives rise to a ~20% decrease in miR34a HG expression levels.
 

### 2018-05-16 R/data.R

@@ -1,34 +1,19 @@
-#' ENCODE RNAseq data for the cellular localization analysis.
+#' miR34a asRNA and miR34a TCGA correlation.
 #'
-#' Quantified RNAseq data from 11 cell lines from the GRCh38 assembly was
-#' downloaded from ENCODE and quantifications for miR34a asRNA
-#' (ENSG00000234546), ACTB (ENSG00000075624), GAPDH (ENSG00000111640), and
-#' MALAT1 (ENSG00000251562) were extracted. Cell lines for which data was
-#' downloaded include: A549, GM12878, HeLa-S3, HepG2, HT1080, K562    MCF-7,
-#' NCI-H460, SK-MEL-5, SK-N-DZ, SK-N-SH. Initial exploratory analysis revealed
-#' that several cell lines should not be included in the final figure for the
-#' following reasons: The SK-N-SH has a larger proportion of GAPDH in the
-#' nucleus than cytoplasm. The variation of miR34a asRNA expression is too
-#' large for SK-MEL-5. K562, HT1080, SK-N-DZ, and NCI-H460 have no or low
-#' miR34a asRNA expression. In addition, both the cytoplasmic markers ACTB and
-#' GAPDH were analyzed for their ability to differentiate between the nuclear
-#' and cytoplasmic fractions, and GAPDH was choosed for the final analysis due
-#' its superior performance. Furthermore, only polyadenylated libraries were
-#' used in the final analysis, due to the fact that the cellular compartment
-#' enrichment was seen to be improved in these samples, and all analyzed genes
-#' are reported to be polyadenylated (MALAT1:
-#' \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2722846/}. Only samples
-#' with 2 biological replicates were retained. For each cell type, gene, and
-#' biological replicate the fraction of transcripts per million (TPM) in each
-#' cellular compartment was calculate as the fraction of TPM in the specific
-#' compartment by the total TPM. The mean and standard deviation for the
-#' fraction was subsequently calculated for each cell type and cellular
-#' compartment and this information was represented in the final figure.
[…]

### 2018-05-16 inst/figure3c/figure3c.Rmd
updating fig3c to use polynomial regression

@@
 
-Three technical triplicates were included in each experiment and these were independantly normalized for each condition to the 0 time point afterwhich the mean was calculated.
-The 95% confidence interval was then calculated based on the three independant experiments which were preformed.
+Three technical triplicates and three biological replicates were included in each experiment and these were independantly normalized for each condition to the 0 time point afterwhich the mean was calculated for the technical replicates.
+A polynomial regression model was then implemented separatley for each culture condition.
+with the mean of the technical replicates as the dependant variable and time and cell line as the independant variables.
 
@@
 
-```{r, out.width = "850px"}
+```{r, out.width = "450px"}
 
@@
 
-#calculate stats
-stats <- data %>%
-  filter(Time != 0) %>%
-  group_by(`Cell line`, Treatment, Time) %>%
-  summarize(
-    min = min(techMean),
-    max = max(techMean),
-    mean = mean(techMean),
-    median = median(techMean),
-    CI95l = t.test(techMean)$conf.int[1],
-    CI95h = t.test(techMean)$conf.int[2]
-  )
-
 #linear model
@@
   group_by(Treatment) %>%
-  mutate(rank = rank(techMean)) %>%
-  do(glance(lm(rank ~ Time +`Cell line`, data = .))) %>%
+  do(glance(lm(techMean ~ poly(Time, 24) +`Cell line`, data = .))) %>%
   ungroup() %>%
@@
   group_by(Treatment) %>%
-  mutate(rank = rank(techMean)) %>%
-  do(tidy(lm(rank ~ Time +`Cell line`, data = .))) %>%
+  do(tidy(lm(techMean ~ poly(Time, 24) +`Cell line`, data = .))) %>%
   ungroup() %>%
@@
 p <- ggplot(data = NULL) +
-  geom_ribbon(
-    data = stats,
+  geom_smooth(
+    data = data,
     aes(
       x = Time,
-      ymin = CI95l, 
-      ymax = CI95h, 
+      y = techMean,
       group = `Cell line`,
-      fill = `Cell line`
+      colour = `Cell line`
     ),
+    method = "lm", 
+    formula = y ~ poly(x, 24),
     alpha = 0.2,
-    show.legend = FALSE
+    size = 0.5,
+    show.legend = TRUE
   ) +
@@
   scale_x_discrete(breaks = seq(0, 35, 5)) +
+  scale_y_continuous(breaks = c(1, 1.2, 1.4, 1.6)) +
   labs(
     x = "Time (hours)", 
-    y = "Normalized % confluency",
+    y = "Fold confluency",
     title = "miR34a asRNA's role in growth regulation."
@@
 markdown <- p +
-  geom_linerange(
-    data = stats,
-    aes(
-      x = Time,
-      colour = `Cell line`,
-      ymin = min,
-      ymax = max
-    ), 
-    position = position_dodge(width = 1),
-    show.legend = FALSE
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.64, label = paste0("estimate=", round(estimate, digits = 4))),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
   ) +
-  geom_point(
-    data = stats,
-    aes(
-      x = Time, 
-      y = median,
-      group = `Cell line`,
-      colour = `Cell line`
-    ), 
-    position = position_dodge(width = 1),
-    show.legend = TRUE
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.62, label = paste0("std.error=", round(std.error, digits = 4))),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
   ) +
-  guides(
-    colour = guide_legend(
-      title = "Cell line", 
-      override.aes = list(size = 3)
-    )
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.6, label = paste0("p=", p.value)),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "bold", family = "Arial Unicode MS", size = 3, hjust = 0
   )
@@
 pdf <- p +
-  geom_linerange(
-    data = stats,
-    aes(
-      x = Time,
-      colour = `Cell line`,
-      ymin = min,
-      ymax = max
-    ), 
-    position = position_dodge(width = 1),
-    lwd = 0.2,
-    show.legend = FALSE
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.68, label = paste0("estimate=", round(estimate, digits = 4))),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
   ) +
-  geom_point(
-    data = stats,
-    aes(
-      x = Time, 
-      y = median,
-      group = `Cell line`,
-      colour = `Cell line`
-    ), 
-    size = 0.25,
-    position = position_dodge(width = 1),
-    show.legend = TRUE
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.64, label = paste0("std.error=", round(std.error, digits = 4))),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
   ) +
-  guides(
-    colour = guide_legend(
-      title = "Cell line", 
-      override.aes = list(size = 2)
-    )
+  geom_label(
+    data = filter(growth.lm, term == "`Cell line`lncTAM34a"),
+    aes(x = 2, y = 1.6, label = paste0("p=", p.value)),
+    fill = "white", label.size = 0, label.padding = unit(0.01, "lines"),
+    position = position_dodge(width = 0.9), show.legend = FALSE,
+    fontface = "plain", family = "Arial Unicode MS", size = 2, hjust = 0
   )
@@
 
-# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3c"][[1]])
-# ggsave(
-#   plot = figure,
-#   filename = path,
-#   device = cairo_pdf,
-#   height = 60,
-#   width = 83,
-#   units = "mm"
-# )
+path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Figure 3c"][[1]])
+ggsave(
+  plot = figure,
+  filename = path,
+  device = cairo_pdf,
+  height = 60,
+  width = 83,
+  units = "mm"
+)
 ```
@@
 The effects of miR34a asRNA overexpression on growth in normal and starvation conditions in the PC3 prostate cancer cell line.
-The points represent the median values obtained from each independant experiment (n = 3) whereas, the shadow represents 95% confidence interval, and the vertical line represents the minimum and maximum values from the independant experiments.
+Fold confluency (% confluency / Time 0 % confluency) is indicated on the y-axis.
+Colored lines indicate the polynomial regression model where mean fold confluency from 3 independant experiments is the dependant variable and time and cell line are independant variables.
+The grey shadows illustrate the 95% confidence interval for the regression.
+Estimates, standard error (std.error), and P values for the cell line covariate for each model are indicated in the upper left hand corner.
 </div>
@@
 
-miR34a asRNA overexpression causes a minor decrease in cell growth under normal conditions (RPMI) although under conditions of cellular stress through starvation, this effect is increased dramatically.
+miR34a asRNA overexpression causes a minor decrease in cell growth under normal conditions (RPMI) although under conditions of cellular stress through starvation, this effect is increased.
 

### 2018-05-16 inst/figure3c/figure3c.Rmd
syncing methods in paper and Rmds for fig3c and supp fig5c

@@
 
-Three technical triplicates and three biological replicates were included in each experiment and these were independantly normalized for each condition to the 0 time point afterwhich the mean was calculated for the technical replicates.
-A polynomial regression model was then implemented separatley for each culture condition.
-with the mean of the technical replicates as the dependant variable and time and cell line as the independant variables.
+Fold confluency was then calculated as % confluency / % confluency time 0 for each condition and the mean of the 3 technical replicates was subsequently calculated for each of the 3 biological replicates.
+A polynomial regression model was then constructed modeling the fold confluency as the dependent variable and time and cell line as independent variables.
+Reported P values are derived from the t-test, testing the null hypothesis that the coefficient estimate of the cell line covariate is equal to 0.
 
@@
 Fold confluency (% confluency / Time 0 % confluency) is indicated on the y-axis.
-Colored lines indicate the polynomial regression model where mean fold confluency from 3 independant experiments is the dependant variable and time and cell line are independant variables.
+Colored lines indicate the polynomial regression model where mean fold confluency from 3 independent experiments was modeled as a function of time and cell line.
 The grey shadows illustrate the 95% confidence interval for the regression.

### 2018-05-16 inst/supp_figure5c/supp_figure5c.Rmd
syncing methods in paper and Rmds for fig3c and supp fig5c

@@
 
-20^4 PC3 cells, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet (Invitrogen) for 5min and subsequently seeded in 12 well plates.
-Time 0 measurements were taken once cells had attatched and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaniously initiated in the remaining cells.
-RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin and 10% Fetal Calf Serum.
+PC3 stable cell lines, either miR34a asRNA overexpressing or mock, were harvested and stained in 1 ml PBS with 5uM CellTrace Violet for 5 minutes and subsequently seeded in 12 well plates at 2 x 104 cells per well.
+Time 0 measurements were taken once cells had attached and treatments with RPMI (Gibco, life technology) 10% FBS, RPMI 0.1% FBS, or HBSS were simultaneously initiated in the remaining cells.
+RPMI mediums were all additionally supplemented with 2mM L-glutamine and 50ug/ml Penicillin-Streptomycin.
 Cells were incubated for the indicated times before harvesting and CellTrace Violet was quantified via flow cytometry (Sony SH800S Cell Sorter).
@@
 
-Each replicate and condition were subsampled so that each had a total of 10000 cells.
-The mean of each technical replicate for time point 0 was calculated and, subsequently, the time 0 flouresence intensity was subtracted from each sample.
-The mean difference in flouresence intensity was then calculated for each biological replicate and condition and used to build a polynomial model per condition (i.e.
-RPMI, 0.1% FBS, and HBSS).
+Analysis was performed by first, subsampling each replicate and condition so that each had a total of 10000 cells.
+The mean of each technical replicate for time point 0 was calculated and, subsequently, the time 0 fluorescence intensity was subtracted from each sample.
+The mean difference in fluorescence intensity was then calculated for each biological replicate and condition and used to build a polynomial regression model per condition (i.e.
+RPMI, 0.1% FBS, and HBSS) where difference in fluorescence intensity was modeled as a function of time and cell line.
+Reported P values are derived from the t-test, testing the null hypothesis that the coefficient estimate of the cell line covariate is equal to 0.
 

### 2018-05-17 inst/supp_figure5b/supp_figure5b.Rmd
removing supp 5b and updating fig nrs

--- 2018-05-16 inst/supp_figure5c/supp_figure5c.Rmd
@@
 ---
-title: "Supplementary Figure 5c"
+title: "Supplementary Figure 5b"
 subtitle: "Monitoring proliferation of miR34a asRNA overexpressings cells under conditions of starvation"
@@
 
-data <- getData("Supplementary Figure 5c")
+data <- getData("Supplementary Figure 5b")
 
@@
   ungroup()
+```
 
+Show stained vs. Unstained
+```{r, fig.align="center", fig.width=10, fig.height=8}
+data %>%
+  ggplot() +
+  geom_histogram(aes(Violet, fill = Type), alpha = 1/2, position = position_dodge(), binwidth = 0.01) +
+  theme_bw() +
+  scale_x_log10() +
+  labs(x = "log10(Fluorescence intensity)", y = "Count") +
+  facet_wrap(~Time)
+```
+
+Show time 0
+```{r, fig.align="center", fig.width=10, fig.height=8}
+data %>%
+  filter(Time == 0) %>%
+  unite(Sample, c("Cell line", "Biological replicate")) %>%
+  mutate(Sample = case_when(
+    str_detect(Sample, "unstained-F4") ~ "unstained-lncTAM34a",
+    str_detect(Sample, "unstained-mock") ~ "unstained-mock",
+    TRUE ~ Sample
+  )) %>%
+  select(Sample, Violet) %>%
+  distinct() %>%
+  ggplot() +
+  geom_boxplot(aes(Sample, Violet)) +
+  scale_y_log10() +
+  theme(axis.text.x = element_text(angle = 90)) +
+  labs(x = "Sample_replicate", y = "log10(Fluorescence intensity)") +
+  theme_bw()
+```
+
+Show fluorescence loss over time
+```{r, fig.align="center", fig.width=10, fig.height=8}
+data %>%
+  mutate(Condition = if_else(Time == "0", "RPMI", Condition)) %>%
+  ggplot() +
+  geom_boxplot(aes(Time, Violet)) +
+  facet_wrap(~Type) +
+  scale_y_log10() +
+  labs(y = "log10(Fluorescence intensity)") +
+  theme_bw()
+```
+
+Show fluorescence per condition
+```{r, fig.align="center", fig.width=10, fig.height=8}
+data %>%
+  filter(Type == "stained") %>%
+  filter(Time != "0") %>%
+  mutate(Condition = parse_factor(Condition, levels = c("RPMI", "0.1% FBS", "HBSS"))) %>%
+  ggplot() +
+  geom_boxplot(aes(Time, Violet)) +
+  facet_wrap(~Condition) +
+  theme_bw() +
+  scale_y_log10() +
+  labs(y = "log10(Fluorescence intensity)")
+```
+
+Show polynomial model info
+```{r}
 #model each condition using the mean of all biological replicates using a lm
@@
 
+```{r, eval = FALSE}
+subData %>% 
+  select(-Violet, -day0Violet) %>% 
+  nest(violetNorm) %>% 
+  spread(Time, data) %>% 
+  mutate(`24-0` = map2_dbl(`0`, `24`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
+  mutate(`48-24` = map2_dbl(`24`, `48`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
+  mutate(`72-48` = map2_dbl(`48`, `72`, function(x, y) mean(unlist(y) - unlist(x)))) %>% 
+  select(-(`0`:`72`)) %>% 
+  gather(Time, diff, -(Type:cellLine)) %>% 
+  group_by(Condition, Time) %>% 
+  summarize(m = mean(diff))
+
+subDataMeans %>% 
+  spread(cellLine, mean) %>% 
+  mutate(diff = lncTAM34a - mock) %>% 
+  group_by(Time, Condition) %>% 
+  summarize(meanDiff = mean(diff)) %>% 
+  print(n = nrow(.))
+```
+
+Plot final figure
 ```{r, fig.align='center', fig.height=8, fig.width=12}
@@
 
-path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 5c"][[1]])
-ggsave(
-  plot = figure,
-  filename = path,
-  device = cairo_pdf,
-  height = 60,
-  width = 100,
-  units = "mm"
-)
+#path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["Supplementary Figure 5b"][[1]])
+#ggsave(
+#  plot = figure,
+#  filename = path,
+#  device = cairo_pdf,
+#  height = 60,
+#  width = 100,
+#  units = "mm"
+#)
 ```

### 2018-05-17 R/utils.R

@@ -56,7 +56,6 @@ fileMap <- function(type) {
     `Supplementary Figure 4d` = "supp_figure4d/supp_figure4d.Rmd",
     `Supplementary Figure 5a` = "supp_figure5a/supp_figure5a.Rmd",
     `Supplementary Figure 5b` = "supp_figure5b/supp_figure5b.Rmd",
-    `Supplementary Figure 5c` = "supp_figure5c/supp_figure5c.Rmd",
     `Supplementary Figure 6` = "supp_figure6/supp_figure6.Rmd",
     `Supplementary Figure 7` = "supp_figure7/supp_figure7.Rmd",
     `Supplementary Figure 8` = "supp_figure8/supp_figure8.Rmd",
@@ -213,7 +212,7 @@ getData <- function(figure) {
     'Supplementary Figure 1b', 'Supplementary Figure 2d',
     'Supplementary Figure 2e', 'Supplementary Figure 3c',
     'Supplementary Figure 4a', 'Supplementary Figure 4c',
-    'Supplementary Figure 4d', 'Supplementary Figure 5c',
+    'Supplementary Figure 4d', 'Supplementary Figure 5b',
     'Supplementary Figure 6', 'Supplementary Figure 7',
     'Supplementary Figure 8'
   )

### 2018-05-17 data-raw/saveRDS.R

@@ -352,9 +352,9 @@ read_tsv('./data-raw/supp_figure4d.txt', col_names = TRUE) %>%
   )) %>%
   write_rds(., path = './data/supp_figure4d.rds')
 
-#Supplementary Figure 5c, Stable line proliferation
+#Supplementary Figure 5b, Stable line proliferation
 f <- list.files(
-  'data-raw/supp_figure5c', pattern = "\\.csv$",
+  'data-raw/supp_figure5b', pattern = "\\.csv$",
   recursive = TRUE, full.names = TRUE
 )
 
@@ -393,7 +393,7 @@ f %>%
     Type = if_else(str_detect(Sample, "unstained"), "unstained", "stained")
   ) %>%
   select(Type, Time, `Cell line`:`Biological replicate`, `FSC-A`:Violet) %>%
-  write_rds(., path = './data/supp_figure5c.rds')
+  write_rds(., path = './data/supp_figure5b.rds')
 
 #Supplementary Figure 7, lnc34a_splice_jnc
 print("processing lnc34a_splice_jnc")

### 2018-05-22 inst/manuscript/CDD/revision/Response to referees.md
adding response to referees md

## Referee #1

We kindly thank the referee for his insightful review of our manuscript. We have addressed all of the referee's concerns and questions with new experiments or textual clarifications, and believe it has increased the overall value of the manuscript. Furthermore, we have taken the opportunity to further clarify several points both in our reply and in the manuscript itself.

#### Referee 1 Comment:

The manuscript is well written, it is logically arranged and easy to follow. Data are clearly presented, analyzed and interpreted. This reviewer has an only concern regarding the biological impact of the observed mechanism. The analysis of cell proliferation and cell cycle. Cell growth and cell proliferation are two different phenotypes. Authors used indirect method for analysis of cell growth - using analysis of confluence. I would recommend to perform direct analysis of cell numbers and determine proliferation rate (growth curve) using ordinary methods - count the cells using cell counter (Coulter, Casy) or using hemocytometer or any other image-based method which is able to identify and count single cells. Confluency of the cells may be affected by morphology, adhesion capabilities etc. Moreover, authors present the values as normalized data. It seems to be important to present the number of cells in time as real numbers normalized per area. Authors need to explain the discrepancy between results of cell cycle analysis and analysis of cell proliferation (cell numbers), growth curve should be presented for both cell lines for time interval 0 – 72 (or 96h) to cover at least 2-3 divisions. Data from the cell cycle analysis (examples of models of histograms from Modfit sw), should be part of supplementary data). HBSS culture condition seems to me not appropriate. I would recommend performing the experiment in low serum or serum free condition but in standard media which is necessary for cell maintenance. Modulation of cell cycle (F3b) seems to be very weak and biologically not significant. In this reviewer opinion, the authors should modify their interpretation and statements in to context of realtively weak phenotypes observed in cell-based experiments.

#### Referee 1 Response:

**In response to the statement:** _“Cell growth and cell proliferation are two different phenotypes. Authors used indirect method for analysis of cell growth - using analysis of confluence. I would recommend to perform direct analysis of cell numbers and determine proliferation rate (growth curve) using ordinary methods - count the cells using cell counter (Coulter, Casy) or using hemocytometer or any other image-based method which is able to identify and count single cells.”_

The authors agree that confluency measurements may incorporate multiple phenotypes that could be affected by the overexpression of lncTAM34a. To address this issue, an additional experiment was performed where proliferation rate was measured using the CellTrace violet assay. CellTrace violet is a fluorescent dye that covalently binds to all free amines on the surface and inside of cells. As cells proliferate, the dye becomes diluted and thus measuring fluorescence intensity via flow cytometry over time allows quantification of proliferation at a single cell level. Importantly, the assay is not affected by cell morphology or cell adhesion capabilities. We believe this method to be more accurate and allow the assaying of a comparatively larger numbers of cells and have, therefore, chosen to use it quantify proliferation rate as per the reviewers suggestion. This data has now been added to the manuscript as Supplementary Figure 5B and is also included below.

<br></br>
<p align="center">
<img src="/Users/jasonserviss/Github/miR34a_asRNA_project/inst/supp_figure5b/supp_figure5b.pdf" alt="Drawing" style="width: 400px;"/>
</p>

_The effects of miR34a asRNA overexpression on proliferation in normal and starvation conditions in the PC3 prostate cancer cell line. The y-axis illustrates the mean difference (∆; Time - Time 0) in flouresence intensity for each biological replicate and condition where decreased flouresence intensity indicates increased proliferation. Boxplots show the distribution of the mean differences from each of the biological replicates (n = 3). Grey lines indicate the polynomial regression model with the shadows indicating the 95% confidence intervals. Estimates, standard error (std.error), and P values for the cell line covariate for each model are indicated in the upper left hand corner._

The results confirm the role of increased lncTAM34a expression resulting in a decrease in proliferation. The results differ somewhat to the confluency analysis in regards to the degree to which these changes occur in the context of cellular stress. Several change have been made in the text to reflect the insights gained from this experiment and are outlined below:

This: "Under normal growth conditions there is a small but significant reduction (P = 3.0e-8; linear regression, Fig. 3c) in confluency in the lncTAM34a over-expressing cell lines compared to mock control. However, these effects on cell growth are drastically increased in starvation conditions (P = 9.5e-67; linear regression; Fig. 3c). This is in agreement with our previous results, and suggests thatlncTAM34a-mediated increases in miR34a expression are crucial under conditions of stress and necessary for the initiation of an appropriate cellular response. In summary, we find that over-expression of lncTAM34a is sufficient to increase miR34a expression and gives rise to known phenotypes observed upon induction of miR34a."

Has been changed to this: "Under normal growth conditions there is a small but significant reduction (P = 3.1e-6; polynomial regression, Fig. 3c, Supplementary Figure 5A) in confluency in the lncTAM34a over-expressing cell lines compared to mock control. However, these effects on cell growth are clearly increased in starvation conditions (P = 4.3e-85; polynomial regression; Fig. 3c, Supplementary Figure 5A). Specifically measuring proliferation rate, as opposed to confluency, largely confirms the observation that increases in lncTAM34a expression mediate decreases in cell cycle, although the degree to which cellular stress effects these changes differs when measuring confluency or proliferation (Supplementary Figure 5B). This suggests that additional cellular phenotypes, such as morphology or cell adhesion capability, may also be affected by increased lncTAM34a expression in contexts of cellular stress. In summary, we find that over-expression of lncTAM34a is sufficient to increase miR34a expression and gives rise to known phenotypes observed upon induction of miR34a."

We would also like to note that the method for modeling the data for Figure 3C was changed from linear regression to polynomial regression as it was found to provide a better fit for the non-linear trends observed in the data. The appropriate changes to reflect this have been made in the figure and throughout the text.

**In response to the statement:** _“It seems to be important to present the number of cells in time as real numbers normalized per area.”_

Upon rereading the materials and methods for the experiment where confluency was measured, we realized that the description of the normalization procedure was incorrect. It has therefore been changed as outlined below.

This: “Percentage of confluency was normalized to the control sample in each condition...”.

Has now been changed to this: “Fold confluency was then calculated as % confluency / % confluency time 0 for each condition and cell line...”

Effectively this calculation causes each data point to represent the fold difference compared to time point 0 within each condition and cell line. This fact was potentially not previously clear to the reader and has now been altered via a) clarification in the materials and methods (outlined above), b) the y-axis of figure 3c is now labeled "Fold confluency", and c) the calculation is present in the figure legend.

We choose to calculate fold confluency instead of showing the percentage confluency values due to the fact that, in our opinion, it better illustrates the differences between the two cell lines, as opposed to the culture conditions, which is in line with the conclusions we draw. To provide the reader with a representative example of the differences in percentage of confluency, photos taken by the plate reader machine and used to quantify confluency during the experiment have now been added as Supplementary Figure 5A and is also shown below.

<br></br>
<p align="center">
<img src="/Users/jasonserviss/Github/miR34a_asRNA_project/inst/supp_figure5a/supp_figure5a.png" alt="Drawing" style="width: 400px;"/>
</p>

_Representative pictures from the growth analysis shown in Figure 3C. The green color indicates the surface covered by cells as detected by the analysis software._

We believe this to provide a good visual proxy for the real number of cells within the culture area. Considering the conclusions drawn from Figure 3c, we feel that expressing the results in fold, and labeled as “Fold confluency” in the figure, instead of "Normalized % Confluency", is the most straightforward and clear way to convey the observed results..

**In response to the statement:** _“Authors need to explain the discrepancy between results of cell cycle analysis and analysis of cell proliferation (cell numbers), growth curve should be presented for both cell lines for time interval 0 – 72 (or 96h) to cover at least 2-3 divisions.”_

The authors are unsure which analyses the reviewer is referring to with the statement "cell cycle analysis and analysis of cell proliferation (cell numbers)". It is clear that the "cell cycle analysis" referes to Figure 3B and we assume that "analysis of cell proliferation (cell numbers)" refers to Figure 3C. Although, if this assumption is correct, we cannot see the discrepancy the reviewer is referring to. The conclusions drawn from Figure 3B are as follows:

"Cell cycle analysis via determination of DNA content showed a significant increase in G1 phase cells and a concomitant decrease in G2 phase cells in the PC3 and Skov3 lncTAM34a over-expressing cell lines, indicating G1 arrest (Fig. 3b, Supplementary Figure 4B)."

The conclusions drawn from Figure 3C under normal (RPMI) culture conditions are as follows:

"Under normal growth conditions there is a small but significant reduction (P = 3.1e-6; polynomial regression, Fig. 3c, Supplementary Figure 5A-B) in confluency in the lncTAM34a over-expressing cell lines compared to mock control."

The conclusions drawn from Figure 3B indicate that we would expect to see a reduction in confluency when lncTAM34a is overexpressed in the experiment performed and shown in Figure 3C and, in fact, that is what is shown. Concordantly, the conclusions drawn from Figure 3C indicate that we would expect a decrease in the proportion of cycling cells in Figure 3B and, again, this is what the data indicates.

Confluency is an indirect measurement of multiple specific cellular phenotypes, as the reviewer has pointed out - including not only proliferation, but also growth, morphology, and adhesion capabilities. The additional experiment performed to specifically measure proliferation (Supplementary Figure 5B), also indicates that there is a reduction of proliferation upon lncTAM34a overexpression in normal (RPMI) culture conditions. Despite this, there is some discrepancy concerning the observed degree of change in confluency and proliferation upon encountering starvation conditions that is now highlighted in the main text. Overall, the results indicate that lncTAM34a overexpression leads to a decrease in proliferation in line with results from previous studies examining the effects of miR34a upregulation on the cell cycle (Raver-Shapira et al., 2007, _Mol. Cell_, Figure 6F). This is specifically stated in the main text in the following manner:

"In summary, we find that over-expression of lncTAM34a is sufficient to increase miR34a expression and gives rise to known phenotypes observed upon induction of miR34a."

Also please note, in addition, that the experiment shown in Supplementary Figure 5B was performed over a 72 hour time frame to cover 2-3 cell divisions as requested by the reviewer.

**In response to the statement:** _“Data from the cell cycle analysis (examples of models of histograms from Modfit sw), should be part of supplementary data).”_

The requested data has now been added as Supplementary Figure 4B.

**In response to the statement:** _“HBSS culture condition seems to me not appropriate. I would recommend performing the experiment in low serum or serum free condition but in standard media which is necessary for cell maintenance.”_

The additional experiment analyzing cellular proliferation rate (Supplementary Figure 5B) was performed with the starvation condition, 0.1% FBS, to address this comment. Supplementary Figure 5A also shows that proliferation is ongoing, especially in the mock cell line, when cells are cultured in HBSS.

**In response to the statement:** _“Modulation of cell cycle (F3b) seems to be very weak and biologically not significant. In this reviewer opinion, the authors should modify their interpretation and statements in to context of realtively weak phenotypes observed in cell-based experiments.”_

Although the effect size specifically in Figure 3B may be relatively small, the authors feel that the conclusions drawn from the data are justified. Specifically, the conclusions are:

"Collectively, these results indicate that lncTAM34a-mediated induction of miR34a is sufficient to result in the corresponding miR34a-directed effects on cell cycle."

The effect sizes in Figure 3B (8% and 9% increase in G1 phase cells in PC3 and Skov3 cells, respectively, upon lncTAM34a overexpression) are > 2 fold larger than what has been observed in a previous study upon direct transfection of miR34a in 293 cells (Raver-Shapira et al., 2007, _Mol. Cell_, Figure 6F). Importantly, miR34a has subsequently been shown to mediate tumor size in _in vivo_ models in multiple studies (examples include: Park et al., 2014, _Cancer res._, Figure 5A-B. Daige et al., 2014, Mol. Cancer Ther., Figure 2D, 3D). The strong effect on tumor size mediated by small changes in cell cycle is expected since they will, over time, result in exponential changes in absolute cell numbers. Effective evaluation of whether this would also be the case upon increased lncTAM34a expression would necessitate appropriate _in vivo_ models which are outside the scope of this study.

## Referee #2

We would like to kindly thank the reviewer for their thorough reading of the manuscript and the useful and constructive comments that were provided. We believe that we have now addressed all of the reviewer comments the replies to which can be found below.

**Referee 2 Comment #1:**

Figure 1B: as normal PCR provides only semiquantitative results, it would be best to provide this data qualitatively, through qPCR as well as providing data on p53 mRNA and protein expression in your panel of cell lines so correlation analysis can be performed. Caution should be taken when using the term ‘correlate’ as this suggests statistical analysis has been performed, of which I could find no evidence for Fig1B. 
Only two cell lines were p53-, and some cell lines which were p53+ had no lncRNA or mirHG expression. Either use more p53- cell lines to support your statement that the p53 negative cell lines had lower expression of these transcripts, or rephrase your sentence.

**Referee 2 Comment #1 Response:**

We agree that our usage of the term “correlate” in context with the data presented in the Figure 1B was unclear and has been altered in the text (see below). Data has been previously produced with additional TP53 null cell lines although this information is not currently included in the figure. We are hesitant to add these additional cell lines due to the fact that they were not run in the same conditions or experiment as the cell lines currently in the figure. We include the data here for the referees review and have, in addition, altered the text to correspond with the reviewer’s suggestion based on the information presented in the manuscript as follows:

This text: “These results indicate that miR34a HG and lncTAM34a are co-expressed and that their expression levels correlate with TP53 status, with TP53-/- cells tending to have decreased or undetectable expression of both transcripts.”

Has been changed to: “These results indicate that miR34a HG and lncTAM34a are co-expressed and that their expression levels are related to TP53 status, with TP53-/- cells tending to have decreased or undetectable expression of both transcripts.”

![](/Users/jasonserviss/Desktop/miR34aOldDontDelete/reviewersComments1/TP53null.png)

In addition we note that, although it would be feasible perform correlation analysis in cell lines that are either TP53 wild-type or TP53-null, many of the cell lines have TP53 mutations or other alterations known to effect TP53 function (indicated with a +<sup>*</sup> in Figure 1B). Due to the fact that these mutations may or may not influence TP53’s function, and additional alterations (e.g. SV40 large T antigen expression in HEK293T cells or human papillomavirus 18 E6 expression in Hela cells) may affect its function to differing degrees, we would be hesitant to consider these cell lines as a homogeneous group in a correlation analysis. Furthermore, for the reasons outlined above, it would seem as though TP53 expression, on an mRNA or protein level, is not an appropriate proxy for its ability to function within the cell. Finally, the primary, and potentially most interesting, evidence for the relationship between TP53 status, miR34a expression, and lncTAM34a expression lies in the analysis performed in patient samples in Figure 1C and Supplementary Figure 1A-B.

**Referee 2 Comment #2:**

Some of the gel figures (Figure 1B, S2) had no labels on the molecular weight markers, please include those so it is easy to cross reference expected product sizes.

**Referee 2 Comment #2 Response:**

Molecular weight labels have now been added to all semi-quantitative PCR figures. These include: Figure 1B, Figure 1E, and Supplementary Figure 2B.

**Referee 2 Comment #3:**

Supplementary figure S3: as P1 is only exon 1 of both the lncRNA and the HG, I have doubts whether the expression of renilla and luciferase indicates transcription of both these genes, rather bidirectional transcription of exon 1 which may not extend to the full transcript. I am not convinced that knocking down renilla (lncTAM34) and the concomitant decrease of luciferase is representative of an actual mir34 HG response. Based on these experiments, I don’t think you can definitely say that lncRNATAM affects mirHG.

**Referee 2 Comment #3 Response:**

The authors agree with the reviewer that this experiment does not, in itself, provide the strongest evidence to support the conclusions drawn in the manuscript. We have now included additional experiments that show a concomitant decrease in miR34a HG levels upon siRNA-mediated targeting of the endogenous lncTAM34a transcript (Fig. 2d, shown below). Taking into account these new results, together with the additional evidence presented in the manuscript, it is of the authors opinion that the conclusion that lncTAM34a positively regulates miR34a is well supported in the data.

<br></br>
<p align="center">
<img src="/Users/jasonserviss/Github/miR34a_asRNA_project/inst/figure2d/figure2d.pdf" alt="Drawing" style="width: 400px;"/>
</p>

_lncTAM34a (n = 4) and miR34a HG (n = 3) levels after 48 hour siRNA-mediated knock down of lncTAM34a in U2OS cells. Individual points represent results from independent experiments, error bars show the 95% CI, black horizontal lines represent the mean, and P values are shown over long horizontal lines indicating the comparison tested._

**Referee 2 Comment #4:**

In figure 2, the P1 construct is employed because of the various isoforms of the lncRNA, but it is then later overexpressed using a lentiviral system without mention of how they tackled this multiple isoform issue.

**Referee 2 Comment #4 Response:**

We agree that this section should be clarified. In these experiments, we chose to overexpress the most abundant isoform in the stable cell lines. Evidence for the fact that there is an isoform that is dominantly expressed is currently in the manuscript (Supplementary Figure 7) although it is not directly pointed out to the reader that a) this is the case or b) that we made this decision. Therefore following text has been altered in the manuscript:

This: "Utilizing a lentiviral system, we stably over-expressed the lncTAM34a transcript in three TP53 -null cell lines, PC3 (prostate cancer), Saos2 (osteogenic sarcoma), and Skov3 (ovarian adenocarcinoma)."

Has been changed to this: "Utilizing a lentiviral system, we stably over-expressed the most abundant isoform (Supplementary Figure 7) of lncTAM34a in three TP53 -null cell lines, PC3 (prostate cancer), Saos2 (osteogenic sarcoma), and Skov3 (ovarian adenocarcinoma)."

In addition we would like to add that, although we were able to successfully clone the dominantly expressed isoform, we are unable to specifically target this isoform due to the structure of the locus. This is due to the fact that many of the more lowly expressed alternatively spliced transcripts include extra exons (Supplementary Figure 2C). This has also been more explicitly stated in the text in the following manner (lines 226-228):

"Knockdown of endogenous lncTAM34a is complicated by its various isoforms (Supplementary Figure 2C) and targeting individual isoforms is not possible due to the structure of the locus."

**Referee 2 Comment #5:**

For supplementary figure 4C, it would be helpful to include a representative western blot figure instead of just the analysis.

**Referee 2 Comment #5 Response:**

We agree that this would be helpful to the reader. A representative figure has now been added to Supplementary Figure 4C.

**Referee 2 Comment #6:**

For supplementary figure 3D, since lncRNA and mirHG share the same promoter which you showed in Figure 2C, how can you be sure that the subsequent increase in pol binding after lncRNA expression is just not because you have introduced overexpression vectors for lncRNA? Is the effect you observe just because in the process of activating the lncRNA, polymerases are recruited to this region?

**Referee 2 Comment #6 Response:**

We assume that the reviewer is referring to Figure 3D in the main text (Supplementary Figure 3D does not exist) that shows increased polII binding at the miR34a locus upon lncTAM34a overexpression. The increase in polII binding is detected via primers located outside of the cloned and overexpressed region and, for this reason, the multiple copies of the over-expressed transcript in the genome have no effect on the detected enrichment of polII binding at the endogenous locus. Although we demonstrate, in Figure 2C, that the promoter region in the P1 construct is sufficient to drive expression of both miR34a HG and lncTAM34a, the full regulatory region that controls transcription may be larger than the region cloned in the P1 construct. In fact, the miR34a HG and lncTAM34a promoter region shows broad enrichment for both activating histone marks (Figure 1A) and phosphorylated polII binding in cell lines where the sense and antisense transcripts are expressed. In the figure below, from the UCSC genome browser, we can see evidence for phosphorylated polII binding, detected via ChIP-seq, in two cell lines that express miR34a HG and lncTAM34a (Hela and HepG2) and one that does not (K562) (please note that all of these cell lines are included in the cell panel screening in Figure 1B). The polII ChIP primers (chipF and chipR) clearly show that they are within the polII-binding region, in cell lines where miR34a and lncTAM34a are expressed, but upstream of the 5’ end (cloningF) of the cloned and overexpressed transcript.

We have made the following modification in the main text to indicate that we have no evidence to believe that P1 constitutes the entire transcriptional regulatory sequence but, instead, have evidence that it is sufficient to drive expression of both transcripts.

This text: “Upon transfection of p1 into HCT116 and HEK293T cell lines we observed increases in both luciferase and renilla indicating that miR34a HG and lncTAM34a expression can be regulated by a single promoter contained within the p1 construct (Fig. 2c).”

Has been changed to this: “Upon transfection of p1 into HCT116 and HEK293T cell lines we observed increases in both luciferase and renilla indicating that the sequence in the P1 construct is sufficient to drive both miR34a HG and lncTAM34a expression (Fig. 2c).”

![](/Users/jasonserviss/Desktop/miR34aOldDontDelete/reviewersComments1/ChipPrimers.png)

**Referee 2 Comment #7:**

For figure 4A, there are only 5 p53 mutated samples in comparison to p53 wild type. Although this is statistically significant, without comparable sample size the relevance of this is questionable.

**Referee 2 Comment #7 Response:**

We are aware that, given the small sample size, the log-rank p-value is relative for TP53 in Figure 4A, although TP53 mutations effect on outcome is well known in the literature. The main message of the figure and the related supplementary figures is to show 1) the correlation between low lncTAM34a/miR34a expression and worse survival and 2) how this effect is similar but also independent on the effect of the TP53 mutation status.

**Referee 2 Comment #8:**

While the characterization of the lncRNA was very thoroughly done, it is difficult to ascertain from these results whether the lncRNA is functional or whether it is because you change expression of the lncRNA, you are inadvertently targeting the mirHG, and it is not the effects of the lncRNA per se.

**Referee 2 Comment #8 Response:**

We believe this comment is mostly based on the issues surrounding Referee 2 comment #6 that, hopefully, were sufficiently addressed in the response. To recapitulate, transcription of miR34a was evaluated via phosphorylated pollII enrichment at the endegenous locus upon overexpression of lncTAM34a. lncTAM34a overexpression caused an increase in phosphorylated polII binding at the miR34a locus and is detected via primers located outside of the cloned and overexpressed region. For this reason, the multiple copies of the over-expressed transcript in the genome have no effect on the detected enrichment of polII binding at the endogenous locus.

### 2018-05-28 inst/manuscript/CDD/revision/Response to referees.md
final update to reviewers reply

@@
 
-We are aware that, given the small sample size, the log-rank p-value is relative for TP53 in Figure 4A, although TP53 mutations effect on outcome is well known in the literature.
-The main message of the figure and the related supplementary figures is to show 1) the correlation between low lncTAM34a/miR34a expression and worse survival and 2) how this effect is similar but also independent on the effect of the TP53 mutation status.
+We wish to stress that the main message of the figure and the related supplementary figures is to show 1) the correlation between low lncTAM34a/miR34a expression and worse survival and 2) how this effect is similar but also independent on the effect of the TP53 mutation status.
+We are aware that, given the small sample size, the log-rank p-value is relative for TP53 in Figure 4A, although TP53 mutations effect on outcome is well known in the literature (Poeta et al., 2007, _New Eng.
+J.
+Med._, 357;25.
+Zenz et al., 2010, _J.
+Clin.
+Oncol._, 28;29.).
+Additionally, the data represented in Figure 4A is only a subset of the total analysis, the results of which are shown in full in Supplementary Figure 6.
 

### 2018-07-03 inst/manuscript/CDD/revision/Response to referees.md
final commit

@@
 <p align="center">
-<img src="/Users/jasonserviss/Github/miR34a_asRNA_project/inst/supp_figure5b/supp_figure5b.pdf" alt="Drawing" style="width: 400px;"/>
+<img src="/Users/jasonserviss/Github/miR34a_asRNA_project/inst/supp_figure5b/supp_figure5b.png" alt="Drawing" style="width: 600px;"/>
 </p>
